### 2018-05-14 structuredJets.tex
first

\documentclass[modern]{aastex62}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}

\newcommand{\eps}{\ensuremath{\epsilon}}
\newcommand{\gam}{\ensuremath{\gamma}}
\newcommand{\Gam}{\ensuremath{\Gamma}}
\newcommand{\Del}{\ensuremath{\Delta}}

\newcommand{\Mej}{\ensuremath{M_{\mathrm{ej}}}}
\newcommand{\tobs}{\ensuremath{t_{\mathrm{obs}}}}
\newcommand{\nuobs}{\ensuremath{\nu_{\mathrm{obs}}}}
\newcommand{\thobs}{\ensuremath{\theta_{\mathrm{obs}}}}

\begin{document}

\title{GRB Afterglows In The Multi-Messenger Era}
\correspondingauthor{Geoffrey Ryan}
\email{gsryan@umd.edu}

\author[0000-0001-9068-7157]{Geoffrey Ryan}
\affil{Joint Space-Science Institute, University of Maryland, College Park, MD 20742, USA}

\author{Hendrik van Eerten}

\begin{abstract}
Abstract abstract abstract.
\end{abstract}

\section{Introduction} \label{sec:intro}

\appendix
\section{Derivation of the Structured Jet equations}\label{sec:derive}

  The \emph{structured jet} model is a generalization of the simple top hat jet where the energy and Lorentz factor vary with the polar angle.  The light curves of structured jets display more complex behavior than top hats, which we can understand through some simple analytic relationships.

  Firstly, the complex behavior of a structured jet is due to relativistic beaming enhancing the jet emission at different angles as a function of time.  Once the jet becomes non-relativistic this effect is suppressed and the entire jet comes into view.  As such we will focus on the emission when the jet remains relativistic, the late-time behavior is the same as any Newtonian jet of comparable total energy.  Numerical simulations and analytic considerations have demonstrated that jet spreading does not begin in earnest until the blast wave approaches sub relativistic velocity so we will also neglect the effects of spreading and assume each sector of the jet evolves independently.  Lastly, we will assume when each sector of the blast wave is visible it is in the deceleration regime.  In this phase of evolution the blast wave Lorentz factor evolves according to:\begin{equation}
	\gamma(t; \theta) \propto \sqrt{\frac{E(\theta)}{n_0}}\ t^{-3/2}\ .
\end{equation}
  In the above $\gamma$ is the Lorentz factor of the shocked fluid at an angle $\theta$ from the jet axis at lab time (in the burster frame) $t$.  The blast wave expands into a medium of constant density $n_0$ and has an angularly dependent isotropic-equivalent energy $E(\theta)$.  The forward shock is at a position $R(t; \theta)$, and moves at a speed $\beta_s = (1-\gamma_s^{-2})^{1/2}$, where $\gamma_s^2 = 2 \gamma^2$ is the Lorentz factor of the shock.  Assuming $\gamma \gg 1$ gives:
\begin{equation}
	R(t; \theta) = ct\left(1-\frac{1}{16 \gamma^2(t; \theta)}\right)\ .
\end{equation}
We denote the angle between the viewer and a particular jet sector as $\psi$ and its cosine and $\mu = \cos \psi$.  Photons emitted at time from a sector of the blast wave at time $t$ will be seen by the observer at $\tobs$:
\begin{equation}
	\tobs = t - \frac{\mu}{c} R(t,\theta) = (1-\mu)t + \frac{\mu}{16}\frac{t}{ \gamma^2(t,\theta)}
\end{equation}

The observed flux depends on the luminosity distance $d_L$, viewing angle $\thobs$, and rest-frame emissivity $\varepsilon'_{\nu'}$.  The Doppler factor is $\delta = \gamma^{-1} (1-\beta\mu)^{-1}$, where $\beta=(1-\gamma^{-2})^{1/2}$ is the fluid three velocity.  The observed flux can then be expressed as a volume integral, where the integrand is evaluated at the time $t$ corresponding to $\tobs$ and position ${\bf r}$.
\begin{equation}
	F_\nu(\tobs, \nuobs) = \frac{1}{4\pi d_L^2} \int d^3{\bf r} \ \delta^2 \varepsilon'_{\nu'}\ .
\end{equation}  
The blast wave emits from a region of width $\Delta R \propto \delta_s \gamma_s \gamma^{-2} R $ where $\delta_s$ is the Doppler factor associated with the shock Lorentz factor $\gamma_s$. At a given observer time, the emission will be dominated by a region of (rest-frame) angular size $\Delta \Omega$.  The flux can then be approximated as:
\begin{equation}
	F_\nu(\tobs, \nuobs) \propto R^2 \Delta R \Delta \Omega \delta^2 \varepsilon'_{\nu'} \propto \Delta \Omega\ t^3 \gamma^{-2} \gamma_s \delta_s \delta^2 \varepsilon'_{\nu'}
\end{equation}.
The emissivity $\varepsilon'_{\nu'}$ depends on the fluid Lorentz factor, the frequency $\nuobs$, and numerous (constant) microphysical parameters.  We parameterize the dynamic dependence as $\varepsilon'_{\nu'} \propto \gamma^{\alpha'} t^{\alpha''} {\nu'}^\beta = t^{\alpha''} \gamma^{\alpha'}\delta^{-\beta} \nuobs^\beta$. The values of $\alpha'$, $\alpha''$, and $\beta$ in synchrotron regimes are given in Table \ref{tab:specSlopes}.  This leads to a flux of:
\begin{equation}
	F_\nu \propto \Delta \Omega\ t^{3+\alpha''} \gamma^{-1+\alpha'} \delta_s \delta^{2-\beta} \nuobs^\beta\ .
\end{equation}

\begin{deluxetable}{CCCC}
	\tablecaption{Dependence of $\varepsilon'_{\nu'} \propto \gamma^{\alpha'} t^{\alpha''} \nu'^{\beta}$ in various spectral regimes. \label{tab:specSlopes}}
	\tablehead{\colhead{Regime}& \colhead{$\alpha'$} & \colhead{$\alpha''$} & \colhead{$\beta$}}
	\startdata
	\nu'<\nu'_m<\nu'_c     & 1 & 0 & 1/3 \\
	\nu'_m<\nu'<\nu'_c     & (3p+1)/2 & 0 & (1-p)/2 \\
	\nu'_m<\nu'_c<\nu'     & 3p/2 & -1 & -p/2 \\ 
	\hline 
	\nu' < \nu'_c < \nu'_m & 7/3 & 2/3 & 1/3 \\
	\nu'_c < \nu' < \nu'_m & 3/2 & -1 & -1/2 \\
	\nu'_c < \nu'_m < \nu' & 3p/2 & -1 & -p/2 \\ 
	\enddata
\end{deluxetable}
The Doppler factor depends on whether the material is on-axis. Assuming $\gamma \gg 1$ one can write:
\begin{equation}
	\delta = \left \{ \begin{matrix}
				\frac{1}{2} \gamma^{-1} \sin^{-2}\psi/2,  & \text{if }2\sin{\psi/2} \gg \gamma^{-1} \ \ \text{(off-axis)} \\
				2 \gamma, & \text{if } 2\sin{\psi/2} \ll \gamma^{-1} \ \  \text{(on-axis)} \end{matrix} \right . \ .
\end{equation}
The observer time can be similarly simplified in both limits:
\begin{equation}
	\tobs = \left \{ \begin{matrix}
				\frac{1}{2} \psi^2 t,  & \text{if }2\sin{\psi/2} \gg \gamma^{-1}\ \ \text{(off-axis)} \\
				\frac{1}{16} \gamma^{-2} t, & \text{if } 2\sin{\psi/2} \ll \gamma^{-1} \ \  \text{(on-axis)} \end{matrix} \right . \ .
\end{equation}
As can the flux:
\begin{equation}
	F_\nu \propto \left \{ \begin{matrix}
				\Delta \Omega t^{3+\alpha''} \gamma^{-4+\alpha'+\beta} \psi^{-6+2\beta}\nuobs^\beta,  & \text{if }2\sin{\psi/2} \gg \gamma^{-1} \ \ \text{(off-axis)} \\
				\Delta \Omega t^{3+\alpha''} \gamma^{2+\alpha'-\beta} \nuobs^\beta, & \text{if } 2\sin{\psi/2} \ll \gamma^{-1} \ \  \text{(on-axis)} \end{matrix} \right . \ .
\end{equation}
The behavior of the Doppler factor informs the scaling of $\Delta \Omega$.  If any part of the jet is on-axis, its emission is enhanced by $\sim \gamma^2$ over the off-axis material and will dominate.  An observer for whom the entire jet is off-axis must be situated at some large $\thobs$, outside the outermost jet material.  At early times the entire jet will be beamed off-axis, with emission from the near edge (with the smallest $\psi$ and presumably $\gamma$) contributing most to the emission.  The absence of any particular angular scale in this regime indicates $\Delta \Omega$ will be roughly constant.  For an on-axis observer $\Delta \Omega \sim \sin^2 \psi_{\rm{max}} \propto \gamma^{-2}$ until the entire jet is on-axis, at which point $\Delta \Omega$ is again constant.  Hence:
\begin{equation}
	F_\nu \propto \left \{ \begin{matrix}
				t^{3+\alpha''} \gamma^{-4+\alpha'+\beta} \psi^{-6+2\beta}\nuobs^\beta,  & \text{if }2\sin{\psi/2} \gg \gamma^{-1} \ \ \text{(off-axis)} \\
				t^{3+\alpha''} \gamma^{\alpha'-\beta} \nuobs^\beta, & \text{if } 2\sin{\psi/2} \ll \gamma^{-1} \ \  \text{(on-axis, pre jet break)} \\
				t^{3+\alpha''} \gamma^{2+\alpha'-\beta} \nuobs^\beta, & \text{if } 2\sin{\psi/2} \ll \gamma^{-1} \ \  \text{(on-axis, post jet break)} \end{matrix} \right . \ .
\end{equation}
Finally, for off-axis emission $t \propto \tobs$ and hence $\gamma \propto \tobs^{-3/2}$.  For on-axis observers $\tobs \propto \gamma{-2} t \propto t^4$, hence $t\propto \tobs^{1/4}$ and $\gamma \propto \tobs^{-3/8}$. Giving finally:
\begin{equation}
	F_\nu \propto \left \{ \begin{matrix}
				\tobs^{9+\alpha'' -3(\alpha'+\beta)/2} \psi^{-6+2\beta}\nuobs^\beta,  & \text{if }2\sin{\psi/2} \gg \gamma^{-1} \ \ \text{(off-axis)} \\
				\tobs^{(3+\alpha'')/4+3(-\alpha'+\beta)/8} \nuobs^\beta, & \text{if } 2\sin{\psi/2} \ll \gamma^{-1} \ \  \text{(on-axis, pre jet break)} \\
				\tobs^{\alpha''/4 + 3(-\alpha'+\beta)/4} \nuobs^\beta, & \text{if } 2\sin{\psi/2} \ll \gamma^{-1} \ \  \text{(on-axis, post jet break)} \end{matrix} \right . \ .
\end{equation}
These formulae capture the standard behavior of top-hat jets, as well as any jet that is \emph{fully} on-axis or off-axis.  What they fail to (easily) demonstrate is the behavior of a structured jet which transitions continuously from one state to the other over the course of observation.

\subsection{The Jet Angular Profile}
\label{sec:jet_angular_shape}

The angular structure of a jet, before deceleration, can be described by angular profiles of energy $\epsilon(\theta, \phi)$ and Lorentz factor $\Gamma(\theta, \phi)$. This structure is acquired by the jet at its initial formation at the central engine and then sculpted by its propagation through the merger ejecta.  Due to the complications of direct numerical simulation much theoretical work has focused on simple analytic prescriptions of jet structure, typically axisymmetric uniform top-hat, Gaussian, or power law (CITE Granot+02, G+K03, K+G03, Rossi+04).

We consider the latter two models, a Gaussian profile
\begin{equation}
	E = E_0 \exp\left( \frac{\theta^2 }{2 \theta_c^2}\right)\ , \label{eq:Gaussian}
\end{equation}
and a $\theta^{-2}$ power law
\begin{equation}
	E = \frac{E_0}{1 + \theta^2/\theta_c^2}\ . \label{eq:powerlaw}
\end{equation}
Both models are truncated at an angle $\theta_w$. It is assumed all observed emission occurs after the jet has entered the deceleration phase, so the Lorentz factor profile is simply $\Gamma \propto E^{1/2}$.

With recent progress in hydrodynamical codes and computer resources, numerical simulation of jet propagation from the central engine to the circumburst medium has become possible.  Figure \ref{fig:jetStructure} shows energy and Lorentz factor distributions from hydrodynamic simulations collected from the recent literature, with representative examples of the Gaussian and power law models. The Lorentz factor distributions show large variation, in part due to differing times of extraction from the numerical simulations.  We focus comparison on the energy profile, as this is largely fixed while the jet remains relativistic.

\begin{figure}
	\plotone{figs/jetStructure.pdf}
   	\figcaption{Energy and Lorentz factor profiles of jet models.  Profiles of numerical simulations are reported in Morsony+2007 (green), Mizuta+2009 (brown), Duffell+2015 (orange), Lazzati+2017 (pink), Kathirgamaraju+2017 (red), and Margutti+2018 (purple). The analytic boosted fireball model (Duffell+2015) is shown in blue.  Energy profiles for Morsony07, Mizuta09, and Duffell15 have been scaled to $dE/d\Omega(\theta=0) = 10^{52}$ erg/sr.  For comparison we also show representative power law ( Eq. \eqref{eq:powerlaw}, $\theta_c=1^\circ$, $\theta_w=60^\circ$, thick grey) and Gaussian (\eqref{eq:Gaussian}, $\theta_c=5.7^\circ$, $\theta_w=23^\circ$, thick black) profiles.  \label{fig:jetStructure}}
\end{figure}

There is agreement between the models that the jet energy is concentrated in a core of half-width $\lesssim 10^\circ$ with wings extending to larger angles.  Some models truncate at $\mathcal{O}(10)$ degrees, while others have large tails extending to near the equator.  The Gaussian and power-law models respectively emulate this behavior, providing a simple parameterized representation of the landscape of numerical models.  Of particular note are the Lazzati 2017 and Margutti 2018 models, both of which were calculated specifically for GW170817. The core of the Margutti model is has a profile very near Gaussian, while the Lazzati model has a strong resemblance to a power law.

\end{document}

### 2018-05-15 structuredJets.tex
Minor formatting changes.

@@
 \usepackage{amsfonts}
+\usepackage{graphicx}
 
@@
 \end{deluxetable}
-The Doppler factor depends on whether the material is on-axis. Assuming $\gamma \gg 1$ one can write:
+The Doppler factor depends on the fluid Lorentz factor and whether the material is on-axis.
+The on/off axis boundary occurs at $\gamma^{-1} \approx \sin \psi$ (ie.
+$\beta \approx \mu$).
+One can write:
 \begin{equation}
 	\delta = \left \{ \begin{matrix}
-				\frac{1}{2} \gamma^{-1} \sin^{-2}\psi/2,  & \text{if }2\sin{\psi/2} \gg \gamma^{-1} \ \ \text{(off-axis)} \\
-				2 \gamma, & \text{if } 2\sin{\psi/2} \ll \gamma^{-1} \ \  \text{(on-axis)} \end{matrix} \right . \ .
+				\frac{1}{2} \gamma^{-1} \sin^{-2}\psi/2,  & \text{if } \gamma \gg 1 \text{ and } \sin{\psi} \gg \gamma^{-1} \ \ \text{(off-axis)} \\
+				2 \gamma, & \text{if } \gamma \gg 1 \text{ and } \sin{\psi} \ll \gamma^{-1} \ \  \text{(on-axis)} \\
+				1  & \text{if } \beta \ll 1\ \  \text{(non-relativistic)} \\ \end{matrix} \right . \ .
 \end{equation}
@@
 	\tobs = \left \{ \begin{matrix}
-				\frac{1}{2} \psi^2 t,  & \text{if }2\sin{\psi/2} \gg \gamma^{-1}\ \ \text{(off-axis)} \\
-				\frac{1}{16} \gamma^{-2} t, & \text{if } 2\sin{\psi/2} \ll \gamma^{-1} \ \  \text{(on-axis)} \end{matrix} \right . \ .
+				\frac{1}{2} \psi^2 t,  & \text{if }\sin{\psi} \gg \gamma^{-1}\ \ \text{(off-axis)} \\
+				\frac{1}{16} \gamma^{-2} t, & \text{if } \sin{\psi} \ll \gamma^{-1} \ \  \text{(on-axis)} \end{matrix} \right . \ .
 \end{equation}
@@
 	F_\nu \propto \left \{ \begin{matrix}
-				\Delta \Omega t^{3+\alpha''} \gamma^{-4+\alpha'+\beta} \psi^{-6+2\beta}\nuobs^\beta,  & \text{if }2\sin{\psi/2} \gg \gamma^{-1} \ \ \text{(off-axis)} \\
-				\Delta \Omega t^{3+\alpha''} \gamma^{2+\alpha'-\beta} \nuobs^\beta, & \text{if } 2\sin{\psi/2} \ll \gamma^{-1} \ \  \text{(on-axis)} \end{matrix} \right . \ .
+				\Delta \Omega t^{3+\alpha''} \gamma^{-4+\alpha'+\beta} \psi^{-6+2\beta}\nuobs^\beta,  & \text{(off-axis)} \\
+				\Delta \Omega t^{3+\alpha''} \gamma^{2+\alpha'-\beta} \nuobs^\beta, & \text{(on-axis)} \end{matrix} \right . \ .
 \end{equation}
@@
 	F_\nu \propto \left \{ \begin{matrix}
-				t^{3+\alpha''} \gamma^{-4+\alpha'+\beta} \psi^{-6+2\beta}\nuobs^\beta,  & \text{if }2\sin{\psi/2} \gg \gamma^{-1} \ \ \text{(off-axis)} \\
-				t^{3+\alpha''} \gamma^{\alpha'-\beta} \nuobs^\beta, & \text{if } 2\sin{\psi/2} \ll \gamma^{-1} \ \  \text{(on-axis, pre jet break)} \\
-				t^{3+\alpha''} \gamma^{2+\alpha'-\beta} \nuobs^\beta, & \text{if } 2\sin{\psi/2} \ll \gamma^{-1} \ \  \text{(on-axis, post jet break)} \end{matrix} \right . \ .
+				t^{3+\alpha''} \gamma^{-4+\alpha'+\beta} \psi^{-6+2\beta}\nuobs^\beta,  & \text{(off-axis)} \\
+				t^{3+\alpha''} \gamma^{\alpha'-\beta} \nuobs^\beta, &  \text{(on-axis, pre jet break)} \\
+				t^{3+\alpha''} \gamma^{2+\alpha'-\beta} \nuobs^\beta, & \text{(on-axis, post jet break)} \end{matrix} \right . \ .
 \end{equation}
@@
 	F_\nu \propto \left \{ \begin{matrix}
-				\tobs^{9+\alpha'' -3(\alpha'+\beta)/2} \psi^{-6+2\beta}\nuobs^\beta,  & \text{if }2\sin{\psi/2} \gg \gamma^{-1} \ \ \text{(off-axis)} \\
-				\tobs^{(3+\alpha'')/4+3(-\alpha'+\beta)/8} \nuobs^\beta, & \text{if } 2\sin{\psi/2} \ll \gamma^{-1} \ \  \text{(on-axis, pre jet break)} \\
-				\tobs^{\alpha''/4 + 3(-\alpha'+\beta)/4} \nuobs^\beta, & \text{if } 2\sin{\psi/2} \ll \gamma^{-1} \ \  \text{(on-axis, post jet break)} \end{matrix} \right . \ .
+				\tobs^{9+\alpha'' -3(\alpha'+\beta)/2} \psi^{-6+2\beta}\nuobs^\beta,  & \text{(off-axis)} \\
+				\tobs^{(3+\alpha'')/4+3(-\alpha'+\beta)/8} \nuobs^\beta, &\text{(on-axis, pre jet break)} \\
+				\tobs^{\alpha''/4 + 3(-\alpha'+\beta)/4} \nuobs^\beta, & \text{(on-axis, post jet break)} \end{matrix} \right . \ .
 \end{equation}
@@
 
-\subsection{The Jet Angular Profile}
-\label{sec:jet_angular_shape}
+\section{The Jet Angular Profile}
+\label{sec:jetAngularShape}
 

### 2018-05-15 structuredJets.tex
Just some theory additions.

@@
 \newcommand{\thobs}{\ensuremath{\theta_{\mathrm{obs}}}}
+\newcommand{\epse}{\ensuremath{\varepsilon_{\mathrm{e}}}}
+\newcommand{\epseb}{\ensuremath{\bar{\varepsilon}_{\mathrm{e}}}}
+\newcommand{\epsB}{\ensuremath{\varepsilon_{\mathrm{B}}}}
+\newcommand{\sigT}{\ensuremath{\sigma_{\mathrm{T}}}}
+\newcommand{\qe}{\ensuremath{q_{\mathrm{e}}}}
+\newcommand{\Mp}{\ensuremath{m_{\mathrm{p}}}}
+\newcommand{\Me}{\ensuremath{m_{\mathrm{e}}}}
 
@@
 \appendix
-\section{Derivation of the Structured Jet equations}\label{sec:derive}
+\section{Derivation of the Off-Axis Jet equations}\label{sec:derive1}
 
@@
 The emissivity $\varepsilon'_{\nu'}$ depends on the fluid Lorentz factor, the frequency $\nuobs$, and numerous (constant) microphysical parameters.
-We parameterize the dynamic dependence as $\varepsilon'_{\nu'} \propto \gamma^{\alpha'} t^{\alpha''} {\nu'}^\beta = t^{\alpha''} \gamma^{\alpha'}\delta^{-\beta} \nuobs^\beta$.
-The values of $\alpha'$, $\alpha''$, and $\beta$ in synchrotron regimes are given in Table \ref{tab:specSlopes}.
+We parameterize the dynamic dependence as $\varepsilon'_{\nu'} \propto \gamma^{s_1} t^{s_2} {\nu'}^\beta = t^{s_2} \gamma^{s_1}\delta^{-\beta} \nuobs^\beta$.
+The values of $s_1$, $s_2$, and $\beta$ in synchrotron regimes are given in Table \ref{tab:specSlopes}.
 This leads to a flux of:
 \begin{equation}
-	F_\nu \propto \Delta \Omega\ t^{3+\alpha''} \gamma^{-1+\alpha'} \delta_s \delta^{2-\beta} \nuobs^\beta\ .
+	F_\nu \propto \Delta \Omega\ t^{3+s_2} \gamma^{-1+s_1} \delta_s \delta^{2-\beta} \nuobs^\beta\ .
 \end{equation}
@@
 \begin{deluxetable}{CCCC}
-	\tablecaption{Dependence of $\varepsilon'_{\nu'} \propto \gamma^{\alpha'} t^{\alpha''} \nu'^{\beta}$ in various spectral regimes. \label{tab:specSlopes}}
-	\tablehead{\colhead{Regime}& \colhead{$\alpha'$} & \colhead{$\alpha''$} & \colhead{$\beta$}}
+	\tablecaption{Dependence of $\varepsilon'_{\nu'} \propto \gamma^{s_1} t^{s_2} \nu'^{\beta}$ in various spectral regimes. \label{tab:specSlopes}}
+	\tablehead{\colhead{Regime}& \colhead{$s_1$} & \colhead{$s_2$} & \colhead{$\beta$}}
 	\startdata
@@
 	F_\nu \propto \left \{ \begin{matrix}
-				\Delta \Omega t^{3+\alpha''} \gamma^{-4+\alpha'+\beta} \psi^{-6+2\beta}\nuobs^\beta,  & \text{(off-axis)} \\
-				\Delta \Omega t^{3+\alpha''} \gamma^{2+\alpha'-\beta} \nuobs^\beta, & \text{(on-axis)} \end{matrix} \right . \ .
+				\Delta \Omega t^{3+s_2} \gamma^{-4+s_1+\beta} \psi^{-6+2\beta}\nuobs^\beta,  & \text{(off-axis)} \\
+				\Delta \Omega t^{3+s_2} \gamma^{2+s_1-\beta} \nuobs^\beta, & \text{(on-axis)} \end{matrix} \right . \ .
 \end{equation}
@@
 	F_\nu \propto \left \{ \begin{matrix}
-				t^{3+\alpha''} \gamma^{-4+\alpha'+\beta} \psi^{-6+2\beta}\nuobs^\beta,  & \text{(off-axis)} \\
-				t^{3+\alpha''} \gamma^{\alpha'-\beta} \nuobs^\beta, &  \text{(on-axis, pre jet break)} \\
-				t^{3+\alpha''} \gamma^{2+\alpha'-\beta} \nuobs^\beta, & \text{(on-axis, post jet break)} \end{matrix} \right . \ .
+				t^{3+s_2} \gamma^{-4+s_1+\beta} \psi^{-6+2\beta}\nuobs^\beta,  & \text{(off-axis)} \\
+				t^{3+s_2} \gamma^{s_1-\beta} \nuobs^\beta, &  \text{(on-axis, pre jet break)} \\
+				t^{3+s_2} \gamma^{2+s_1-\beta} \nuobs^\beta, & \text{(on-axis, post jet break)} \end{matrix} \right . \ .
 \end{equation}
@@
 	F_\nu \propto \left \{ \begin{matrix}
-				\tobs^{9+\alpha'' -3(\alpha'+\beta)/2} \psi^{-6+2\beta}\nuobs^\beta,  & \text{(off-axis)} \\
-				\tobs^{(3+\alpha'')/4+3(-\alpha'+\beta)/8} \nuobs^\beta, &\text{(on-axis, pre jet break)} \\
-				\tobs^{\alpha''/4 + 3(-\alpha'+\beta)/4} \nuobs^\beta, & \text{(on-axis, post jet break)} \end{matrix} \right . \ .
+				\tobs^{9+s_2 -3(s_1+\beta)/2} \psi^{-6+2\beta}\nuobs^\beta,  & \text{(off-axis)} \\
+				\tobs^{(3+s_2)/4+3(-s_1+\beta)/8} \nuobs^\beta, &\text{(on-axis, pre jet break)} \\
+				\tobs^{s_2/4 + 3(-s_1+\beta)/4} \nuobs^\beta, & \text{(on-axis, post jet break)} \end{matrix} \right . \ .
 \end{equation}
@@
 What they fail to (easily) demonstrate is the behavior of a structured jet which transitions continuously from one state to the other over the course of observation.
+
+\section{Derivation of the Structured Jet equations}\label{sec:derive2}
+
+A jet with a non-trivial angular distribution of energy can exhibit qualitatively different behaviour than a simple top hat, particularly when observed at a significant viewing angle.
+While the initial off-axis and final on-axis post jet-break evolutions are identical, these are separated by a transition phase where the sector dominating the emission scans over the jet surface.
+This transition phase begins at the end of the off-axis phase: when a sector of the jet first decelerates to include the observer in its beaming cone.
+This will necessarily be from the wings/edge of the jet, the material with the lowest Lorentz factor and smallest angle $\psi$ to the observer.
+As the blastwave decelerates more energetic material from nearer the core will come into view and the high latitude emission will dim.
+Finally the core of the jet ($\theta = 0$ or $\psi = \thobs$) decelerates and becomes visible to the observer.
+At this point the entire jet is on-axis and evolution continues as in the post jet-break phase.
+
+At each moment during the structure phase the emission is dominated by material that just came on-axis, where $\gamma^{-1} = \sin \psi$.
+
+\section{Shock Jump Conditions and Synchrotron Parameters}
+\label{sec:shockJump}
+
+Table \ref{tab:shockSync} lists the necessary quantities for calculating synchrotron emission from a forward shock.
+Asymptotic expressions are given in the ultra-relativistic and non-relativistic limits.
+The synchrotron emissivity in the fluid rest frame is:
+\begin{equation}
+	\varepsilon'_{\nu'} = \varepsilon_P \times \left \{ \begin{matrix}
+											\left(\nu' / \nu_m\right)^{1/3} & \text{if } \nu' < \nu_m < \nu_c \\
+											\left(\nu' / \nu_m\right)^{(1-p)/2} & \text{if } \nu_m < \nu'  < \nu_c \\
+											\left(\nu_c/\nu_m\right)^{(1-p)/2}\left(\nu' / \nu_c\right)^{-p/2} & \text{if }\nu_m < \nu_c < \nu'\\
+											\left(\nu' / \nu_c\right)^{1/3} & \text{if } \nu' < \nu_c < \nu_m \\
+											\left(\nu' / \nu_c\right)^{-1/2} & \text{if } \nu_c <\nu' <  \nu_m \\
+											\left(\nu_m / \nu_c\right)^{-1/2}\left(\nu' / \nu_m\right)^{-p/2} & \text{if } \nu_c < \nu_m < \nu'
+											\end{matrix} \right .
+\end{equation}
+
+\begin{deluxetable}{CC|CCC}
+\tablehead{ & \colhead{Expression} & \colhead{Coefficient} & \colhead{$ u \gg 1$} & \colhead{$ u \ll 1$}}
+\tablecaption{Emission parameters at forward shock. \label{tab:shockSync}}
+\startdata
+n & 4 \gamma n_0 & 4 n_0 & \gamma & 1 \\
+e & (\gamma-1)n \Mp c^2 & 4 \Mp c^2 n_0 &  \gamma^2 & \frac{1}{2} \beta^2 \\
+B & \sqrt{8\pi e \epsB} & 4(2 \pi)^{1/2}(\Mp c^2)^{1/2} n_0^{1/2} \epsB^{1/2} & \gamma & 2^{-1/2} \beta \\ 
+\hline
+\gamma_m &  \frac{\epseb e}{n \Me c^2} & \frac{\Mp}{\Me} \epseb &  \gamma & \frac{1}{2} \beta^2 \\
+\gamma_c & \frac{3 \Me c \gamma}{4 \sigT \epsB e t} & \frac{3}{16} \frac{\Me}{\Mp\sigT c}n_0 ^{-1} \epsB^{-1} & \gamma^{-1} t^{-1} & 2 \beta^{-2} t^{-1} \\
+\varepsilon_P & \frac{\sqrt{3}}{2}\frac{\qe^3}{\Me c^2}(p-1)n B & 8 (6\pi)^{1/2} \frac{\Mp^{1/2} \qe^3}{\Me c} (p-1) n_0^{3/2} \epsB^{1/2} & \gamma^2 & 2^{-1/2} \beta \\ 
+\nu_m & \frac{3}{4\pi}\frac{\qe}{\Me c} \gamma_m^2 B & 6 (2\pi)^{-1/2} \frac{\Mp^{5/2} \qe}{\Me^3} n_0^{1/2} \epseb^2 \epsB^{1/2} & \gamma^3 & 2^{-5/2} \beta^5 \\
+\nu_c & \frac{3}{4\pi}\frac{\qe}{\Me c} \gamma_c^2 B & \frac{27}{128} (2\pi)^{-1/2} \frac{\Me \qe}{\Mp^{3/2}\sigT^2 c^2} n_0^{-3/2}  \epsB^{-3/2} & \gamma^{-1}t^{-2} & 2^{3/2}\beta^{-3}t^{-2} \\
+\hline
+E & \frac{4\pi}{9} \rho_0 c^2 R^3(4u^2+3)\beta^2 & \frac{16\pi}{9}\rho_0 c^2 & R^3 \gamma^2 & \frac{3}{4} R^3 \beta^2 \\
+\beta_s & \frac{4 u \gamma}{4u^2+3} & 1 & 1 & \frac{4}{3}\beta 
+\enddata
+\end{deluxetable}
 

### 2018-05-16 structuredJets.tex
Added structured jet slopes (appendix B)

@@
 \newcommand{\thobs}{\ensuremath{\theta_{\mathrm{obs}}}}
+\newcommand{\thW}{\ensuremath{\theta_{\mathrm{w}}}}
 \newcommand{\epse}{\ensuremath{\varepsilon_{\mathrm{e}}}}
@@
 Lastly, we will assume when each sector of the blast wave is visible it is in the deceleration regime.
-In this phase of evolution the blast wave Lorentz factor evolves according to:\begin{equation}
-	\gamma(t; \theta) \propto \sqrt{\frac{E(\theta)}{n_0}}\ t^{-3/2}\ .
+In this phase of evolution the blast wave Lorentz factor evolves according to:
+  \begin{equation}
+	\gamma(t; \theta) \propto \sqrt{\frac{E(\theta)}{n_0}}\ t^{-3/2}\ . \label{eq:lorentzEvolution}
 \end{equation}
@@
 \begin{equation}
-	\tobs = t - \frac{\mu}{c} R(t,\theta) = (1-\mu)t + \frac{\mu}{16}\frac{t}{ \gamma^2(t,\theta)}
+	\tobs = t - \frac{\mu}{c} R(t,\theta) = (1-\mu)t + \frac{\mu}{16}\frac{t}{ \gamma^2(t,\theta)} \label{eq:tobs}
 \end{equation}
@@
 \begin{equation}
-	F_\nu \propto \Delta \Omega\ t^{3+s_2} \gamma^{-1+s_1} \delta_s \delta^{2-\beta} \nuobs^\beta\ .
+	F_\nu \propto \Delta \Omega\ t^{3+s_2} \gamma^{-1+s_1} \delta_s \delta^{2-\beta} \nuobs^\beta\ . \label{eq:fluxApprox}
 \end{equation}
@@
 At each moment during the structure phase the emission is dominated by material that just came on-axis, where $\gamma^{-1} = \sin \psi$.
+To find the overall behaviour we first determine $\tobs(\psi)$ and $F_\nu(\psi)$ for material whose emission is peaking (coming on-axis).
+Since the structure phase occurs when motion is still relativistic, we can assume $\gamma \gg 1$ and hence $\sin \psi \ll 1$.
+In this approximation:
+\begin{eqnarray}
+	\mu \approx 1 - \frac{1}{2}\sin^2\psi \ , \label{eq:muPsi}\\
+	\delta_s \approx \delta \approx \gamma = \csc \psi\ . \label{eq:deltaPsi}
+\end{eqnarray}
+The material dominating the emission is in the plane between the observer and the jet axis, denoted by $\phi = 0$.
+Along this line we have $\psi = \thobs - \theta$, and can use $\psi$ or $\theta$ interchangeably to denote latitude.
+From Equation \eqref{eq:lorentzEvolution} we have $t\propto E(\theta)^{1/3} \gamma^{-2/3}$.
+Using Equation \eqref{eq:tobs} and \eqref{eq:muPsi} we find that material at $\psi$ will come on-axis at observer time:
+\begin{equation}
+	\tobs(\psi) = \frac{9}{16} t \sin^2\psi  \propto E(\theta)^{1/3} \sin^{8/3} \psi\ . \label{eq:tobsPsi}
+\end{equation}
+The peak flux from material at $\psi$ can be determined from Equation \eqref{eq:fluxApprox}.
+Using Equation \eqref{eq:deltaPsi} and taking $\Delta \Omega \propto \gamma^{-s_3}$ gives an observed flux:
+\begin{equation}
+	F_\nu(\psi) \propto t^{3+s_2} \gamma^{2+s_1-s_3-\beta} \nuobs^\beta \propto E(\theta)^{1+s_2/3} (\sin \psi)^{-s_1 + 2 s_2/3 +s_3+\beta} \nuobs^\beta  \ . \label{eq:FnuPsi}
+\end{equation}
+	Equations \eqref{eq:tobsPsi} and \eqref{eq:FnuPsi} describe the evolution of the flux in the structure phase in terms of the parameter $\psi$, which varies from $\mathrm{min} (0, \thobs-\thW)$ to $\thobs$.
+In principle one would like to invert Equation \eqref{eq:tobsPsi} and substitute into Equation \eqref{eq:FnuPsi} to obtain $F_\nu(\tobs)$ itself.
+Unfortunately, in general this is impossible to do in closed form because $E(\theta)$ is non-trivial.
+
+	We can obtain the temporal power law slope of the light curve by differentiating both Equations \eqref{eq:tobsPsi} and \eqref{eq:FnuPsi} with respect to $\psi$.
+Noting that $dE/d\psi = -dE/d\theta$ we obtain for the individual derivatives:
+\begin{eqnarray}
+	\frac{d \log \tobs}{d \psi} = \frac{8}{3} \cot \psi - \frac{1}{3} \frac{d \log E}{d \theta}\ , \\
+	\frac{d \log F_\nu}{d \psi} = \left(-s_1 + \frac{2}{3} s_2 +s_3+\beta\right)\cot \psi - \left(1+\frac{1}{3}s_3\right) \frac{d \log E}{d \theta}\ .
+\end{eqnarray}
+Taking the ratio and simplifying gives:
+\begin{eqnarray}
+	\frac{d \log F_\nu}{d \log \tobs}(\psi) = \frac{3 \beta - 3s_1 + 2s_2+3s_3 + g(\psi)}{ 8+g(\psi)} \\
+	g(\psi) \equiv -\tan \psi \frac{d \log E}{d \theta}\ .
+\end{eqnarray}
+The parameter $g$ is directly measurable from the light curve, given the spectral information which fixes $\beta$, $s_1$, and $s_2$.
 

### 2018-06-20 structuredJets.tex
Minor additions

@@
 \newcommand{\Del}{\ensuremath{\Delta}}
+
+\newcommand{\gwbns}{GW170817}
 
@@
 \begin{abstract}
-Abstract abstract abstract.
+	Abstract abstract abstract
 \end{abstract}
@@
 \section{Introduction} \label{sec:intro}
+	The binary neutron star (BNS) merger \gwbns\ displayed many of the predicted electromagnetic counterparts.
+Prompt gamma-ray emission in the form of a short gamma-ray burst (sGRB) in the first seconds after merger, an optical and infrared kilonova visible for hours and days, and a broadband synchrotron afterglow first observed 9 days after merger which may remain visible for a year or more.
+
+	While this event qualitatively matched the community's expectations, the details of the emission from each counterpart were very unexpected.
+The sGRB was delayed by $1.7$s after the GW chirp and was the lowest luminosity sGRB ever observed, the kilonova contained a rapidly varying blue component in tension with numerical models, and the afterglow demonstrated a long power-law \emph{rise} for roughly 150 days, a feature never before seen in GRB afterglows.
+
+	In this paper we discuss this new \emph{structured} phase of GRB afterglow evolution and its interpretation in terms of dynamics of a relativistic blast wave.
+We provide analytic formula for the start and end times of this phase and for the approximate power-law slope of the light curve.
+The approximate analytic formula are validated by a numerical model which we have made publicly available.
+
+\section{The Single Shell Framework}
+
+	GRB afterglows are synchrotron radiation emitted from a relativistic blast wave propagating through the GRB circumburst medium, which we take to be a uniform ISM.
+Models of this process have two components: the hydrodynamics of the blast wave and the radiative transfer of the synchrotron radiation.
+
+	We describe both components with a trans-relativistic single shell model (CITE Hendrik's review).
+In such a model the blast wave is approximated as a homogenous slab of hot plasma comprising both the forward shock and contact discontinuity.
+The Rankine-Huginot (CITE RH) shock jump conditions can be used to write all other fluid variables in terms of external quantities and the fluid four-velocity $u$.
+
+	The blast wave is comprised of two components, prompt ejecta with mass \Mej and shocked ISM with energy density $\tau$, radial width $\Delta r$, and angular width $\Delta \Omega$.
+Both components share a four-velocity $u$ and expand into a medium of constant density $\rho_0$.
 
@@
 	\frac{d \log \tobs}{d \psi} = \frac{8}{3} \cot \psi - \frac{1}{3} \frac{d \log E}{d \theta}\ , \\
-	\frac{d \log F_\nu}{d \psi} = \left(-s_1 + \frac{2}{3} s_2 +s_3+\beta\right)\cot \psi - \left(1+\frac{1}{3}s_3\right) \frac{d \log E}{d \theta}\ .
+	\frac{d \log F_\nu}{d \psi} = \left(-s_1 + \frac{2}{3} s_2 +s_3+\beta\right)\cot \psi - \left(1+\frac{1}{3}s_2\right) \frac{d \log E}{d \theta}\ .
 \end{eqnarray}
@@
 \begin{eqnarray}
-	\frac{d \log F_\nu}{d \log \tobs}(\psi) = \frac{3 \beta - 3s_1 + 2s_2+3s_3 + g(\psi)}{ 8+g(\psi)} \\
+	\frac{d \log F_\nu}{d \log \tobs}(\psi) = \frac{3 \beta - 3s_1 + 2s_2+3s_3 + (3+s_2)g(\psi)}{ 8+g(\psi)} \\
 	g(\psi) \equiv -\tan \psi \frac{d \log E}{d \theta}\ .

### 2018-07-10 structuredJets.tex
Added rough temporal slope figures.
adding in the flux equations for the different regimes into the appendix.

@@
 Both components share a four-velocity $u$ and expand into a medium of constant density $\rho_0$.
+
+\section{Structured Phase}
+
+\begin{figure}
+	\plottwo{figs/slopesJet.png}{figs/slopesCocoon.png}
+	\caption{Temporal slopes for the jet (left) and cocoon (right).}
+\end{figure}
 
@@
 
+The full flux scaling equations also require an updated energy and circumburst density scaling. For energy, it follows that (below $\nu_c$)
+\begin{equation}
+\frac{d \log F}{d \log E} = \frac{d \log F}{d \Psi} \frac{d \Psi}{d \log E} = - \frac{d \log F}{d \Psi} \frac{d \theta}{d \log E} = \left(s_1 - \frac{2}{3} s_2 - s_3 -\beta\right) h(\Psi) + 1 + \frac{1}{3} s_2,
+\end{equation}
+where
+\begin{equation}
+h(\Psi) \equiv \cot \Psi \frac{d \log E}{d \theta}.
+\end{equation}
+For the density $n_0$ we have (below $\nu_c$)
+\begin{equation}
+\frac{d \log F}{d \log n_0} = \frac{2+s_3}{8}
+\end{equation}
+
+Altogether, we obtain
+\begin{eqnarray}
+F_D & \propto & \epsilon_e^{-2/3} \epsilon_B^{1/3} n_0^{(2+s_3)/8} E^{\left(2/3 - s_3\right) h(\Psi) + 1} t_{obs}^{[-2+3s_3+3g(\Psi)]/[8+g(\Psi)]} \nu^{1/3} \nonumber \\
+F_E & \propto & \epsilon_B^{1} n_0^{}
+F_G & \propto & \epsilon_e^{p-1} \epsilon_B^{(1+p)/4} n_0^{(2+s_3)/8} E^{2ph(\Psi)+1} t_{obs}^{3[-2p+s_3+g(\Psi)]/[8+g(\Psi)]} \nu^{(1-p)/2} \nonumber \\
+F_H & \propto & \epsilon_e^{p-1} \epsilon_B^{(p-2)/4} n_0^{(-2+s_3)/8} E^{(2p + 2/3 - s_3)h(\Psi) + 2/3} t_{obs}^{[-6p-2+3s_3+2g(\Psi)]/[8+g(\Psi)]} \nu^{-p/2}
+\end{eqnarray}
+
 \section{Shock Jump Conditions and Synchrotron Parameters}

### 2018-07-10 structuredJets.tex
Some Text! Also some code and plots.

--- 2018-05-16 structuredJets.tex
@@
-\documentclass[modern]{aastex62}
+\documentclass[twocolumn]{aastex62}
 
@@
 
+\newcommand{\gwbns}{GW170817}
+\newcommand{\afterglowpy}{{\tt afterglowpy}}
+\newcommand{\python}{\tt{Python}}
+
+\newcommand{\dd}{\ensuremath{\mathrm{d}}}
 \newcommand{\Mej}{\ensuremath{M_{\mathrm{ej}}}}
 \newcommand{\tobs}{\ensuremath{t_{\mathrm{obs}}}}
+\newcommand{\tW}{\ensuremath{t_{\mathrm{w}}}}
+\newcommand{\tb}{\ensuremath{t_{\mathrm{b}}}}
+\newcommand{\tdec}{\ensuremath{t_{\mathrm{dec}}}}
+\newcommand{\tumin}{\ensuremath{t_{\mathrm{min}}}}
 \newcommand{\nuobs}{\ensuremath{\nu_{\mathrm{obs}}}}
@@
 \newcommand{\thW}{\ensuremath{\theta_{\mathrm{w}}}}
+\newcommand{\thC}{\ensuremath{\theta_{\mathrm{c}}}}
 \newcommand{\epse}{\ensuremath{\varepsilon_{\mathrm{e}}}}
@@
 \newcommand{\sigT}{\ensuremath{\sigma_{\mathrm{T}}}}
+\newcommand{\dL}{\ensuremath{d_{\mathrm{L}}}}
 \newcommand{\qe}{\ensuremath{q_{\mathrm{e}}}}
@@
 \newcommand{\Me}{\ensuremath{m_{\mathrm{e}}}}
+\newcommand{\Eiso}{\ensuremath{E_{\mathrm{iso}}}}
+\newcommand{\geff}{\ensuremath{g_{\mathrm{eff}}}}
+\newcommand{\umin}{\ensuremath{u_{\mathrm{min}}}}
+\newcommand{\umax}{\ensuremath{u_{\mathrm{max}}}}
 
@@
 \begin{abstract}
-Abstract abstract abstract.
+	Abstract abstract abstract
 \end{abstract}
 
-\section{Introduction} \label{sec:intro}
+\section{outline}
+
+\begin{itemize}
+	\item Need to consider the \emph{structure} of GRB explosions (esp.
+binary neutron stars).
+Structure may be radial (velocity stratification, $E(u)$) or angular ($E(\theta)$).
+Both modes affect the afterglow.
+	\item Analytic description: \begin{itemize}
+		\item Velocity stratification / refreshed shock / cocoon leads to simple power-law behaviour depending on $k$ ($E_{>u} \propto u^{-k}$).
+Breaks occur at deceleration time and when $E_{>u}$ shuts off.
+		\item Angular structure / structured jet leads to not-quite power-law behaviour, depending on $g \approx (\thobs - \theta)d \log E / d\theta$.
+Breaks occur when $\thobs - \thW \approx 1/\gamma(\thW)$ and $\thobs \approx 1/\gamma(0)$.
+$g = g(\theta)$, but $g\approx g_{eff}$ where $g_{eff} = g(\thobs/2)$.
+		\end{itemize}
+	\item Numerical description: \begin{itemize}
+		\item Single-shell ODE for shock evolution
+		\item Integrate over equal-$\tobs$ surfaces
+		\item Structured components independent.
+		\item public and open: install with \tt{pip}.
+		\end{itemize}
+	\item GW170817A - Both models are similar, fit GW170817A well!
+	\item Future observations: Rate of observed counter-parts will depend on degree of collimation of afterglow (jets have lower observed rates than cocoons).
+Radial structure may have $k$ vary from object to object.
+Angular structure WILL have $g$ vary from object to object.
+	\item Can we determine structure from the afterglow???
+\end{itemize}
+
+\section{Introduction}
+
+GRB afterglows are commonly modeled as top hat blast waves with no internal structure pointed directly at the observer.
+This has been largely sufficient given the data.
+(Although: viewing angle effects can be measured (Ryan+ 2015)).
+New observational capabilities have witnessed new phases of afterglow evolution, such as the discovery of plateaus with Swift.
+Real jets (of course) have internal structure, but the top hat assumption has been a sufficiently spherical cow.
+
+GW170817 changes the picture: new object with a strange afterglow.
+Steep/late rise, LONG slow rise, turnover at 160d.
+The slow rise is impossible to reproduce with standard afterglow evolution: first observation of a \emph{structured} phase of evolution.
+
+The dominant contribution may be an angular distribution of energy within the blast wave (``structured jet'') combined with off-axis viewing (CITE Rossi04).
+For 170817 this corresponds to the ``successful jet'' picture.
+Alternately, radial stratification of velocity (``refreshed shock'') can cause a similar phase, most simply with a quasi-spherical (or at least top-hat) angular structure.
+This situation is produced by the ``choked jet''  or ``cocoon'' picture of 170817.
+Understanding the effects of both structures on afterglows, and their dependence on the parameters of the burst, are vital to understanding GW counterparts.
+
+To this end, we have calculated the power-law temporal slope of the structured phase in both angular and radial structure dominated cases, along with the corresponding observed break times.
+We have developed a semi-analytic numerical model of structured GRB afterglows for detailed comparison to data, which is now publicly available.
+
+Summary: In section 2 we discuss structured jets, in section 3 refreshed shocks, in section 4 our numerical model, section 5 application to GW170817, and section 6 future applications and discussion.
+
+\section{Structured Jets}\label{sec:structuredJets}
+
+The \emph{structured jet} is a model where the isotropic-equivalent energy of a blast wave is a function of the angle from the jet axis: $\Eiso = E(\theta)$.
+The specific structure of a jet is determined by the intrinsic structure of the jet launching mechanism as well as the sculpting that occurs as the jet burrows out of the encasing ejecta debris (as in a binary neutron star merger) or stellar envelope (as in a collapsar).
+
+Numerical simulations have revealed a variety of jet angular energy distributions, often containing an energetic core with power-law tails.
+Figure \ref{fig:jetStruct} shows a collection of jet energy distributions from the literature (CITE curves in plots).
+Lacking a well-established physical model of the true $E(\theta)$, in particular its dependence on the parameters of the system, we consider two simple parameterized models: a Gaussian jet and a power-law.
+
+\begin{align}
+	E(\theta) &= E_0 \exp\left(-\frac{\theta^2}{2\thC^2}\right)  && \text{Gaussian} \label{eq:gauss}\\
+	E(\theta) &= \frac{E_0}{1 + (\theta/ \thC)^2}  && \text{power-law} \label{eq:pl}
+\end{align}
+
+\begin{figure}
+	\plotone{figs/jetStruct.pdf}
+	\caption{Jet Structure.  Temporary version.  Remove $\Gamma$ subplot.  Add Aloy. \label{fig:jetStruct}}
+\end{figure}
+
+Each model is parameterized by a normalization $E_0$, a width $\thC$, and a truncation angle $\thW$.
+Outside $\thW$ the energy is initially zero.
+Figure \ref{fig:jetStruct} shows an example of each model fit to recent simulation results.
+The Gaussian model emulates jets with sharp edges, while the power-law emulates jets with narrow cores and large wings (AWK.
+jargon?).
+
+To observers, an energy gradient along the blast wave surface presents itself as a slow, rising or decaying, evolution of the flux.
+The usual (pre-jet break) decay is compensated for by regions of higher energy continuously coming into view.
+These new contributions to the emission slow the decay and can even cause the observed flux to increase with time.
+
+We call this the \emph{structured} phase of emission.
+It begins at observer time $\tW$, once the blast wave is decelerating and the observer is within the beaming cone of any part of the emitting surface.
+It ends at observer time $\tb$, when the jet core has become fully visible.
+These times are:
+\begin{align}
+	\tW &= \left(\frac{9}{16\pi} \frac{E(\thW)}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thobs-\thW}{2}\right)\right)^{8/3} \ ,\label{eq:tw} \\
+	\tb &= \left(\frac{9}{16\pi} \frac{E_0}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thobs}{2}\right)\right)^{8/3} \ .\label{eq:tb}
+\end{align}
+
+\begin{figure}
+	\plotone{figs/jetDecomp.pdf}
+	\caption{A structured jet, decomposed into emission from different latitudes $\theta$.
+The structured phase is the result of the brightest point of the blast-wave tracking from the wings to the jet core.
+\label{fig:decomp}}
+\end{figure}
+Figure \ref{fig:decomp} shows the light curve of a structured jet along with the emissions from different latitudes.
+The part of the blast wave dominating the emission tracks from the high latitude wings $\theta \approx \thW$ to the core $\theta \approx 0$.
+
+During the structured phase, the afterglow has a temporal spectral slope which depends on the parameter $g(\theta)$:
+\begin{equation}
+	g(\theta) \equiv -2 \tan\left(\frac{\thobs - \theta}{2}\right)\frac{d \log E}{d \theta}\ . \label{eq:gdef}
+\end{equation}
+
+The temporal and spectral slopes for various regimes are given in Table \ref{tab:slopes}.  The derivation of the slopes, $\tW$, and $\tb$ are given in Appendix \ref{sec:derive1}.
+
+\begin{deluxetable*}{CCCCCC}
+	\tablecaption{Structured jet temporal and spectral slopes: $F_\nu \propto \tobs^\alpha \nu^\beta$.
+See Equations \eqref{eq:gdef} and \eqref{eq:geff} for the definition and effective values of $g$.
+For a refreshed-shock model replace $g$ with $k$, defined in Equation \eqref{eq:Eu}.
+\label{tab:slopes}}
+	\tablehead{\colhead{Regime}& \colhead{Label} & \colhead{$\alpha_{\mathrm{off-axis}}$}& \colhead{$\alpha_{\mathrm{struct}}$}& \colhead{$\alpha_{\mathrm{struct,max}}$} & \colhead{$\beta$}}
+	\startdata
+	\nu<\nu_m<\nu_c     & D & 7 			& \frac{-2+3s_3 + 3g}{8+g} 		& 3		& 1/3 \\
+	\nu_m<\nu<\nu_c     & G & 15/2 - 3p/2 	& \frac{- 6p + 3s_3 + 3g}{8+g} 		& 3		& (1-p)/2 \\
+	\nu < \nu_c < \nu_m & E & 17/3 		& \frac{-14/3 + 3s_3 + 11g/3}{8+g} 	& 11/3	& 1/3 \\
+	\nu_c < \nu < \nu_m & F & 13/2 		& \frac{-8+3s_3 + 2g}{8+g} 		& 2		& -1/2 \\
+	\nu_c < \nu_m < \nu & H & 8 - 3p/2 		& \frac{-6p - 2 + 3s_3 + 2g}{8+g} 	& 2		& -p/2 \\ 
+	\enddata
+\end{deluxetable*}
+
+The $g$ parameter evolves with time as the brightest sector of the jet sweeps from the edge to the core.
+This produces deviations in the light curve from a pure power-law.
+However, we find ultimately these deviations are not too large and the average slope is well approximated by $\geff  = g(\thobs/2)$.
+For the power-law and Gaussian jet models this gives:
+\begin{align}
+	\geff &= \frac{\thobs^2}{4\thC^2} && \text{Gaussian}\ , \\
+	\geff &= \frac{2 \thobs^2}{4 \thC^2+\thobs^2} && \text{power-law}\ . \label{eq:geff}
+\end{align}
+These values may be used in Table \ref{tab:slopes} for an approximate power-law model of a structured jet with an appropriate viewing angle dependent temporal evolution.
+These analytic results are in agreement with previous work on structured jets (CITE ROSSI) and the trans-relativistic numerical model described in Section \ref{sec:numerical}.
+
+In the structured phase, the temporal slope depends directly on the ratio $\thobs/\thC$.
+Therefore any measurement of the effective power law slope of an afterglow light curve can be used to measure this parameter.
+
+\section{Refreshed Shocks}\label{sec:refreshedShocks}
+
+An alternative mechanism to produce slow decays or rises in afterglow light curves is the \emph{refreshed shock}, where velocity stratification of the ejecta causes a prolonged period of energy injection.
+Slow material initially coasting behind the shock is gradually incorporated into the blast wave as it decelerates, ``refreshing'' the shock.
+This mechanism was first proposed as an energy injection scenario (CITE), and recently has been proposed as the mechanism behind GW170817 in the choked-jet scenario.
+(CITE Mooley, Hotokezaka, etc).
+
+In the simplest case the visible part of the blast wave is assumed to be quasi-spherical.
+The distribution of material behind the blast wave is specified by $E_{>}(u)$, the energy of all material in the ejecta with four-velocity greater than $u$.
+This is typically taken to be a power-law in $u$ within the finite domain $[\umin, \umax]$:
+\begin{equation}
+	E_>(u) = E_r u^{-k}\ , \label{eq:Eu}
+\end{equation}
+where $u \in (\umin, \umax)$ is the dimensionless four-velocity, $k>0$ is the power law index, and $E_r$ is a normalization factor.
+
+A blast wave will have an initial coasting period before sweeping up enough mass in the ambient medium to begin deceleration and be subject to refreshed shocks.
+The shock refreshment ends when the blast wave decelerates past $\umin$.
+These times are given by:
+\begin{align}
+	\tdec &= ... \ ,\label{eq:tdec} \\
+	\tumin &= \left(\frac{9}{16\pi} \frac{E_r}{n_0 \Mp c^5}\right)^{1/3} \umin^{-8/3} \ .\label{eq:tumin}
+\end{align}
+The temporal and spectral slopes in this mechanism are identical to the structured jet, but with the replacement $k \leftrightarrow g$.  For a derivation see Appendix \ref{sec:derive3}.
+
+\section{Numerical Model: The \afterglowpy{} Package}\label{sec:numerical}
+
+To examine the detailed behavior of structured afterglows we constructed a numerical model, publicly available as the \afterglowpy{} Python package.
+
+The numerical model employs a trans-relativistic equation of state to evolve a blast wave in the single-shell approximation from the initial coasting phase through deceleration and spreading into the non-relativistic Sedov phase.
+The observed flux density $F_\nu$ is calculated by numerically integrating the synchrotron emissivity over equal-observer-time surfaces.
+
+The flux calculation follows the semi-analytic method of (CITE Hendrik 2010) using the shock evolution prescription outlined in (CITE Hendrik Review) modified to include refreshed shocks, energy injection, and jet spreading.
+For a structured jet, the surface is divided into $N_\theta$ annular regions each of which is allocated an energy according to $E(\theta)$.
+Each segment evolves independently and is otherwise treated as a section of a top-hat jet.
+
+\subsection{Numerical Algorithm}\label{subsec:algo}
+
+To compute the light curve of a top-hat jet we first must calculate the time evolution of the blast wave.
+We utilize the single-shell approximation, treating the ejecta mass, contact discontinuity, and forward shock as a single unit propagating through a cold ambient medium with constant rest-mass density $\rho_0 = \Mp n_0$.
+For a detailed derivation see Appendix \ref{sec:deriveNum} and (CITE Hendrik 2010 + Hendrik Review).
+The forward shock is a radius $R$ from the explosion and moves at a velocity $\beta_s$.
+In terms of the fluid four-velocity behind the shock $u$ and its Lorentz factor $\gamma$ this may be written as:
+\begin{equation}
+	\dot{R} = \frac{4 u \gamma}{4 u^2 +3}c\ . \label{eq:Rdot}
+\end{equation}
+Here the time derivative $\dot{R}$ is taken with respect to elapsed time in the bursters' frame $t$.
+
+ The evolution of the four velocity is determined through conservation of energy.  The total energy in the trans-relativistic single shell approximation is:
+\begin{equation}
+	E = (\gamma - 1)\Mej c^2 + \frac{4\pi}{9} \rho_0 c^2 R^3 (4 u^2 + 3) \beta^2 \Omega\ . \label{eq:E}
+\end{equation}
+In Equation \eqref{eq:E} the first term is the kinetic energy of the ejected mass $\Mej$, assumed to have already accelerated and adiabatically cooled to its coasting velocity.
+The second term is the kinetic and thermal energy of the shocked ISM with three-velocity $\beta = u / \gamma$.
+The shocked ISM is confined to a cone of solid angle $\Omega = 2 \sin^2 (\theta_0/2)$ where $\theta_0$ is the half-opening angle of the jet.
+While the blast wave is relativistic $\theta_0$ is constant, but once the jet becomes non-relativistic it begins to spread due to its own internal pressure until the blast wave is spherical.
+The spreading occurs at sound speed $c_s$ in the fluid rest-frame (CITE Hendrik 2010, Duffell+Laskar 2017):
+\begin{equation}
+	\dot{\theta_0} = \frac{c_s}{\gamma R}\ , \qquad \text{if } u < 1\text{ and } \theta_0 > \pi/2\ . \label{eq:thetadot}
+\end{equation}
+Given a (possibly constant) expression for $E$ Equation \eqref{eq:E} may be differentiated with respect to $t$ and solved for $\dot{u}$.
+In a refreshed shock scenario $E = E_{>}(u)$, whereas for a standard energy injection model one may take $E \propto t^{-q}$.
+In either case, Equation \eqref{eq:E} produces an equation for $\dot{u}$.
+This defines a three dimensional system of ordinary differential equations in the variables $(R, u, \theta_0)$.
+We solve this system using RK4 on a sequence of geometrically spaced values of $t$, typically $10^3$ points per decade.
+This produces a numerical table of $R(t)$, $u(t)$, and $\theta_0(t)$ in terms of the burster time $t$.
+The beginning and end points of the solution are chosen to encompass all required values of $\tobs$.
+
+Once the shock evolution is known, the flux is given by the integral:
+\begin{equation}
+	F_\nu(\tobs, \nuobs) = \frac{1}{4\pi \dL^2} \int \! \dd \Omega\ R^2\ \Delta R\  \delta^2\ \epsilon'_{\nu'} \ , \label{eq:flux}
+\end{equation}
+where $\tobs$ is the time in the observer's frame, $\nuobs$ the observational frequency, $\dL$ the luminosity distance, $\Delta R$ the shock width, $\delta$ the Doppler factor of the fluid, and $\epsilon'_{\nu'}$ the synchrotron emissivity in the fluid rest frame.
+The integral is taken in spherical polar coordinates $(\theta, \phi$) where $\theta = 0$ aligns with the jet axis and $\phi=0$ is directed towards the observer.
+The observer is at an angle $\thobs$ with the jet axis.
+The integrand is evaluated at a constant observer time $\tobs$, related to $t$ by:
+\begin{equation}
+	\tobs = t - \mu(\theta, \phi) R(t)/c\ , \label{eq:tobs}
+\end{equation}
+where 
+\begin{equation}
+	\mu = \cos \theta \cos \thobs + \sin \theta \sin \thobs \cos \phi\ . \label{eq:mu}
+\end{equation}
+The integral \eqref{eq:flux} is evaluated numerically using an adaptive Romberg integrator in each dimension, with a typical relative tolerances of $10^{-6}$.
+Each evaluation of the integrand requires a binary search to determine the burster time $t$ at which to evaluate $R$, $u$, and $\theta_0$.
+Fluid quantities are then calculated using the shock-jump conditions and the synchrotron emissivity is evaluated using the standard external shock formulae (CITE Hendrik, Granot+Sari).
+
+The numerical accuracy of a top-hat light curve is typically better than $10^{-4}$.
+The structured jet calculation splits the integration domain into $N_\theta$ disjoint annuli, each evaluated as an independent top-hat and summed.
+By default $N_\theta$ is chosen such that there will be 5 zones per $\thC$-sized interval, giving final light curves with a numerical accuracy of $10^{-2}$.
+
+\subsection{\afterglowpy{}}
+
+We have constructed the \afterglowpy{} Python package to implement this algorithm and provide it to the community.
+The integration routine itself is written in C, wrapped as an extension for Python, and has been optimized to be used in intensive data analysis routines such as Markov Chain Monte-carlo which can require many thousands of evaluations.
+
+\afterglowpy{} is available on PyPI and may be installed with {\tt pip}.  The source code is open and available at https://github.com/geoffryan/afterglowpy.
+
+\section{Application: GW170817A}
+
+\section{Discussion}
+
+\newpage
+
+\section{Structured Phase}
+
+\begin{figure}
+	\plottwo{figs/slopesJet.png}{figs/slopesCocoon.png}
+	\caption{Temporal slopes for the jet (left) and cocoon (right).}
+\end{figure}
 

### 2018-07-10 code/plotClosure.py

@@ -307,7 +307,20 @@ def plot_lc_jet(t, thV, thC, thW, E0, n0, p, jetType=0, seg='G'):
     #F0 = FnuSA[ip]
     #FnuSA /= F0
 
-    Fnu = pl_lc_jet(t, thV, thC, thW, E0, n0, p, jetType, seg)
+    if seg is not None:
+        Fnu = pl_lc_jet(t, thV, thC, thW, E0, n0, p, jetType, seg)
+    else:
+        FnuSAb = grb.fluxDensity(t, nu*2, jetType, 0, *Y)
+        FnuSAa = grb.fluxDensity(t, nu*0.5, jetType, 0, *Y)
+        beta = np.log(FnuSAb/FnuSAa) / np.log(2/0.5)
+        bD = 1.0/3.0
+        bE = 1.0/3.0
+        bF = -0.5
+        bG = 0.5*(1-p)
+        bH = -0.5*p
+        HHH = beta < 0.25-0.5*p
+        FFF = (beta >= 0.25-0.5*p)
+
     
     ir = np.searchsorted(t, 0.1*tp)
     F0 = FnuSA[ir]/Fnu[ir]
@@ -589,7 +602,7 @@ if __name__ == "__main__":
     n0 = 1.0e-2
     p = 2.3
     jetType = 0
-    seg = 'G'
+    seg = 'D'
 
     umax = 10.0
     umin = 3.0

### 2018-07-10 code/plotStructDecomp.py

@@ -1,0 +1,59 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import grbpy as grb
+
+
+jetType = 0
+
+thV = 0.5
+thC = 0.1
+thW = 0.4
+E0 = 1.0e52
+n0 = 1.0e-2
+p = 2.3
+epse = 0.1
+epsB = 0.001
+dL = 1.0e27
+
+
+t = np.logspace(3, 8, 200)
+nu = np.empty(t.shape)
+nu[:] = 1.0e14
+
+Y = np.array([thV, E0, thC, thW, 0, 0, 0, n0, p, epse, epsB, 1.0, dL])
+
+Fnu = grb.fluxDensity(t, nu, jetType, 0, *Y)
+
+Nth = 10
+
+FnuR = np.empty((Nth, t.shape[0]))
+dth = thW/Nth
+
+for i in range(Nth):
+    thout = thW - i*dth
+    thin = thW - (i+1)*dth
+    if thout < 0.0:
+        thin = 0.0
+    x = float(i)/(Nth-1)
+    th = x*thin+(1-x)*thout
+    E = E0*np.exp(-0.5*th*th/(thC*thC))
+    Y[1] = E
+    Y[2] = thin
+    Y[3] = thout
+    FnuR[i,:] = grb.fluxDensity(t, nu, -2, 0, *Y)
+
+fig, ax =  plt.subplots(1,1)
+for i in range(Nth):
+    ax.plot(t, FnuR[i])
+ax.plot(t, Fnu, color='k')
+ax.set_xscale('log')
+ax.set_yscale('log')
+ax.set_xlabel(r'$t$ (s)')
+ax.set_ylabel(r'$F_{\nu}$ (erg/cm$^2$s Hz)')
+
+ax.set_ylim(1.0e-12, None)
+
+name = "jetDecomp.pdf"
+
+print("Saving "+name)
+fig.savefig(name)

### 2018-07-13 structuredJets.tex
Fixed merge typo
I have added the scaling equations for the different spectral regimes, computing using scale invariance. The Maple worksheet for this is included as well, in the code subdirectory

@@
 
+The full flux scaling equations also require an updated energy and circumburst density scaling.
+We can obtain the scalings for energy and density from dimensional analysis, following \cite{vanEertenMacFadyen2012} (specifically, by making use of the fact that the overall flux scalings for the different spectral regimes should obey those presented in table 1 of that paper).
+
+{\color{red}[RED STUFF IS WRONG SOMEHOW]
+  For energy, it follows that (below $\nu_c$)
+\begin{equation}
+	\frac{d \log F}{d \log E} = \frac{d \log F}{d \Psi} \frac{d \Psi}{d \log E} = - \frac{d \log F}{d \Psi} \frac{d \theta}{d \log E} = \left(s_1 - \frac{2}{3} s_2 - s_3 -\beta\right) h(\Psi) + 1 + \frac{1}{3} s_2,
+\end{equation}
+where
+\begin{equation}
+	h(\Psi) \equiv \cot \Psi \frac{d \log E}{d \theta}.
+\end{equation}
+For the density $n_0$ we have (below $\nu_c$)
+\begin{equation}
+	\frac{d \log F}{d \log n_0} = \frac{2+s_3}{8}
+\end{equation}
+}
+Altogether, we obtain
+\begin{eqnarray}
+F_D & \propto & \epsilon_e^{-2/3} \epsilon_B^{1/3} n_0^{(6+4g+3s_3)/3(8+g(\Psi))} E_0^{(26-3s_3)/3(8+g(\Psi))} t_{obs}^{(-2+3s_3+3g(\Psi))/(8+g(\Psi))} \nu^{1/3} \nonumber \\
+F_E & \propto & \epsilon_B^{1} n_0^{(14+6g(\Psi)+3s_3)/3(8+g(\Psi))} E_0^{(34-3s_3)/3(8+g(\Psi))} t_{obs}^{(-14+9s_3+11g(\Psi))/3(8+g(\Psi))} \nu^{1/3} \nonumber \\
+F_F & \propto & \epsilon_B^{-1/4} n_0^{(-8+3g(\Psi)+4s_3)/4(8+g(\Psi))} E_0^{(8-s_3)/(8+g(\Psi))} t_{obs}^{(-8+3s_3+2g(\Psi))/(8+g(\Psi))} \nu^{-1/2} \nonumber \\
+F_G & \propto & \epsilon_e^{p-1} \epsilon_B^{(1+p)/4} n_0^{(g(\Psi)p + 5 g(\Psi) + 4s_3 + 8)/4(8+g(\Psi))} E_0^{(8+2p-s_3)/(8+g(\Psi))} t_{obs}^{3(-2p+s_3+g(\Psi))/(8+g(\Psi))} \nu^{(1-p)/2} \nonumber \\
+F_H & \propto & \epsilon_e^{p-1} \epsilon_B^{(p-2)/4} n_0^{(g(\Psi)p+2g(\Psi)+4s_3-8)/4(8+g(\Psi))} E_0^{(6+2p-s_3)/(8+g)} t_{obs}^{(-6p-2+3s_3+2g(\Psi))/(8+g(\Psi))} \nu^{-p/2} \nonumber \\
+\nu_m & \propto & \epsilon_e^2 \epsilon_B^{1/2} n_0^{g(\Psi)/(16+2g(\Psi))} E_0^{4/(8+g(\Psi))} t_{obs}^{-12/(8+g(\Psi))} \nonumber \\
+\nu_c & \propto & \epsilon_B^{-3/2} n_0^{-(3g(\Psi)+16)/2(8+g(\Psi))} E_0^{-4/(8+g(\Psi))} t_{obs}^{-2(2+g(\Psi))/(8+g(\Psi))} \nonumber \\
+F_{peak} & \propto & \epsilon_B^{1/2} n_0^{(4+3g(\Psi)+2s_3)/2(8+g(\Psi))} E_0^{(10-s_3)/(8+g(\Psi))} t_{obs}^{3(-2+s_3+g(\Psi))/(8+g(\Psi))}
+\end{eqnarray}
+
 \section{Shock Jump Conditions and Synchrotron Parameters}

### 2018-07-13 structuredJets.tex
added redshifts to the flux equations

--- 2018-07-10 structuredJets.tex
@@
 
+The full flux scaling equations also require an updated energy and circumburst density scaling.
+We can obtain the scalings for energy and density from dimensional analysis, following \cite{vanEertenMacFadyen2012} (specifically, by making use of the fact that the overall flux scalings for the different spectral regimes should obey those presented in table 1 of that paper).
+
+{\color{red}[RED STUFF IS WRONG SOMEHOW]
+  For energy, it follows that (below $\nu_c$)
+\begin{equation}
+	\frac{d \log F}{d \log E} = \frac{d \log F}{d \Psi} \frac{d \Psi}{d \log E} = - \frac{d \log F}{d \Psi} \frac{d \theta}{d \log E} = \left(s_1 - \frac{2}{3} s_2 - s_3 -\beta\right) h(\Psi) + 1 + \frac{1}{3} s_2,
+\end{equation}
+where
+\begin{equation}
+	h(\Psi) \equiv \cot \Psi \frac{d \log E}{d \theta}.
+\end{equation}
+For the density $n_0$ we have (below $\nu_c$)
+\begin{equation}
+	\frac{d \log F}{d \log n_0} = \frac{2+s_3}{8}
+\end{equation}
+}
+Altogether, we obtain
+\begin{eqnarray}
+F_D & \propto & (1+z)^{(38-5g(\Psi)-9s_3)/3(8+g(\Psi))} \epsilon_e^{-2/3} \epsilon_B^{1/3} n_0^{(6+4g+3s_3)/3(8+g(\Psi))} E_0^{(26-3s_3)/3(8+g(\Psi))} t_{obs}^{(-2+3s_3+3g(\Psi))/(8+g(\Psi))} \nu^{1/3} \nonumber \\
+F_E & \propto & (1+z)^{(46-7g(\Psi)-9s_3)/3(8+g(\Psi))} \epsilon_B^{1} n_0^{(14+6g(\Psi)+3s_3)/3(8+g(\Psi))} E_0^{(34-3s_3)/3(8+g(\Psi))} t_{obs}^{(-14+9s_3+11g(\Psi))/3(8+g(\Psi))} \nu^{1/3} \nonumber \\
+F_F & \propto & (1+z)^{(24-3g(\Psi)-6s_3)/2(8+g(\Psi))} \epsilon_B^{-1/4} n_0^{(-8+3g(\Psi)+4s_3)/4(8+g(\Psi))} E_0^{(8-s_3)/(8+g(\Psi))} t_{obs}^{(-8+3s_3+2g(\Psi))/(8+g(\Psi))} \nu^{-1/2} \nonumber \\
+F_G & \propto & (1+z)^{\frac{(-pg(\Psi)-3g(\Psi)+4p-6s_3+24)}{2(8+g(\Psi))}} \epsilon_e^{p-1} \epsilon_B^{(1+p)/4} n_0^{(g(\Psi)p + 5 g(\Psi) + 4s_3 + 8)/4(8+g(\Psi))} E_0^{(8+2p-s_3)/(8+g(\Psi))} t_{obs}^{3(-2p+s_3+g(\Psi))/(8+g(\Psi))} \nu^{(1-p)/2} \nonumber \\
+F_H & \propto & (1+z)^{\frac{(-pg(\Psi)-2g(\Psi)+4p-6s_3+20)}{2(8+g(\Psi))}} \epsilon_e^{p-1} \epsilon_B^{(p-2)/4} n_0^{(g(\Psi)p+2g(\Psi)+4s_3-8)/4(8+g(\Psi))} E_0^{(6+2p-s_3)/(8+g)} t_{obs}^{(-6p-2+3s_3+2g(\Psi))/(8+g(\Psi))} \nu^{-p/2} \nonumber \\
+\nu_m & \propto & (1+z)^{\frac{4-g(\Psi)}{8+g(\Psi)}} \epsilon_e^2 \epsilon_B^{1/2} n_0^{g(\Psi)/(16+2g(\Psi))} E_0^{4/(8+g(\Psi))} t_{obs}^{-12/(8+g(\Psi))} \nonumber \\
+\nu_c & \propto & (1+z)^{\frac{-4+g(\Psi)}{8+g(\Psi)}} \epsilon_B^{-3/2} n_0^{-(3g(\Psi)+16)/2(8+g(\Psi))} E_0^{-4/(8+g(\Psi))} t_{obs}^{-2(2+g(\Psi))/(8+g(\Psi))} \nonumber \\
+F_{peak} & \propto & (1+z)^{\frac{14-2g(\Psi)-3s_3}{8+g(\Psi)}} \epsilon_B^{1/2} n_0^{(4+3g(\Psi)+2s_3)/2(8+g(\Psi))} E_0^{(10-s_3)/(8+g(\Psi))} t_{obs}^{3(-2+s_3+g(\Psi))/(8+g(\Psi))}
+\end{eqnarray}
+
 \section{Shock Jump Conditions and Synchrotron Parameters}

### 2018-12-11 structuredJets.tex
Writing and code updates.

@@
 \begin{abstract}
-	Abstract abstract abstract
+	Gamma-ray bursts (GRBs) associated with gravitational wave events are, and will likely continue to be, viewed at a larger inclination than their fellow GRBs without gravitational wave detections.
+As demonstrated by the afterglow of GW170817A, this requires an extension of the common GRB afterglow models which typically assume emission from an on-axis top hat jet.
+We present a characterization of the afterglows arising from structured jets, utilizing both trans-relativistic numerical calculations and simple analytic approximations.
+The temporal slope before the jet break is found to be a simple function of the ratio between the inclination angle and effective half opening angle of the jet.
+Our models, both numerical and analytic, are publicly available as an open source Python package.
+
 \end{abstract}
@@
 Figure \ref{fig:jetStruct} shows a collection of jet energy distributions from the literature (CITE curves in plots).
-Lacking a well-established physical model of the true $E(\theta)$, in particular its dependence on the parameters of the system, we consider two simple parameterized models: a Gaussian jet and a power-law.
+Lacking a well-established physical model of the true $E(\theta)$, in particular its dependence on the parameters of the system, we consider two simple parameterized models: a Gaussian jet and a softened power-law.
 
@@
 
-To observers, an energy gradient along the blast wave surface presents itself as a slow, rising or decaying, evolution of the flux.
-The usual (pre-jet break) decay is compensated for by regions of higher energy continuously coming into view.
+A generic energy profile $E(\theta)$ may have several more parameters, but one can still associate an on-axis energy $E_0 = E(0)$ and an effective core width $\thC \sim |E''(0)/E_0|^{-1/2}$ which should fully specify the leading order near on-axis behaviour.
+The afterglow light curve of a structured jet follows one of two qualitatively different regimes depending on the orientation of the viewer with respect to $\thC$.
+We refer to the regimes as ``on-axis'' when $\thobs < \thC$, and ``off-axis'' when $\thobs > \thC$.
+
+\subsection{On-Axis Evolution: $\thobs \lesssim \thC$}
+
+The on-axis light curve of a structured jet is essentially identical to that of a standard top-hat viewed within the jet cone.
+The afterglow is comprised of four phases, \emph{pre-jet break}, \emph{transition}, \emph{post-jet break}, \emph{Newtonian}.
+These are well described in the literature and are only briefly reviewed here.
+
+\emph{Pre-jet break} ---  At early times the flux is dominated by the small patch of material whose emission is beamed towards the observer: $\psi = |\theta-\thobs| \lesssim \gamma^{-1}$.
+This patch is within the $\theta < \thC$ region where $E(\theta) \approx E_0$ and the structure plays a sub-dominant role.
+The visible patch grows as $\gamma^{-2}$.
+Closure relations and scalings of the standard on-axis top-hat apply.
+(CITE Sari, Piran Narayan)
+
+\emph{Transition} ---  When $\gamma^{-1} \sim \thC-\thobs$ the near edge of the jet comes in to view.
+Material outside $\thC$ is less energetic and contributes sub-dominantly to the afterglow emission.
+The visible patch grows more slowly and the decay of the afterglow steepens slightly.
+Closure relations and scalings of the standard on-axis top-hat apply only approximately (CITE vanEerten MacFadyen 2010).
+
+\emph{Post-jet break} ---  When $\gamma^{-1} \sim \thC+\thobs$ the far edge of the jet comes in to view and growth of the visible patch ceases.
+The power-law slope of the light curve is decreased by -3/4 relative to the pre-jet break slope.
+
+\emph{Newtownian} ---  The decelerating blast wave becomes non-relativistic, spreads sonically, and approaches a Sedov-Taylor solution.
+
+\subsection{Off-Axis Evolution: $\thobs \gtrsim \thC$}
+
+When viewed at angles larger than $\thC$ the gradient $E'(\theta)$ over the visible patch becomes non-negligible.
+To observers this energy gradient presents itself as a slowly rising or decaying afterglow light curve.
+The afterglow is comprised of three or four phases depending on whether the observer lies within the truncation angle, \emph{off-axis}, \emph{structured}, \emph{post-jet break}, and \emph{Newtonian}.
+
+\emph{Off-axis} --- If the viewer lies outside the truncation angle, $\thobs > \thW$, then at early times the entire blast wave surface is off-axis and all emission is beaming suppressed.
+This greatly reduces the early flux and leads to a dim but steeply rising light curve as the blast wave decelerates.
+Emission is dominated by material on the edge nearest the observer and the angular size of the visible patch is constant in time.
+This phase ends at $\tW$ when $\gamma^{-1} \sim \thobs-\thW$.
+If $\thobs < \thW$ this phase is entirely absent.
+
+\emph{Structured} --- The structured phase is the direct result of the energy gradient along the observer's line of site.
+The usual (pre-jet break) decay is compensated for by regions of higher energy continuously coming into view as the jet decelerates.
 These new contributions to the emission slow the decay and can even cause the observed flux to increase with time.
 
-We call this the \emph{structured} phase of emission.
  It begins at observer time $\tW$, once the blast wave is decelerating and the observer is within the beaming cone of any part of the emitting surface.
@@
 Figure \ref{fig:decomp} shows the light curve of a structured jet along with the emissions from different latitudes.
-The part of the blast wave dominating the emission tracks from the high latitude wings $\theta \approx \thW$ to the core $\theta \approx 0$.
+The part of the blast wave dominating the emission tracks from the high latitude wings $\theta \approx \thW$ to the core $\theta \approx 0$ and the angular size of the visible patch grows approximately as $\gamma^{-1.5}$.
 
@@
 
+\emph{Post-jet break} --- Once the entire jet is visible (ie.
+the observer is within the beaming cone of the entire jet) the visible patch no longer grows and emission is dominated by the decelerating core.
+This phase follows exactly the post-jet break scalings of the on-axis case, except with a much delayed break time $\tb$.
+
+\emph{Newtonian} --- The approach to a Newtonian Sedov solution proceeds in a similar manner to the on-axis case.
+Relativistic beaming ceases to be an important effect and the afterglow light curve looks similar at all viewing angles.
+
 \section{Refreshed Shocks}\label{sec:refreshedShocks}
@@
 The temporal and spectral slopes in this mechanism are identical to the structured jet, but with the replacement $k \leftrightarrow g$.  For a derivation see Appendix \ref{sec:derive3}.
+
+\subsection{Relation to Energy Injection Models}
+
+The refreshed shock model as constructed here is equivalent to the similar energy injection models in (CITE Zhang09).
+That work specifies the index $s$ of the mass distribution $M_{>u} \propto u^{-s}$, which is related simply to the index $k$ by $k = s-1$.
+Under this mapping the closure relations in Table \ref{tab:slopes} are equivalent to those in (CITE Zhang 09).
+The numerical model described in Section \ref{sec:numerical} improves on these analytic approximations by ...
+
+The structured jet $g(\theta)$ parameter can similarly...
 
@@
 				\tobs^{(3+s_2)/4+3(-s_1+\beta)/8} \nuobs^\beta, &\text{(on-axis, pre jet break)} \\
-				\tobs^{s_2/4 + 3(-s_1+\beta)/4} \nuobs^\beta, & \text{(on-axis, post jet break)} \end{matrix} \right . \ .
+				\tobs^{s_2/4 + 3(-s_1+\beta)/8} \nuobs^\beta, & \text{(on-axis, post jet break)} \end{matrix} \right . \ .
 \end{equation}

### 2018-12-11 code/plotClosure.py

@@ -5,6 +5,7 @@ import grbpy as grb
 
 decompPlot = False
 
+
 def f_struct(th, thC, jetType=0):
 
     if jetType == -1:
@@ -15,6 +16,7 @@ def f_struct(th, thC, jetType=0):
         return 1.0/(1.0 + th*th/(thC*thC))
 
     return 1.0
+
 
 def t_on(thV, thC, thW, E0, n0, p, jetType=0):
 
@@ -27,8 +29,10 @@ def t_on(thV, thC, thW, E0, n0, p, jetType=0):
 
     t0 = math.pow(9.0/(16.0*np.pi) * E0*fW/(n0*grb.mp*c5), 1.0/3.0)
 
-    #return t0 * math.pow(math.sin(thV-thW), 8.0/3.0)
-    return t0 * math.pow(2,-1.6) * math.pow(2*math.sin(0.5*(thV-thW)), 8.0/3.0)
+    # return t0 * math.pow(math.sin(thV-thW), 8.0/3.0)
+    return t0 * math.pow(2, -1.6) * math.pow(2*math.sin(0.5*(thV-thW)),
+                                             8.0/3.0)
+
 
 def t_peak(thV, thC, thW, E0, n0, p):
 
@@ -39,13 +43,15 @@ def t_peak(thV, thC, thW, E0, n0, p):
 
     t0 = math.pow(9.0/(16.0*np.pi) * E0/(n0*grb.mp*c5), 1.0/3.0)
 
-    #return t0 * math.pow(math.sin(thV-thC), 8.0/3.0)
+    # return t0 * math.pow(math.sin(thV-thC), 8.0/3.0)
     return t0 * math.pow(2*math.sin(0.5*thV), 8.0/3.0)
 
+
 def t_newt(E0, n0):
-    
+
     c5 = grb.c ** 5
     return math.pow(9.0/(16.0*np.pi) * E0/(n0*grb.mp*c5), 1.0/3.0)
+
 
 def t_coast(umax, umin, Er, k, Mej_solar, n0, p):
 
@@ -66,6 +72,7 @@ def t_coast(umax, umin, Er, k, Mej_solar, n0, p):
 
     return td_obs
 
+
 def t_end(umax, umin, Er, k, Mej_solar, n0, p):
 
     c5 = grb.c ** 5
@@ -75,6 +82,7 @@ def t_end(umax, umin, Er, k, Mej_solar, n0, p):
[…]

### 2018-12-11 code/structComp.py

@@ -352,8 +352,47 @@ if __name__ == "__main__":
     ax[1].set_yscale('log')
     fig.tight_layout()
 
-    print("Saving structComp.pdf")
-    fig.savefig("structComp.pdf")
+    print("Saving structCompE.pdf")
+    fig.savefig("structCompE.pdf")
+
+    print("Plotting")
+    figE, axE = plt.subplots(1,1, figsize=(12,9))
+
+    clr = ["k", "grey", "tab:blue", "tab:orange", "tab:green", "tab:red",
+                "tab:purple", "tab:brown", "tab:pink", "tab:olive", "tab:cyan"]
+    ls = ['-', '--', ':', '-.']
+
+    axE.plot(theta*deg, EG, label="Gaussian", lw=4.0,
+                                    color=clr[0], ls=ls[0])
+    axE.plot(theta*deg, EPL, label="Power law", lw=4.0,
+                                    color=clr[1], ls=ls[0])
+    axE.plot(theta*deg, EBF1003, label="Boosted Fireball $\gamma_B=10$ $\eta_0=3$", 
+                                    color=clr[2], ls=ls[0])
+    axE.plot(theta*deg, ED15o, label="Duffell 2015 Oblate",
+                                    color=clr[3], ls=ls[0])
+    axE.plot(theta*deg, EM07r5, label="Morsony 2007 realg5",
+                                    color=clr[4], ls=ls[0])
+    axE.plot(theta*deg, EM07p2, label="Morsony 2007 powg2",
+                                    color=clr[4], ls=ls[1])
+    axE.plot(theta*deg, EK17, label="Kathirgamaraju 2017",
+                                    color=clr[5], ls=ls[0])
+    axE.plot(theta*deg, EM18, label="Margutti 2018",
+                                    color=clr[6], ls=ls[0])
+    axE.plot(theta*deg, EM09, label="Mizuta 2009",
+                                    color=clr[7], ls=ls[0])
+    axE.plot(theta*deg, EL17, label="Lazzati 2017",
+                                    color=clr[8], ls=ls[0])
+
+    axE.legend(loc='upper right', fontsize=12)
+
+    axE.set_xlabel(r'$\theta$ $({}^\circ)$', fontsize=16)
+    axE.set_ylabel(r'$dE/d\Omega$ (erg/sr)', fontsize=16)
+    axE.set_yscale('log')
+    axE.set_ylim(3.0e48, 1.0e53)
[…]

### 2018-12-12 structuredJets.tex
Updates, figures, and code.

@@
 \newcommand{\tb}{\ensuremath{t_{\mathrm{b}}}}
+\newcommand{\tbm}{\ensuremath{t_{\mathrm{b-}}}}
+\newcommand{\tbp}{\ensuremath{t_{\mathrm{b+}}}}
 \newcommand{\tdec}{\ensuremath{t_{\mathrm{dec}}}}
@@
 \newcommand{\thobs}{\ensuremath{\theta_{\mathrm{obs}}}}
+\newcommand{\phobs}{\ensuremath{\phi_{\mathrm{obs}}}}
 \newcommand{\thW}{\ensuremath{\theta_{\mathrm{w}}}}
@@
 Figure \ref{fig:jetStruct} shows a collection of jet energy distributions from the literature (CITE curves in plots).
-Lacking a well-established physical model of the true $E(\theta)$, in particular its dependence on the parameters of the system, we consider two simple parameterized models: a Gaussian jet and a softened power-law.
+Lacking a well-established physical model of the true $E(\theta)$, in particular its dependence on the parameters of the system, we consider two simple parameterized models: a Gaussian jet and a power-law with a smooth core.
 
@@
 A generic energy profile $E(\theta)$ may have several more parameters, but one can still associate an on-axis energy $E_0 = E(0)$ and an effective core width $\thC \sim |E''(0)/E_0|^{-1/2}$ which should fully specify the leading order near on-axis behaviour.
+
 The afterglow light curve of a structured jet follows one of two qualitatively different regimes depending on the orientation of the viewer with respect to $\thC$.
 We refer to the regimes as ``on-axis'' when $\thobs < \thC$, and ``off-axis'' when $\thobs > \thC$.
+
+In the ensuing discussion we often refer to sections of the blast wave surface by their angular coordinates $(\theta, \phi)$.
+These are the standard angles associated with a spherical polar coordinate system whose $z$-axis is oriented along the jet axis.
+The observer is located in a direction $\hat{\bf n}$ which makes an angle $\thobs$ with the $z$-axis, $\hat{\bf n} \cdot \hat{\bf z} = \cos \thobs$, and is oriented along the $x$-axis, $\phobs = 0$.
+A particular point on the blast wave $\hat{\bf r} = (\theta, \phi)$ makes an angle $\psi$ with the viewer, $\cos \psi = \hat{\bf n} \cdot \hat{\bf r}$.
+We denote the cosine of this angle as $\mu$, $\cos \psi = \mu$.
 
@@
 The on-axis light curve of a structured jet is essentially identical to that of a standard top-hat viewed within the jet cone.
-The afterglow is comprised of four phases, \emph{pre-jet break}, \emph{transition}, \emph{post-jet break}, \emph{Newtonian}.
-These are well described in the literature and are only briefly reviewed here.
+The relativistic afterglow is comprised of three phases, \emph{pre-jet break}, \emph{transition}, and \emph{post-jet break}.
+These are well described in the literature and are briefly reviewed here.
 
-\emph{Pre-jet break} ---  At early times the flux is dominated by the small patch of material whose emission is beamed towards the observer: $\psi = |\theta-\thobs| \lesssim \gamma^{-1}$.
+\emph{Pre-jet break} ---  At early times the flux is dominated by the small patch of material whose emission is beamed towards the observer of angular width $\psi = |\theta-\thobs| \sim \gamma^{-1}$.
 This patch is within the $\theta < \thC$ region where $E(\theta) \approx E_0$ and the structure plays a sub-dominant role.
-The visible patch grows as $\gamma^{-2}$.
+The angular size of the visible patch grows as $\gamma^{-2}$.
 Closure relations and scalings of the standard on-axis top-hat apply.
-(CITE Sari, Piran Narayan)
+(CITE Granot and Sari)
 
@@
 
-\emph{Newtownian} ---  The decelerating blast wave becomes non-relativistic, spreads sonically, and approaches a Sedov-Taylor solution.
+The onset of the transition phase (ie. the start of the jet-break), occurs at $\tbm$ and completes at $\tbp$, given by:
+\begin{align}
+	\tbm &= \left(\frac{9}{16\pi} \frac{E_0}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thC-\thobs}{2}\right)\right)^{8/3} ,\label{eq:tbm} \\
+	\tbp &= \left(\frac{9}{16\pi} \frac{E_0}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thC+\thobs}{2}\right)\right)^{8/3} .\label{eq:tbp}
+\end{align}
+
+\begin{figure}
+	\plotone{figs/lc_on.pdf}
+	\caption{On-axis ($\thobs = \thC/2$) afterglow light curves for top-hat (blue), Gaussian (orange), and power-law (green) jets.
+When viewed on-axis, jets containing angular structure are very difficult to distinguish from top-hats.
+The transition phase marking the onset of the jet break begins at $\tbm\sim3$ days with a shallow break and ends sharply at $\tbp \sim 100$ days.
+These particular light curves use $\thC = 0.1$ rad, $\thW = 0.4$ rad, $E_0 = 10^{52}$erg, $n_0=10^{-2}$cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, $\epsB = 10^{-3}$, and $d_L=40$Mpc.
+\label{fig:onaxis}}
+\end{figure}
+
+Figure \ref{fig:onaxis} shows representative top-hat, Gaussian, and power-law jet light curves in the on-axis regime.
+The light curves nearly overlap, demonstrating the similar evolution of all structured jet afterglows when viewed on-axis.
+Although we expect all afterglow blast waves to contain angular structure, the simple top-hat jet model is sufficient for on-axis viewing.
+
+The relativistic stages of evolution are followed by a Newtonian phase when the decelerating blast wave becomes non-relativistic, spreads sonically, and approaches a Sedov-Taylor solution.
+We do not address the Newtonian phase of evolution in this work.
 
@@
 To observers this energy gradient presents itself as a slowly rising or decaying afterglow light curve.
-The afterglow is comprised of three or four phases depending on whether the observer lies within the truncation angle, \emph{off-axis}, \emph{structured}, \emph{post-jet break}, and \emph{Newtonian}.
+The relativistic afterglow is comprised of two or three phases depending on whether the observer lies within the truncation angle, \emph{off-axis}, \emph{structured},  and \emph{post-jet break}.
 
@@
 If $\thobs < \thW$ this phase is entirely absent.
+Table \ref{tab:slopes} gives the temporal power-law slope of the light curve in this phase.
+These slopes are derived in Appendix \ref{sec:derive1}.
 
@@
 
- It begins at observer time $\tW$, once the blast wave is decelerating and the observer is within the beaming cone of any part of the emitting surface.
+ This phase begins at observer time $\tW$, once the blast wave is decelerating and the observer is within the beaming cone of any part of the emitting surface.
 It ends at observer time $\tb$, when the jet core has become fully visible.
@@
 	\plotone{figs/jetDecomp.pdf}
-	\caption{A structured jet, decomposed into emission from different latitudes $\theta$.
-The structured phase is the result of the brightest point of the blast-wave tracking from the wings to the jet core.
+	\caption{A Gaussian structured jet, decomposed into emission from different latitudes $\theta$.
+The off-axis, structured, and post-jet break phases are all clearly visible.
+The structured phase is the result of the brightest point of the blast-wave tracking from the wings $(\theta =\thW$) to the jet core ($\theta=\thC$).
 \label{fig:decomp}}
 \end{figure}
-Figure \ref{fig:decomp} shows the light curve of a structured jet along with the emissions from different latitudes.
-The part of the blast wave dominating the emission tracks from the high latitude wings $\theta \approx \thW$ to the core $\theta \approx 0$ and the angular size of the visible patch grows approximately as $\gamma^{-1.5}$.
+Figure \ref{fig:decomp} shows the light curve of a Gaussian structured jet along with the emissions from different latitudes.
+The part of the blast wave dominating the emission tracks from the high latitude wings $\theta \approx \thW$ to the core $\theta \approx 0$.
+The angular size of the visible patch grows approximately as $\gamma^{-1.5}$.
+(NEED PLOT?)
 
-During the structured phase, the afterglow has a temporal spectral slope which depends on the parameter $g(\theta)$:
+During the structured phase, the afterglow has a temporal spectral slope which depends on the parameter $g(\theta^*)$, where $\theta^*$ is the latitude of material dominating the emission:
 \begin{equation}
-	g(\theta) \equiv -2 \tan\left(\frac{\thobs - \theta}{2}\right)\frac{d \log E}{d \theta}\ . \label{eq:gdef}
+	g(\theta^*) \equiv -2 \tan\left(\frac{\thobs - \theta^*}{2}\right)\frac{d \log E}{d \theta}\ . \label{eq:gdef}
 \end{equation}
@@
 
-The $g$ parameter evolves with time as the brightest sector of the jet sweeps from the edge to the core.
+The $g$ parameter evolves with time as $\theta^*$ sweeps from the jet edge to the core.
 This produces deviations in the light curve from a pure power-law.
@@
 In the structured phase, the temporal slope depends directly on the ratio $\thobs/\thC$.
-Therefore any measurement of the effective power law slope of an afterglow light curve can be used to measure this parameter.
+Therefore any measurement of the effective power law slope of an afterglow light curve in the structured phase can be used to measure this parameter.
 
@@
 
-\emph{Newtonian} --- The approach to a Newtonian Sedov solution proceeds in a similar manner to the on-axis case.
-Relativistic beaming ceases to be an important effect and the afterglow light curve looks similar at all viewing angles.
+\begin{figure}
+	\plotone{figs/lc_off1.pdf}
+	\caption{As Figure \ref{fig:onaxis} but $\thobs = 2\thC$.
+The top-hat jet (with opening angle $\thC$) begins in the off-axis phase.
+The Gaussian and power-law jets begin in the structured phase as $\thobs < \thW$.
+All three models enter similar post-jet break phases.
+\label{fig:offaxis1}}
+\end{figure}
+\begin{figure}
+	\plotone{figs/lc_off2.pdf}
+	\caption{As Figure \ref{fig:onaxis} but $\thobs = 6\thC$.
+All three models exhibit off-axis, structured, and post-jet break phases of evolution.
+At larger opening angles the difference between structured models is more evident.
+\label{fig:offaxis2}}
+\end{figure}
+
+Figures \ref{fig:offaxis1} and \ref{fig:offaxis2} display afterglows from the fiducial models in the off-axis regime at $\thobs = 2\thC$ and $\thobs=6\thC$ respectively.
+At the moderate $2\thC$ viewing angle both structured models exhibit similar decaying light curves with slopes somewhat shallower than the on-axis case.
+In this case $\thobs < \thW$ so neither model exhibits an off-axis phase.
+The similar temporal evolution is easy to understand as at this angle both models have $\geff = 1$ and hence approximately equal power-law slopes in the structured phase.
+At late times as more of the jet comes in to view the difference between all three models becomes negligible.
+
+At the larger $6\thC$ viewing angle all three models exhibit off-axis, structured, and post-jet break phases of the afterglow.
+The different $\tW$ between the Gaussian and power-law models is due to the different $E(\thW)$ of the two models.
+In the structured phase the Gaussian shows a rising light curve with slope $~1$ due to the large $\geff = 9$.
+The power-law meanwhile has a smaller $\geff$ of $9/5$, giving rise to a very shallow decay.
+As at the other viewing angles, once the entire jet is visible at $\tb$ all models follow similar post-jet break evolutions.
+
+\begin{figure}
+	\plotone{figs/slopesJet.png}
+	\caption{Temporal slopes for the off-axis structured jet as a function of the structure parameter $g$ for the synchrotron spectral regimes D (blue, narrow), E (orange, narrow),  F (green, narrow), G (red, wide), and H (purple, wide).
+The width of the G and H bands shows the dependency on $p$, the upper curves for $p=2$ and the lower for $p=3$.
+The temporal power-law slope of a structured jet afterglow increases with $g$ in all spectral regimes.
+\label{fig:slopesG}}
+\end{figure}
+
+Figure \ref{fig:slopesG} shows the structured phase power-law temporal slope as a function of $g$ for spectral regimes $D$--$H$.
+In the $G$ and $H$ regimes the spectral slope is a function of $p$, this dependence carries over into the temporal slope as well.
+The temporal slope is an increasing function of $g$ in all regimes.
+At sufficiently large $g$ all regimes exhibit rising light curves, the specific $g$ at which the light curve begins to rise is regime dependent.
 
@@
 
+\begin{figure}
+	\plotone{figs/slopesCocoon.png}
+	\caption{Temporal slopes for the cocoon.}
+\end{figure}
+
 \subsection{Relation to Energy Injection Models}
@@
 We utilize the single-shell approximation, treating the ejecta mass, contact discontinuity, and forward shock as a single unit propagating through a cold ambient medium with constant rest-mass density $\rho_0 = \Mp n_0$.
-For a detailed derivation see Appendix \ref{sec:deriveNum} and (CITE Hendrik 2010 + Hendrik Review).
+For a detailed derivation (CITE Hendrik 2010 + Hendrik Review).
 The forward shock is a radius $R$ from the explosion and moves at a velocity $\beta_s$.
@@
 Fluid quantities are then calculated using the shock-jump conditions and the synchrotron emissivity is evaluated using the standard external shock formulae (CITE Hendrik, Granot+Sari).
-
-The numerical accuracy of a top-hat light curve is typically better than $10^{-4}$.
+The numerical accuracy of a top-hat light curve with this scheme is typically better than $10^{-4}$.
 The structured jet calculation splits the integration domain into $N_\theta$ disjoint annuli, each evaluated as an independent top-hat and summed.
@@
 The integration routine itself is written in C, wrapped as an extension for Python, and has been optimized to be used in intensive data analysis routines such as Markov Chain Monte-carlo which can require many thousands of evaluations.
+
+\afterglowpy{} uses a standard RK4 algorithm to evolve the $(R(t), u(t), \theta_0(t))$ system of equations on a fixed logarithmically spaced grid of $t$.
+The endpoints of the $t$-grid are chosen to bracket the burster frame times required to calculate the requested $\tobs$ with at least a decade of tolerance.
+Initial conditions for $R$, $u$, and $\theta_0$ are those of a decelerating ultra-relativistic blast wave.
+The user can set the density of the $t$-grid with the $n_t$ parameter: the number of grid points per decade of $t$.
+The default value for $n_t$ is 1000, which is sufficiently dense that the shock ODE evolution is not the dominant error source but not so dense as to adversely impact performance.
+
+Each top-hat jet component is integrated in $\theta$ and $\phi$ using an adaptive Romberg scheme with a fixed relative tolerance and an adaptive absolute tolerance.
+When summing over top-hat components of a structured jet, the innermost (core) component is calculated first.
+As the calculation proceeds, the current running sum of the flux is used to set absolute tolerance in the Romberg integrator for each component.
+This minimizes the computations performed on dim, off-axis sectors of the jet.
+
+The structured jet is split into concentric top-hat components with a density $n_\theta$ per $\thC$-sized interval.
+The choice of $n_\theta$ has the largest impact on the code performance and accuracy.
+We find the choice $n_\theta = 5$ gives sufficiently quick performance at acceptable errors, typically on the order of $10^{-2}$.
+TODO SHOW CONVERGENCE PLOT
+
+It should be noted all errors quoted here are numerical errors associated with the schemes used to solve Equations \ref{eq:Rdot}, \ref{eq:E}, and \ref{eq:thetadot} and perform the integral in Equation \ref{eq:flux}.
+That is, they are the errors relative to solving these equations perfectly.
+The equations themselves are, however, an approximation themselves to the full physics of an afterglow light curve.
+Comparison and calibration against analytic calculations and hydrodynamic simulations is necessary to ensure physically realistic results.
 
@@
 \section{Structured Phase}
-
-\begin{figure}
-	\plottwo{figs/slopesJet.png}{figs/slopesCocoon.png}
-	\caption{Temporal slopes for the jet (left) and cocoon (right).}
-\end{figure}
 

### 2018-12-12 code/paperPlots.py

@@ -1,0 +1,330 @@
+import numpy as np
+import matplotlib as mpl
+import matplotlib.cm as cm
+import matplotlib.pyplot as plt
+import matplotlib.patches as patches
+import matplotlib.collections as collections
+import grbpy as grb
+
+sec2year = grb.sec2day / 365.25
+year2sec = grb.day2sec * 365.25
+
+labelsize = 12
+ticksize = 8
+legendsize = 12
+
+
+def makeThVPlots():
+
+    E0 = 1.0e52
+    thC = 0.05
+    thV = 0.6
+    thW = 0.5*np.pi
+    n0 = 1.0e-3
+    p = 2.2
+    epse = 0.1
+    epsB = 0.01
+    xiN = 1.0
+    dL = 1.23e26
+
+    Y = np.array([thV, E0, thC, thW, 0.0, 0.0, 0.0, n0, p, epse, epsB, xiN,
+                  dL])
+
+    parstr = r"$n_0$={0:.01f}x$10^{{-3}}cm^{{-3}}$".format(n0/1.0e-3)
+    parstr += r"  $p$={0:.01f}".format(p)
+    parstr += r"  $\epsilon_e$={0:g}".format(epse)
+    parstr += r"  $\epsilon_B$={0:g}".format(epsB)
+    parstr += r"  $d_L$={0:.02f}x$10^{{26}}$cm".format(dL/1.0e26)
+
+    N = 300
+    nuO = (grb.c / 6.0e-5) * np.ones(N)
+
+    t = grb.day2sec * np.geomspace(0.1, 300, N)
+
+    thV = 0.0
+    Y[0] = thV
+    FnuA = grb.fluxDensity(t, nuO, 0, 0, *Y)
+    thV = 2*thC
+    Y[0] = thV
+    FnuB = grb.fluxDensity(t, nuO, 0, 0, *Y)
+    thV = 4*thC
+    Y[0] = thV
+    FnuC = grb.fluxDensity(t, nuO, 0, 0, *Y)
+    thV = 6*thC
+    Y[0] = thV
+    FnuD = grb.fluxDensity(t, nuO, 0, 0, *Y)
+
+    fig, ax = plt.subplots(1, 1, figsize=(4, 3))
+
+    ax.plot(t * grb.sec2day, FnuA, label=r'$\theta_V = 0$', color='k')
+    ax.plot(t * grb.sec2day, FnuB, label=r'$\theta_V = 2\theta_C$',
[…]

### 2019-01-16 structuredJets.tex
updates.

@@
 \newcommand{\tbp}{\ensuremath{t_{\mathrm{b+}}}}
+\newcommand{\tbpm}{\ensuremath{t_{\mathrm{b\pm}}}}
 \newcommand{\tdec}{\ensuremath{t_{\mathrm{dec}}}}
@@
 \newcommand{\umax}{\ensuremath{u_{\mathrm{max}}}}
+\newcommand{\gmin}{\ensuremath{\gamma_{\mathrm{min}}}}
+\newcommand{\gmax}{\ensuremath{\gamma_{\mathrm{max}}}}
+\newcommand{\bmin}{\ensuremath{\beta_{\mathrm{min}}}}
+\newcommand{\bmax}{\ensuremath{\beta_{\mathrm{max}}}}
 
@@
 The afterglow light curve of a structured jet follows one of two qualitatively different regimes depending on the orientation of the viewer with respect to $\thC$.
-We refer to the regimes as ``on-axis'' when $\thobs < \thC$, and ``off-axis'' when $\thobs > \thC$.
+We refer to the regimes as ``aligned'' when $\thobs < \thC$, and ``misaligned'' when $\thobs > \thC$.
 
@@
 
-\subsection{On-Axis Evolution: $\thobs \lesssim \thC$}
+\subsection{Aligned Evolution: $\thobs \lesssim \thC$}
 
-The on-axis light curve of a structured jet is essentially identical to that of a standard top-hat viewed within the jet cone.
+The aligned light curve of a structured jet is essentially identical to that of a standard top-hat viewed within the jet cone.
 The relativistic afterglow is comprised of three phases, \emph{pre-jet break}, \emph{transition}, and \emph{post-jet break}.
@@
 \begin{align}
-	\tbm &= \left(\frac{9}{16\pi} \frac{E_0}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thC-\thobs}{2}\right)\right)^{8/3} ,\label{eq:tbm} \\
-	\tbp &= \left(\frac{9}{16\pi} \frac{E_0}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thC+\thobs}{2}\right)\right)^{8/3} .\label{eq:tbp}
+	\tbpm &= \left(\frac{9}{16\pi} \frac{E_0}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thC\pm\thobs}{2}\right)\right)^{8/3} ,\label{eq:tbpm}
 \end{align}
@@
 	\plotone{figs/lc_on.pdf}
-	\caption{On-axis ($\thobs = \thC/2$) afterglow light curves for top-hat (blue), Gaussian (orange), and power-law (green) jets.
+	\caption{Aligned ($\thobs = \thC/2$) afterglow light curves for top-hat (blue), Gaussian (orange), and power-law (green) jets.
 When viewed on-axis, jets containing angular structure are very difficult to distinguish from top-hats.
@@
 
-Figure \ref{fig:onaxis} shows representative top-hat, Gaussian, and power-law jet light curves in the on-axis regime.
-The light curves nearly overlap, demonstrating the similar evolution of all structured jet afterglows when viewed on-axis.
-Although we expect all afterglow blast waves to contain angular structure, the simple top-hat jet model is sufficient for on-axis viewing.
+Figure \ref{fig:onaxis} shows representative top-hat, Gaussian, and power-law jet light curves in the aligned regime.
+The light curves nearly overlap, demonstrating the similar evolution of all structured jet afterglows when viewed within the jet core.
+Although we expect all afterglow blast waves to contain angular structure, the simple top-hat jet model is sufficient for aligned viewing.
 
@@
 
-\subsection{Off-Axis Evolution: $\thobs \gtrsim \thC$}
+\subsection{Misaligned Evolution: $\thobs \gtrsim \thC$}
 
@@
 
-\begin{deluxetable*}{CCCCCC}
-	\tablecaption{Structured jet temporal and spectral slopes: $F_\nu \propto \tobs^\alpha \nu^\beta$.
+\begin{deluxetable*}{CCCCCCC}
+	\tablecaption{Structured jet temporal and spectral slopes: $F_\nu \propto \tobs^{-\alpha} \nu^{-\beta}$.
+See Equations \eqref{eq:gdef} and \eqref{eq:geff} for the definition and effective values of $g$.
+\label{tab:slopes}}
+	\tablehead{\colhead{Regime}& \colhead{Label} & \colhead{$\alpha_{\mathrm{off-axis}}$}& \colhead{$\alpha_{\mathrm{struct}}$}& \colhead{$\alpha_{\mathrm{struct,max}}$}& \colhead{$\alpha_{\mathrm{post, analytic}}$} & \colhead{$\beta$}}
+	\startdata
+	\nu<\nu_m<\nu_c     & D & -7 			& -\frac{5/2 + 3g}{8+g} 		& -3		& 1/4			& -1/3 \\
+	\nu_m<\nu<\nu_c     & G & -15/2 + 3p/2 	& \frac{-9/2 + 6p - 3g}{8+g} 	& -3		& 3p/4		& (p-1)/2 \\
+	\nu < \nu_c < \nu_m & E & -17/3 		& \frac{1/6 - 11g/3}{8+g} 		& -11/3	& 7/12		& -1/3 \\
+	\nu_c < \nu < \nu_m & F & -13/2 		& \frac{7/2 - 2g}{8+g} 		& -2		& 1			& 1/2 \\
+	\nu_c < \nu_m < \nu & H & -8 + 3p/2 		& \frac{-5/2 +6p  -2g}{8+g} 	& -2		& (3p+1)/4	& p/2 \\ 
+	\enddata
+\end{deluxetable*}
+
+%\begin{deluxetable*}{CCCCCC}
+%	\tablecaption{Structured jet temporal and spectral slopes: $F_\nu \propto \tobs^{-\alpha} \nu^{-\beta}$.
 See Equations \eqref{eq:gdef} and \eqref{eq:geff} for the definition and effective values of $g$.
 For a refreshed-shock model replace $g$ with $k$, defined in Equation \eqref{eq:Eu}.
-\label{tab:slopes}}
-	\tablehead{\colhead{Regime}& \colhead{Label} & \colhead{$\alpha_{\mathrm{off-axis}}$}& \colhead{$\alpha_{\mathrm{struct}}$}& \colhead{$\alpha_{\mathrm{struct,max}}$} & \colhead{$\beta$}}
-	\startdata
-	\nu<\nu_m<\nu_c     & D & 7 			& \frac{-2+3s_3 + 3g}{8+g} 		& 3		& 1/3 \\
-	\nu_m<\nu<\nu_c     & G & 15/2 - 3p/2 	& \frac{- 6p + 3s_3 + 3g}{8+g} 		& 3		& (1-p)/2 \\
-	\nu < \nu_c < \nu_m & E & 17/3 		& \frac{-14/3 + 3s_3 + 11g/3}{8+g} 	& 11/3	& 1/3 \\
-	\nu_c < \nu < \nu_m & F & 13/2 		& \frac{-8+3s_3 + 2g}{8+g} 		& 2		& -1/2 \\
-	\nu_c < \nu_m < \nu & H & 8 - 3p/2 		& \frac{-6p - 2 + 3s_3 + 2g}{8+g} 	& 2		& -p/2 \\ 
-	\enddata
-\end{deluxetable*}
+\label{tab:generalSlopes}}
+%	\tablehead{\colhead{Regime}& \colhead{Label} & \colhead{$\alpha_{\mathrm{off-axis}}$}& \colhead{$\alpha_{\mathrm{struct}}$}& \colhead{$\alpha_{\mathrm{struct,max}}$} & \colhead{$\beta$}}
+%	\startdata
+%	\nu<\nu_m<\nu_c     & D & -7 			& -\frac{-2+3s_3 + 3g}{8+g} 		& -3		& -1/3 \\
+%	\nu_m<\nu<\nu_c     & G & -15/2 + 3p/2 	& -\frac{- 6p + 3s_3 + 3g}{8+g} 		& -3		& (p-1)/2 \\
+%	\nu < \nu_c < \nu_m & E & -17/3 		& -\frac{-14/3 + 3s_3 + 11g/3}{8+g} 	& -11/3	& -1/3 \\
+%	\nu_c < \nu < \nu_m & F & -13/2 		& -\frac{-8+3s_3 + 2g}{8+g} 		& -2		& 1/2 \\
+%	\nu_c < \nu_m < \nu & H & -8 + 3p/2 		& -\frac{-6p - 2 + 3s_3 + 2g}{8+g} 	& -2		& p/2 \\ 
+%	\enddata
+%\end{deluxetable*}
 
@@
 the observer is within the beaming cone of the entire jet) the visible patch no longer grows and emission is dominated by the decelerating core.
-This phase follows exactly the post-jet break scalings of the on-axis case, except with a much delayed break time $\tb$.
+This phase follows exactly the post-jet break scalings of the aligned case, except with a much delayed break time $\tb$.
 
@@
 
-Figures \ref{fig:offaxis1} and \ref{fig:offaxis2} display afterglows from the fiducial models in the off-axis regime at $\thobs = 2\thC$ and $\thobs=6\thC$ respectively.
-At the moderate $2\thC$ viewing angle both structured models exhibit similar decaying light curves with slopes somewhat shallower than the on-axis case.
+Figures \ref{fig:offaxis1} and \ref{fig:offaxis2} display afterglows from the fiducial models in the misaligned regime at $\thobs = 2\thC$ and $\thobs=6\thC$ respectively.
+At the moderate $2\thC$ viewing angle both structured models exhibit similar decaying light curves with slopes somewhat shallower than the aligned case.
 In this case $\thobs < \thW$ so neither model exhibits an off-axis phase.
@@
 
-\section{Refreshed Shocks}\label{sec:refreshedShocks}
+\section{Refreshed Shocks --- Fast Tails and Spherical Cocoons}\label{sec:refreshedShocks}
 
-An alternative mechanism to produce slow decays or rises in afterglow light curves is the \emph{refreshed shock}, where velocity stratification of the ejecta causes a prolonged period of energy injection.
-Slow material initially coasting behind the shock is gradually incorporated into the blast wave as it decelerates, ``refreshing'' the shock.
-This mechanism was first proposed as an energy injection scenario (CITE), and recently has been proposed as the mechanism behind GW170817 in the choked-jet scenario.
+An alternative mechanism to produce slow decays or rises in afterglow light curves is the \emph{refreshed shock}, where velocity stratification of the ejecta causes a prolonged period of energy injection in the afterglow.
+This material may be a tail of fast outflowing ejecta or ejecta material accelerated through interaction with a possibly choked jet (e.g.
+a cocoon).
+(CITE Mooley, Hotokezaka, Nakar\&Piran, etc).
+In either case, slow material initially coasting behind the shock is gradually incorporated into the blast wave as it decelerates, ``refreshing'' the shock.
+This mechanism was first proposed as an energy injection scenario (CITE), and was proposed as the mechanism behind the GW170817 afterglow in the choked-jet scenario.
 (CITE Mooley, Hotokezaka, etc).
@@
 \end{equation}
-where $u \in (\umin, \umax)$ is the dimensionless four-velocity, $k>0$ is the power law index, and $E_r$ is a normalization factor.
+where $u \in (\umin, \umax)$ is the dimensionless four-velocity, $k>0$ is the power law index, and $E_r$ is a normalization factor.  The mass ejected with velocity $\umax$ is $\Mej$.
 
@@
 The shock refreshment ends when the blast wave decelerates past $\umin$.
-These times are given by:
+In the single shell model with trans-relativistic equation of state used here, these times are:
 \begin{align}
-	\tdec &= ... \ ,\label{eq:tdec} \\
+	\tdec &= \left(\frac{9}{4\pi} \frac{\Mej}{n_0 \Mp c^3} \frac{\gmax^2}{\bmax^3(\gmax+1)(4\umax^2+3)} \right)^{1/3}  \ ,\label{eq:tdec} \\
 	\tumin &= \left(\frac{9}{16\pi} \frac{E_r}{n_0 \Mp c^5}\right)^{1/3} \umin^{-8/3} \ .\label{eq:tumin}
 \end{align}
-The temporal and spectral slopes in this mechanism are identical to the structured jet, but with the replacement $k \leftrightarrow g$.  For a derivation see Appendix \ref{sec:derive3}.
+Equation \eqref{eq:tumin} assumes $E_r \gg \Mej c^2$.
+The temporal and spectral slopes in this mechanism depend on the energy distribution index $k$ and are given in Table \ref{tab:refreshSlopes}.
+Figure \ref{fig:slopesK} shows the temporal slopes in each spectral regime as a function of $k$.
+As in Figure \ref{fig:slopesG} the width of the $G$ and $H$ regimes reflects varying the value of $p$ between two and three.
+For a derivation see Appendix \ref{sec:derive3}.
 
@@
 	\plotone{figs/slopesCocoon.png}
-	\caption{Temporal slopes for the cocoon.}
+	\caption{The temporal power-law slope of the spherical refreshed-shock afterglow light curve as a function of $k$.
+Otherwise as Figure \ref{fig:slopesG}.
+The temporal power-law slope of a structured jet afterglow increases with $k$ in all spectral regimes.
+\label{fig:slopesK}}
 \end{figure}
 
-\subsection{Relation to Energy Injection Models}
+\begin{deluxetable*}{CCCCCCC}
+	\tablecaption{Refreshed shock temporal and spectral slopes: $F_\nu \propto \tobs^{-\alpha} \nu^{-\beta}$. See Equation \eqref{eq:Eu} for the definition of $k$.  \label{tab:refreshSlopes}}
+	\tablehead{\colhead{Regime}& \colhead{Label} & \colhead{$\alpha_{\mathrm{coast}}$}& \colhead{$\alpha_{\mathrm{refresh}}$}& \colhead{$\alpha_{\mathrm{refresh,max}}$}& \colhead{$\alpha_{\mathrm{post}}$}  & \colhead{$\beta$}}
+	\startdata
+	\nu<\nu_m<\nu_c     & D & 3 	& -\frac{4 + 3k}{8+k} 		& -3		& -1/2	& -1/3 \\
+	\nu_m<\nu<\nu_c     & G & 3 	& \frac{-6 + 6p - 3k}{8+k} 	& -3		& 3(p-1)/4	& (p-1)/2 \\
+	\nu < \nu_c < \nu_m & E & 3 	& -\frac{4/3 + 11k/3}{8+k} 	& -11/3	& -1/6	& -1/3 \\
+	\nu_c < \nu < \nu_m & F & 3 	& \frac{2 - 2k}{8+k} 		& -2		& 1/4		& 1/2 \\
+	\nu_c < \nu_m < \nu & H & 3 	& \frac{- 4 +6p - 2k}{8+k}	& -2		& (3p-2)/4	& p/2 \\ 
+	\enddata
+\end{deluxetable*}
 
-The refreshed shock model as constructed here is equivalent to the similar energy injection models in (CITE Zhang09).
+\section{Relation to Energy Injection Models}
+
+The light curves of both the angularly structured jet and refreshed shock models can be understood in terms of general energy injection mechanisms, which are typically parameterized as an additional power $L$ delivered to the blast wave.
+This power is typically taken to decay in time as a power law, $L \propto t^{-q}$, with $q \in [0,1]$.
+
+The mapping between energy injection and refreshed shocks was done in (CITE Zhang06).
 That work specifies the index $s$ of the mass distribution $M_{>u} \propto u^{-s}$, which is related simply to the index $k$ by $k = s-1$.
-Under this mapping the closure relations in Table \ref{tab:slopes} are equivalent to those in (CITE Zhang 09).
+Under this mapping the closure relations in Table \ref{tab:slopes} are equivalent to those in (CITE Zhang06) and the model can be seen as equivalent to an energy injection model with $q = (8-2k) / (8+k)$.
+
+The mapping between structured jet and refreshed shock (and hence energy injection) models is a two step process.
+Firstly, a visual comparison between $\alpha_{\text{struct}}$ in Table \ref{tab:slopes} and $\alpha_{\text{refresh}}$ in Table \ref{tab:refreshSlopes} indicate the identical roles played by $g$ and $k$.
+Indeed, a stru
+
   The numerical model described in Section \ref{sec:numerical} improves on these analytic approximations by ...
+
+\begin{deluxetable*}{CCCCCC}
+	\tablecaption{Generic structured phase temporal and spectral slopes: $F_\nu \propto \tobs^{-\alpha} \nu^{-\beta}$.
+The visible patch of the jet has a solid angle which scales as $\gamma^{-s_3}$.
+See Equations \eqref{eq:gdef} and \eqref{eq:geff} for the definition and effective values of $g$.
+A uniform relativistic blast wave pre-jet break has $s_3=2$, a relativistic blast wave with angular structure pre-jet break has $s_3 \approx 1.5$, and a relativistic blast wave post jet-break has $s_3 = 0$.
+For a refreshed-shock model replace $g$ with $k$, defined in Equation \eqref{eq:Eu}.
+\label{tab:generalSlopes}}
+	\tablehead{\colhead{Regime}& \colhead{Label} & \colhead{$\alpha_{\mathrm{struct}}$} & \colhead{$\beta$}}
+	\startdata
+	\nu<\nu_m<\nu_c     & D & \frac{2-3s_3 - 3g}{8+g} 		& -1/3 \\
+	\nu_m<\nu<\nu_c     & G & \frac{6p - 3s_3 - 3g}{8+g} 	& (p-1)/2 \\
+	\nu < \nu_c < \nu_m & E & \frac{14/3 - 3s_3 -11g/3}{8+g} 	& -1/3 \\
+	\nu_c < \nu < \nu_m & F & \frac{8-3s_3 -2g}{8+g} 		& 1/2 \\
+	\nu_c < \nu_m < \nu & H & \frac{6p - 2 - 3s_3 - 2g}{8+g} 	& p/2 \\ 
+	\enddata
+\end{deluxetable*}
 

### 2019-01-16 code/paperPlots.py

@@ -324,7 +324,106 @@ def makeCentralPlots(modelPlots=True):
     plt.close(fig)
 
 
+def makeConvergencePlots():
+
+    lrs = [1, 3, 5, 10, 20, 40]
+    trs = [250, 500, 1000, 2000, 4000, 8000]
+    lrRef = 80
+    trRef = 16000
+
+    # lss = ['-', '--', '-.', ':', '-']
+    # cols = ['tab:blue', 'tab:orange', 'tab:green', 'tab:red', 'tab:purple']
+
+    E0 = 1.0e52
+    thC = 0.05
+    thV = 0.3
+    thW = 0.5
+    n0 = 1.0
+    p = 2.2
+    epse = 0.1
+    epsB = 0.01
+    xiN = 1.0
+    dL = 1.23e26
+
+    Y = np.array([thV, E0, thC, thW, 0.0, 0.0, 0.0, n0, p, epse, epsB, xiN,
+                  dL])
+    jetType = 0
+
+    t = np.geomspace(1.0e3, 1.0e8, 100)
+    nu = np.empty(t.shape)
+    nu[:] = 1.0e18
+
+    FnuRef = grb.fluxDensity(t, nu, jetType, 0, *Y, latRes=lrRef, tRes=trRef)
+    fig, ax = plt.subplots(1, 1, figsize=(4, 3))
+    ax.plot(t, FnuRef)
+
+    ax.set_xlabel(r'$t$ (s)')
+    ax.set_ylabel('')
+    ax.set_xscale('log')
+    ax.set_yscale('log')
+    fig.tight_layout()
+    print("Saving conv_ref.pdf")
+    fig.savefig("conv_ref.pdf")
+    plt.close(fig)
+
+    fig, ax = plt.subplots(1, 1, figsize=(4, 3))
+    fig2, ax2 = plt.subplots(1, 1, figsize=(4, 3))
+
+    for i, lr in enumerate(lrs):
+        Fnu = grb.fluxDensity(t, nu, jetType, 0, *Y, latRes=lr, tRes=trRef)
+        err = np.fabs(Fnu-FnuRef)/FnuRef
+        ax.plot(t, err)
+        ax2.plot(t, Fnu)
+    ax2.plot(t, FnuRef, lw=0.5, color='k')
+
+    ax.set_xlabel(r'$t$ (s)')
+    ax.set_ylabel('Error')
+    ax.set_xscale('log')
+    ax.set_yscale('log')
+    fig.tight_layout()
[…]

### 2019-01-23 structuredJets.tex
sketched section 6

@@
 \end{align}
+
+%
+% Update jet Structure models paper.
+%
 
@@
 
+%
+% Comment: Add dashed line at 0 to slopes plot.
+%
+
 \begin{figure}
@@
 
+%
+% Comment: define tdec, tmin IN THE TEXT.   Add (brief) discussion of light curve phases.
+%
+
 A blast wave will have an initial coasting period before sweeping up enough mass in the ambient medium to begin deceleration and be subject to refreshed shocks.
@@
 For a derivation see Appendix \ref{sec:derive3}.
+
+%
+% Comment: Add dashed line at 0 to slopes plot.
+%
 
@@
 
-The mapping between structured jet and refreshed shock (and hence energy injection) models is a two step process.
-Firstly, a visual comparison between $\alpha_{\text{struct}}$ in Table \ref{tab:slopes} and $\alpha_{\text{refresh}}$ in Table \ref{tab:refreshSlopes} indicate the identical roles played by $g$ and $k$.
-Indeed, a stru
+There is no single mapping between the structured jet and energy injection or refreshed shock models.
+However, a visual comparison between $\alpha_{\text{struct}}$ in Table \ref{tab:slopes} and $\alpha_{\text{refresh}}$ in Table \ref{tab:refreshSlopes} indicate the identical roles played by $g$ and $k$.
+Indeed, a simple swap $g \leftrightarrow k$ produces almost identical closure relations.
+However, as seen in Tables \ref{tab:slopes} and \ref{tab:refreshSlopes} or
+
+The mapping between structured jet and refreshed shock (and hence energy injection) models is a two step process.   Indeed, a stru
+
+%
+% Comment: replace s_3 with s_Omega, s_{1,2} with s_gamma, s_t.
+%
+% "It is insightful..."
+%
 
 The numerical model described in Section \ref{sec:numerical} improves on these analytic approximations by ...
+
+%
+% Comment: Emphasize this is in "misaligned" case for structured case, but also applies to refreshed shock.  Just use "alpha".
+%
+
+%
+% Comment: THE JET BREAK *IS* WHEN THE VISIBLE PATCH STOPS GROWING
+%
 
@@
 
+We use the electromagnetic afterglow of GW170817A (GRB170817A?) as an example application of both the analytic and numerical structured jet afterglow models.
+
+Figure \ref{fig:170817Alc} shows the observations in radio, optical, and x-ray bands of the GW170817A afterglow.
+No afterglow emission was detected until an x-ray detection by the Chandra observatory nine days after the GW trigger (CITE TrojaNature).
+Further radio, optical, and x-ray observations showed a steady rising light curve with constant power-law slope until a peak near day 160.
+At this point the light curve turned over and began a steep decay that continues to the present (CITE YearInTheLife).
+
+Interpreting the afterglow as arising from a structured jet allows one to quickly draw the following conclusions:
+\begin{enumerate}
+	\item The spectral slope $\beta = 0.585$ (CITE, +uncertainties) throughout the entire evolution, identifying the relevant spectral regime as G: $\nu_m < \nuobs < \nu_c$, and $p = 2.17$.
+	\item The initial rising ($\alpha < 0$) light curve with declining spectrum ($\beta > 0$) identify this as a \emph{misaligned} evolution ($\thobs > \thC$).
+Aligned jets may only have a rising light curve when viewed at frequencies below the peak frequency, that is when $\beta < 0$.
+	\item The rising light curve maintains $\alpha  = 0.90 \pm 0.06$ (CITE YITL).
+Using the closure relations from Table \ref{tab:slopes} we can identify this as the \emph{structured} phase and determine $\geff = 7.5 \pm 0.4$.
+If the light curve underwent an \emph{off-axis} phase, it concluded before the afterglow was detected: $\tW < 9$d.
+The peak can be identified as the jet-break: $\tb = 164 \pm 12$ d.
+	\item In the context of a Gaussian jet, the measurement of $\geff$ leads immediately to $\thobs / \thC = 5.5 \pm 0.2$.
+	\item Using the Fong 2015 (CITE Fong 2015) fiducial values of $E_0 \sim 2\times 10^{51}$erg and $n_0 \sim 10^{-2}$cm$^{-3}$ we can use the jet break $\tb$ measurement to determine $\thobs \approx 0.5 \pm 0.2$ rad ($29^\circ \pm 12^\circ$), assuming 1 dex uncertainties on $E_0$ and $n_0$.
+This is in agreement with the LIGO measurement $\thobs \approx 28^\circ \pm 15^\circ$ (assuming the SHoES $H_0$).
+	\item The combined measurements of $\thobs$ and $\thobs/\thC$ then imply $\thC \approx 0.09 \pm 0.04$ rad ($5^\circ  \pm 2^\circ$).
+
+\end{enumerate}
+
 \section{Discussion}
@@
 \section{Structured Phase}
+
+(-9/2+6p-3g) / (8+g) = a
+-9/2+6p-3g = a(8+g)
+-9/2+6p-8a = ag + 3g
+-9/2+6p-8a = (a + 3)g
+g = (-9/2+6p-8a) / (a+3)
 

### 2019-01-23 code/paperPlots.py

@@ -1,3 +1,4 @@
+import math
 import numpy as np
 import matplotlib as mpl
 import matplotlib.cm as cm
@@ -70,6 +71,7 @@ def makeThVPlots():
     ax.set_yscale('log')
     ax.set_title(parstr)
 
+    print("Saving GaussianThV.pdf")
     fig.savefig('GaussianThV.pdf')
     plt.close(fig)
 
@@ -110,6 +112,7 @@ def makeThVPlots():
     ax.set_ylim(*ylim)
     ax.set_title(parstr)
 
+    print('Saving PowerlawThV.pdf')
     fig.savefig('PowerlawThV.pdf')
     plt.close(fig)
 
@@ -422,8 +425,465 @@ def makeConvergencePlots():
     plt.close(fig2)
 
 
+def get_powers(regime='D', p=2.2):
+    if regime is 'D':
+        beta = 1.0/3.0
+        s1 = 1.0
+        s2 = 0.0
+    elif regime is 'E':
+        beta = 1.0/3.0
+        s1 = 7.0/3.0
+        s2 = 2.0/3.0
+    elif regime is 'F':
+        beta = -0.5
+        s1 = 1.5
+        s2 = -1.0
+    elif regime is 'G':
+        beta = 0.5*(1-p)
+        s1 = 0.5*(3*p+1)
+        s2 = 0.0
+    elif regime is 'H':
+        beta = -0.5*p
+        s1 = 1.5*p
+        s2 = -1.0
+
+    al1 = s1 - 2.0*s2/3.0 - beta
+    D = 12 - 1.5*al1 - 4*beta
+
+    return beta, al1, D, s1, s2, p
+
+
+def f_cone(th, thC, thW):
+    ath = np.atleast_1d(th)
+    f = np.empty(ath.shape)
+    valid = ath >= thC & ath <= thW
+    f[valid] = 1.0
+    f[~valid] = 0.0
+    return f
+
+
+def f_tophat(th, thC, thW):
+    ath = np.atleast_1d(th)
+    f = np.empty(ath.shape)
+    valid = ath <= thC
+    f[valid] = 1.0
+    f[~valid] = 0.0
+    return f
+
+
+def f_gaussian(th, thC, thW):
+    ath = np.atleast_1d(th)
[…]

### 2019-02-04 structuredJets.tex
updates.

@@
 We present a characterization of the afterglows arising from structured jets, utilizing both trans-relativistic numerical calculations and simple analytic approximations.
-The temporal slope before the jet break is found to be a simple function of the ratio between the inclination angle and effective half opening angle of the jet.
+In many cases the temporal slope before the jet break is found to be a simple function of the ratio between the inclination angle and effective half opening angle of the jet.
 Our models, both numerical and analytic, are publicly available as an open source Python package.
@@
 
-The \emph{structured jet} is a model where the isotropic-equivalent energy of a blast wave is a function of the angle from the jet axis: $\Eiso = E(\theta)$.
+The \emph{structured jet} is a GRB emission model where the isotropic-equivalent energy of a blast wave is a function of the angle from the jet axis: $\Eiso = E(\theta)$.
 The specific structure of a jet is determined by the intrinsic structure of the jet launching mechanism as well as the sculpting that occurs as the jet burrows out of the encasing ejecta debris (as in a binary neutron star merger) or stellar envelope (as in a collapsar).
@@
 	E(\theta) &= E_0 \exp\left(-\frac{\theta^2}{2\thC^2}\right)  && \text{Gaussian} \label{eq:gauss}\\
-	E(\theta) &= \frac{E_0}{1 + (\theta/ \thC)^2}  && \text{power-law} \label{eq:pl}
+	E(\theta) &= E_0 \left(1 + \frac{\theta^2}{\thC^2} \right)^{-b/2}  && \text{power-law} \label{eq:pl}
 \end{align}
@@
 
-Each model is parameterized by a normalization $E_0$, a width $\thC$, and a truncation angle $\thW$.
-Outside $\thW$ the energy is initially zero.
+Each fiducial model is parameterized by a normalization $E_0$, a width $\thC$, and a truncation angle $\thW$.
+The power-law model also retains a power-law index $b$.
+Outside $\thW$ the energy is initially zero, this acts as an outer truncation angle for the jet.
 Figure \ref{fig:jetStruct} shows an example of each model fit to recent simulation results.
-The Gaussian model emulates jets with sharp edges, while the power-law emulates jets with narrow cores and large wings (AWK.
-jargon?).
+The Gaussian model emulates jets with a flat core and sharp edges (e.g.
+CITE Margutti), while the power-law emulates jets with narrow cores and large wings (AWK.
+jargon?
+CITE Lazzati, Mizuta).
 
@@
 
+The transition between phases of evolution depends on the effective solid angle $\Delta \Omega$ of the patch of blast wave dominating the emission.
+The size of this patch scales with the Lorentz factor $\gamma$ of the dominant region as:
+\begin{equation}
+	\Delta \Omega = \gamma^{-s_\Omega} \ .
+\end{equation}
+The parameter $s_\Omega$ controls the growth rate of the visible patch, and is typically between 0 and 2.
+
 \subsection{Aligned Evolution: $\thobs \lesssim \thC$}
@@
 The aligned light curve of a structured jet is essentially identical to that of a standard top-hat viewed within the jet cone.
+(CITE Panaitescu \& Kumar).
 The relativistic afterglow is comprised of three phases, \emph{pre-jet break}, \emph{transition}, and \emph{post-jet break}.
@@
 This patch is within the $\theta < \thC$ region where $E(\theta) \approx E_0$ and the structure plays a sub-dominant role.
-The angular size of the visible patch grows as $\gamma^{-2}$.
+The angular size of the visible patch grows with $s_\Omega = 2$.
 Closure relations and scalings of the standard on-axis top-hat apply.
@@
 Material outside $\thC$ is less energetic and contributes sub-dominantly to the afterglow emission.
-The visible patch grows more slowly and the decay of the afterglow steepens slightly.
+The effective visible patch grows more slowly, $s_\Omega \lesssim 2$, and the decay of the afterglow steepens slightly.
 Closure relations and scalings of the standard on-axis top-hat apply only approximately (CITE vanEerten MacFadyen 2010).
 
-\emph{Post-jet break} ---  When $\gamma^{-1} \sim \thC+\thobs$ the far edge of the jet comes in to view and growth of the visible patch ceases.
-The power-law slope of the light curve is decreased by -3/4 relative to the pre-jet break slope.
+\emph{Post-jet break} ---  When $\gamma^{-1} \sim \thC+\thobs$ the far edge of the jet comes in to view and growth of the visible patch ceases, $s_\Omega = 0$.
+If the blast wave remains relativistic and non-spreading, the slope of the light curve is reduced by $-3/4$ relative to the pre-jet break slope.
+However, in many circumstances the jet break begins when the blast wave is only trans-relativistic and spreading may have begun.
+In these cases an analytic treatment of the light curve is slope is more difficult, but numerical simulations and analytic work estimate an additional reduction of "???" over the simple analytic result.
 
-The onset of the transition phase (ie. the start of the jet-break), occurs at $\tbm$ and completes at $\tbp$, given by:
+The transition phase occurs at $\tbm$ and completes at $\tbp$, given in the single shell approximation (see Appendix \ref{sec:derive1}) by:
 \begin{align}
-	\tbpm &= \left(\frac{9}{16\pi} \frac{E_0}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thC\pm\thobs}{2}\right)\right)^{8/3} ,\label{eq:tbpm}
+	\tbpm &= \left(\frac{9}{16\pi} \frac{E_0}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thC\pm\thobs}{2}\right)\right)^{8/3} .\label{eq:tbpm}
 \end{align}
+
+It is important to note that when $\thobs \neq 0$ the transition period is extended, and the most significant transition in the light curve occurs at $\tbp$, the \emph{jet break}.
+The jet break occurs, in all jets, when the effective angular size of the visible patch of the jet ceases to increase, that is when $s_\Omega = 0$.
 
@@
 
-The relativistic stages of evolution are followed by a Newtonian phase when the decelerating blast wave becomes non-relativistic, spreads sonically, and approaches a Sedov-Taylor solution.
+The relativistic stages of evolution are followed by a Newtonian phase ($t > 200$ days in Figure \ref{fig:onaxis}) when the decelerating blast wave becomes non-relativistic, spreads sonically, and approaches a Sedov-Taylor solution.
 We do not address the Newtonian phase of evolution in this work.
@@
 To observers this energy gradient presents itself as a slowly rising or decaying afterglow light curve.
-The relativistic afterglow is comprised of two or three phases depending on whether the observer lies within the truncation angle, \emph{off-axis}, \emph{structured},  and \emph{post-jet break}.
+The relativistic afterglow is comprised of two or three phases depending on whether the observer lies within the truncation angle, \emph{wing}, \emph{structured}, and \emph{post-jet break}.
 
-\emph{Off-axis} --- If the viewer lies outside the truncation angle, $\thobs > \thW$, then at early times the entire blast wave surface is off-axis and all emission is beaming suppressed.
+\emph{Wing} --- If the viewer lies outside the truncation angle, $\thobs > \thW$, then at early times the entire blast wave surface is off-axis and all emission is beaming suppressed.
 This greatly reduces the early flux and leads to a dim but steeply rising light curve as the blast wave decelerates.
@@
 
-The temporal and spectral slopes for various regimes are given in Table \ref{tab:slopes}.  The derivation of the slopes, $\tW$, and $\tb$ are given in Appendix \ref{sec:derive1}.
+The temporal and spectral slopes for various regimes are given in Table \ref{tab:slopes}.  The derivation of the closure relations, $\tW$, and $\tb$ are given in Appendix \ref{sec:derive1}.
 
@@
 	\geff &= \frac{\thobs^2}{4\thC^2} && \text{Gaussian}\ , \\
-	\geff &= \frac{2 \thobs^2}{4 \thC^2+\thobs^2} && \text{power-law}\ . \label{eq:geff}
+	\geff &= \frac{b \thobs^2}{4 \thC^2+\thobs^2} && \text{power-law}\ . \label{eq:geff}
 \end{align}
@@
 
-\section{Structured Phase}
-
-(-9/2+6p-3g) / (8+g) = a
--9/2+6p-3g = a(8+g)
--9/2+6p-8a = ag + 3g
--9/2+6p-8a = (a + 3)g
-g = (-9/2+6p-8a) / (a+3)
-
 \appendix

### 2019-02-04 code/paperPlots.py

@@ -5,6 +5,7 @@ import matplotlib.cm as cm
 import matplotlib.pyplot as plt
 import matplotlib.patches as patches
 import matplotlib.collections as collections
+import h5py as h5
 import grbpy as grb
 
 sec2year = grb.sec2day / 365.25
@@ -21,6 +22,7 @@ def makeThVPlots():
     thC = 0.05
     thV = 0.6
     thW = 0.5*np.pi
+    b = 2
     n0 = 1.0e-3
     p = 2.2
     epse = 0.1
@@ -28,8 +30,8 @@ def makeThVPlots():
     xiN = 1.0
     dL = 1.23e26
 
-    Y = np.array([thV, E0, thC, thW, 0.0, 0.0, 0.0, n0, p, epse, epsB, xiN,
-                  dL])
+    Y = np.array([thV, E0, thC, thW, b, 0.0, 0.0, 0.0, n0, p, epse, epsB,
+                  xiN, dL])
 
     parstr = r"$n_0$={0:.01f}x$10^{{-3}}cm^{{-3}}$".format(n0/1.0e-3)
     parstr += r"  $p$={0:.01f}".format(p)
@@ -71,8 +73,7 @@ def makeThVPlots():
     ax.set_yscale('log')
     ax.set_title(parstr)
 
-    print("Saving GaussianThV.pdf")
-    fig.savefig('GaussianThV.pdf')
+    save(fig, 'GaussianThV.pdf')
     plt.close(fig)
 
     thC = 0.05
@@ -112,8 +113,7 @@ def makeThVPlots():
     ax.set_ylim(*ylim)
     ax.set_title(parstr)
 
-    print('Saving PowerlawThV.pdf')
-    fig.savefig('PowerlawThV.pdf')
+    save(fig, 'PowerlawThV.pdf')
     plt.close(fig)
 
 
@@ -121,6 +121,7 @@ def makeCentralPlots(modelPlots=True):
 
     thC = 0.1
     thW = 0.4
+    b = 2
     E0 = 1.0e52
     n0 = 1.0e-2
     p = 2.2
@@ -129,7 +130,7 @@ def makeCentralPlots(modelPlots=True):
     xiN = 1.0
     dL = 1.23e26
 
-    Y = np.array([0.0, E0, thC, thW, 0.0, 0.0, 0.0, n0, p, epse, epsB, xiN,
[…]

### 2019-02-04 code/structComp.py

@@ -6,49 +6,53 @@ c = 2.99792458e10
 me = 9.1093897e-28
 mp = 1.6726231e-24
 
+
 def gaussian(theta, thC=0.1, thW=0.4, E0=1.0e53, n0=1.0, t0=1.0e7):
     atheta = np.atleast_1d(theta)
     onaxis = theta < thW
     offaxis = theta >= thW
     th = atheta[onaxis]
-    
+
     E = np.empty(atheta.shape)
     g = np.empty(atheta.shape)
 
     E[onaxis] = E0/(4*np.pi) * np.exp(-0.5*(th*th)/(thC*thC))
-    g[onaxis] = np.sqrt(17*E[onaxis] / (2*n0*mp*c*c*c*c*c)) * math.pow(t0,-1.5)
+    g[onaxis] = np.sqrt(17*E[onaxis]/(2*n0*mp*c*c*c*c*c)) * math.pow(t0, -1.5)
 
     if offaxis.any():
         E[offaxis] = 0.0
         g[offaxis] = 1.0
 
-    E[g<1.0] = 0.0
-    g[g<1.0] = 1.0
+    E[g < 1.0] = 0.0
+    g[g < 1.0] = 1.0
 
     return g, E
 
-def powerlaw(theta, thC=0.1, thW=0.4, E0=1.0e53, n0=1.0, t0=1.0e7):
+
+def powerlaw(theta, thC=0.1, thW=0.4, E0=3.0e53, n0=1.0, t0=1.0e7, b=3):
 
     atheta = np.atleast_1d(theta)
     onaxis = theta < thW
     offaxis = theta >= thW
     th = atheta[onaxis]
-    
+
     E = np.empty(atheta.shape)
     g = np.empty(atheta.shape)
 
-    E[onaxis] = E0/(4*np.pi) / (1.0 + (th*th)/(thC*thC))
-    g[onaxis] = np.sqrt(17*E[onaxis] / (2*n0*mp*c*c*c*c*c)) * math.pow(t0,-1.5)
+    Th = np.sqrt(1.0 + th*th/(thC*thC))
+
+    E[onaxis] = E0/(4*np.pi) * np.power(Th, -b)
+    g[onaxis] = np.sqrt(17*E[onaxis]/(2*n0*mp*c*c*c*c*c)) * math.pow(t0, -1.5)
 
     if offaxis.any():
         E[offaxis] = 0.0
         g[offaxis] = 1.0
 
[…]

### 2019-02-06 structuredJets.tex
Started with some references, refurbished structure comparison plot.

@@
 \begin{figure}
-	\plotone{figs/jetStruct.pdf}
-	\caption{Jet Structure.  Temporary version.  Remove $\Gamma$ subplot.  Add Aloy. \label{fig:jetStruct}}
+	\plotone{figs/jetStructureComparison.pdf}
+	\caption{Lateral profiles of isotropic equivalent energy $\Eiso$ as a function of angle from the jet axis $\theta$, individually rescaled to group similar profile shapes.
+The thick grey lines show fiducial profiles with simple analytic expressions (Equations \eqref{eq:gauss} and \eqref{eq:pl}) while the thin colored lines show results from numerical simulations and analytic models chosen from the literature.
+The blue line is the B1 numerical simulation of \cite{Aloy:2005aa}, orange the HE16N numerical simulation of \cite{Mizuta:2009aa}, green an analytic ``boosted fireball'' model with $\gamma_{\rm{B}}=10$ and $\eta_0=3$ from \cite{Duffell:2013aa}, red the numerical simulation from \cite{Lazzati:2017aa} (L17), and purple the numerical simulation from \cite{Margutti:2018aa} (M18).
+The thick solid grey line is a Gaussian profile (Equation \eqref{eq:gauss}) with $E_0 = 3\times 10^{52}$ erg, $\thC = 6^\circ$, and $\thW=12^\circ$ and the thick dashed grey line is a smoothed power law profile (Equation \eqref{eq:pl}) with $E_0 = 10^{52}$ erg, $\thC = 4^\circ$, $\thW=20^\circ$, and $b=4.5$.
+The Gaussian and power law profiles can emulate the basic properties of the energy profiles found in the literature.
+\label{fig:jetStruct}}
 \end{figure}
@@
 Outside $\thW$ the energy is initially zero, this acts as an outer truncation angle for the jet.
-Figure \ref{fig:jetStruct} shows an example of each model fit to recent simulation results.
-The Gaussian model emulates jets with a flat core and sharp edges (e.g.
-CITE Margutti), while the power-law emulates jets with narrow cores and large wings (AWK.
-jargon?
-CITE Lazzati, Mizuta).
+
+Figure \ref{fig:jetStruct} shows an example of each model together with jet energy profiles drawn from the literature, mostly the result of numerical relativistic hydrodynamic simulations.
+The Gaussian profile emulates jets with a flat core and sharp edges, typically the result of powerful successful jets \citep{Aloy:2005aa, Margutti:2018aa}.
+Jets which are subject to stronger interactions with the surrounding medium can develop a profile with energetic wings and a narrow core, emulated by the analytic power law profile \citep{Mizuta:2009aa, Duffell:2013aa, Lazzati:2017aa}.
 
@@
 To observers this energy gradient presents itself as a slowly rising or decaying afterglow light curve.
-The relativistic afterglow is comprised of two or three phases depending on whether the observer lies within the truncation angle, \emph{wing}, \emph{structured}, and \emph{post-jet break}.
+The relativistic afterglow is comprised of two or three phases depending on whether the observer lies within the truncation angle, \emph{far off-axis}, \emph{structured}, and \emph{post-jet break}.
 
-\emph{Wing} --- If the viewer lies outside the truncation angle, $\thobs > \thW$, then at early times the entire blast wave surface is off-axis and all emission is beaming suppressed.
+\emph{Far off-axis} --- If the viewer lies outside the truncation angle, $\thobs > \thW$, then at early times the entire blast wave surface is off-axis and all emission is beaming suppressed.
 This greatly reduces the early flux and leads to a dim but steeply rising light curve as the blast wave decelerates.
@@
 
+\bibliography{structuredJets_sources}
+
 \end{document}

### 2019-02-06 code/structComp.py

@@ -48,13 +48,15 @@ def powerlaw(theta, thC=0.1, thW=0.4, E0=3.0e53, n0=1.0, t0=1.0e7, b=3):
         E[offaxis] = 0.0
         g[offaxis] = 1.0
 
-    E[g < 1.0] = 0.0
+    # E[g < 1.0] = 0.0
     g[g < 1.0] = 1.0
 
     return g, E
 
 
 def boostedFireball(theta, gb=3.0, eta0=3.0, E0=1.0e53):
+
+    # returns dE/dOmega scaled to Eiso(0) = E0
 
     ub = math.sqrt(1.0 + gb*gb)
     vb = ub/gb
@@ -120,10 +122,16 @@ def loadTxt(filename, cols, skiprows, delimiter=None):
 
 def duffell2015Oblate(theta, Etot=1.0e49):
 
+    # data is dE/dOmega, scaled as Etot/M_0 c^2 = 0.024
+
     filename = "StructureData/duffell2015_data.csv"
 
     thg, gp = loadTxt(filename, cols=[6, 7], skiprows=2, delimiter=',')
     thE, Ep = loadTxt(filename, cols=[4, 5], skiprows=2, delimiter=',')
+
+    # Msun = 1.989e33
+    # c = 2.99792458e10
+    # M0 = 1.0e-4 * Msun
     Ep *= Etot/0.024
 
     g = np.interp(theta, thg, gp, right=1.0)
@@ -133,6 +141,8 @@ def duffell2015Oblate(theta, Etot=1.0e49):
 
 
 def duffell2015Spherical(theta, Etot=1.0e49):
+
+    # data is dE/dOmega
 
     filename = "StructureData/duffell2015_data.csv"
 
@@ -148,6 +158,8 @@ def duffell2015Spherical(theta, Etot=1.0e49):
 
 def morsony2007realg5(theta, Etot=3.0e51):
 
+    # data is E_iso, total energy is 2.66e52 erg
+
     filename = "StructureData/morsony2007realg5E.csv"
     thp, Ep = np.loadtxt(filename, skiprows=2, unpack=True, delimiter=',')
 
@@ -161,6 +173,8 @@ def morsony2007realg5(theta, Etot=3.0e51):
 
 
 def morsony2007realg2(theta, Etot=3.0e51):
+
+    # data is E_iso, total energy is 2.66e52 erg
 
     filename = "StructureData/morsony2007realg2E.csv"
[…]

### 2019-02-07 structuredJets.tex
Began references

@@
 	\item Analytic description: \begin{itemize}
-		\item Velocity stratification / refreshed shock / cocoon leads to simple power-law behaviour depending on $k$ ($E_{>u} \propto u^{-k}$).
+		\item Velocity stratification / refreshed shock / cocoon leads to simple power law behaviour depending on $k$ ($E_{>u} \propto u^{-k}$).
 Breaks occur at deceleration time and when $E_{>u}$ shuts off.
-		\item Angular structure / structured jet leads to not-quite power-law behaviour, depending on $g \approx (\thobs - \theta)d \log E / d\theta$.
+		\item Angular structure / structured jet leads to not-quite power law behaviour, depending on $g \approx (\thobs - \theta)d \log E / d\theta$.
 Breaks occur when $\thobs - \thW \approx 1/\gamma(\thW)$ and $\thobs \approx 1/\gamma(0)$.
@@
 
-To this end, we have calculated the power-law temporal slope of the structured phase in both angular and radial structure dominated cases, along with the corresponding observed break times.
+To this end, we have calculated the power law temporal slope of the structured phase in both angular and radial structure dominated cases, along with the corresponding observed break times.
 We have developed a semi-analytic numerical model of structured GRB afterglows for detailed comparison to data, which is now publicly available.
@@
 
-Numerical simulations have revealed a variety of jet angular energy distributions, often containing an energetic core with power-law tails.
-Figure \ref{fig:jetStruct} shows a collection of jet energy distributions from the literature (CITE curves in plots).
-Lacking a well-established physical model of the true $E(\theta)$, in particular its dependence on the parameters of the system, we consider two simple parameterized models: a Gaussian jet and a power-law with a smooth core.
+Numerical simulations have revealed a variety of jet angular energy distributions, often containing an energetic core with power law tails.
+Figure \ref{fig:jetStruct} shows a collection of jet energy distributions from the literature \citep{Aloy:2005aa, Mizuta:2009aa, Duffell:2013aa, Lazzati:2017aa, Margutti:2018aa}.
+Lacking a well-established physical model of the true $E(\theta)$, in particular its dependence on the parameters of the system, we consider two simple parameterized models: a Gaussian jet and a power law with a smooth core.
 
@@
 	E(\theta) &= E_0 \exp\left(-\frac{\theta^2}{2\thC^2}\right)  && \text{Gaussian} \label{eq:gauss}\\
-	E(\theta) &= E_0 \left(1 + \frac{\theta^2}{\thC^2} \right)^{-b/2}  && \text{power-law} \label{eq:pl}
+	E(\theta) &= E_0 \left(1 + \frac{\theta^2}{\thC^2} \right)^{-b/2}  && \text{power law} \label{eq:pl}
 \end{align}
@@
 Each fiducial model is parameterized by a normalization $E_0$, a width $\thC$, and a truncation angle $\thW$.
-The power-law model also retains a power-law index $b$.
+The power law model also retains a power law index $b$.
 Outside $\thW$ the energy is initially zero, this acts as an outer truncation angle for the jet.
@@
 	\plotone{figs/lc_on.pdf}
-	\caption{Aligned ($\thobs = \thC/2$) afterglow light curves for top-hat (blue), Gaussian (orange), and power-law (green) jets.
+	\caption{Aligned ($\thobs = \thC/2$) afterglow light curves for top-hat (blue), Gaussian (orange), and power law (green) jets.
 When viewed on-axis, jets containing angular structure are very difficult to distinguish from top-hats.
@@
 
-Figure \ref{fig:onaxis} shows representative top-hat, Gaussian, and power-law jet light curves in the aligned regime.
+Figure \ref{fig:onaxis} shows representative top-hat, Gaussian, and power law jet light curves in the aligned regime.
 The light curves nearly overlap, demonstrating the similar evolution of all structured jet afterglows when viewed within the jet core.
@@
 If $\thobs < \thW$ this phase is entirely absent.
-Table \ref{tab:slopes} gives the temporal power-law slope of the light curve in this phase.
+Table \ref{tab:slopes} gives the temporal power law slope of the light curve in this phase.
 These slopes are derived in Appendix \ref{sec:derive1}.
@@
 The $g$ parameter evolves with time as $\theta^*$ sweeps from the jet edge to the core.
-This produces deviations in the light curve from a pure power-law.
+This produces deviations in the light curve from a pure power law.
 However, we find ultimately these deviations are not too large and the average slope is well approximated by $\geff  = g(\thobs/2)$.
-For the power-law and Gaussian jet models this gives:
+For the power law and Gaussian jet models this gives:
 \begin{align}
 	\geff &= \frac{\thobs^2}{4\thC^2} && \text{Gaussian}\ , \\
-	\geff &= \frac{b \thobs^2}{4 \thC^2+\thobs^2} && \text{power-law}\ . \label{eq:geff}
+	\geff &= \frac{b \thobs^2}{4 \thC^2+\thobs^2} && \text{power law}\ . \label{eq:geff}
 \end{align}
-These values may be used in Table \ref{tab:slopes} for an approximate power-law model of a structured jet with an appropriate viewing angle dependent temporal evolution.
+These values may be used in Table \ref{tab:slopes} for an approximate power law model of a structured jet with an appropriate viewing angle dependent temporal evolution.
 These analytic results are in agreement with previous work on structured jets (CITE ROSSI) and the trans-relativistic numerical model described in Section \ref{sec:numerical}.
@@
 The top-hat jet (with opening angle $\thC$) begins in the off-axis phase.
-The Gaussian and power-law jets begin in the structured phase as $\thobs < \thW$.
+The Gaussian and power law jets begin in the structured phase as $\thobs < \thW$.
 All three models enter similar post-jet break phases.
@@
 In this case $\thobs < \thW$ so neither model exhibits an off-axis phase.
-The similar temporal evolution is easy to understand as at this angle both models have $\geff = 1$ and hence approximately equal power-law slopes in the structured phase.
+The similar temporal evolution is easy to understand as at this angle both models have $\geff = 1$ and hence approximately equal power law slopes in the structured phase.
 At late times as more of the jet comes in to view the difference between all three models becomes negligible.
@@
 At the larger $6\thC$ viewing angle all three models exhibit off-axis, structured, and post-jet break phases of the afterglow.
-The different $\tW$ between the Gaussian and power-law models is due to the different $E(\thW)$ of the two models.
+The different $\tW$ between the Gaussian and power law models is due to the different $E(\thW)$ of the two models.
 In the structured phase the Gaussian shows a rising light curve with slope $~1$ due to the large $\geff = 9$.
-The power-law meanwhile has a smaller $\geff$ of $9/5$, giving rise to a very shallow decay.
+The power law meanwhile has a smaller $\geff$ of $9/5$, giving rise to a very shallow decay.
 As at the other viewing angles, once the entire jet is visible at $\tb$ all models follow similar post-jet break evolutions.
@@
 The width of the G and H bands shows the dependency on $p$, the upper curves for $p=2$ and the lower for $p=3$.
-The temporal power-law slope of a structured jet afterglow increases with $g$ in all spectral regimes.
+The temporal power law slope of a structured jet afterglow increases with $g$ in all spectral regimes.
 \label{fig:slopesG}}
@@
 
-Figure \ref{fig:slopesG} shows the structured phase power-law temporal slope as a function of $g$ for spectral regimes $D$--$H$.
+Figure \ref{fig:slopesG} shows the structured phase power law temporal slope as a function of $g$ for spectral regimes $D$--$H$.
 In the $G$ and $H$ regimes the spectral slope is a function of $p$, this dependence carries over into the temporal slope as well.
@@
 The distribution of material behind the blast wave is specified by $E_{>}(u)$, the energy of all material in the ejecta with four-velocity greater than $u$.
-This is typically taken to be a power-law in $u$ within the finite domain $[\umin, \umax]$:
+This is typically taken to be a power law in $u$ within the finite domain $[\umin, \umax]$:
 \begin{equation}
@@
 	\plotone{figs/slopesCocoon.png}
-	\caption{The temporal power-law slope of the spherical refreshed-shock afterglow light curve as a function of $k$.
+	\caption{The temporal power law slope of the spherical refreshed-shock afterglow light curve as a function of $k$.
 Otherwise as Figure \ref{fig:slopesG}.
-The temporal power-law slope of a structured jet afterglow increases with $k$ in all spectral regimes.
+The temporal power law slope of a structured jet afterglow increases with $k$ in all spectral regimes.
 \label{fig:slopesK}}
@@
 No afterglow emission was detected until an x-ray detection by the Chandra observatory nine days after the GW trigger (CITE TrojaNature).
-Further radio, optical, and x-ray observations showed a steady rising light curve with constant power-law slope until a peak near day 160.
+Further radio, optical, and x-ray observations showed a steady rising light curve with constant power law slope until a peak near day 160.
 At this point the light curve turned over and began a steep decay that continues to the present (CITE YearInTheLife).
@@
 Some models truncate at $\mathcal{O}(10)$ degrees, while others have large tails extending to near the equator.
-The Gaussian and power-law models respectively emulate this behavior, providing a simple parameterized representation of the landscape of numerical models.
+The Gaussian and power law models respectively emulate this behavior, providing a simple parameterized representation of the landscape of numerical models.
 Of particular note are the Lazzati 2017 and Margutti 2018 models, both of which were calculated specifically for GW170817.

### 2019-02-07 code/structComp.py

@@ -120,7 +120,7 @@ def loadTxt(filename, cols, skiprows, delimiter=None):
     return datT
 
 
-def duffell2015Oblate(theta, Etot=1.0e49):
+def duffell2015Oblate(theta, Etot=1.0e47):
 
     # data is dE/dOmega, scaled as Etot/M_0 c^2 = 0.024
 
@@ -312,8 +312,8 @@ if __name__ == "__main__":
     deg = 180.0/np.pi
     rad = np.pi/180.0
 
-    gG, EG = gaussian(theta, thC=6*rad, thW=15*rad, E0=3e52)
-    gPL, EPL = powerlaw(theta, thW=60*deg, thC=4*deg, b=4.0, E0=1e52)
+    gG, EG = gaussian(theta, thC=6*rad, thW=13*rad, E0=5e52)
+    gPL, EPL = powerlaw(theta, thW=60*rad, thC=4*rad, b=4.0, E0=1e52)
     gBF0303, EBF0303 = boostedFireball(theta)
     gBF1003, EBF1003 = boostedFireball(theta, gb=10)
     gBF0310, EBF0310 = boostedFireball(theta, eta0=10)
@@ -414,42 +414,47 @@ if __name__ == "__main__":
     ax[1].set_yscale('log')
     fig.tight_layout()
 
-    print("Saving structCompE.pdf")
-    fig.savefig("structCompE.pdf")
+    print("Saving structComp.pdf")
+    fig.savefig("structComp.pdf")
 
     print("Plotting")
-    figE, axE = plt.subplots(1, 1, figsize=(12, 9))
+    figE, axE = plt.subplots(1, 1, figsize=(8, 6))
 
     clr = ["k", "grey", "tab:blue", "tab:orange", "tab:green", "tab:red",
                 "tab:purple", "tab:brown", "tab:pink", "tab:olive", "tab:cyan"]
     ls = ['-', '--', ':', '-.']
 
-    axE.plot(theta*deg, EG, label="Gaussian", lw=4.0,
-             color=clr[0], ls=ls[0])
-    axE.plot(theta*deg, EPL, label="Power law", lw=4.0,
-             color=clr[1], ls=ls[0])
-    axE.plot(theta*deg, EBF1003,
-             label="Boosted Fireball $\gamma_B=10$ $\eta_0=3$",
+    axE.plot(theta*deg, EG, label="Gaussian", lw=3.0,
+             color=clr[1], ls=ls[0], alpha=0.65)
[…]

### 2019-02-28 structuredJets.tex
some updates

@@
 \newcommand{\bmax}{\ensuremath{\beta_{\mathrm{max}}}}
+\newcommand{\som}{\ensuremath{s_{\Omega}}}
 
@@
 \begin{equation}
-	\Delta \Omega = \gamma^{-s_\Omega} \ .
+	\Delta \Omega = \gamma^{-\som} \ .
 \end{equation}
-The parameter $s_\Omega$ controls the growth rate of the visible patch, and is typically between 0 and 2.
+The parameter $\som$ controls the growth rate of the visible patch, and is typically between 0 and 2.
 
@@
 This patch is within the $\theta < \thC$ region where $E(\theta) \approx E_0$ and the structure plays a sub-dominant role.
-The angular size of the visible patch grows with $s_\Omega = 2$.
+The angular size of the visible patch grows with $\som = 2$.
 Closure relations and scalings of the standard on-axis top-hat apply.
@@
 Material outside $\thC$ is less energetic and contributes sub-dominantly to the afterglow emission.
-The effective visible patch grows more slowly, $s_\Omega \lesssim 2$, and the decay of the afterglow steepens slightly.
+The effective visible patch grows more slowly, $\som \lesssim 2$, and the decay of the afterglow steepens slightly.
 Closure relations and scalings of the standard on-axis top-hat apply only approximately (CITE vanEerten MacFadyen 2010).
 
-\emph{Post-jet break} ---  When $\gamma^{-1} \sim \thC+\thobs$ the far edge of the jet comes in to view and growth of the visible patch ceases, $s_\Omega = 0$.
+\emph{Post-jet break} ---  When $\gamma^{-1} \sim \thC+\thobs$ the far edge of the jet comes in to view and growth of the visible patch ceases, $\som = 0$.
 If the blast wave remains relativistic and non-spreading, the slope of the light curve is reduced by $-3/4$ relative to the pre-jet break slope.
@@
 It is important to note that when $\thobs \neq 0$ the transition period is extended, and the most significant transition in the light curve occurs at $\tbp$, the \emph{jet break}.
-The jet break occurs, in all jets, when the effective angular size of the visible patch of the jet ceases to increase, that is when $s_\Omega = 0$.
+The jet break occurs, in all jets, when the effective angular size of the visible patch of the jet ceases to increase, that is when $\som = 0$.
 
@@
 	\startdata
-	\nu<\nu_m<\nu_c     & D & -7 			& -\frac{5/2 + 3g}{8+g} 		& -3		& 1/4			& -1/3 \\
-	\nu_m<\nu<\nu_c     & G & -15/2 + 3p/2 	& \frac{-9/2 + 6p - 3g}{8+g} 	& -3		& 3p/4		& (p-1)/2 \\
-	\nu < \nu_c < \nu_m & E & -17/3 		& \frac{1/6 - 11g/3}{8+g} 		& -11/3	& 7/12		& -1/3 \\
-	\nu_c < \nu < \nu_m & F & -13/2 		& \frac{7/2 - 2g}{8+g} 		& -2		& 1			& 1/2 \\
-	\nu_c < \nu_m < \nu & H & -8 + 3p/2 		& \frac{-5/2 +6p  -2g}{8+g} 	& -2		& (3p+1)/4	& p/2 \\ 
+	\nu<\nu_m<\nu_c     & D & 7 			& \frac{1 + 3g}{8+g} 		& 3		& -1/4		& 1/3 \\
+	\nu_m<\nu<\nu_c     & G & 15/2 - 3p/2 	& \frac{3 - 6p +3g}{8+g} 	& 3		& -3p/4		& (1-p)/2 \\
+	\nu < \nu_c < \nu_m & E & 17/3 		& \frac{-5/3 + 11g/3}{8+g} 	& 11/3	& -7/12		& 1/3 \\
+	\nu_c < \nu < \nu_m & F & 13/2 		& \frac{-5 + 2g}{8+g} 		& 2		& -1			& -1/2 \\
+	\nu_c < \nu_m < \nu & H & 8 - 3p/2 		& \frac{1-6p  +2g}{8+g} 	& 2		& -(3p+1)/4	& -p/2 \\ 
 	\enddata
@@
 In the simplest case the visible part of the blast wave is assumed to be quasi-spherical.
-The distribution of material behind the blast wave is specified by $E_{>}(u)$, the energy of all material in the ejecta with four-velocity greater than $u$.
+The velocity distribution of material behind the blast wave is specified by $E_{>}(u)$, the energy of all material in the ejecta with four-velocity greater than $u$.
 This is typically taken to be a power law in $u$ within the finite domain $[\umin, \umax]$:
@@
 A blast wave will have an initial coasting period before sweeping up enough mass in the ambient medium to begin deceleration and be subject to refreshed shocks.
-The shock refreshment ends when the blast wave decelerates past $\umin$.
+The transition between coasting and decelerating occurs in the bursters frame at $\tdec$.
+The shock refreshment ends when the blast wave decelerates past $\umin$, in the observers frame at $\tumin$.
 In the single shell model with trans-relativistic equation of state used here, these times are:
@@
 
-The light curves of both the angularly structured jet and refreshed shock models can be understood in terms of general energy injection mechanisms, which are typically parameterized as an additional power $L$ delivered to the blast wave.
+The light curves of both the misaligned angularly structured jet and refreshed shock models can be understood in terms of general energy injection mechanisms, parameterized as an additional power $L$ delivered to the blast wave.
 This power is typically taken to decay in time as a power law, $L \propto t^{-q}$, with $q \in [0,1]$.
 
-The mapping between energy injection and refreshed shocks was done in (CITE Zhang06).
+The mapping between energy injection and refreshed shocks was done by \cite{Zhang:2006aa}.
 That work specifies the index $s$ of the mass distribution $M_{>u} \propto u^{-s}$, which is related simply to the index $k$ by $k = s-1$.
-Under this mapping the closure relations in Table \ref{tab:slopes} are equivalent to those in (CITE Zhang06) and the model can be seen as equivalent to an energy injection model with $q = (8-2k) / (8+k)$.
+Under this mapping the closure relations in Table \ref{tab:slopes} are equivalent to those in \cite{Zhang:2006aa} and the model can be seen as equivalent to an energy injection model with $q = (8-2k) / (8+k)$.
 
-There is no single mapping between the structured jet and energy injection or refreshed shock models.
-However, a visual comparison between $\alpha_{\text{struct}}$ in Table \ref{tab:slopes} and $\alpha_{\text{refresh}}$ in Table \ref{tab:refreshSlopes} indicate the identical roles played by $g$ and $k$.
-Indeed, a simple swap $g \leftrightarrow k$ produces almost identical closure relations.
-However, as seen in Tables \ref{tab:slopes} and \ref{tab:refreshSlopes} or
+Misaligned structured jets do not map as neatly onto energy injection models as the scaling of the visible patch, $\som = 1.0$, is different than in standard afterglows, $\som = 2$.
+Once this change is accounted for, the $g$ parameter plays the same role as $k$, as can be seen by a simple comparison between $\alpha_{\text{struct}}$ in Table \ref{tab:slopes} and $\alpha_{\text{refresh}}$ in Table \ref{tab:refreshSlopes}.
+That is, a structured jet light curve is equivalent to a standard energy injection model with:
+\begin{align}
+	q &= (8-2g) / (8+g)  \label{eq:struct2ei} \\
+	\som &= 1
+\end{align}
 
-The mapping between structured jet and refreshed shock (and hence energy injection) models is a two step process.   Indeed, a stru
+Generic closure relations leaving the dependence on $\som$ explicit are presented in Table \ref{tab:generalSlopes}.
 
@@
 %
-
-The numerical model described in Section \ref{sec:numerical} improves on these analytic approximations by ...
 
@@
 \begin{deluxetable*}{CCCCCC}
-	\tablecaption{Generic structured phase temporal and spectral slopes: $F_\nu \propto \tobs^{-\alpha} \nu^{-\beta}$.
-The visible patch of the jet has a solid angle which scales as $\gamma^{-s_3}$.
-See Equations \eqref{eq:gdef} and \eqref{eq:geff} for the definition and effective values of $g$.
-A uniform relativistic blast wave pre-jet break has $s_3=2$, a relativistic blast wave with angular structure pre-jet break has $s_3 \approx 1.5$, and a relativistic blast wave post jet-break has $s_3 = 0$.
+	\tablecaption{Generic closure relations for the afterglow of a relativistic blast wave in a homogeneous medium: $F_\nu \propto \tobs^{\alpha} \nu^{\beta}$.
+See Equations \eqref{eq:gdef} and \eqref{eq:geff} for the definition and effective values of $g$ for misaligned structured jets.
+Jets aligned with the viewer or without angular structure have $g=0$.
+The visible patch of the jet has a solid angle which scales as $\gamma^{-\som}$.
+A uniform relativistic blast wave pre-jet break has $\som=2$, a relativistic blast wave with angular structure pre-jet break has $\som \approx 1$, and a relativistic blast wave post jet-break has $\som = 0$.
 For a refreshed-shock model replace $g$ with $k$, defined in Equation \eqref{eq:Eu}.
 \label{tab:generalSlopes}}
-	\tablehead{\colhead{Regime}& \colhead{Label} & \colhead{$\alpha_{\mathrm{struct}}$} & \colhead{$\beta$}}
+	\tablehead{\colhead{Regime}& \colhead{Label} & \colhead{$\alpha$} & \colhead{$\beta$}}
 	\startdata
-	\nu<\nu_m<\nu_c     & D & \frac{2-3s_3 - 3g}{8+g} 		& -1/3 \\
-	\nu_m<\nu<\nu_c     & G & \frac{6p - 3s_3 - 3g}{8+g} 	& (p-1)/2 \\
-	\nu < \nu_c < \nu_m & E & \frac{14/3 - 3s_3 -11g/3}{8+g} 	& -1/3 \\
-	\nu_c < \nu < \nu_m & F & \frac{8-3s_3 -2g}{8+g} 		& 1/2 \\
-	\nu_c < \nu_m < \nu & H & \frac{6p - 2 - 3s_3 - 2g}{8+g} 	& p/2 \\ 
+	\nu<\nu_m<\nu_c     & D & \frac{-2 + 3\som + 3g}{8+g} 		& 1/3 \\
+	\nu_m<\nu<\nu_c     & G & \frac{-6p + 3\som + 3g}{8+g} 	& (1-p)/2 \\
+	\nu < \nu_c < \nu_m & E & \frac{-14/3 + 3\som + 11g/3}{8+g} 	& 1/3 \\
+	\nu_c < \nu < \nu_m & F & \frac{-8 + 3\som + 2g}{8+g} 		& -1/2 \\
+	\nu_c < \nu_m < \nu & H & \frac{-6p - 2 + 3\som + 2g}{8+g} 	& -p/2 
 	\enddata
 \end{deluxetable*}
-
-The structured jet $g(\theta)$ parameter can similarly...
-
-\section{Numerical Model: The \afterglowpy{} Package}\label{sec:numerical}
-
-To examine the detailed behavior of structured afterglows we constructed a numerical model, publicly available as the \afterglowpy{} Python package.
-
-The numerical model employs a trans-relativistic equation of state to evolve a blast wave in the single-shell approximation from the initial coasting phase through deceleration and spreading into the non-relativistic Sedov phase.
-The observed flux density $F_\nu$ is calculated by numerically integrating the synchrotron emissivity over equal-observer-time surfaces.
-
-The flux calculation follows the semi-analytic method of (CITE Hendrik 2010) using the shock evolution prescription outlined in (CITE Hendrik Review) modified to include refreshed shocks, energy injection, and jet spreading.
-For a structured jet, the surface is divided into $N_\theta$ annular regions each of which is allocated an energy according to $E(\theta)$.
-Each segment evolves independently and is otherwise treated as a section of a top-hat jet.
-
-\subsection{Numerical Algorithm}\label{subsec:algo}
-
-To compute the light curve of a top-hat jet we first must calculate the time evolution of the blast wave.
-We utilize the single-shell approximation, treating the ejecta mass, contact discontinuity, and forward shock as a single unit propagating through a cold ambient medium with constant rest-mass density $\rho_0 = \Mp n_0$.
-For a detailed derivation (CITE Hendrik 2010 + Hendrik Review).
-The forward shock is a radius $R$ from the explosion and moves at a velocity $\beta_s$.
-In terms of the fluid four-velocity behind the shock $u$ and its Lorentz factor $\gamma$ this may be written as:
-\begin{equation}
-	\dot{R} = \frac{4 u \gamma}{4 u^2 +3}c\ . \label{eq:Rdot}
-\end{equation}
-Here the time derivative $\dot{R}$ is taken with respect to elapsed time in the bursters' frame $t$.
-
- The evolution of the four velocity is determined through conservation of energy.  The total energy in the trans-relativistic single shell approximation is:
-\begin{equation}
-	E = (\gamma - 1)\Mej c^2 + \frac{4\pi}{9} \rho_0 c^2 R^3 (4 u^2 + 3) \beta^2 \Omega\ . \label{eq:E}
-\end{equation}
-In Equation \eqref{eq:E} the first term is the kinetic energy of the ejected mass $\Mej$, assumed to have already accelerated and adiabatically cooled to its coasting velocity.
-The second term is the kinetic and thermal energy of the shocked ISM with three-velocity $\beta = u / \gamma$.
-The shocked ISM is confined to a cone of solid angle $\Omega = 2 \sin^2 (\theta_0/2)$ where $\theta_0$ is the half-opening angle of the jet.
-While the blast wave is relativistic $\theta_0$ is constant, but once the jet becomes non-relativistic it begins to spread due to its own internal pressure until the blast wave is spherical.
-The spreading occurs at sound speed $c_s$ in the fluid rest-frame (CITE Hendrik 2010, Duffell+Laskar 2017):
-\begin{equation}
-	\dot{\theta_0} = \frac{c_s}{\gamma R}\ , \qquad \text{if } u < 1\text{ and } \theta_0 > \pi/2\ . \label{eq:thetadot}
-\end{equation}
-Given a (possibly constant) expression for $E$ Equation \eqref{eq:E} may be differentiated with respect to $t$ and solved for $\dot{u}$.
-In a refreshed shock scenario $E = E_{>}(u)$, whereas for a standard energy injection model one may take $E \propto t^{-q}$.
-In either case, Equation \eqref{eq:E} produces an equation for $\dot{u}$.
-This defines a three dimensional system of ordinary differential equations in the variables $(R, u, \theta_0)$.
-We solve this system using RK4 on a sequence of geometrically spaced values of $t$, typically $10^3$ points per decade.
-This produces a numerical table of $R(t)$, $u(t)$, and $\theta_0(t)$ in terms of the burster time $t$.
-The beginning and end points of the solution are chosen to encompass all required values of $\tobs$.
-
-Once the shock evolution is known, the flux is given by the integral:
-\begin{equation}
-	F_\nu(\tobs, \nuobs) = \frac{1}{4\pi \dL^2} \int \! \dd \Omega\ R^2\ \Delta R\  \delta^2\ \epsilon'_{\nu'} \ , \label{eq:flux}
-\end{equation}
-where $\tobs$ is the time in the observer's frame, $\nuobs$ the observational frequency, $\dL$ the luminosity distance, $\Delta R$ the shock width, $\delta$ the Doppler factor of the fluid, and $\epsilon'_{\nu'}$ the synchrotron emissivity in the fluid rest frame.
-The integral is taken in spherical polar coordinates $(\theta, \phi$) where $\theta = 0$ aligns with the jet axis and $\phi=0$ is directed towards the observer.
-The observer is at an angle $\thobs$ with the jet axis.
-The integrand is evaluated at a constant observer time $\tobs$, related to $t$ by:
-\begin{equation}
-	\tobs = t - \mu(\theta, \phi) R(t)/c\ , \label{eq:tobs}
-\end{equation}
-where 
-\begin{equation}
-	\mu = \cos \theta \cos \thobs + \sin \theta \sin \thobs \cos \phi\ . \label{eq:mu}
-\end{equation}
-The integral \eqref{eq:flux} is evaluated numerically using an adaptive Romberg integrator in each dimension, with a typical relative tolerances of $10^{-6}$.
-Each evaluation of the integrand requires a binary search to determine the burster time $t$ at which to evaluate $R$, $u$, and $\theta_0$.
-Fluid quantities are then calculated using the shock-jump conditions and the synchrotron emissivity is evaluated using the standard external shock formulae (CITE Hendrik, Granot+Sari).
-The numerical accuracy of a top-hat light curve with this scheme is typically better than $10^{-4}$.
-The structured jet calculation splits the integration domain into $N_\theta$ disjoint annuli, each evaluated as an independent top-hat and summed.
-By default $N_\theta$ is chosen such that there will be 5 zones per $\thC$-sized interval, giving final light curves with a numerical accuracy of $10^{-2}$.
-
-\subsection{\afterglowpy{}}
-
-We have constructed the \afterglowpy{} Python package to implement this algorithm and provide it to the community.
-The integration routine itself is written in C, wrapped as an extension for Python, and has been optimized to be used in intensive data analysis routines such as Markov Chain Monte-carlo which can require many thousands of evaluations.
-
-\afterglowpy{} uses a standard RK4 algorithm to evolve the $(R(t), u(t), \theta_0(t))$ system of equations on a fixed logarithmically spaced grid of $t$.
-The endpoints of the $t$-grid are chosen to bracket the burster frame times required to calculate the requested $\tobs$ with at least a decade of tolerance.
-Initial conditions for $R$, $u$, and $\theta_0$ are those of a decelerating ultra-relativistic blast wave.
-The user can set the density of the $t$-grid with the $n_t$ parameter: the number of grid points per decade of $t$.
-The default value for $n_t$ is 1000, which is sufficiently dense that the shock ODE evolution is not the dominant error source but not so dense as to adversely impact performance.
-
-Each top-hat jet component is integrated in $\theta$ and $\phi$ using an adaptive Romberg scheme with a fixed relative tolerance and an adaptive absolute tolerance.
-When summing over top-hat components of a structured jet, the innermost (core) component is calculated first.
-As the calculation proceeds, the current running sum of the flux is used to set absolute tolerance in the Romberg integrator for each component.
-This minimizes the computations performed on dim, off-axis sectors of the jet.
-
-The structured jet is split into concentric top-hat components with a density $n_\theta$ per $\thC$-sized interval.
-The choice of $n_\theta$ has the largest impact on the code performance and accuracy.
-We find the choice $n_\theta = 5$ gives sufficiently quick performance at acceptable errors, typically on the order of $10^{-2}$.
-TODO SHOW CONVERGENCE PLOT
-
-It should be noted all errors quoted here are numerical errors associated with the schemes used to solve Equations \ref{eq:Rdot}, \ref{eq:E}, and \ref{eq:thetadot} and perform the integral in Equation \ref{eq:flux}.
-That is, they are the errors relative to solving these equations perfectly.
-The equations themselves are, however, an approximation themselves to the full physics of an afterglow light curve.
-Comparison and calibration against analytic calculations and hydrodynamic simulations is necessary to ensure physically realistic results.
-
-\afterglowpy{} is available on PyPI and may be installed with {\tt pip}.  The source code is open and available at https://github.com/geoffryan/afterglowpy.
 
@@
 Figure \ref{fig:170817Alc} shows the observations in radio, optical, and x-ray bands of the GW170817A afterglow.
-No afterglow emission was detected until an x-ray detection by the Chandra observatory nine days after the GW trigger (CITE TrojaNature).
+No afterglow emission was detected until an x-ray detection by the Chandra observatory nine days after the GW trigger \cite{Troja:2017aa}.
 Further radio, optical, and x-ray observations showed a steady rising light curve with constant power law slope until a peak near day 160.
@@
 	\item The spectral slope $\beta = 0.585$ (CITE, +uncertainties) throughout the entire evolution, identifying the relevant spectral regime as G: $\nu_m < \nuobs < \nu_c$, and $p = 2.17$.
-	\item The initial rising ($\alpha < 0$) light curve with declining spectrum ($\beta > 0$) identify this as a \emph{misaligned} evolution ($\thobs > \thC$).
+	\item The initial rising ($\alpha > 0$) light curve with declining spectrum ($\beta < 0$) identify this as a \emph{misaligned} evolution ($\thobs > \thC$).
 Aligned jets may only have a rising light curve when viewed at frequencies below the peak frequency, that is when $\beta < 0$.
@@
 The full flux scaling equations also require an updated energy and circumburst density scaling.
-We can obtain the scalings for energy and density from dimensional analysis, following \cite{vanEertenMacFadyen2012} (specifically, by making use of the fact that the overall flux scalings for the different spectral regimes should obey those presented in table 1 of that paper).
+We can obtain the scalings for energy and density from dimensional analysis, following \cite{van-Eerten:2012ac} (specifically, by making use of the fact that the overall flux scalings for the different spectral regimes should obey those presented in table 1 of that paper).
 

### 2019-02-28 code/paperPlots.py

@@ -825,7 +825,7 @@ def getRegimePars(regime='D'):
     thC = 0.1
     thW = 0.4
     thV = 0.0
-    b = 4.0
+    b = 8.0
 
     p = 2.2
     epse_slow = 0.1
@@ -1215,12 +1215,14 @@ def calcSlopePost(jetModel, Y, regime):
 
 def makeAnalyticTestPlots():
 
-    regimes = ['D', 'E', 'F', 'G', 'H']
+    # regimes = ['D', 'E', 'F', 'G', 'H']
+    regimes = ['E', 'G', 'H']
     # regimes = ['D']
     jetModel = 4
     spread = False
 
-    thWs = [0.15, 0.25, 0.35, 0.45, 0.55, 0.65, 0.75, 0.85, 0.95]
+    # thWs = [0.15, 0.25, 0.35, 0.45, 0.55, 0.65, 0.75, 0.85, 0.95]
+    thWs = [0.25, 0.45, 0.65, 0.85]
     # thCs = [0.02, 0.04, 0.08, 0.12, 0.24, 0.48]
     if jetModel is 4:
         thCs = [0.02, 0.04, 0.08, 0.16]
@@ -1243,6 +1245,7 @@ def makeAnalyticTestPlots():
     alOffN = np.empty((NW, NV, NC))
     # alPreN = np.empty((NW, NV, NC))
     alStructN = np.empty((NW, NV, NC))
+    alStructN2 = np.empty((NW, NV, NC))
     alStructNAveLin = np.empty((NW, NV, NC))
     alStructNAveLog = np.empty((NW, NV, NC))
     alPostN = np.empty((NW, NV, NC))
@@ -1307,6 +1310,9 @@ def makeAnalyticTestPlots():
                                             spread=spread)
 
                     al = np.log(Fnutr/Fnutl) / np.log(tfac*tfac)
+                    al2 = np.log(Fnutr*Fnutl/(Fnu*Fnu)) / np.log(tfac)**2
+                    al3 = np.zeros(al.shape)
+                    al3[1:-1] = (al2[2:]-al2[:-2]) / np.log(tfac*tfac)
                     beta = np.log(Fnunr/Fnunl) / np.log(nufac*nufac)
 
                     if tW > 0.0:
@@ -1342,6 +1348,16 @@ def makeAnalyticTestPlots():
                     alStructNAveLin[k, j, i] = alNlin
                     alStructNAveLog[k, j, i] = alNlog
 
[…]

### 2019-03-05 structuredJets.tex
Updates, recovered from headless branch, moved methods section.

@@
 
-\section{Structured Jets}\label{sec:structuredJets}
+\section{Motivation: Why Structured Jets?}\label{sec:motivation}
 
@@
 
-In the ensuing discussion we often refer to sections of the blast wave surface by their angular coordinates $(\theta, \phi)$.
-These are the standard angles associated with a spherical polar coordinate system whose $z$-axis is oriented along the jet axis.
+%%%%%%%
+% METHODS
+%%%%%%%
+
+\section{Methods And The \afterglowpy{} Package}\label{sec:numerical}
+
+To compute the light curves of structured jet afterglows we constructed numerical and analytic models utilizing the single shell approximation of \cite{van-Eerten:2010aa, van-Eerten:2018ab}.
+This approach integrates over the massive ejecta, contact discontinuity, and forward shock complex, treating it as a single fluid element with uniform radial structure.
+We utilize a trans-relativistic equation of state which smoothly interpolates between the ultra-relativistic and non-relativistic limits and include an approximate prescription for jet spreading.
+This approach, with a simplified equation of state and jet spreading model, has been used successfully to model the synthetic light curves of top hat jets from multidimensional numerical relativistic hydrodynamics simulations \citep{van-Eerten:2010aa}.
+
+In the ultra-relativistic limit the single shell approximation provides useful scaling relations to compute the structured jet closure relations presented in Section \ref{sec:structuredjets}.
+The full trans-relativistic numerical model is publicly available as the \afterglowpy{} Python package, described in more detail in Section \ref{subsec:afterglowpy}.
+
+We utilize a standard spherical coordinate system $(r, \theta, \phi)$ with origin at the GRB central engine and polar axis aligned with the jet axis.
+The blast wave forward shock has a radial position $R(t, \theta)$, where $t$ is the time measured in the burster frame.
 The observer is located in a direction $\hat{\bf n}$ which makes an angle $\thobs$ with the $z$-axis, $\hat{\bf n} \cdot \hat{\bf z} = \cos \thobs$, and is oriented along the $x$-axis, $\phobs = 0$.
-A particular point on the blast wave $\hat{\bf r} = (\theta, \phi)$ makes an angle $\psi$ with the viewer, $\cos \psi = \hat{\bf n} \cdot \hat{\bf r}$.
-We denote the cosine of this angle as $\mu$, $\cos \psi = \mu$.
+A particular point on the blast wave $\hat{\bf r} = (\theta, \phi)$ makes an angle $\psi$ (with cosine $\mu$) with the viewer, $\mu = \cos \psi = \hat{\bf n} \cdot \hat{\bf r}$.
+
+\subsection{The Single Shell Approximation}\label{subsec:algo}
+
+The observed flux $F_\nu(\tobs, \nuobs)$ at observer time $\tobs$ and frequency $\nuobs$ is calculated via:
+\begin{equation}
+	F_\nu(\tobs, \nuobs) = \frac{1+z}{4\pi \dL^2} \int \! \dd \Omega\  \dd r\ r^2 \delta^2\ \epsilon'_{\nu'} \ , \label{eq:flux}
+\end{equation}
+where $z$ is the redshift of the source, $\dL$ is the luminosity distance, $\delta$ the doppler factor of the emitting fluid with respect to the observer, and $\epsilon'_{\nu'}$ the fluid rest-frame emissivity.
+
+To accommodate an initial structure profile $E(\theta)$ we consider the integrand of Equation \eqref{eq:flux} as a function of the polar angle $\theta$.
+We assume each constant $\theta$ annulus evolves independently, as an equivalent top hat of width $\thC = \theta$.
+This is a very good approximation when transverse velocities are low: when the blast wave is ultra-relativistic and has not begun to spread and when the blast wave is non-relativistic and the spreading has ceased \citep{van-Eerten:2010aa}.
+Once jet spreading begins in earnest the errors are larger, and this approach can be best viewed as an interpolation between the correct ultra-relativistic and non-relativistic limits \citep{van-Eerten:2010aa}.
+
+To compute the light curve of a top-hat jet of width $\theta$ we first must calculate the time evolution of the blast wave.
+In the single-shell approximation we treat the ejecta mass, contact discontinuity, and forward shock as a single unit propagating through a cold ambient medium with constant rest-mass density $\rho_0 = \Mp n_0$.
+The forward shock is a radius $R$ from the explosion and moves at a velocity $\beta_s$.
+In terms of the fluid four-velocity behind the shock $u$ and its Lorentz factor $\gamma$ this may be written as:
+\begin{equation}
+	\dot{R} = \frac{4 u \gamma}{4 u^2 +3}c\ . \label{eq:Rdot}
+\end{equation}
+Here the time derivative $\dot{R}$ is taken with respect to elapsed time in the bursters' frame $t$.
+
+ The evolution of the four velocity is determined through conservation of energy.  The total energy in the trans-relativistic single shell approximation is:
+\begin{equation}
+	E = (\gamma - 1)\Mej c^2 + \frac{4\pi}{9} \rho_0 c^2 R^3 (4 u^2 + 3) \beta^2 \Omega\ . \label{eq:E}
+\end{equation}
+In Equation \eqref{eq:E} the first term is the kinetic energy of the ejected mass $\Mej$, assumed to have already accelerated and adiabatically cooled to its coasting velocity.
+The second term is the kinetic and thermal energy of the shocked ISM with three-velocity $\beta = u / \gamma$.
+The shocked ISM is confined to a cone of solid angle $\Omega = 2 \sin^2 (\theta_0/2)$ where $\theta_0$ is the half-opening angle of the jet.
+While the blast wave is relativistic $\theta_0$ is constant, but once the jet becomes non-relativistic it begins to spread due to its own internal pressure until the blast wave is spherical.
+The spreading occurs at sound speed $c_s$ in the fluid rest-frame \citep{van-Eerten:2010aa, Duffell:2018aa}:
+\begin{equation}
+	\dot{\theta_0} = \frac{c_s}{\gamma R}\ , \qquad \text{if } u < 1\text{ and } \theta_0 > \pi/2\ . \label{eq:thetadot}
+\end{equation}
+Given a (possibly constant) expression for $E$ Equation \eqref{eq:E} may be differentiated with respect to $t$ and solved for $\dot{u}$.
+In a refreshed shock scenario $E = E_{>}(u)$, whereas for a standard energy injection model one may take $E \propto t^{-q}$.
+In either case, Equation \eqref{eq:E} produces an equation for $\dot{u}$.
+This defines a three dimensional system of ordinary differential equations in the variables $(R, u, \theta_0)$ which may be solved numerically or, in certain limits, analytically.
+
+Once the shock evolution is known, the flux is given by the integral:
+\begin{equation}
+	F_\nu(\tobs, \nuobs) = \frac{1+z}{4\pi \dL^2} \int \! \dd \Omega\ R^2\ \Delta R\  \delta^2\ \epsilon'_{\nu'} \ , \label{eq:flux2}
+\end{equation}
+where $\Delta R$ is the shock width contributing to the emission. The integrand is evaluated at a constant observer time $\tobs$ and observer frequency $\nuobs$, related to $t$ and $\nu'$ by:
+\begin{align}
+	\tobs &= (1+z) \left(t - \mu(\theta, \phi) R(t)/c\right)\ , \label{eq:tobs} \\
+	\nuobs &= (1+z)^{-1} \delta \nu' , \label{eq:nuobs}
+\end{align}
+
+The integral \eqref{eq:flux2} may now be computed numerically or, in certain limits, analytically.
+
+\subsection{\afterglowpy{}} \label{subsec:afterglowpy}
+
+The integral \eqref{eq:flux2} is evaluated numerically using an adaptive Romberg integrator in each dimension, with a typical relative tolerances of $10^{-6}$.
+
+We have constructed the \afterglowpy{} Python package to implement the numerical computation of light curves according to Section \ref{subsec:algpo} and provide it to the community.
+The integration routine itself is written in C, wrapped as an extension for Python, and has been optimized to be used in intensive data analysis routines such as Markov Chain Monte-carlo which can require many thousands of evaluations.
+
+\afterglowpy{} uses a standard RK4 algorithm to evolve the $(R(t), u(t), \theta_0(t))$ system of equations on a fixed logarithmically spaced grid of $t$.
+The endpoints of the $t$-grid are chosen to bracket the burster frame times required to calculate the requested $\tobs$ with at least a decade of tolerance.
+Initial conditions for $R$, $u$, and $\theta_0$ are those of a decelerating ultra-relativistic blast wave.
+The user can set the density of the $t$-grid with the $n_t$ parameter: the number of grid points per decade of $t$.
+The default value for $n_t$ is 1000, which is sufficiently dense that the shock ODE evolution is not the dominant error source but not so dense as to adversely impact performance.
+
+Each top-hat jet component is integrated in $\theta$ and $\phi$ using an adaptive Romberg scheme with a fixed relative tolerance and an adaptive absolute tolerance.
+When summing over top-hat components of a structured jet, the innermost (core) component is calculated first.
+As the calculation proceeds, the current running sum of the flux is used to set absolute tolerance in the Romberg integrator for each component.
+This minimizes the computations performed on dim, off-axis sectors of the jet.
+
+Each evaluation of the integrand requires a binary search to determine the burster time $t$ at which to evaluate $R$, $u$, and $\theta_0$.
+Fluid quantities are then calculated using the shock-jump conditions and the synchrotron emissivity is evaluated using the standard external shock formulae \citep{Granot:2002aa,van-Eerten:2010aa}.
+
+The numerical accuracy of a top-hat light curve with this scheme is typically better than $10^{-4}$.
+The structured jet calculation splits the integration domain into $N_\theta$ disjoint annuli, each evaluated as an independent top-hat and summed.
+By default $N_\theta$ is chosen such that there will be 5 zones per $\thC$-sized interval.
+The choice of $N_\theta$ has the largest impact on the code performance and accuracy.
+We find the choice $N_\theta = 5$ gives sufficiently quick performance at acceptable errors, typically on the order of $10^{-2}$.
+TODO SHOW CONVERGENCE PLOT
+
+It should be noted all errors quoted here are numerical errors associated with the schemes used to solve Equations \ref{eq:Rdot}, \ref{eq:E}, and \ref{eq:thetadot} and perform the integral in Equation \ref{eq:flux2}.
+That is, they are the errors relative to solving these equations perfectly.
+The equations themselves are, however, an approximation themselves to the full physics of an afterglow light curve.
+Comparison and calibration against analytic calculations and hydrodynamic simulations is necessary to ensure physically realistic results.
+
+\afterglowpy{} is available on PyPI and may be installed with {\tt pip}.  The source code is open and available at https://github.com/geoffryan/afterglowpy.
+
+\section{Structured Jet Light Curves}\label{sec:structuredJets}
 
@@
 The part of the blast wave dominating the emission tracks from the high latitude wings $\theta \approx \thW$ to the core $\theta \approx 0$.
-The angular size of the visible patch grows approximately as $\gamma^{-1.5}$.
+The angular size of the visible patch grows approximately as $\gamma^{-1.0}$.
 (NEED PLOT?)
@@
 \section{Discussion}
+
+\section{Summary}
 

### 2019-03-05 structuredJets.tex
Minor typos fixed

@@
 
-In the ultra-relativistic limit the single shell approximation provides useful scaling relations to compute the structured jet closure relations presented in Section \ref{sec:structuredjets}.
+In the ultra-relativistic limit the single shell approximation provides useful scaling relations to compute the structured jet closure relations presented in Section \ref{sec:structuredJets}.
 The full trans-relativistic numerical model is publicly available as the \afterglowpy{} Python package, described in more detail in Section \ref{subsec:afterglowpy}.
@@
 \end{equation}
-where $\Delta R$ is the shock width contributing to the emission. The integrand is evaluated at a constant observer time $\tobs$ and observer frequency $\nuobs$, related to $t$ and $\nu'$ by:
+where $\Delta R$ (TODO: add eq for Delta R) is the shock width contributing to the emission.
+The integrand is evaluated at a constant observer time $\tobs$ and observer frequency $\nuobs$, related to $t$ and $\nu'$ by:
 \begin{align}
@@
 \end{align}
+
+TODO: Give formulae or reference for $\epsilon'_{\nu'}$.
 

### 2019-03-26 structuredJets.tex
Added first tb figure.

@@
 
-The transition between phases of evolution depends on the effective solid angle $\Delta \Omega$ of the patch of blast wave dominating the emission.
-The size of this patch scales with the Lorentz factor $\gamma$ of the dominant region as:
+To fully characterize the light curves of structured jets we use \afterglowpy{} to construct light curves exploring dependence on jet structure model, viewing angle $\thobs$, opening angle $\thC$, and synchrotron regime.
+
+We find the light curves of structured jets show two modes of behaviour, depending on whether the observer is \emph{aligned} ($\thobs < \thC$) or misaligned ($\thobs > \thC$).
+In the \emph{aligned} case, the light curves follow the standard on-axis top hat behaviour modified slightly for non-zero viewing angle.
+There is little to distinguish between different structure $E(\theta)$, and the light curve is well-approximated by a broken power law with characteristic break times.
+The \emph{misaligned} light curve also may present as a broken power law, but with closure relations explicitly dependent on viewing angle and jet angular structure.
+
+We discuss aligned evolution in detail in Section \ref{subsec:aligned} and misaligned in Section \ref{subsec:misaligned}.
+In both cases the transition between phases of evolution depends on the effective solid angle $\Delta \Omega$ of the patch of blast wave dominating the emission.
+The size of this patch tends to scale with the Lorentz factor $\gamma$ of the dominant region as:
 \begin{equation}
@@
 
-\subsection{Aligned Evolution: $\thobs \lesssim \thC$}
+\subsection{Aligned Evolution: $\thobs \lesssim \thC$} \label{subsec:aligned}
 
@@
 
-The transition phase occurs at $\tbm$ and completes at $\tbp$, given in the single shell approximation (see Appendix \ref{sec:derive1}) by:
+The transition between pre-jet break and post-jet break begins at $\tbm$ and completes at $\tbp$, given in the single shell approximation (see Appendix \ref{sec:derive1}) by:
 \begin{align}
@@
 \end{align}
+\begin{figure}
+	\plotone{figs/breaks_alignedOA_all.pdf}
+	\caption{Jet break time for on-axis ($\thobs=0$) observers for top-hat (blue circles), Gaussian (orange inverted triangles), and power law (green triangles) jets as a function of $\thC$.
+The dashed grey line is the analytic approximation $t_b = t_N \thC^{8/3}$.
+These particular light curves use $\thW = 5 \thC$, $E_0 = 10^{52}$erg, $n_0=10^{-3}$cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, and $\epsB = 10^{-4}$.
+\label{fig:tbOA}}
+\end{figure}
 
@@
 
-\subsection{Misaligned Evolution: $\thobs \gtrsim \thC$}
+\subsection{Misaligned Evolution: $\thobs \gtrsim \thC$}\ref{subsec:misaligned}
 
@@
 
+\begin{itemize}
+	\item Comparison with boxfit
+	\item Comparison with other GW170817A fits
+	\item Degeneracy between $E(\theta)$ and $\thobs$
+	\item $g$ vs $\thobs / \thC$ plot with GW170817
+	\item Looking forward to O3
+\end{itemize}
+
 \section{Summary}

### 2019-03-26 code/tbScalings.py

@@ -1,0 +1,763 @@
+import math
+import numpy as np
+import scipy.optimize as opt
+import matplotlib.pyplot as plt
+import grbpy as grb
+
+
+def slopeSpec(p, regime='G'):
+    if regime is 'D':
+        return 1.0/3.0
+    elif regime is 'E':
+        return 1.0/3.0
+    elif regime is 'F':
+        return -0.5
+    elif regime is 'G':
+        return 0.5*(1-p)
+    else:
+        return -0.5*p
+
+
+def slopePre(p, regime='G'):
+    if regime is 'D':
+        return 0.5
+    elif regime is 'E':
+        return 1.0/6.0
+    elif regime is 'F':
+        return -0.25
+    elif regime is 'G':
+        return 0.75*(1-p)
+    else:
+        return 0.25*(2-3*p)
+
+
+def slopePost(p, regime='G'):
+    if regime is 'D':
+        return -0.25
+    elif regime is 'E':
+        return -7.0/12.0
+    elif regime is 'F':
+        return -1.0
+    elif regime is 'G':
+        return -0.75*p
+    else:
+        return -0.25*(1+3*p)
+
+
+def f_pl(t, a, b):
+    return a * np.power(t, b)
+
+
+def f_pl2(t, F0, t0, b0, b1):
+    F = np.empty(t.shape)
+    A = t <= t0
+    B = ~A
+    F[A] = F0*np.power(t[A]/t0, b0)
+    F[B] = F0*np.power(t[B]/t0, b1)
+    return F
+
+
+def f_pl3(t, F0, t0, t1, b0, b1, b2):
+    F = np.empty(t.shape)
+    A = t <= t0
+    B = (t > t0) & (t <= t1)
+    C = t > t1
+    F[A] = F0*np.power(t[A]/t0, b0)
+    F[B] = F0*np.power(t[B]/t0, b1)
+    F[C] = F0*math.pow(t1/t0, b1) * np.power(t[C]/t1, b2)
+    return F
+
+
+def chi2(x, t, F, f):
+    y = x.copy()
+    if len(x) is 4:
+        y[0:2] = np.power(10.0, x[0:2])
+    elif len(x) is 6:
+        y[0:3] = np.power(10.0, x[0:3])
+    Fm = f(t, *y)
+    dF = (F-Fm)/(0.1*F)
+    return (dF*dF).sum()
+
+
[…]

### 2019-03-26 structuredJets.tex
modified figure

@@
 
-We find the light curves of structured jets show two modes of behaviour, depending on whether the observer is \emph{aligned} ($\thobs < \thC$) or misaligned ($\thobs > \thC$).
+We find the light curves of structured jets show two modes of behaviour, depending on whether the observer is \emph{aligned} ($\thobs < \thC$) or \emph{misaligned} ($\thobs > \thC$).
 In the \emph{aligned} case, the light curves follow the standard on-axis top hat behaviour modified slightly for non-zero viewing angle.
@@
 	\plotone{figs/breaks_alignedOA_all.pdf}
-	\caption{Jet break time for on-axis ($\thobs=0$) observers for top-hat (blue circles), Gaussian (orange inverted triangles), and power law (green triangles) jets as a function of $\thC$.
-The dashed grey line is the analytic approximation $t_b = t_N \thC^{8/3}$.
+	\caption{Jet break time for on-axis ($\thobs=0$) observers for top-hat (blue circles), Gaussian (orange squares), and power law (green triangles) jets as a function of $\thC$.
+The dashed grey line is the analytic approximation $\tbpm = t_N (2\sin \thC/2)^{8/3}$.
 These particular light curves use $\thW = 5 \thC$, $E_0 = 10^{52}$erg, $n_0=10^{-3}$cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, and $\epsB = 10^{-4}$.
@@
 The jet break occurs, in all jets, when the effective angular size of the visible patch of the jet ceases to increase, that is when $\som = 0$.
+
+Figure \ref{fig:tbOA} shows the jet break time for on-axis ($\thobs = 0$) viewers as a function of $\thC$ for top-hat, Gaussian, and power law jets calculated with \afterglowpy{}.
+Break times were extracted by fitting the numerical light curve with a two-component broken power law.
 
@@
 
-\subsection{Misaligned Evolution: $\thobs \gtrsim \thC$}\ref{subsec:misaligned}
+\subsection{Misaligned Evolution: $\thobs \gtrsim \thC$} \label{subsec:misaligned}
 

### 2019-03-26 code/tbScalings.py

@@ -425,7 +425,7 @@ def makeOnAPlot():
 
     fig, ax = plt.subplots(1, 1)
     ax.plot(thCs, tbTH/tN, marker='o', ls='')
-    ax.plot(thCs, tbG/tN, marker='v', ls='')
+    ax.plot(thCs, tbG/tN, marker='s', ls='')
     ax.plot(thCs, tbPL/tN, marker='^', ls='')
     ax.plot(thCs, np.power(2*np.sin(0.5*thCs), 8./3.), lw=4, ls='--',
             color='grey')

### 2019-04-11 structuredJets.tex
updates

@@
 \newcommand{\afterglowpy}{{\tt afterglowpy}}
+\newcommand{\boxfit}{{\tt BoxFit}}
 \newcommand{\python}{\tt{Python}}
@@
 \end{abstract}
-
-\section{outline}
-
-\begin{itemize}
-	\item Need to consider the \emph{structure} of GRB explosions (esp.
-binary neutron stars).
-Structure may be radial (velocity stratification, $E(u)$) or angular ($E(\theta)$).
-Both modes affect the afterglow.
-	\item Analytic description: \begin{itemize}
-		\item Velocity stratification / refreshed shock / cocoon leads to simple power law behaviour depending on $k$ ($E_{>u} \propto u^{-k}$).
-Breaks occur at deceleration time and when $E_{>u}$ shuts off.
-		\item Angular structure / structured jet leads to not-quite power law behaviour, depending on $g \approx (\thobs - \theta)d \log E / d\theta$.
-Breaks occur when $\thobs - \thW \approx 1/\gamma(\thW)$ and $\thobs \approx 1/\gamma(0)$.
-$g = g(\theta)$, but $g\approx g_{eff}$ where $g_{eff} = g(\thobs/2)$.
-		\end{itemize}
-	\item Numerical description: \begin{itemize}
-		\item Single-shell ODE for shock evolution
-		\item Integrate over equal-$\tobs$ surfaces
-		\item Structured components independent.
-		\item public and open: install with \tt{pip}.
-		\end{itemize}
-	\item GW170817A - Both models are similar, fit GW170817A well!
-	\item Future observations: Rate of observed counter-parts will depend on degree of collimation of afterglow (jets have lower observed rates than cocoons).
-Radial structure may have $k$ vary from object to object.
-Angular structure WILL have $g$ vary from object to object.
-	\item Can we determine structure from the afterglow???
-\end{itemize}
 
@@
 The shocked ISM is confined to a cone of solid angle $\Omega = 2 \sin^2 (\theta_0/2)$ where $\theta_0$ is the half-opening angle of the jet.
-While the blast wave is relativistic $\theta_0$ is constant, but once the jet becomes non-relativistic it begins to spread due to its own internal pressure until the blast wave is spherical.
+While the blast wave is relativistic $\theta_0$ is constant, but once the jet edge comes in causal contact with the core it begins to spread due to its own internal pressure until the blast wave is spherical.
 The spreading occurs at sound speed $c_s$ in the fluid rest-frame \citep{van-Eerten:2010aa, Duffell:2018aa}:
 \begin{equation}
-	\dot{\theta_0} = \frac{c_s}{\gamma R}\ , \qquad \text{if } u < 1\text{ and } \theta_0 > \pi/2\ . \label{eq:thetadot}
+	\dot{\theta_0} = \frac{c_s}{\gamma R}\ , \qquad \text{if } u < 3/\theta_0 \text{ and } \theta_0 > \pi/2\ . \label{eq:thetadot}
 \end{equation}
+The criterion $u < 3/\theta_0$ is satisfied when enough time has elapsed that a sound wave can propagate from $\theta = \theta_0$ to $\theta=0$ in a blast wave propagating in an ISM (CITE HENDRIK).
+It is similar to the condition given in \cite{Duffell:2018aa}, which found a numerical factor of 2.5 (instead of 3) after calibrating to numerical simulations.
+Our criteria differs from that used in (CITE Troja+) which used an overly simplistic $u < 1$ criterion to begin jet spreading.
+
 Given a (possibly constant) expression for $E$ Equation \eqref{eq:E} may be differentiated with respect to $t$ and solved for $\dot{u}$.
@@
 
-It should be noted all errors quoted here are numerical errors associated with the schemes used to solve Equations \ref{eq:Rdot}, \ref{eq:E}, and \ref{eq:thetadot} and perform the integral in Equation \ref{eq:flux2}.
+These errors quoted are numerical errors associated with the schemes used to solve Equations \ref{eq:Rdot}, \ref{eq:E}, and \ref{eq:thetadot} and perform the integral in Equation \ref{eq:flux2}.
 That is, they are the errors relative to solving these equations perfectly.
@@
 Comparison and calibration against analytic calculations and hydrodynamic simulations is necessary to ensure physically realistic results.
+
+\begin{figure*}
+	\plotone{figs/boxfit_comp.pdf}
+	\caption{Top Panel: Comparison between top hat jet light curves from \afterglowpy{} (solid lines) and \boxfit{} (dashed lines).
+Bottom Panel: fraction difference between \afterglowpy{} and \boxfit{} light curves.
+Four representative light curves are shown: radio on-axis ($\thobs=0$, $\nu=10^9$Hz, blue), radio off-axis ($\thobs=0.16$rad, $\nu=10^9$Hz, orange), x-ray on-axis ($\thobs=0$, $\nu=10^{18}$Hz, green), and x-ray off-axis ($\thobs=0.16$rad, $\nu=10^{18}$Hz, red).
+Remaining parameters are shared: $\thC=0.1$rad, $\Eiso=10^{52}$erg, $\Eiso=10^{52}$erg, $n_0 = 10^{-3}$cm$^{-3}$, $p=2.2$, $\epse=10^{-1}$, $\epsB=10^{-2}$, $\dL=3.09 \times 10^{26}$cm, $z=0.028$.
+\label{fig:boxfitComp}}
+\end{figure*}
+
+Figure \ref{fig:boxfitComp} shows a comparison between top-hat light curves calculated with \afterglowpy{} and \boxfit{}.
+The \boxfit{} code uses two-dimensional relativistic hydrodynamic simulations to fully capture the non-linear hydrodynamics of a decelerating blast wave and a ray tracing radiative transfer module to compute observed synchrotron light curves.
+Figure \ref{fig:boxfitComp} shows the light curve of a $\thC=0.1$rad top-hat at radio and x-ray frequencies ($10^9$Hz and $10^{18}$Hz, respectively) with aligned ($\thobs = 0$) and misaligned ($\thobs=0.16$rad) viewing angles.
+The overall agreement is good: \afterglowpy{} captures the salient features of both aligned and misaligned light curves including the jet break, spectral shape, and transition to the Sedov phase.
+The relative error is less than 50\% before the onset of spreading.
 
@@
 	\item The combined measurements of $\thobs$ and $\thobs/\thC$ then imply $\thC \approx 0.09 \pm 0.04$ rad ($5^\circ  \pm 2^\circ$).
+\end{enumerate}
 
-\end{enumerate}
+Bayesian parameter estimation utilizing \afterglowpy{} and a Markov chain Monte Carlo sampler was performed in \cite{van-eerten:2018aa}.
+The conclusions were very similar to the above analytic estimates, inferring for a Gaussian jet model $\thobs = 0.52\pm0.16$ and $\thC=0.08\pm0.02$.
+Incorporating the LIGO posterior for $\thobs$, assuming the Planck value for $H_0$, tightens the constraints to $\thobs = 0.38\pm0.11$ and $\thC=0.06\pm0.02$.
+Utilizing the full numerical \afterglowpy{} model allows $E_0$, $n_0$, $p$, $\epse$, and $\epsB$ to also be inferred, although given the lack of observed spectral features in the GW170817 afterglow the resulting constraints are quite broad.
 
@@
 \begin{itemize}
-	\item Comparison with boxfit
 	\item Comparison with other GW170817A fits
@@
 \end{itemize}
+
+Many groups have used structured jet models to analyze the afterglow of GW170817A \citep{Mooley:2018ab, Ghirlanda:2019aa, Lamb:2019aa, Wu:2018aa}.
 

### 2019-04-11 code/tbScalings.py

@@ -95,12 +95,18 @@ def fit_pl(t, F, printOutput=False):
     return res.x, res.fun, 2
 
 
-def fit_pl2(t, F, printOutput=False):
+def fit_pl2(t, F, tN, thV, thC, printOutput=False):
 
-    N = len(t)
-    b0 = np.log(F[-1]/F[0]) / np.log(t[-1]/t[0])
-    t0 = t[N//2]
-    F0 = F[N//2]
+    tbp = tN * np.power(2*np.sin(0.5*np.fabs(thV+thC)), 8.0/3.0)
+
+    try:
+        ip = np.argwhere(t > tbp)[0]
+    except IndexError:
+        ip = len(t)//2
+    b0 = np.log(F[ip]/F[0]) / np.log(t[ip]/t[0])
+    b1 = np.log(F[-1]/F[ip]) / np.log(t[-1]/t[ip])
+    t0 = t[ip]
+    F0 = F[ip]
 
     bounds = [(math.log10(F.min())-1, math.log10(F.max())+1),
               (math.log10(t.min()), math.log10(t.max())),
@@ -110,7 +116,7 @@ def fit_pl2(t, F, printOutput=False):
     lt0 = math.log10(t0)
 
     print("chi2(x0) = {0:.3e}".format(
-          chi2([lF0, lt0, b0, b0], t, F, f_pl2)))
+          chi2([lF0, lt0, b0, b1], t, F, f_pl2)))
 
     res = opt.minimize(chi2, [lF0, lt0, b0, b0], (t, F, f_pl2),
                        bounds=bounds, method='TNC',
@@ -126,17 +132,31 @@ def fit_pl2(t, F, printOutput=False):
     return y, res.fun, 4
 
 
-def fit_pl3(t, F, printOutput=False):
+def fit_pl3(t, F, tN, thV, thC, printOutput=False):
 
-    N = len(t)
-    b0 = np.log(F[-1]/F[0]) / np.log(t[-1]/t[0])
-    t0 = t[N//3]
-    t1 = t[(2*N)//3]
-    F0 = F[N//3]
+    tbm = tN * np.power(2*np.sin(0.5*np.fabs(thV-thC)), 8.0/3.0)
+    tbp = tN * np.power(2*np.sin(0.5*np.fabs(thV+thC)), 8.0/3.0)
 
-    lF0 = math.log10(F0)
-    lt0 = math.log10(t0)-0.1
-    lt1 = math.log10(t1)+0.1
[…]

### 2019-05-06 structuredJets.tex
Added MCMC discussion.

--- 2019-03-26 structuredJets.tex
@@
 
+\usepackage{natbib}
 \usepackage{amsmath}
@@
 
-\newcommand{\gwbns}{GW170817}
+\newcommand{\gwbns}{GW170817A}
 \newcommand{\afterglowpy}{{\tt afterglowpy}}
-\newcommand{\python}{\tt{Python}}
+\newcommand{\boxfit}{{\tt BoxFit}}
+\newcommand{\python}{{\tt Python}}
+\newcommand{\emcee}{{\tt emcee}}
+
+\newcommand{\hubble}{{\em Hubble Space Telescope}}
+\newcommand{\planck}{{\em Planck}}
 
@@
 \newcommand{\Eiso}{\ensuremath{E_{\mathrm{iso}}}}
+\newcommand{\Etot}{\ensuremath{E_{\mathrm{tot}}}}
 \newcommand{\geff}{\ensuremath{g_{\mathrm{eff}}}}
@@
 	Gamma-ray bursts (GRBs) associated with gravitational wave events are, and will likely continue to be, viewed at a larger inclination than their fellow GRBs without gravitational wave detections.
-As demonstrated by the afterglow of GW170817A, this requires an extension of the common GRB afterglow models which typically assume emission from an on-axis top hat jet.
+As demonstrated by the afterglow of \gwbns{}, this requires an extension of the common GRB afterglow models which typically assume emission from an on-axis top hat jet.
 We present a characterization of the afterglows arising from structured jets, utilizing both trans-relativistic numerical calculations and simple analytic approximations.
@@
 
-GW170817 changes the picture: new object with a strange afterglow.
+\gwbns{} changes the picture: new object with a strange afterglow.
 Steep/late rise, LONG slow rise, turnover at 160d.
@@
 The dominant contribution may be an angular distribution of energy within the blast wave (``structured jet'') combined with off-axis viewing (CITE Rossi04).
-For 170817 this corresponds to the ``successful jet'' picture.
+For \gwbns{} this corresponds to the ``successful jet'' picture.
 Alternately, radial stratification of velocity (``refreshed shock'') can cause a similar phase, most simply with a quasi-spherical (or at least top-hat) angular structure.
-This situation is produced by the ``choked jet''  or ``cocoon'' picture of 170817.
+This situation is produced by the ``choked jet''  or ``cocoon'' picture of \gwbns{}.
 Understanding the effects of both structures on afterglows, and their dependence on the parameters of the burst, are vital to understanding GW counterparts.
@@
 
-Summary: In section 2 we discuss structured jets, in section 3 refreshed shocks, in section 4 our numerical model, section 5 application to GW170817, and section 6 future applications and discussion.
+Summary: In section 2 we discuss structured jets, in section 3 refreshed shocks, in section 4 our numerical model, section 5 application to \gwbns{}, and section 6 future applications and discussion.
 
@@
 The shocked ISM is confined to a cone of solid angle $\Omega = 2 \sin^2 (\theta_0/2)$ where $\theta_0$ is the half-opening angle of the jet.
-While the blast wave is relativistic $\theta_0$ is constant, but once the jet becomes non-relativistic it begins to spread due to its own internal pressure until the blast wave is spherical.
+While the blast wave is relativistic $\theta_0$ is constant, but once the jet edge comes in causal contact with the core it begins to spread due to its own internal pressure until the blast wave is spherical.
 The spreading occurs at sound speed $c_s$ in the fluid rest-frame \citep{van-Eerten:2010aa, Duffell:2018aa}:
 \begin{equation}
-	\dot{\theta_0} = \frac{c_s}{\gamma R}\ , \qquad \text{if } u < 1\text{ and } \theta_0 > \pi/2\ . \label{eq:thetadot}
+	\dot{\theta_0} = \frac{c_s}{\gamma R}\ , \qquad \text{if } u < 1/3\thC \text{ and } \theta_0 > \pi/2\ . \label{eq:thetadot}
 \end{equation}
+The criterion $u < 1/3\theta_0$ is satisfied when enough time has elapsed that a sound wave can propagate from $\theta = \thC$ to $\theta=0$ in a blast wave propagating in a uniform ISM (CITE HENDRIK).
+It is similar to the condition given in \cite{Duffell:2018aa}, which found a numerical factor of 2.5 (instead of 3) after calibrating to numerical simulations.
+Our criteria differs from that used in (CITE Troja+) which used an overly simplistic $u < 1$ criterion to begin jet spreading.
+
 Given a (possibly constant) expression for $E$ Equation \eqref{eq:E} may be differentiated with respect to $t$ and solved for $\dot{u}$.
@@
 
-We have constructed the \afterglowpy{} Python package to implement the numerical computation of light curves according to Section \ref{subsec:algpo} and provide it to the community.
+We have constructed the \afterglowpy{} Python package to implement the numerical computation of light curves according to Section \ref{subsec:algo} and provide it to the community.
 The integration routine itself is written in C, wrapped as an extension for Python, and has been optimized to be used in intensive data analysis routines such as Markov Chain Monte-carlo which can require many thousands of evaluations.
@@
 
-It should be noted all errors quoted here are numerical errors associated with the schemes used to solve Equations \ref{eq:Rdot}, \ref{eq:E}, and \ref{eq:thetadot} and perform the integral in Equation \ref{eq:flux2}.
+\subsection{Comparison To \boxfit{}} \label{subsec:boxfitcomp}
+
+\afterglowpy{}, in utilizing the semi-analytic methods of Section \ref{subsec:algo}, trades some amount of physical accuracy for great flexibility.
+We gauge this trade-off by comparing to the \boxfit{} code, a standard tool which calculates high fidelity afterglow light curves based on numerical simulations.
+
+%These errors quoted are numerical errors associated with the schemes used to solve Equations \ref{eq:Rdot}, \ref{eq:E}, and \ref{eq:thetadot} and perform the integral in Equation \ref{eq:flux2}.
 That is, they are the errors relative to solving these equations perfectly.
@@
 Comparison and calibration against analytic calculations and hydrodynamic simulations is necessary to ensure physically realistic results.
+%
+%\begin{figure*}
+%	\plotone{figs/boxfit_comp.pdf}
+%	\caption{Top Panel: Comparison between top hat jet light curves from \afterglowpy{} (solid lines) and \boxfit{} (dashed lines).
+Bottom Panel: fraction difference between \afterglowpy{} and \boxfit{} light curves.
+Four representative light curves are shown: radio on-axis ($\thobs=0$, $\nu=10^9$Hz, blue), radio off-axis ($\thobs=0.16$rad, $\nu=10^9$Hz, orange), x-ray on-axis ($\thobs=0$, $\nu=10^{18}$Hz, green), and x-ray off-axis ($\thobs=0.16$rad, $\nu=10^{18}$Hz, red).
+Remaining parameters are shared: $\thC=0.1$rad, $\Eiso=10^{52}$erg, $\Eiso=10^{52}$erg, $n_0 = 10^{-3}$cm$^{-3}$, $p=2.2$, $\epse=10^{-1}$, $\epsB=10^{-2}$, $\dL=3.09 \times 10^{26}$cm, $z=0.028$.
+\label{fig:boxfitComp}}
+%\end{figure*}
+%
+%Figure \ref{fig:boxfitComp} shows a comparison between top-hat light curves calculated with \afterglowpy{} and \boxfit{}.
+The \boxfit{} code uses two-dimensional relativistic hydrodynamic simulations to fully capture the non-linear hydrodynamics of a decelerating blast wave and a ray tracing radiative transfer module to compute observed synchrotron light curves.
+Figure \ref{fig:boxfitComp} shows the light curve of a $\thC=0.1$rad top-hat at radio and x-ray frequencies ($10^9$Hz and $10^{18}$Hz, respectively) with aligned ($\thobs = 0$) and misaligned ($\thobs=0.16$rad) viewing angles.
+The overall agreement is good: \afterglowpy{} captures the salient features of both aligned and misaligned light curves including the jet break, spectral shape, and transition to the Sedov phase.
+The relative error is less than 50\% before the onset of spreading.
 
@@
 In either case, slow material initially coasting behind the shock is gradually incorporated into the blast wave as it decelerates, ``refreshing'' the shock.
-This mechanism was first proposed as an energy injection scenario (CITE), and was proposed as the mechanism behind the GW170817 afterglow in the choked-jet scenario.
+This mechanism was first proposed as an energy injection scenario (CITE), and was proposed as the mechanism behind the \gwbns{} afterglow in the choked-jet scenario.
 (CITE Mooley, Hotokezaka, etc).
@@
 
-\section{Application: GW170817A}
+\section{Application: \gwbns{}}
 
-We use the electromagnetic afterglow of GW170817A (GRB170817A?) as an example application of both the analytic and numerical structured jet afterglow models.
+We use the electromagnetic afterglow of \gwbns{} as an example application of both the analytic and numerical structured jet afterglow models.
 
-Figure \ref{fig:170817Alc} shows the observations in radio, optical, and x-ray bands of the GW170817A afterglow.
+Figure \ref{fig:170817Alc} shows the observations in radio, optical, and x-ray bands of the \gwbns{} afterglow.
 No afterglow emission was detected until an x-ray detection by the Chandra observatory nine days after the GW trigger \cite{Troja:2017aa}.
@@
 	\item The combined measurements of $\thobs$ and $\thobs/\thC$ then imply $\thC \approx 0.09 \pm 0.04$ rad ($5^\circ  \pm 2^\circ$).
+\end{enumerate}
 
-\end{enumerate}
+For a more detailed analysis we performed Bayesian parameter estimation utilizing \afterglowpy{} and the \emcee{} Markov chain Monte Carlo sampler \citep{Foreman-Mackey:2013aa}.
+We used the light curve data reported in \citet{van-Eerten:2018aa} with additional \hubble{} observations reported in \citet{Lamb:2019aa}.
+Reported measurement uncertainties were assumed to be independ
+ent and Gaussian, upper limits were treated as observations of zero flux with a 1-sigma Gaussian uncertainty.
+
+We fit both the Gaussian and power law structured jet models, fixing $\xi_N = 1$ and $\dL = 1.23 \times 10^{26}$cm.
+The fit parameters, their priors, and their marginalized posteriors are given in Table \ref{tab:MCMC}.
+Both models were run with 300 walkers for 64 000 iterations, discarding the first 16 000 iterations as a burn-in.
+The viewing angle prior is the posterior found in analysis of the \gwbns{} gravitational wave signal assuming the value of $H_0$ reported by the \planck{} collaboration \citep{Abbott:2017aa, Planck-Collaboration:2016aa, Troja:2018aa}.
+
+\begin{deluxetable*}{CCCCCC}
+	\tablecaption{Parameter estimation priors and marginalized posteriors for the \gwbns{} afterglow using the \afterglowpy{} Gaussian and power law jet models, including viewing angle constraints from LIGO assuming the \planck{} value of $H_0$.
+Given posterior values for each model are the median, 16\%, and 84\% quantiles.
+Parameters in the lower section are derived from the posterior distributions of the fit parameters in the upper sections.
+\label{tab:MCMC}}
+	\tablehead{\colhead{Parameter}& \colhead{Unit} & \colhead{Prior Form} & \colhead{Bounds} & \colhead{Gaussian Jet Posterior} & \colhead{Power Law Jet Posterior}}
+	\startdata
+		\thobs	& \text{rad	} & \sin \thobs \times p_\mathrm{LIGO}(\cos \thobs)	& [0, 0.8] 	& 0.48^{+0.08}_{-0.09} & 0.36^{+0.14}_{-0.11} \\
+		\log_{10} E_0	& \text{erg	}	& \text{uniform}	& [45, 57] 			& 52.92^{+0.62}_{-0.49} & 53.01^{+0.99}_{-0.70}\\
+		\thC			& \text{rad	}	& \text{uniform}	& [0.01, $\pi/2$]		& 0.07^{+0.01}_{-0.01} & 0.10^{+0.06}_{-0.03}\\
+		\thW			& \text{rad}	& \text{uniform}	& [0.01, 12$\thC$]	& 0.77^{+0.43}_{-0.38} & 0.18^{+0.07}_{-0.05}\\
+		b			& - 			& \text{uniform}	& [0, 10] 			& - & 7.15^{+2.02}_{-1.12}\\
+		\log_{10}n_0	& \text{cm}^{-3} & \text{uniform}	& [-10, 10] 		& -1.94^{+0.62}_{-0.65} & -2.66^{+1.03}_{-1.11}\\
+		p			& - 			& \text{uniform}	& [2, 5] 			& 2.17^{+0.01}_{-0.01} & 2.17^{+0.01}_{-0.01}\\
+		\log_{10}\epse& - 			& \text{uniform}	& [-5, 0] 			& -1.24^{+0.48}_{-0.69} &-1.30^{+0.66}_{-1.07} \\
+		\log_{10}\epsB	& - 			& \text{uniform}	& [-5, 0] 			& -4.32^{+0.72}_{-0.49} & -3.84^{+1.01}_{-0.80}\\
+		\hline
+		\log_{10}\Etot	& \text{erg}	&	-		&	-			& 50.61^{+0.58}_{-0.44} &50.85^{+0.93}_{-0.63} \\
+		\thobs/\thC	& -			&	-		&	-			& 6.76^{+0.21}_{-0.21} & 3.78^{+0.58}_{-0.84}\\
+	\enddata
+\end{deluxetable*}
+
+\begin{figure*}
+	\plotone{figs/cornerGaussian.png}
+	\caption{Views of the posterior parameter distribution for a Gaussian jet fit to the \gwbns{} afterglow.
+The diagonal contains one-dimensional marginalized posteriors for each fit parameter, while the off-diagonal plots contain two-dimensional maps of the posterior marginalized over all but the two corresponding parameters.
+\label{fig:cornerGaussian}}
+\end{figure*}
+
+\begin{figure*}
+	\plotone{figs/cornerPowerlaw.png}
+	\caption{Views of the posterior parameter distribution for a power law jet fit to the \gwbns{} afterglow.
+The diagonal contains one-dimensional marginalized posteriors for each fit parameter, while the off-diagonal plots contain two-dimensional maps of the posterior marginalized over all but the two corresponding parameters.
+\label{fig:cornerPowerlaw}}
+\end{figure*}
+
+Figures \ref{fig:cornerGaussian} and \ref{fig:cornerPowerlaw} show the one- and two-dimensional marginalized views of the posterior distribution for the Gaussian.
+and power law jet model fits, respectively.
+Table \ref{tab:MCMC} additionally gives constraints on the total jet energy \Etot{} and the ratio $\thobs/\thC$.
+The parameters $E_0$, $n_0$, $\epse$, and $\epsB$ are only constrained to within an order of magnitude, due partially to the observed radio, optical, and x-ray data all lying on the same synchrotron power-law segment.
+These parameters are shared between jet models, and are broadly consistent between the two fits with the possible exception of $n_0$.
+The electron energy index $p$ is extremely well constrained by both models, of course, due precisely to the large range of data laying on the same synchrotron segment.
+The total jet energy in both models in constrained to be on the order $10^{51}$erg.
+
+Of most interest are the geometric parameters: the viewing angle $\thobs$ and the jet structure parameters $\thC$, $\thW$, and $b$.
+Both models constrain $\thobs$ and $\thC$ reasonably well, but constrain the combination $\thobs/\thC$ far better.
+This is very evident by the corresponding map of the posterior in Figures \ref{fig:cornerGaussian} and \ref{fig:cornerPowerlaw}, which clearly displays a preferred linear relationship between $\thobs$ and $\thC$.
+This is the manifestation of the structured jet closure relations with $g \approx \geff(\thobs/\thC)$.
+The looser constraint on $\thobs/\thC$ in the power law jet comes from the additional freedom of the $b$ parameter, which has an effect on $\geff$ in that model (see Equation \eqref{eq:geff}).
+The truncation angle $\thW$ is essentially unconstrained in the Gaussian fit as a far off-axis phase was not observed.
+In the power law fit, however, $\thW$ is constrained to be quite narrow so as to avoid the early bright wings.
+
+Despite the tight constraints each model gives on $\thobs$, $\thC$, and especially $\thobs/\thC$, the resulting posteriors are incompatible with each other.
+The median and 68\% uncertainties in Table \ref{tab:MCMC} display only a mild tension in $\thobs$  and $\thC$ themselves, but a very large discrepancy in $\thobs/\thC$.
+This is, of course, due to the very different energy profiles $E(\theta)$ in each model.
+Both models can easily accommodate a rising light curve $F_\nu \sim t^{0.9}$, that is produce an effective structure parameter $\geff = 7.5$, but do so using very different geometries.
 
@@
 \begin{itemize}
-	\item Comparison with boxfit
-	\item Comparison with other GW170817A fits
+	\item Comparison with other \gwbns{} fits
 	\item Degeneracy between $E(\theta)$ and $\thobs$
-	\item $g$ vs $\thobs / \thC$ plot with GW170817
+	\item $g$ vs $\thobs / \thC$ plot with \gwbns{}
 	\item Looking forward to O3
 \end{itemize}
+
+Many groups have used structured jet models to analyze the afterglow of \gwbns{}, among the most recent with comparable models are \citet{Hotokezaka:2018aa, Ghirlanda:2019aa, Lamb:2019aa, Wu:2018aa}.
+Of these, \citet{Hotokezaka:2018aa, Ghirlanda:2019aa, Lamb:2019aa} use semi-analytic methods similar to the present work to construct afterglow light curves, while \citet{Wu:2018aa} utilizes analytic scaling relations and a template bank constructed from numerical simulations.
+Additionally, \citet{Hotokezaka:2018aa, Ghirlanda:2019aa} include constraints from the VLBI measurements of the \gwbns{} radio centroid's apparent superluminal motion.
+
+Of these, \citet{Mooley:2018ab, Hotokezaka:2018aa, Ghirlanda:2019aa} include the apparent superluminal motion
+
+The misaligned structured jet afterglow's primary feature is the viewing-angle-dependent extended rise or decline before the jet break.
+This phase is well described by the closure relations in Table \ref{tab:slopes} and depends on the single parameter $g$.
+For better or for worse, this single parameter
+
+The observational signature of a misaligned structured jet is the extended rise or slow decline before the jet break, $F_\nu \propto t^{\alpha(g)}$.  Unfortunately
 
@@
 The Gaussian and power law models respectively emulate this behavior, providing a simple parameterized representation of the landscape of numerical models.
-Of particular note are the Lazzati 2017 and Margutti 2018 models, both of which were calculated specifically for GW170817.
-The core of the Margutti model is has a profile very near Gaussian, while the Lazzati model has a strong resemblance to a power law.
+Of particular note are the Lazzati 2017 and Margutti 2018 models, both of which were calculated specifically for \gwbns{} The core of the Margutti model is has a profile very near Gaussian, while the Lazzati model has a strong resemblance to a power law.
 

### 2019-05-06 structuredJets.tex
More Discussion, added g_Plot

@@
 Further radio, optical, and x-ray observations showed a steady rising light curve with constant power law slope until a peak near day 160.
-At this point the light curve turned over and began a steep decay that continues to the present (CITE YearInTheLife).
+At this point the light curve turned over and began a steep decay that continues to the present \citep{van-Eerten:2018aa}.
 
@@
 We used the light curve data reported in \citet{van-Eerten:2018aa} with additional \hubble{} observations reported in \citet{Lamb:2019aa}.
-Reported measurement uncertainties were assumed to be independ
-ent and Gaussian, upper limits were treated as observations of zero flux with a 1-sigma Gaussian uncertainty.
+Reported measurement uncertainties were assumed to be independent and Gaussian, upper limits were treated as observations of zero flux with a 1-sigma Gaussian uncertainty.
 
@@
 Of most interest are the geometric parameters: the viewing angle $\thobs$ and the jet structure parameters $\thC$, $\thW$, and $b$.
+Encouragingly, the fits agree with the back-of-the-envelope reasoning from the analytic closure relations and break time scalings.
 Both models constrain $\thobs$ and $\thC$ reasonably well, but constrain the combination $\thobs/\thC$ far better.
@@
 
+\subsection{Inferring $\thobs$ and $E(\theta)$}
+
+Information about the viewing angle and jet structure is clearly encoded within misaligned afterglow light curves, primarily through the temporal slope $\alpha$ during the structured phase.
+This parameter alone, however, does not uniquely identify a particular structure model or observer inclination.
+When trying to infer information about a particular afterglow, there is a massive degeneracy between $E(\theta)$ and $\thobs$.
+
+This degeneracy is a blessing and a curse.
+The presence of an extended slowly decaying or rising afterglow is a largely model independent prediction of misaligned viewing and the presence of non-trivial jet structure.
+Unfortunately, this same model independence makes it very difficult to distinguish between jet structure profiles, leaving both $E(\theta)$ and $\thobs$ uncertain.
+
+There are at least two ways of easing this degeneracy: incorporating data other than the afterglow light curve itself and looking at population-level statistics.
+Utilizing posteriors from the gravitational wave signal or fitting the VLBI observations of superluminal apparent motion can greatly improve constraints on $\thobs$ \citep{Troja:2018aa, Hotokezaka:2018aa, Ghirlanda:2019aa}.
+Since the afterglow presumably provides good constraints on $\geff$ (via $\alpha$), improved knowledge of $\thobs$ immediately improves knowledge of $\thC$, $b$, and any other parameters relevant to $E(\theta)$.
+In some cases this may rule out a particular $E(\theta)$ entirely by pushing the relevant parameters to extreme values, for instance it is hard (but not impossible) to reconcile the observations of \gwbns{} with a power law jet with $b=2$.
+
+\begin{figure}
+	\plotone{figs/g_plot.pdf}
+	\caption{Structure parameter $g$ as a function of $\thobs/\thC$ for different structured jet models: Gaussian (blue), $b=2$ power law (orange), $b=4$ power law (green), and $b=6$ power law (red).
+The inferred value $g = 8.2\pm0.5$ for \gwbns{} is shown in as the grey band.
+\label{fig:gPop}}
+\end{figure}
+
+In the future, it may be possible to attack the question of determining $E(\theta)$ at the population level.
+Figure \ref{fig:gPop} shows the structure parameter $g$ as a function of $\thobs/\thC$ for several jet models, as well as the inferred value from \gwbns{}.
+If all short GRB jets share a jet profile shape, they should trace out a single curve in this space.
+As more misaligned afterglows are observed, measurements of $g$ can populate this diagram and potentially rule out models (such as potentially the $b=2$ power law).
+Model-independent constraints on $\thobs/\thC$ will greatly aid this procedure.
+Moreover, each structure model should predict a different observed distribution of $g$, depending on the shape of the $g(\thobs/\thC)$ curve and the detectability of each burst.
+With sufficient observations of $g$ alone and understanding of the observational biases, it may be possible to infer the underlying $g(\thobs/\thC)$ curve and $E(\theta)$ itself.
+
+\subsection{Comparison With Other \gwbns{} Analyses}
+
 Many groups have used structured jet models to analyze the afterglow of \gwbns{}, among the most recent with comparable models are \citet{Hotokezaka:2018aa, Ghirlanda:2019aa, Lamb:2019aa, Wu:2018aa}.
@@
 
-The misaligned structured jet afterglow's primary feature is the viewing-angle-dependent extended rise or decline before the jet break.
-This phase is well described by the closure relations in Table \ref{tab:slopes} and depends on the single parameter $g$.
-For better or for worse, this single parameter
-
-The observational signature of a misaligned structured jet is the extended rise or slow decline before the jet break, $F_\nu \propto t^{\alpha(g)}$.  Unfortunately
+\subsection{O3 And Beyond}
 

### 2019-05-06 code/gPlot.py

@@ -1,0 +1,75 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+def calc_gG(thV, thC):
+
+    return 0.25*thV*thV/(thC*thC)
+
+
+def calc_gPL(thV, thC, b):
+
+    th = 0.2*thV + 2.0*thC/3.0
+
+    g = (thV-th) * b * th / (thC*thC + th*th)
+
+    return g
+
+
+x = np.linspace(0.0, 10.0, 300)
+
+gG = calc_gG(x, 1.0)
+gPL2 = calc_gPL(x, 1.0, 2)
+gPL4 = calc_gPL(x, 1.0, 4)
+gPL6 = calc_gPL(x, 1.0, 6)
+
+p = 2.17
+al = 0.9
+dal = 0.06
+al1 = 2*p
+al2 = 3.0
+s = 1.0
+
+g = (8*al + 3*al1 - 3*s) / (al2 - al)
+
+dgda = (8*al2 + 3*al1 - 3*s) / ((al2-al)*(al2-al))
+
+dg = np.fabs(dgda) * dal
+
+print("al = {0:.3f} +/- {1:.3f}".format(al, dal))
+print("g  = {0:.3f} +/- {1:.3f}".format(g, dg))
+
+lw = 3.0
+fontsize = 24
+ticksize = 18
+legendsize = 18
+"""
+fig, ax = plt.subplots(1, 1, figsize=(8, 6))
+"""
+fig, ax = plt.subplots(1, 1)
+ax.plot(x, gG, lw=lw, label=r'Gaussian')
+ax.plot(x, gPL2, lw=lw, label=r'Power Law $b=2$')
+ax.plot(x, gPL4, lw=lw, label=r'Power Law $b=4$')
+ax.plot(x, gPL6, lw=lw, label=r'Power Law $b=6$')
+
+ax.fill_between(x, g-dg, g+dg, color='lightgrey', label='GW170817')
+
+"""
+ax.legend(loc='upper left', fontsize=legendsize)
+ax.set_xlabel(r'$\theta_V / \theta_C$', fontsize=fontsize)
+ax.set_ylabel(r'g', fontsize=fontsize)
+ax.tick_params(labelsize=ticksize)
+"""
+ax.legend(loc='upper left')
+ax.set_xlabel(r'$\theta_V / \theta_C$')
+ax.set_ylabel(r'g')
+ax.tick_params()
+
+ax.set_ylim(0, 16)
[…]

### 2019-05-06 structuredJets.tex
Updates

@@
 
-\title{GRB Afterglows In The Multi-Messenger Era}
+\title{GRB Afterglows In The Multi-Messenger Era  OR  Electromagnetic Afterglows Of Structured Jets  OR  Structured Jets At All Angles}
 \correspondingauthor{Geoffrey Ryan}
@@
 
+\author{Eleonora Troja}
+
+\author{Luigi Piro}
+
 \begin{abstract}
@@
 We present a characterization of the afterglows arising from structured jets, utilizing both trans-relativistic numerical calculations and simple analytic approximations.
-In many cases the temporal slope before the jet break is found to be a simple function of the ratio between the inclination angle and effective half opening angle of the jet.
-Our models, both numerical and analytic, are publicly available as an open source Python package.
+In many cases the temporal slope before the jet break is found to be a simple function of the ratio between the viewing angle and effective half opening angle of the jet.
+This provides a useful handle in the analysis of structured GRB afterglow light curves, but does not completely resolve the degeneracy between viewing angle and jet structure model.
+Our models, both numerical and analytic, are publicly available as the open source \python{} package \afterglowpy{}.
 
@@
 
-GRB afterglows are commonly modeled as top hat blast waves with no internal structure pointed directly at the observer.
-This has been largely sufficient given the data.
-(Although: viewing angle effects can be measured (Ryan+ 2015)).
+Gamma-ray burst (GRB) afterglows are commonly modeled as top hat blast waves with no internal structure pointed directly at the observer.
+This has been largely sufficient given the available data, although some evidence of viewing angle effects has been found \citep{Ryan:2015aa}.
 New observational capabilities have witnessed new phases of afterglow evolution, such as the discovery of plateaus with Swift.
@@
 %
-%\begin{figure*}
-%	\plotone{figs/boxfit_comp.pdf}
-%	\caption{Top Panel: Comparison between top hat jet light curves from \afterglowpy{} (solid lines) and \boxfit{} (dashed lines).
+\begin{figure*}
+	\plotone{figs/boxfit_comp.pdf}
+	\caption{Top Panel: Comparison between top hat jet light curves from \afterglowpy{} (solid lines) and \boxfit{} (dashed lines).
 Bottom Panel: fraction difference between \afterglowpy{} and \boxfit{} light curves.
@@
 \label{fig:boxfitComp}}
-%\end{figure*}
-%
-%Figure \ref{fig:boxfitComp} shows a comparison between top-hat light curves calculated with \afterglowpy{} and \boxfit{}.
+\end{figure*}
+
+Figure \ref{fig:boxfitComp} shows a comparison between top-hat light curves calculated with \afterglowpy{} and \boxfit{}.
 The \boxfit{} code uses two-dimensional relativistic hydrodynamic simulations to fully capture the non-linear hydrodynamics of a decelerating blast wave and a ray tracing radiative transfer module to compute observed synchrotron light curves.
@@
 The relative error is less than 50\% before the onset of spreading.
+
+TODO: FINISH THIS SECTION.
 
@@
 
-\begin{itemize}
-	\item Comparison with other \gwbns{} fits
-	\item Degeneracy between $E(\theta)$ and $\thobs$
-	\item $g$ vs $\thobs / \thC$ plot with \gwbns{}
-	\item Looking forward to O3
-\end{itemize}
-
 \subsection{Inferring $\thobs$ and $E(\theta)$}
@@
 
-Of these, \citet{Mooley:2018ab, Hotokezaka:2018aa, Ghirlanda:2019aa} include the apparent superluminal motion
+TODO: INCLUDE BRIEF COMPARISON TO EACH.  NOTE DIFFERENT MODELS PRODUCE SAME LIGHT CURVE, STRONG EFFECT OF VLBI.
 
@@
 
+In the coming years there will be more \gwbns{}-like events, although perhaps few with as extensive followup campaigns.
+Since many of these events may be faint and distant, it will be important to leverage as much information from the afterglow light curve as possible.
+As shown here, and evidenced by the diversity of models that have ``fit'' the \gwbns{} afterglow, there is a large degeneracy between viewing angle and jet structure profile.
+To make robust inferences about these events, several flexible jet models must be included in the analysis.
+
+We hope \afterglowpy{} and similar products will aid these analyses in the future.
+
 \section{Summary}
+
+We have constructed flexible models for the electromagnetic afterglows of angularly structured relativistic jets.
+Through analytic approximations we can identify the basic phases of the structured afterglow light curve, determining formulae for the characteristic break time scales and closure relations.
+We find the closure relations depend on a single parameter we call $g$ relating to the jet structure and viewing angle.
+Measurements of $g$ itself are model independent, but relating it back to physical parameters of the jet is not.
+
+We also constructed a numerical model of the afterglows of structured jets, implemented in the public \python{} package \afterglowpy{}.
+\afterglowpy{} computes afterglow light curves on the fly utilizing semi-analytic approximations to the jet evolution and synchrotron emission, taking into account relativistic beaming, the equal time of arrival surface, jet angular structure, trans-relativistic evolution, and jet spreading.
+It is fast enough to be incorporated in MCMC parameter estimation routines.
+Fitting the \gwbns{} afterglow with multiple \afterglowpy{} models reveals the degeneracy between jet structure and viewing angle.
 
@@
 
-\section{The Jet Angular Profile}
-\label{sec:jetAngularShape}
-
-The angular structure of a jet, before deceleration, can be described by angular profiles of energy $\epsilon(\theta, \phi)$ and Lorentz factor $\Gamma(\theta, \phi)$.
-This structure is acquired by the jet at its initial formation at the central engine and then sculpted by its propagation through the merger ejecta.
-Due to the complications of direct numerical simulation much theoretical work has focused on simple analytic prescriptions of jet structure, typically axisymmetric uniform top-hat, Gaussian, or power law (CITE Granot+02, G+K03, K+G03, Rossi+04).
-
-We consider the latter two models, a Gaussian profile
-\begin{equation}
-	E = E_0 \exp\left( \frac{\theta^2 }{2 \theta_c^2}\right)\ , \label{eq:Gaussian}
-\end{equation}
-and a $\theta^{-2}$ power law
-\begin{equation}
-	E = \frac{E_0}{1 + \theta^2/\theta_c^2}\ . \label{eq:powerlaw}
-\end{equation}
-Both models are truncated at an angle $\theta_w$.
-It is assumed all observed emission occurs after the jet has entered the deceleration phase, so the Lorentz factor profile is simply $\Gamma \propto E^{1/2}$.
-
-With recent progress in hydrodynamical codes and computer resources, numerical simulation of jet propagation from the central engine to the circumburst medium has become possible.
-Figure \ref{fig:jetStructure} shows energy and Lorentz factor distributions from hydrodynamic simulations collected from the recent literature, with representative examples of the Gaussian and power law models.
-The Lorentz factor distributions show large variation, in part due to differing times of extraction from the numerical simulations.
-We focus comparison on the energy profile, as this is largely fixed while the jet remains relativistic.
-
-\begin{figure}
-	\plotone{figs/jetStructure.pdf}
-   	\figcaption{Energy and Lorentz factor profiles of jet models.
-Profiles of numerical simulations are reported in Morsony+2007 (green), Mizuta+2009 (brown), Duffell+2015 (orange), Lazzati+2017 (pink), Kathirgamaraju+2017 (red), and Margutti+2018 (purple).
-The analytic boosted fireball model (Duffell+2015) is shown in blue.
-Energy profiles for Morsony07, Mizuta09, and Duffell15 have been scaled to $dE/d\Omega(\theta=0) = 10^{52}$ erg/sr.
-For comparison we also show representative power law ( Eq.
-\eqref{eq:powerlaw}, $\theta_c=1^\circ$, $\theta_w=60^\circ$, thick grey) and Gaussian (\eqref{eq:Gaussian}, $\theta_c=5.7^\circ$, $\theta_w=23^\circ$, thick black) profiles.
-\label{fig:jetStructure}}
-\end{figure}
-
-There is agreement between the models that the jet energy is concentrated in a core of half-width $\lesssim 10^\circ$ with wings extending to larger angles.
-Some models truncate at $\mathcal{O}(10)$ degrees, while others have large tails extending to near the equator.
-The Gaussian and power law models respectively emulate this behavior, providing a simple parameterized representation of the landscape of numerical models.
-Of particular note are the Lazzati 2017 and Margutti 2018 models, both of which were calculated specifically for \gwbns{} The core of the Margutti model is has a profile very near Gaussian, while the Lazzati model has a strong resemblance to a power law.
-
 \bibliography{structuredJets_sources}

### 2019-05-08 structuredJets.tex
Updates to Section 3

@@
 \usepackage{graphicx}
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks=true,
+    linkcolor=blue,
+    filecolor=magenta,      
+    urlcolor=cyan,
+}
 
@@
 
-\author{Eleonora Troja}
+% \author{Eleonora Troja}
 
-\author{Luigi Piro}
+% \author{Luigi Piro}
 
@@
 To accommodate an initial structure profile $E(\theta)$ we consider the integrand of Equation \eqref{eq:flux} as a function of the polar angle $\theta$.
-We assume each constant $\theta$ annulus evolves independently, as an equivalent top hat of width $\thC = \theta$.
+We assume each constant $\theta$ annulus evolves independently, as an equivalent top hat of initial width $\thC = \theta$.
 This is a very good approximation when transverse velocities are low: when the blast wave is ultra-relativistic and has not begun to spread and when the blast wave is non-relativistic and the spreading has ceased \citep{van-Eerten:2010aa}.
@@
 
-To compute the light curve of a top-hat jet of width $\theta$ we first must calculate the time evolution of the blast wave.
+To compute the light curve of a top-hat jet of initial width $\thC$ we first must calculate the time evolution of the blast wave.
 In the single-shell approximation we treat the ejecta mass, contact discontinuity, and forward shock as a single unit propagating through a cold ambient medium with constant rest-mass density $\rho_0 = \Mp n_0$.
-The forward shock is a radius $R$ from the explosion and moves at a velocity $\beta_s$.
-In terms of the fluid four-velocity behind the shock $u$ and its Lorentz factor $\gamma$ this may be written as:
+We utilize the TM trans-relativistic equation of state to describe the fluid consistently throughout its evolution \citep{Mignone:2005aa}.
+The forward shock is a radius $R$ from the explosion, and the fluid behind the shock has four-velocity $u$ and Lorentz factor $\gamma$.
+The shock jump conditions can be used to determine the shock speed:
 \begin{equation}
@@
  The evolution of the four velocity is determined through conservation of energy.  The total energy in the trans-relativistic single shell approximation is:
-\begin{equation}
-	E = (\gamma - 1)\Mej c^2 + \frac{4\pi}{9} \rho_0 c^2 R^3 (4 u^2 + 3) \beta^2 \Omega\ . \label{eq:E}
-\end{equation}
+\begin{align}
+	E &= (\gamma - 1)\Mej c^2 + \frac{4\pi}{9} \rho_0 c^2 R^3 (4 u^2 + 3) \beta^2 f_\Omega \ , \label{eq:E} \\
+	f_\Omega &= 2 \sin^2\left( \theta_j / 2 \right)\ . \label{eq:fOm}
+\end{align}
 In Equation \eqref{eq:E} the first term is the kinetic energy of the ejected mass $\Mej$, assumed to have already accelerated and adiabatically cooled to its coasting velocity.
 The second term is the kinetic and thermal energy of the shocked ISM with three-velocity $\beta = u / \gamma$.
-The shocked ISM is confined to a cone of solid angle $\Omega = 2 \sin^2 (\theta_0/2)$ where $\theta_0$ is the half-opening angle of the jet.
-While the blast wave is relativistic $\theta_0$ is constant, but once the jet edge comes in causal contact with the core it begins to spread due to its own internal pressure until the blast wave is spherical.
-The spreading occurs at sound speed $c_s$ in the fluid rest-frame \citep{van-Eerten:2010aa, Duffell:2018aa}:
+Equation \eqref{eq:fOm} describes the fractional solid angle of the jet in terms of the time dependent opening angle $\theta_j(t)$.
+While the blast wave is relativistic $\theta_j = \thC$ and $f_\Omega$ is constant, but once the jet edge comes in causal contact with the core it begins to spread due to its own internal pressure.
+The jet spreads and $\theta_j$ increases until the blast wave is spherical and $f_\Omega=1$.
+The spreading occurs at sound speed $c_s$ in the fluid rest-frame, causing the opening angle of the jet to increase as \citep{van-Eerten:2010aa, Duffell:2018aa}:
 \begin{equation}
-	\dot{\theta_0} = \frac{c_s}{\gamma R}\ , \qquad \text{if } u < 1/3\thC \text{ and } \theta_0 > \pi/2\ . \label{eq:thetadot}
+	\dot{\theta_j} = \frac{c_s}{\gamma R}\ , \qquad \text{if } u < 1/3\thC \text{ and } \theta_j > \pi/2\ . \label{eq:thetadot}
 \end{equation}
-The criterion $u < 1/3\theta_0$ is satisfied when enough time has elapsed that a sound wave can propagate from $\theta = \thC$ to $\theta=0$ in a blast wave propagating in a uniform ISM (CITE HENDRIK).
+The criterion $u < 1/3\thC$ is satisfied when a sound wave can propagate from $\theta = \thC$ to $\theta=0$ in a blast wave propagating in a uniform ISM (CITE HENDRIK).
 It is similar to the condition given in \cite{Duffell:2018aa}, which found a numerical factor of 2.5 (instead of 3) after calibrating to numerical simulations.
-Our criteria differs from that used in (CITE Troja+) which used an overly simplistic $u < 1$ criterion to begin jet spreading.
+Our criteria differs from that used in \citet{Troja:2018aa, Piro:2019aa, van-Eerten:2018aa} which used an overly simplistic $u < 1$ criterion to begin jet spreading.
 
-Given a (possibly constant) expression for $E$ Equation \eqref{eq:E} may be differentiated with respect to $t$ and solved for $\dot{u}$.
-In a refreshed shock scenario $E = E_{>}(u)$, whereas for a standard energy injection model one may take $E \propto t^{-q}$.
-In either case, Equation \eqref{eq:E} produces an equation for $\dot{u}$.
-This defines a three dimensional system of ordinary differential equations in the variables $(R, u, \theta_0)$ which may be solved numerically or, in certain limits, analytically.
+Given an expression for $E$ in terms of $t$, $R$, $u$, and $\theta_j$, Equation \eqref{eq:E} may be differentiated with respect to $t$ and solved for $\dot{u}$.
+A standard adiabatic evolution will maintain $E=$ constant, while in a continuously refreshed shock scenario $E = E_{>u}(u)$ and in standard energy injection models $E \propto t^-q$.
+This defines a three dimensional system of ordinary differential equations (ODEs) in the variables $(R, u, \theta_j)$ which may be solved numerically or, in certain limits, analytically from appropriate initial conditions.
 
-Once the shock evolution is known, the flux is given by the integral:
+Once the shock evolution ($R(t)$, $u(t)$, $\theta_j(t)$) is known, the flux is given by the integral:
+\begin{align}
+	F_\nu(\tobs, \nuobs) &= \frac{1+z}{4\pi \dL^2} \int \! \dd \Omega\ R^2\ \Delta R\  \delta^2\ \epsilon'_{\nu'} \ , \label{eq:flux2}
+\end{align}
+where $\Delta R$ is the effective shock width contributing to the emission \citep{van-Eerten:2010aa}:
 \begin{equation}
-	F_\nu(\tobs, \nuobs) = \frac{1+z}{4\pi \dL^2} \int \! \dd \Omega\ R^2\ \Delta R\  \delta^2\ \epsilon'_{\nu'} \ , \label{eq:flux2}
+	\Delta R = \frac{1}{1-\mu \dot{R}} \frac{R}{12\gamma^2} \ . \label{eq:dr}
 \end{equation}
-where $\Delta R$ (TODO: add eq for Delta R) is the shock width contributing to the emission.
  The integrand is evaluated at a constant observer time $\tobs$ and observer frequency $\nuobs$, related to $t$ and $\nu'$ by:
@@
 
-TODO: Give formulae or reference for $\epsilon'_{\nu'}$.
-
-The integral \eqref{eq:flux2} may now be computed numerically or, in certain limits, analytically.
+The rest-frame synchrotron emissivity may be calculated to numerous ways with varying degrees of physics and accuracy.
+We use the standard broken power law formalism with characteristic frequencies $\nu_m$ and $\nu_c$, with the cooling frequency $\nu_c$ calculated via the global cooling approximation \citep{Granot:2002aa, van-Eerten:2010aa}.
 
@@
 
-The integral \eqref{eq:flux2} is evaluated numerically using an adaptive Romberg integrator in each dimension, with a typical relative tolerances of $10^{-6}$.
+We have constructed the \afterglowpy{} Python package to implement the numerical computation of light curves according to Section \ref{subsec:algo} and provide it to the community.
+The integration routine itself is written in C, wrapped as an extension for Python, and has been optimized to be used in intensive data analysis routines such as Markov Chain Monte-carlo which can require many thousands or millions of evaluations.
 
-We have constructed the \afterglowpy{} Python package to implement the numerical computation of light curves according to Section \ref{subsec:algo} and provide it to the community.
-The integration routine itself is written in C, wrapped as an extension for Python, and has been optimized to be used in intensive data analysis routines such as Markov Chain Monte-carlo which can require many thousands of evaluations.
+\afterglowpy{} uses a standard RK4 algorithm to evolve the $(R(t), u(t), \theta_j(t))$ system of equations on a fixed logarithmically spaced grid of $t$.
+The endpoints of the $t$-grid are chosen to bracket the burster frame times required to calculate the requested $\tobs$.
+Initial conditions for $R$, $u$, and $\theta$ are typically those of a decelerating ultra-relativistic blast wave.
+The user can set the density of the $t$-grid with the {\tt tRes} parameter: the number of grid points per decade of $t$.
+The default value for {\tt tRes} is 1000, which is sufficiently dense that the shock ODE evolution is not the dominant error source but not so dense as to adversely impact performance.
 
-\afterglowpy{} uses a standard RK4 algorithm to evolve the $(R(t), u(t), \theta_0(t))$ system of equations on a fixed logarithmically spaced grid of $t$.
-The endpoints of the $t$-grid are chosen to bracket the burster frame times required to calculate the requested $\tobs$ with at least a decade of tolerance.
-Initial conditions for $R$, $u$, and $\theta_0$ are those of a decelerating ultra-relativistic blast wave.
-The user can set the density of the $t$-grid with the $n_t$ parameter: the number of grid points per decade of $t$.
-The default value for $n_t$ is 1000, which is sufficiently dense that the shock ODE evolution is not the dominant error source but not so dense as to adversely impact performance.
-
-Each top-hat jet component is integrated in $\theta$ and $\phi$ using an adaptive Romberg scheme with a fixed relative tolerance and an adaptive absolute tolerance.
+Each top-hat jet component is integrated in $\theta$ and $\phi$ using an adaptive Romberg scheme with a fixed relative tolerance of $10^{-6}$ and an adaptive absolute tolerance.
 When summing over top-hat components of a structured jet, the innermost (core) component is calculated first.
-As the calculation proceeds, the current running sum of the flux is used to set absolute tolerance in the Romberg integrator for each component.
+As the calculation proceeds, the current running sum of the flux is used to set absolute tolerance for the next component.
 This minimizes the computations performed on dim, off-axis sectors of the jet.
 
-Each evaluation of the integrand requires a binary search to determine the burster time $t$ at which to evaluate $R$, $u$, and $\theta_0$.
+Each evaluation of the integrand requires a binary search to determine the burster time $t$ at which to evaluate $R$, $u$, and $\theta_j$.
 Fluid quantities are then calculated using the shock-jump conditions and the synchrotron emissivity is evaluated using the standard external shock formulae \citep{Granot:2002aa,van-Eerten:2010aa}.
 
-The numerical accuracy of a top-hat light curve with this scheme is typically better than $10^{-4}$.
-The structured jet calculation splits the integration domain into $N_\theta$ disjoint annuli, each evaluated as an independent top-hat and summed.
-By default $N_\theta$ is chosen such that there will be 5 zones per $\thC$-sized interval.
-The choice of $N_\theta$ has the largest impact on the code performance and accuracy.
-We find the choice $N_\theta = 5$ gives sufficiently quick performance at acceptable errors, typically on the order of $10^{-2}$.
+The numerical accuracy of a top-hat light curve with this integration scheme is typically better than $10^{-4}$.
+The structured jet calculation splits the integration domain into {\tt latRes} disjoint annuli, each evolved as an independent top-hat and their emission summed.
+By default {\tt latRes} is chosen such that there will be 5 zones per $\thC$-sized interval of $\theta$.
+The choice of  {\tt latRes} has the largest impact on the code performance and accuracy.
+We find the choice $\mathtt{latRes} = 5$ gives sufficiently quick performance at acceptable errors, typically on the order of $10^{-2}$.
 TODO SHOW CONVERGENCE PLOT
@@
 We gauge this trade-off by comparing to the \boxfit{} code, a standard tool which calculates high fidelity afterglow light curves based on numerical simulations.
+\boxfit{} uses two-dimensional relativistic hydrodynamic simulations to fully capture the non-linear hydrodynamics of a decelerating blast wave and a ray tracing radiative transfer module to compute observed synchrotron light curves.
+
+Comparing to \boxfit{} tests the fidelity of some of the assumptions and approximations of the single shell approach used by \afterglowpy{}.
+The simpler analytic version of the scheme on which \afterglowpy{} is based differed from \boxfit{} by factors from 2 to 8 \citep{vanEerten:2010aa}.
+We find \afterglowpy{} performs much better, with a relative difference of less than 50\% for the bulk of the evolution.
+The difference is worst, up to a factor of 3 relative to \boxfit{}, at the onset of jet spreading.
 
@@
 	\caption{Top Panel: Comparison between top hat jet light curves from \afterglowpy{} (solid lines) and \boxfit{} (dashed lines).
-Bottom Panel: fraction difference between \afterglowpy{} and \boxfit{} light curves.
+Bottom Panel: Fractional difference between \afterglowpy{} and \boxfit{} light curves.
 Four representative light curves are shown: radio on-axis ($\thobs=0$, $\nu=10^9$Hz, blue), radio off-axis ($\thobs=0.16$rad, $\nu=10^9$Hz, orange), x-ray on-axis ($\thobs=0$, $\nu=10^{18}$Hz, green), and x-ray off-axis ($\thobs=0.16$rad, $\nu=10^{18}$Hz, red).
-Remaining parameters are shared: $\thC=0.1$rad, $\Eiso=10^{52}$erg, $\Eiso=10^{52}$erg, $n_0 = 10^{-3}$cm$^{-3}$, $p=2.2$, $\epse=10^{-1}$, $\epsB=10^{-2}$, $\dL=3.09 \times 10^{26}$cm, $z=0.028$.
+Remaining parameters are shared: $\thC=0.1$rad, $\Eiso=10^{52}$erg, $n_0 = 10^{-3}$cm$^{-3}$, $p=2.2$, $\epse=10^{-1}$, $\epsB=10^{-2}$, $\dL=3.09 \times 10^{26}$cm, $z=0.028$.
 \label{fig:boxfitComp}}
@@
 Figure \ref{fig:boxfitComp} shows a comparison between top-hat light curves calculated with \afterglowpy{} and \boxfit{}.
-The \boxfit{} code uses two-dimensional relativistic hydrodynamic simulations to fully capture the non-linear hydrodynamics of a decelerating blast wave and a ray tracing radiative transfer module to compute observed synchrotron light curves.
-Figure \ref{fig:boxfitComp} shows the light curve of a $\thC=0.1$rad top-hat at radio and x-ray frequencies ($10^9$Hz and $10^{18}$Hz, respectively) with aligned ($\thobs = 0$) and misaligned ($\thobs=0.16$rad) viewing angles.
-The overall agreement is good: \afterglowpy{} captures the salient features of both aligned and misaligned light curves including the jet break, spectral shape, and transition to the Sedov phase.
-The relative error is less than 50\% before the onset of spreading.
+Figure \ref{fig:boxfitComp} shows the light curve of a $\thC=0.1$ rad top-hat jet at radio and x-ray frequencies ($10^9$Hz and $10^{18}$Hz, respectively) with aligned ($\thobs = 0$) and misaligned ($\thobs=0.16$rad) viewing angles.
+The light curves begin in the ultra relativistic Blandford-Mckee phase and continue to the Newtonian Sedov phase.
 
-TODO: FINISH THIS SECTION.
+The overall agreement is good: \afterglowpy{} captures the salient features of both aligned and misaligned light curves including the jet break, spectral shape, transition to the Sedov phase, and the early steep rise for misaligned viewing.
+At early times, \boxfit{} lacks the simulation coverage to produce accurate fluxes, leading to a large discrepancy.
+Once proper coverage is attained, \boxfit{} and \afterglowpy{} show less than 50\% relative discrepancy until the jet break passes and jet spreading begins.
+After the jet break the \afterglowpy{} light curves show a marked excess relative to \boxfit{}, the relative error increasing to approximately 1.0 and 2.0 for the aligned and misaligned radio light curves, respectively.
+The x-ray light curves achieve approximately half the error of the radio.
+After a short period the \afterglowpy{} light curves begin to decrease, recovering the \boxfit{} slope, and asymptote to similar light curves in the Newtonian regime with a small constant offset from \boxfit{}.
 
-\afterglowpy{} is available on PyPI and may be installed with {\tt pip}.  The source code is open and available at https://github.com/geoffryan/afterglowpy.
+As expected, \afterglowpy{} models the early and late afterglow well, but struggles in an intermediate phase during jet spreading.
+In particular it appears that \afterglowpy{} begins its spreading late relative to \boxfit{}.
+This phase is precisely where the non-linear hydrodynamics of the blast wave are most important, and hardest to model with simple semi-analytic approximations.
+Any work utilizing \afterglowpy{} should be aware of this fact, and be careful when treating data from this regime.
+
+It bears pointing out that some of the hard discrepancy between the codes is due to the test itself: the sharp-edged nature of the top-hat jet exacerbates discrepancies in how these edges are treated.
+An angularly structured jet with non-trivial $E(\theta)$ may smooth over the differences in approach between the codes: we may expect \afterglowpy{} to be more accurate for structured jets than top-hats.
+\afterglowpy{} is by no means a replacement for full numerical simulations, but is a useful and flexible tool which captures much of the important physics of GRB afterglows at a very small fraction of the cost of a relativistic numerical hydrodynamic simulation.
+
+\afterglowpy{} is available on PyPI and may be installed with {\tt pip}.  The source code is open and available at \url{https://github.com/geoffryan/afterglowpy}.
 

### 2019-05-08 structuredJets.tex
Fixed figure sizes, added light curve grid figure

@@
 \usepackage{hyperref}
-\hypersetup{
-    colorlinks=true,
-    linkcolor=blue,
-    filecolor=magenta,      
-    urlcolor=cyan,
-}
+%\hypersetup{
+%    colorlinks=true,
+%    linkcolor=blue,
+%    filecolor=magenta,      
+%    urlcolor=cyan,
+%}
 
@@
 \begin{figure}
-	\plotone{figs/jetStructureComparison.pdf}
+	\includegraphics[width=\columnwidth]{figs/jetStructureComparison.pdf}
 	\caption{Lateral profiles of isotropic equivalent energy $\Eiso$ as a function of angle from the jet axis $\theta$, individually rescaled to group similar profile shapes.
@@
 \begin{figure*}
-	\plotone{figs/boxfit_comp.pdf}
+	\includegraphics[width=\textwidth]{figs/boxfit_comp.pdf}
 	\caption{Top Panel: Comparison between top hat jet light curves from \afterglowpy{} (solid lines) and \boxfit{} (dashed lines).
@@
 
+%%%%%%%%%%%%%%%%%%
+%
+% Afterglows Section
+%
+%%%%%%%%%%%%%%%%%%%%
+
 \section{Structured Jet Light Curves}\label{sec:structuredJets}
@@
 
-We find the light curves of structured jets show two modes of behaviour, depending on whether the observer is \emph{aligned} ($\thobs < \thC$) or \emph{misaligned} ($\thobs > \thC$).
+We find the light curves of structured jets show two modes of behaviour, depending on whether the observer is \emph{aligned} ($\thobs < \thC$) or \emph{misaligned} ($\thobs > \thC$) TODO: CITE PREVIOUS STRUCTURED JET WORK
  In the \emph{aligned} case, the light curves follow the standard on-axis top hat behaviour modified slightly for non-zero viewing angle.
-There is little to distinguish between different structure $E(\theta)$, and the light curve is well-approximated by a broken power law with characteristic break times.
+There is little to distinguish between different structure $E(\theta)$, and the light curve is well-approximated by a broken power law with characteristic break times \citep{Granot:2002aa}.
 The \emph{misaligned} light curve also may present as a broken power law, but with closure relations explicitly dependent on viewing angle and jet angular structure.
@@
 \begin{figure}
-	\plotone{figs/breaks_alignedOA_all.pdf}
+	\includegraphics[width=\columnwidth]{figs/breaks_alignedOA_all.pdf}
 	\caption{Jet break time for on-axis ($\thobs=0$) observers for top-hat (blue circles), Gaussian (orange squares), and power law (green triangles) jets as a function of $\thC$.
@@
 \begin{figure}
-	\plotone{figs/lc_on.pdf}
+	\includegraphics[width=\columnwidth]{figs/lc_on.pdf}
 	\caption{Aligned ($\thobs = \thC/2$) afterglow light curves for top-hat (blue), Gaussian (orange), and power law (green) jets.
@@
 \end{figure}
+
+\begin{figure*}
+	\includegraphics[width=\textwidth]{figs/lc_thV_model_multi.pdf}
+	\caption{Aligned ($\thobs = \thC/2$) afterglow light curves for top-hat (blue), Gaussian (orange), and power law (green) jets.
+When viewed on-axis, jets containing angular structure are very difficult to distinguish from top-hats.
+The transition phase marking the onset of the jet break begins at $\tbm\sim3$ days with a shallow break and ends sharply at $\tbp \sim 100$ days.
+These particular light curves use $\thC = 0.1$ rad, $\thW = 0.4$ rad, $E_0 = 10^{52}$erg, $n_0=10^{-2}$cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, $\epsB = 10^{-3}$, and $d_L=40$Mpc.
+\label{fig:onaxis}}
+\end{figure*}
 
@@
 \begin{figure}
-	\plotone{figs/jetDecomp.pdf}
+	\includegraphics[width=\columnwidth]{figs/jetDecomp.pdf}
 	\caption{A Gaussian structured jet, decomposed into emission from different latitudes $\theta$.
@@
 \begin{figure}
-	\plotone{figs/lc_off1.pdf}
+	\includegraphics[width=\columnwidth]{figs/lc_off1.pdf}
 	\caption{As Figure \ref{fig:onaxis} but $\thobs = 2\thC$.
@@
 \begin{figure}
-	\plotone{figs/lc_off2.pdf}
+	\includegraphics[width=\columnwidth]{figs/lc_off2.pdf}
 	\caption{As Figure \ref{fig:onaxis} but $\thobs = 6\thC$.
@@
 \begin{figure}
-	\plotone{figs/slopesJet.png}
+	\includegraphics[width=\columnwidth]{figs/slopesJet.png}
 	\caption{Temporal slopes for the off-axis structured jet as a function of the structure parameter $g$ for the synchrotron spectral regimes D (blue, narrow), E (orange, narrow),  F (green, narrow), G (red, wide), and H (purple, wide).
@@
 \begin{figure}
-	\plotone{figs/slopesCocoon.png}
+	\includegraphics[width=\columnwidth]{figs/slopesCocoon.png}
 	\caption{The temporal power law slope of the spherical refreshed-shock afterglow light curve as a function of $k$.
@@
 \begin{figure*}
-	\plotone{figs/cornerGaussian.png}
+	\includegraphics[width=\textwidth]{figs/cornerGaussian.png}
 	\caption{Views of the posterior parameter distribution for a Gaussian jet fit to the \gwbns{} afterglow.
@@
 \begin{figure*}
-	\plotone{figs/cornerPowerlaw.png}
+	\includegraphics[width=\textwidth]{figs/cornerPowerlaw.png}
 	\caption{Views of the posterior parameter distribution for a power law jet fit to the \gwbns{} afterglow.
@@
 \begin{figure}
-	\plotone{figs/g_plot.pdf}
+	\includegraphics[width=\columnwidth]{figs/g_plot.pdf}
 	\caption{Structure parameter $g$ as a function of $\thobs/\thC$ for different structured jet models: Gaussian (blue), $b=2$ power law (orange), $b=4$ power law (green), and $b=6$ power law (red).

### 2019-05-08 code/plotModelThV.py

@@ -1,0 +1,121 @@
+import numpy as np
+import grbpy as grb
+import matplotlib.pyplot as plt
+
+
+def plotPanel(fig, gs0, t, nu, thV, Y, Z, modelLegend=False):
+
+    gs = gs0.subgridspec(3, 1, hspace=0.0)
+    axF = fig.add_subplot(gs[0:-1, 0])
+    axa = fig.add_subplot(gs[-1, 0])
+
+    tfac = 0.3
+
+    tb = t * (1.0 + tfac)
+    ta = t / (1.0 - tfac)
+
+    c = ['C0', 'C2', 'C1', 'C3']
+    ls = ['--', '-', '-.', ':']
+
+    thC = Y[2]
+
+    Y[0] = thV
+
+    FnuTH = grb.fluxDensity(t, nu, -1, 0, *Y, **Z)
+    FnuTHa = grb.fluxDensity(ta, nu, -1, 0, *Y, **Z)
+    FnuTHb = grb.fluxDensity(tb, nu, -1, 0, *Y, **Z)
+
+    FnuG = grb.fluxDensity(t, nu, 0, 0, *Y, **Z)
+    FnuGa = grb.fluxDensity(ta, nu, 0, 0, *Y, **Z)
+    FnuGb = grb.fluxDensity(tb, nu, 0, 0, *Y, **Z)
+
+    Y[4] = 2
+    FnuPL1 = grb.fluxDensity(t, nu, 4, 0, *Y, **Z)
+    FnuPL1a = grb.fluxDensity(ta, nu, 4, 0, *Y, **Z)
+    FnuPL1b = grb.fluxDensity(tb, nu, 4, 0, *Y, **Z)
+
+    Y[4] = 6
+    # Y[2] = np.sqrt(3)*thC
+    FnuPL2 = grb.fluxDensity(t, nu, 4, 0, *Y, **Z)
+    FnuPL2a = grb.fluxDensity(ta, nu, 4, 0, *Y, **Z)
+    FnuPL2b = grb.fluxDensity(tb, nu, 4, 0, *Y, **Z)
+    Y[2] = thC
+
+    alTH = np.log(FnuTHb/FnuTHa) / np.log(tb/ta)
+    alG = np.log(FnuGb/FnuGa) / np.log(tb/ta)
+    alPL1 = np.log(FnuPL1b/FnuPL1a) / np.log(tb/ta)
+    alPL2 = np.log(FnuPL2b/FnuPL2a) / np.log(tb/ta)
+
[…]

### 2019-05-16 structuredJets.tex
small updates.

@@
 \newcommand{\planck}{{\em Planck}}
+\newcommand{\beppoSAX}{{\em BeppoSAX}}
 
@@
 
+% Present new closure relations for structured jets, compare with established relations for choked jet models...
+
 \end{abstract}
@@
 \section{Introduction}
+
+\begin{itemize}
+\item \citet{Meszaros:1998aa} First discusses effect of angular structure in $E$ and $\Gamma$, predicts rising light curves when seen off axis, calculates closure relations in various cases.
+\item \citet{Dalal:2002aa} Considers emission from boosted lightbulb, refers to $\thobs > \theta_j$ as ``off-axis,'' points out off-axis jet breaks will be delayed and dim, light curves converge at late time.
+\item \citet{Moderski:2000aa} Relativistic effects (equal arrival time surface, etc) smear jet-break.
+\item \citet{Rossi:2002aa} Considers jets with $E\propto \theta^{-2}$.
+Verifies at early times line-of-sight material dominates over core and wings, light curves resemble on-axis top-hats, but jet break is due to observer angle.
+Simple emission model.
+Postulates variety of jet-breaks due to off-axis structured jets, instead of distribution of $\Eiso$, $\thC$.
+$t_b \propto \thobs^{8/3}$.
+\item \citet{Granot:2002ab} Off-axis viewing of top hat jets, computed as boosted light bulb, analytic top-hat, and hydro sim.
+$\thobs < \theta_j$ look like on-axis top-hats, jet breaks increase with $\thobs$, evidence for $\thobs$-dependent slope before jet break in hydro models.
+\item \citet{Lipunov:2001aa, Zhang:2002aa} universal structured jet, $\theta^{-2}$, may explain jet breaks, etc.
+\item \citet{Panaitescu:2003aa} Off-axis viewing of power-law jets $E\propto \theta^{-q}$ with sharp cores.
+Analytic blast waves, detailed treatment of relativistic emission and synchrotron spectrum.
+When viewing within the core, no large effect so long as $q \geq 2$.
+Analytic formulae for aligned observers, numerical only for misaligned.
+Core visible at $t_a \sim E_0^{1/3} \thobs^{8/3}$ in ISM.
+Structure may only steepen jet breaks, proposes examining pre- and post- jet break slopes to determine whether structure is evident.
+\item \citet{Kumar:2003aa} Numerical evolution of radially-integrated Gaussian, top-hat, and power-law jets/  ``Therefore, a simple model in which the energy per unit solid angle is taken to be time independent and each element of the jet behaves as if it were part of a spherical flow with the same can serve as a useful approximation for the jet dynamics, as long as the jet is sufficiently relativistic.''
+\item \citet{Granot:2003aa} ``structured jet:'' jet with angular structure.
+Smooth power law in $\Theta = \sqrt{1 + \theta^2/\thC^2}$.
+Analysis of power-law jet light curves from \citet{Kumar:2003aa}.
+Only considers USJ, top-hat, and permutations.
+Find deviations from top-hat appearance small, USJ must have $E\approx \theta^{-2}$, $\Gamma\approx \theta^{0 < 1}$.
+\item \citet{Salmonson:2003aa} Numerical and analytic study of top-hat and structured jets.
+Computes doppler factor and angular size in asymptotic limits (no cooling frequency), finds far-off-axis closure relations.
+Examines `bump' seen when initially strongly beamed emission becomes structured, then proceeds to jet break.
+\item \citet{Nakar:2004aa} Distribution of luminosity and jet-breaks rules out USJ. 
+\item \citet{Rossi:2004aa}.
+Light curves and polarization for top-hat, USJ, and Gaussian jet.
+Gaussian jet shows slowly rising flux at sufficiently large viewing angles.
+Time dependence of polarization signal may distinguish between USJ and Gaussian.
+\end{itemize}
+
+The electromagnetic afterglow of \gwbns{} gave, quite literally, a new view on gamma-ray burst (GRB) afterglows.
+
+A canonical afterglow was almost immediately ruled out \citep{Troja:2017aa}.
+
+The structure of the blast wave giving rise to gamma-ray burst (GRB) afterglows has been a subject of interest since their discovery by \beppoSAX{} in GRB 970228 \citep{Wijers:1997aa}.
+
+{\color{blue} LUIGI: ?was found since early afterglow observations with BeppoSAX, when the
+presence of a structured outflow has been considered for explaining some of the
+temporal breaks observed in the light curves of a number of GRBs (Panaitescu and
+Kumar 2003, Apj 592: 390, Panaitescu 2005 MNRAS 362, 921). Candidates for
+structured jet exhibit a variation of the decay index at the break smaller that that
+expected for a top-hat spreading jet ($\Delta \alpha \approx 0.8$) and larger than
+that induced by the crossing of the cooling frequency ($\Delta\alpha=0.25$). Energy
+injection by a long lasting central engine can also induce temporal breaks, either
+flattening or steepening. Other effects such as transition to non-relativistic
+expansion, the transition from wind-like to ISM (Piro et al. 2005, Apj 623 314) or the
+emergence of an Inverse compton component (Corsi \& Piro
+2006A\&A...458..741C) can also produce breaks, in these case associated with a
+flattening of the light curve.
+More recenlty Ryan et al (2015) presented evidence of a structured jet in a sample
+based on SWIFT observations. Considering the number of processes that can
+produce breaks mentioned above, no undisputable observational evidence of a
+structured jet became available till the observations of GW170817. Real jets}
+
+Gamma-ray burst (GRB) afterglows, since their discovery by \beppoSAX{} in GRB 970228, have been a potent tool for studying GRBs and their progenitors.
 
@@
 
-A generic energy profile $E(\theta)$ may have several more parameters, but one can still associate an on-axis energy $E_0 = E(0)$ and an effective core width $\thC \sim |E''(0)/E_0|^{-1/2}$ which should fully specify the leading order near on-axis behaviour.
+A generic energy profile $E(\theta)$ may have several more parameters, but one can still associate with it an on-axis energy $E_0 = E(0)$ and an effective core width $\thC \sim |E''(0)/E_0|^{-1/2}$ which should fully specify the leading order near on-axis behaviour.
 
@@
 We refer to the regimes as ``aligned'' when $\thobs < \thC$, and ``misaligned'' when $\thobs > \thC$.
-
-%%%%%%%
-% METHODS
-%%%%%%%
 
@@
 To accommodate an initial structure profile $E(\theta)$ we consider the integrand of Equation \eqref{eq:flux} as a function of the polar angle $\theta$.
-We assume each constant $\theta$ annulus evolves independently, as an equivalent top hat of initial width $\thC = \theta$.
+We assume each constant-$\theta$ annulus evolves independently, as an equivalent top hat of initial width $\theta_j = \theta$.
 This is a very good approximation when transverse velocities are low: when the blast wave is ultra-relativistic and has not begun to spread and when the blast wave is non-relativistic and the spreading has ceased \citep{van-Eerten:2010aa}.
@@
 Comparing to \boxfit{} tests the fidelity of some of the assumptions and approximations of the single shell approach used by \afterglowpy{}.
-The simpler analytic version of the scheme on which \afterglowpy{} is based differed from \boxfit{} by factors from 2 to 8 \citep{vanEerten:2010aa}.
+The simpler analytic version of the scheme on which \afterglowpy{} is based differed from \boxfit{} by factors from 2 to 8 \citep{van-Eerten:2010aa}.
 We find \afterglowpy{} performs much better, with a relative difference of less than 50\% for the bulk of the evolution.
@@
 	\includegraphics[width=\textwidth]{figs/lc_thV_model_multi.pdf}
-	\caption{Aligned ($\thobs = \thC/2$) afterglow light curves for top-hat (blue), Gaussian (orange), and power law (green) jets.
-When viewed on-axis, jets containing angular structure are very difficult to distinguish from top-hats.
-The transition phase marking the onset of the jet break begins at $\tbm\sim3$ days with a shallow break and ends sharply at $\tbp \sim 100$ days.
-These particular light curves use $\thC = 0.1$ rad, $\thW = 0.4$ rad, $E_0 = 10^{52}$erg, $n_0=10^{-2}$cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, $\epsB = 10^{-3}$, and $d_L=40$Mpc.
-\label{fig:onaxis}}
+	\caption{X-ray afterglow light curves from structured jets at different viewing angles $\thobs$, calculated with \afterglowpy{}.
+Each panel shows the 1 keV flux density $F_\nu$ and the corresponding temporal slope $\alpha = d\log F_\nu / d\log \tobs$.
+Included models are the top-hat jet (dashed blue), Gaussian jet (solid green), $b=2$ power law (dot-dashed orange), and $b=6$ power law at $\thobs=0$ (upper left), $\thobs=2\thC=0.16$ rad (upper right), $\thobs=4\thC=0.32$ rad (lower left), and $\thobs=6\thC=0.48$ rad (lower right).
+These particular light curves all use $\thC = 0.08$ rad, $\thW = 0.24$ rad, $E_0 = 10^{53}$erg, $n_0=1$ cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, $\epsB = 10^{-2}$, $d_L=10^{28}$cm and $z=0.5454$.
+\label{fig:thVmodel}}
 \end{figure*}
@@
 
-\section{Refreshed Shocks --- Fast Tails and Spherical Cocoons}\label{sec:refreshedShocks}
+\subsection{Refreshed Shocks --- Fast Tails and Spherical Cocoons}\label{subsec:refreshedShocks}
 
@@
 
-\section{Relation to Energy Injection Models}
+\subsection{Relation to Energy Injection Models}
 
@@
 
+%%%%%%%%%%%%%%%
+%
+%.  DISCUSSION
+%
+%%%%%%%%%%%%%%%
+
 \section{Discussion}
@@
 Unfortunately, this same model independence makes it very difficult to distinguish between jet structure profiles, leaving both $E(\theta)$ and $\thobs$ uncertain.
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{figs/fit_E_theta.pdf}
+	\caption{Inferred $E(\theta)$ for \gwbns{} assuming Gaussian (blue, solid line) or power law (orange, dashed line) structure models.
+Lines show the median posterior value for $E(\theta)$ at each fixed value of $\theta$, shaded regions show the symmetric 68\% confidence interval (16\% and 84\% quantiles) at each $\theta$.
+\label{fig:fit_E_theta.pdf}}
+\end{figure}
 

### 2019-05-16 code/fitClosureBreaks.py

@@ -1,0 +1,158 @@
+import numpy as np
+import h5py as h5
+import matplotlib.pyplot as plt
+# import grbpy as grb
+import tbScalings as tbpy
+
+pltDir = "scalingsGaussian/"
+
+regime = 'G'
+nu = 1.0e16
+jetModel = 0
+b = 0
+Y = np.array([0.6, 1.0e53, 0.1, 0.4, b, 0.0, 0.0, 0.0, 1.0, 2.2,
+              0.1, 1.0e-6, 1.0, 1.0e26])
+spread = False
+n = 3
+
+NW = 3
+NV = 5
+NC = 3
+
+panelSize = 2
+
+thVs = np.linspace(0.0, 1.0, NV)
+thCs = np.linspace(0.05, 0.2, NC)
+thWs = np.linspace(0.1, 0.8, NW)
+
+tb0 = np.empty((NV, NC, NW))
+tb1 = np.empty((NV, NC, NW))
+al0 = np.empty((NV, NC, NW))
+al1 = np.empty((NV, NC, NW))
+al2 = np.empty((NV, NC, NW))
+
+color = ['C{0:d}'.format(i) for i in range(10)]
+ls = ['-', '--', '-.', ':']
+
+for k in range(NW):
+    fig = plt.figure(figsize=(NC*2, NV*2))
+    gs0 = fig.add_gridspec(NV, NC)
+
+    thW = thWs[k]
+
+    for i in range(NV):
+        thV = thVs[i]
+        for j in range(NC):
+            thC = thCs[j]
+            print("thW = {0:.3f} thV={0:.3f} thC={1:.3f}".format(
+                    thW, thV, thC))
+            gs = gs0[i, j].subgridspec(4, 1, hspace=0)
+            ax0 = fig.add_subplot(gs[:-1])
+            ax1 = fig.add_subplot(gs[-1])
+            ax = [ax0, ax1]
+
+            Y[0] = thV
+            Y[2] = thC
+            Y[3] = thW
+            _, t0, t1, a0, a1, a2 = tbpy.findBreaks(
+                regime, nu, jetModel, Y, 3, spread,
+                True,  ax, fig, printMode='summary')
+            tb0[i, j,  k] = t0
+            tb1[i, j,  k] = t1
+            al0[i, j,  k] = a0
+            al1[i, j,  k] = a1
+            al2[i, j,  k] = a2
+    fig.tight_layout()
+
[…]

### 2019-05-16 code/tbScalings.py

@@ -44,6 +44,30 @@ def slopePost(p, regime='G'):
         return -0.25*(1+3*p)
 
 
+def Etheta(jetType, th, Y):
+    E0 = Y[1]
+    thC = Y[2]
+    thW = Y[3]
+    b = Y[4]
+    if jetType == 0:
+        if th > thW:
+            return 0
+        return E0*math.exp(-0.5*th*th/(thC*thC))
+    elif jetType == 4:
+        if th > thW:
+            return 0
+        TH = math.sqrt(1.0 + th*th/(thC*thC))
+        return E0*math.pow(TH, -b)
+    elif jetType == -2:
+        if th > thW or th < thC:
+            return 0
+        return E0
+    else:
+        if th > thC:
+            return 0
+        return E0
+
+
 def f_pl(t, a, b):
     return a * np.power(t, b)
 
@@ -68,6 +92,27 @@ def f_pl3(t, F0, t0, t1, b0, b1, b2):
     return F
 
 
+def al_pl(t, a, b):
+    al = np.empty(t.shape)
+    al[:] = b
+    return al
+
+
+def al_pl2(t, F0, t0, b0, b1):
+    al = np.empty(t.shape)
+    al[t < t0] = b0
+    al[t >= t0] = b1
+    return al
+
+
+def al_pl3(t, F0, t0, t1, b0, b1, b2):
+    al = np.empty(t.shape)
+    al[t < t0] = b0
+    al[t >= t0] = b1
+    al[t >= t1] = b2
+    return al
+
+
 def chi2(x, t, F, f):
     y = x.copy()
     if len(x) is 4:
@@ -79,7 +124,7 @@ def chi2(x, t, F, f):
     return (dF*dF).sum()
 
 
-def fit_pl(t, F, printOutput=False):
+def fit_pl(t, F, printMode=None):
 
     b0 = np.log(F[-1]/F[0]) / np.log(t[-1]/t[0])
     a0 = (np.log(F[0])*np.log(t[-1])
@@ -89,13 +134,16 @@ def fit_pl(t, F, printOutput=False):
 
     res = opt.minimize(chi2, [a0, b0], (t, F, f_pl), bounds=bounds,
                        tol=1.0e-16)
-    if printOutput or not res.success:
+    if printMode is 'all':
         print(res)
+    elif printMode is 'summary':
+        print("Success: " + str(res.success) + " chi2={0:.2e}".format(
[…]

### 2019-06-21 structuredJets.tex
power law updates

@@
 \newcommand{\geff}{\ensuremath{g_{\mathrm{eff}}}}
+\newcommand{\theff}{\ensuremath{\theta_{\mathrm{eff}}}}
 \newcommand{\umin}{\ensuremath{u_{\mathrm{min}}}}
@@
 \author{Hendrik van Eerten}
-
-% \author{Eleonora Troja}
-
-% \author{Luigi Piro}
+\author{Luigi Piro}
+\author{Eleonora Troja}
 
@@
 Figure \ref{fig:jetStruct} shows a collection of jet energy distributions from the literature \citep{Aloy:2005aa, Mizuta:2009aa, Duffell:2013aa, Lazzati:2017aa, Margutti:2018aa}.
-Lacking a well-established physical model of the true $E(\theta)$, in particular its dependence on the parameters of the system, we consider two simple parameterized models: a Gaussian jet and a power law with a smooth core.
+Lacking a well-established physical model of the true $E(\theta)$, in particular its dependence on the parameters of the system, we consider two simple parameterized models: a Gaussian jet and a power law jet with a smooth core.
 
@@
 	E(\theta) &= E_0 \exp\left(-\frac{\theta^2}{2\thC^2}\right)  && \text{Gaussian} \label{eq:gauss}\\
-	E(\theta) &= E_0 \left(1 + \frac{\theta^2}{\thC^2} \right)^{-b/2}  && \text{power law} \label{eq:pl}
+	E(\theta) &= E_0 \left(1 + \frac{\theta^2}{b\thC^2} \right)^{-b/2}  && \text{power law} \label{eq:pl}
 \end{align}
@@
 The blue line is the B1 numerical simulation of \cite{Aloy:2005aa}, orange the HE16N numerical simulation of \cite{Mizuta:2009aa}, green an analytic ``boosted fireball'' model with $\gamma_{\rm{B}}=10$ and $\eta_0=3$ from \cite{Duffell:2013aa}, red the numerical simulation from \cite{Lazzati:2017aa} (L17), and purple the numerical simulation from \cite{Margutti:2018aa} (M18).
-The thick solid grey line is a Gaussian profile (Equation \eqref{eq:gauss}) with $E_0 = 3\times 10^{52}$ erg, $\thC = 6^\circ$, and $\thW=12^\circ$ and the thick dashed grey line is a smoothed power law profile (Equation \eqref{eq:pl}) with $E_0 = 10^{52}$ erg, $\thC = 4^\circ$, $\thW=20^\circ$, and $b=4.5$.
+The thick solid grey line is a Gaussian profile (Equation \eqref{eq:gauss}) with $E_0 = 3\times 10^{52}$ erg, $\thC = 6^\circ$, and $\thW=12^\circ$ and the thick dashed grey line is a smoothed power law profile (Equation \eqref{eq:pl}) with $E_0 = 10^{52}$ erg, $\thC = 2^\circ$, $\thW=20^\circ$, and $b=4.5$.
 The Gaussian and power law profiles can emulate the basic properties of the energy profiles found in the literature.
@@
 Outside $\thW$ the energy is initially zero, this acts as an outer truncation angle for the jet.
+Our power law profile includes a factor of $b^{-1}$ in the base which does not usually appear in the literature \citep{Granot:2003aa, Hotokezaka:2018aa}.
+This serves to normalize the value of $\thC$ and make it comparable between power laws of different $b$ and Gaussian jets.
+Both structure profiles obey
+\begin{equation}
+	\left . \frac{d^2}{d\theta^2} \log E \right \rvert_{\theta=0} = -\frac{1}{\thC^2}\ , \label{eq:thCdef}
+\end{equation} 
+which we take as a generic definition for $\thC$.
 
@@
 
-A generic energy profile $E(\theta)$ may have several more parameters, but one can still associate with it an on-axis energy $E_0 = E(0)$ and an effective core width $\thC \sim |E''(0)/E_0|^{-1/2}$ which should fully specify the leading order near on-axis behaviour.
+A generic energy profile $E(\theta)$, for instance from a numerical hydrodynamics simulation, may have several more parameters, but one can still associate with it an on-axis energy $E_0 = E(0)$ and an effective core width $\thC \sim |E''(0)/E_0|^{-1/2}$ which should fully specify the leading order near on-axis behaviour.
 
@@
 For the power law and Gaussian jet models this gives:
+\begin{align}
+	\theff &= \frac{\thobs}{2}&& \text{Gaussian}\ , \\
+	\theff &= \frac{\thobs}{\sqrt{1.8+2.1b^{-1.25} + (0.49-0.86b^{-1.25})\thobs/\thC}}&& \text{power law}\ . \label{eq:theff}
+\end{align}
 \begin{align}

### 2019-06-21 code/fitClosureBreaks.py

@@ -9,21 +9,21 @@ pltDir = "scalingsGaussian/"
 regime = 'G'
 nu = 1.0e16
 jetModel = 0
-b = 0
+b = 8
 Y = np.array([0.6, 1.0e53, 0.1, 0.4, b, 0.0, 0.0, 0.0, 1.0, 2.2,
               0.1, 1.0e-6, 1.0, 1.0e26])
-spread = False
-n = 3
+spread = True
+# n = 3
 
-NW = 3
-NV = 5
-NC = 3
+NW = 4
+NV = 11
+NC = 7
 
 panelSize = 2
 
 thVs = np.linspace(0.0, 1.0, NV)
-thCs = np.linspace(0.05, 0.2, NC)
-thWs = np.linspace(0.1, 0.8, NW)
+thCs = np.linspace(0.04, 0.24, NC)
+thWs = np.linspace(0.15, 0.75, NW)
 
 tb0 = np.empty((NV, NC, NW))
 tb1 = np.empty((NV, NC, NW))
@@ -44,7 +44,7 @@ for k in range(NW):
         thV = thVs[i]
         for j in range(NC):
             thC = thCs[j]
-            print("thW = {0:.3f} thV={0:.3f} thC={1:.3f}".format(
+            print("thW = {0:.3f} thV={1:.3f} thC={2:.3f}".format(
                     thW, thV, thC))
             gs = gs0[i, j].subgridspec(4, 1, hspace=0)
             ax0 = fig.add_subplot(gs[:-1])
@@ -149,7 +149,7 @@ fig, ax = plt.subplots(1, 1)
 for k in range(NW):
     for i in range(NC):
         ax.plot(thVs/thCs[i], al1[:, i, k], color=color[i], ls=ls[k])
-ax.set_xlabel(r'$\theta_{\mathrm{obs}}$')
+ax.set_xlabel(r'$\theta_{\mathrm{obs}} / \theta_C$')
 ax.set_ylabel(r'$\alpha_1$')
 fig.tight_layout()
 figname = pltDir + "al1_thVothC.pdf"

### 2019-06-21 code/paperPlots.py

@@ -476,7 +476,8 @@ def f_powerlaw(th, thC, thW, b=2):
     ath = np.atleast_1d(th)
     f = np.empty(ath.shape)
     valid = ath <= thW
-    f[valid] = 1.0 / np.power(np.sqrt(1.0 + (ath[valid] / thC)**2), b)
+    # f[valid] = 1.0 / np.power(np.sqrt(1.0 + (ath[valid] / thC)**2), b)
+    f[valid] = 1.0 / np.power(np.sqrt(1.0 + ((ath[valid] / thC)**2)/b), b)
     f[~valid] = 0.0
     return f
 
@@ -825,7 +826,7 @@ def getRegimePars(regime='D'):
     thC = 0.1
     thW = 0.4
     thV = 0.0
-    b = 8.0
+    b = 7.0
 
     p = 2.2
     epse_slow = 0.1
@@ -1215,11 +1216,12 @@ def calcSlopePost(jetModel, Y, regime):
 
 def makeAnalyticTestPlots():
 
-    # regimes = ['D', 'E', 'F', 'G', 'H']
-    regimes = ['E', 'G', 'H']
+    regimes = ['D', 'E', 'F', 'G', 'H']
+    # regimes = ['E', 'G', 'H']
     # regimes = ['D']
+    # regimes = ['H']
     jetModel = 4
-    spread = False
+    spread = True
 
     # thWs = [0.15, 0.25, 0.35, 0.45, 0.55, 0.65, 0.75, 0.85, 0.95]
     thWs = [0.25, 0.45, 0.65, 0.85]
@@ -1281,7 +1283,7 @@ def makeAnalyticTestPlots():
 
             # fig, ax = plt.subplots(3*NV, NC, figsize=(2*NC, 6*NV))
             panelWidth = 6.0
-            panelHeight = 6.0
+            panelHeight = 9.0
             fig = plt.figure(figsize=(panelWidth*NV, panelHeight*NC))
             gs0 = fig.add_gridspec(NC, NV)
 
@@ -1296,7 +1298,7 @@ def makeAnalyticTestPlots():
 
                     tW = calcTW(jetModel, Y, regime)
                     tb = calcTB(jetModel, Y, regime)
-                    # tbpm = calcTBpm(jetModel, Y, regime)
+                    tbpm = calcTBpm(jetModel, Y, regime)
 
                     Fnu = grb.fluxDensity(t, nu, jetModel, 0, *Y,
                                           spread=spread)
[…]

### 2019-06-21 code/spreadMathTest.py

@@ -1,0 +1,361 @@
+import math
+import numpy as np
+import matplotlib.pyplot as plt
+import grbpy as grb
+
+
+def f_tophat(th, **kwargs):
+    return np.ones(th.shape)
+
+
+def f_Gaussian(th, **kwargs):
+    thC = kwargs['thC']
+    return np.exp(-0.5 * th*th/(thC*thC))
+
+
+def f_powerlaw(th, **kwargs):
+    thC = kwargs['thC']
+    b = kwargs['b']
+    return np.power(1 + th*th/(b*thC*thC), -0.5*b)
+
+
+def frexp10(x):
+
+    exp = int(math.floor(math.log10(abs(x))))
+    man = x / 10**exp
+    return man, exp
+
+
+def get_t(th, f, f_kwargs, ta, t0):
+
+    Ith = np.zeros(th.shape)
+
+    thC = 0.5*(th[:-1]+th[1:])
+    dth = np.fabs(th[1:]-th[:-1])
+
+    dIdth = np.sqrt(f(thC, **f_kwargs))
+
+    Ith[1:] = np.cumsum(dIdth*dth)
+
+    t = t0 * np.power(3*math.sqrt(2) * Ith + math.pow(ta/t0, 1.5), 2.0/3.0)
+
+    return t
+
+
+def make_travelTimes_plot():
+
+    thC = 0.08
+    thW = 0.4
+    b = 5
+    t0 = 1.0
+
+    kw_tophat = {'thC': thC}
+    kw_Gaussian = {'thC': thC}
+    kw_powerlaw = {'thC': thC*math.sqrt(b), 'b': b}
+
+    TH = np.linspace(0.0, thW, 20)
+
+    t_a2C_tophat = np.empty(TH.shape)
+    t_C2a_tophat = np.empty(TH.shape)
+    t_b2C_tophat = np.empty(TH.shape)
+    t_C2b_tophat = np.empty(TH.shape)
+    t_a2C_Gaussian = np.empty(TH.shape)
+    t_C2a_Gaussian = np.empty(TH.shape)
+    t_b2C_Gaussian = np.empty(TH.shape)
+    t_C2b_Gaussian = np.empty(TH.shape)
+    t_a2C_powerlaw = np.empty(TH.shape)
+    t_C2a_powerlaw = np.empty(TH.shape)
+    t_b2C_powerlaw = np.empty(TH.shape)
+    t_C2b_powerlaw = np.empty(TH.shape)
+
[…]

### 2019-06-21 code/structComp.py

@@ -39,7 +39,7 @@ def powerlaw(theta, thC=0.1, thW=0.4, E0=3.0e53, n0=1.0, t0=1.0e7, b=3):
     E = np.empty(atheta.shape)
     g = np.empty(atheta.shape)
 
-    Th = np.sqrt(1.0 + th*th/(thC*thC))
+    Th = np.sqrt(1.0 + th*th/(b*thC*thC))
 
     E[onaxis] = E0/(4*np.pi) * np.power(Th, -b)
     g[onaxis] = np.sqrt(17*E[onaxis]/(2*n0*mp*c*c*c*c*c)) * math.pow(t0, -1.5)
@@ -313,7 +313,7 @@ if __name__ == "__main__":
     rad = np.pi/180.0
 
     gG, EG = gaussian(theta, thC=6*rad, thW=13*rad, E0=5e52)
-    gPL, EPL = powerlaw(theta, thW=60*rad, thC=4*rad, b=4.0, E0=1e52)
+    gPL, EPL = powerlaw(theta, thW=60*rad, thC=2*rad, b=4.0, E0=1e52)
     gBF0303, EBF0303 = boostedFireball(theta)
     gBF1003, EBF1003 = boostedFireball(theta, gb=10)
     gBF0310, EBF0310 = boostedFireball(theta, eta0=10)
@@ -464,7 +464,7 @@ if __name__ == "__main__":
     figE2, axE2 = plt.subplots(1, 1, figsize=(6, 4.5))
 
     gG, EG = gaussian(theta, thC=6*rad, thW=13*rad, E0=3e52)
-    gPL, EPL = powerlaw(theta, thW=60*rad, thC=4*rad, b=4.5, E0=1e52)
+    gPL, EPL = powerlaw(theta, thW=60*rad, thC=2*rad, b=4.5, E0=1e52)
 
     clr = ["k", "grey", "tab:blue", "tab:orange", "tab:green", "tab:red",
                 "tab:purple", "tab:brown", "tab:pink", "tab:olive", "tab:cyan"]
@@ -517,7 +517,7 @@ if __name__ == "__main__":
     figEc, axEc = plt.subplots(1, 1, figsize=(3.5, 3.0))
 
     gG, EG = gaussian(theta, thC=6*rad, thW=12*rad, E0=3e52)
-    gPL, EPL = powerlaw(theta, thW=60*rad, thC=4*rad, b=4.5, E0=1e52)
[…]

### 2019-06-21 code/tbScalings.py

@@ -271,6 +271,8 @@ def findBreaks(regime, NU, jetModel, Y, n=None, spread=False,
     """
 
     t0 = min(t0_OnA, t0_OfA)
+    # if t0 < 1.0:
+    #     t0 = 1.0
     t = np.geomspace(1.0e-1 * t0, min(0.8*tN, 3*tN*math.pow(chip, 8.0/3.0)),
                      300)
     # t = np.geomspace(0.1 * tN * math.pow(chim, 8.0/3.0),

### 2019-07-06 code/boxfitComp.py
Added a bunch of code and data

@@ -1,0 +1,173 @@
+import numpy as np
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+import grbpy as grb
+
+dataDir = "data/"
+
+
+def processBoxfitFile(filename):
+
+    t, nu, Fnu = np.loadtxt(filename, unpack=True, usecols=[1, 2, 3],
+                            delimiter=',')
+
+    Eiso = 0.0
+    n0 = 0.0
+    th0 = 0.0
+    thV = 0.0
+    p = 0.0
+    epse = 0.0
+    epsB = 0.0
+    dL = 0.0
+    z = 0.0
+    ksiN = 0.0
+
+    f = open(filename, "r")
+    for line in f:
+        if len(line) <= 0:
+            continue
+        words = line.split()
+        if len(words) < 3:
+            continue
+        if words[1] == "theta_0":
+            th0 = float(words[3])
+        elif words[1] == "E_iso":
+            Eiso = float(words[3])
+        elif words[1] == "n_0":
+            n0 = float(words[3])
+        elif words[1] == "theta_obs":
+            thV = float(words[3])
+        elif words[1] == "p":
+            p = float(words[3])
+        elif words[1] == "epsilon_B":
+            epsB = float(words[3])
+        elif words[1] == "epsilon_E":
+            epse = float(words[3])
+        elif words[1] == "ksi_N":
+            ksiN = float(words[3])
+        elif words[1] == "redshift:":
+            z = float(words[2])
+        elif words[1] == "luminosity" and words[2] == "distance:":
+            dL = float(words[3])
+
+    Y = np.array([thV, Eiso, th0, th0, 0.0, 0.0, 0.0, 0.0, n0, p,
+                  epse, epsB, ksiN, dL])
+    jetType = -1
+    specType = 0
+
+    return t, nu, Fnu, jetType, specType, Y, z
+
+
+def compareAll():
+
+    NC = 3
+    NV = 6
+    NN = 3
+
+    colors = ['C0', 'C1', 'C2', 'C3', 'C4']
+
+    for i in range(NC):
+        for j in range(NV):
+            fig, ax = plt.subplots(1, 1, figsize=(8, 6))
+            thV = 0.0
+            thC = 0.0
+            for k in range(NN):
[…]

### 2019-07-06 code/compXie.py

@@ -1,0 +1,218 @@
+import sys
+import numpy as np
+import matplotlib.pyplot as plt
+import grbpy as grb
+
+
+def loadXieData(filename):
+
+    f = open(filename, 'r')
+    line = f.readline()
+    f.close()
+    headers = line.split(',')[::2]
+    n = len(headers)
+
+    datasets = []
+
+    for i in range(n):
+        t, Fnu = np.genfromtxt(filename, skip_header=2, usecols=[2*i, 2*i+1],
+                               delimiter=',', unpack=True)
+        name = headers[i]
+
+        good = np.isfinite(t) & (t > 0) & np.isfinite(Fnu) & (Fnu > 0)
+        t = t[good]
+        Fnu = Fnu[good]
+
+        if 'x5 ' in name:
+            Fnu /= 5.0
+        elif 'x100 ' in name:
+            Fnu /= 100.0
+        elif 'x1000 ' in name:
+            Fnu /= 1000.0
+
+        if '3GHz' in name:
+            nu = 3.0e9
+        elif '6GHz' in name:
+            nu = 6.0e9
+        elif '5e14Hz' in name:
+            nu = 5.0e14
+        else:
+            nu = 1000.0 * grb.eV2Hz
+
+        if 'n1e-4' in name:
+            Y = np.array([0.34, 9.6e52, 0.15, 0.6, 1.93, 0.0, 0.0, 0.0, 1e-4,
+                          2.16, 0.02, 1e-3, 1.0, 1.234e26])
+        else:
+            Y = np.array([0.3, 9.6e52, 0.15, 0.6, 1.93, 0.0, 0.0, 0.0, 1e-5,
+                          2.16, 0.1, 5e-4, 1.0, 1.234e26])
+
+        datasets.append((name, nu, t, Fnu, Y))
+
+    return datasets
+
+
+def loadLazzatiData(filename):
+
+    f = open(filename, 'r')
+    line = f.readline()
+    f.close()
+    headers = line.split(',')[::2]
+    n = len(headers)
+
+    datasets = []
+
+    for i in range(n):
+        t, Fnu = np.genfromtxt(filename, skip_header=2, usecols=[2*i, 2*i+1],
+                               delimiter=',', unpack=True)
[…]

### 2019-07-06 code/gEffFit.py

@@ -1,0 +1,188 @@
+import h5py as h5
+import numpy as np
+import matplotlib.pyplot as plt
+import scipy.optimize as opt
+
+f = h5.File("gFit.h5", "r")
+
+thV = f['thV'][...]
+thC = f['thC'][...]
+thW = f['thW'][...]
+
+b = np.array([float(x) for x in f['D'].keys()])
+
+NV = len(thV)
+NC = len(thC)
+NW = len(thW)
+Nb = len(b)
+
+g_D = np.empty((Nb, NW, NC, NV))
+g_E = np.empty((Nb, NW, NC, NV))
+g_F = np.empty((Nb, NW, NC, NV))
+g_G = np.empty((Nb, NW, NC, NV))
+g_H = np.empty((Nb, NW, NC, NV))
+
+for i, bb in enumerate(b):
+    g_D[i, :, :, :] = f['D'][str(bb)][...]
+    g_E[i, :, :, :] = f['E'][str(bb)][...]
+    g_F[i, :, :, :] = f['F'][str(bb)][...]
+    g_G[i, :, :, :] = f['G'][str(bb)][...]
+    g_H[i, :, :, :] = f['H'][str(bb)][...]
+f.close()
+
+athV = []
+athC = []
+athW = []
+ab = []
+ag = []
+
+for i in range(Nb):
+    for j in range(NW):
+        for k in range(NC):
+            for l in range(NV):
+                g = g_E[i, j, k, l]
+                if np.isfinite(g):
+                    ab.append(b[i])
+                    athW.append(thW[j])
+                    athC.append(thC[k])
+                    athV.append(thV[l])
+                    ag.append(g)
+                g = g_G[i, j, k, l]
+                if np.isfinite(g):
+                    ab.append(b[i])
+                    athW.append(thW[j])
+                    athC.append(thC[k])
+                    athV.append(thV[l])
+                    ag.append(g)
+                g = g_H[i, j, k, l]
+                if np.isfinite(g):
+                    ab.append(b[i])
+                    athW.append(thW[j])
+                    athC.append(thC[k])
+                    athV.append(thV[l])
+                    ag.append(g)
+
+ab = np.array(ab)
+athW = np.array(athW)
[…]

### 2019-07-06 code/jetBreakTime.py

@@ -1,0 +1,129 @@
+import math
+import numpy as np
+import matplotlib.pyplot as plt
+import grbpy as grb
+import paperPlots as pp
+
+
+def analyzeBreakTimes(regime, jetModel):
+
+    NU, tN, Y, betaE = pp.getRegimePars(regime)
+
+    tfac = 1.1
+    nufac = 1.1
+
+    if jetModel is 4:
+        bs = np.array([2.0, 3, 4.0, 5.0, 6.0, 7.0, 8.0, 9.0, 10.0])
+    else:
+        bs = np.array([1.0])
+    thCs = np.array([0.04, 0.06, 0.08, 0.10, 0.12, 0.14, 0.16])
+    thW = 0.4
+
+    Nb = len(bs)
+    Nc = len(thCs)
+
+    panelWidth = 6.0
+    panelHeight = 6.0
+    fig = plt.figure(figsize=(panelWidth*Nb, panelHeight*Nc))
+    gs0 = fig.add_gridspec(Nc, Nb)
+
+    # minTb = math.pow(min(thCs), 8.0/3.0)
+
+    t = np.geomspace(1.0e-6*tN, 0.03*tN, 100)
+    nu = np.empty(t.shape)
+    nu[:] = NU
+
+    print("Calculating")
+
+    tb = np.empty((Nc, Nb))
+
+    for i, thC in enumerate(thCs):
+        for j, b in enumerate(bs):
+
+            Y[0] = 0.0
+            Y[2] = thC
+            Y[3] = thW
+            Y[4] = b
+
+            Fnu = grb.fluxDensity(t, nu, jetModel, 0, *Y, latRes=10)
+            Fnutr = grb.fluxDensity(t*tfac, nu, jetModel, 0, *Y, latRes=10)
+            Fnutl = grb.fluxDensity(t/tfac, nu, jetModel, 0, *Y, latRes=10)
+            Fnunr = grb.fluxDensity(t, nu*nufac, jetModel, 0, *Y, latRes=10)
+            Fnunl = grb.fluxDensity(t, nu/nufac, jetModel, 0, *Y, latRes=10)
+
+            alpha = np.log(Fnutr/Fnutl) / np.log(tfac*tfac)
+            beta = np.log(Fnunr/Fnunl) / np.log(nufac*nufac)
+
+            alPre = pp.calcSlopePre(jetModel, Y, regime)
+            alPost = pp.calcSlopePost(jetModel, Y, regime)
+
[…]

### 2019-07-06 code/slopePlots.py

@@ -1,0 +1,369 @@
+import sys
+import math
+import numpy as np
+import h5py as h5
+import matplotlib.pyplot as plt
+import paperPlots as pp
+
+
+def calcG(alpha, p, s, regime):
+    beta, al1, D, s1, s2, p = pp.get_powers(regime, p)
+    al2 = 3+s2
+
+    """
+    if regime is 'D':
+        return (-2-8*alpha+3*s) / (alpha-3-s)
+    elif regime is 'E':
+        return (-14./3.+3*s-8*alpha) / (alpha-3-s)
+    elif regime is 'F':
+        return (-8+3*s-8*alpha) / (alpha-3-s)
+    elif regime is 'G':
+        return (-6*p+3*s-8*alpha) / (alpha-3-s)
+    elif regime is 'H':
+        return (-6*p-2+3*s-8*alpha) / (alpha-3-s)
+    """
+
+    return (8*alpha + 3*al1 - 3*s) / (al2 - alpha)
+    # return ((8-4*s/D)*alpha + 3*al1 - 3*s*al1/(2*D)) / (al2 - alpha)
+
+
+def calcTh(g, jetModel, Y):
+
+    thV = Y[0]
+    thC = Y[2]
+    # thW = Y[3]
+    b = Y[4]
+
+    if jetModel is 0:
+        thS = 0.5*thV*(1.0-np.sqrt(1.0-4*g*thC*thC/(thV*thV)))
+    elif jetModel is 4:
+        gob = g/b
+        # des = 4*thC*thC*gob*(1+gob)/(thV*thV)
+        des = 4*thC*thC*g*(1+gob)/(thV*thV)
+        thS = 0.5*thV*(1.0+np.sqrt(1.0-des)) / (1+gob)
+
+    return thS
+
+
+def geff(jetModel, thV, thC, thW, b):
+    if jetModel is 0:
+        return 0.25*thV*thV/(thC*thC)
+    elif jetModel is 4:
+        # return 2*thV*thV / (thW*thW)
+        # return 2*thV*thV / (4*thC*thC + thV*thV)
+        return thV*thV / (4*thC*thC + thV*thV/b)
+
+
+def f_g(jetModel, thV, thC, thW, b, th):
+    if th > thW:
+        mdlogEdth = 0.0
+    elif jetModel is 0:
+        mdlogEdth = th/(thC*thC)
+    elif jetModel is 4:
[…]

### 2019-07-06 code/tbPlots.py

@@ -1,0 +1,8 @@
+import numpy as np
+import paperPlots as pp
+import grbpy as grb
+
+
+if __name__ == "__main__":
+
+

### 2019-07-06 code/thetaStarFit.py

@@ -1,0 +1,199 @@
+import h5py as h5
+import numpy as np
+import matplotlib.pyplot as plt
+import scipy.optimize as opt
+
+f = h5.File("thetaFit.h5", "r")
+
+thV = f['thV'][...]
+thC = f['thC'][...]
+thW = f['thW'][...]
+
+b = np.array([float(x) for x in f['D'].keys()])
+
+NV = len(thV)
+NC = len(thC)
+NW = len(thW)
+Nb = len(b)
+
+thS_D = np.empty((Nb, NW, NC, NV))
+thS_E = np.empty((Nb, NW, NC, NV))
+thS_F = np.empty((Nb, NW, NC, NV))
+thS_G = np.empty((Nb, NW, NC, NV))
+thS_H = np.empty((Nb, NW, NC, NV))
+
+for i, bb in enumerate(b):
+    thS_D[i, :, :, :] = f['D'][str(bb)][...]
+    thS_E[i, :, :, :] = f['E'][str(bb)][...]
+    thS_F[i, :, :, :] = f['F'][str(bb)][...]
+    thS_G[i, :, :, :] = f['G'][str(bb)][...]
+    thS_H[i, :, :, :] = f['H'][str(bb)][...]
+f.close()
+
+athV = []
+athC = []
+athW = []
+ab = []
+athS = []
+
+for i in range(Nb):
+    for j in range(NW):
+        for k in range(NC):
+            for l in range(NV):
+                thS = thS_E[i, j, k, l]
+                if np.isfinite(thS) and thS > 0:
+                    ab.append(b[i])
+                    athW.append(thW[j])
+                    athC.append(thC[k])
+                    athV.append(thV[l])
+                    athS.append(thS)
+                thS = thS_G[i, j, k, l]
+                if np.isfinite(thS) and thS > 0:
+                    ab.append(b[i])
+                    athW.append(thW[j])
+                    athC.append(thC[k])
+                    athV.append(thV[l])
+                    athS.append(thS)
+                thS = thS_H[i, j, k, l]
+                if np.isfinite(thS) and thS > 0:
+                    ab.append(b[i])
+                    athW.append(thW[j])
+                    athC.append(thC[k])
[…]

### 2019-07-08 structuredJets.tex
exploding the intro

@@
 \newcommand{\gwbns}{GW170817A}
+\newcommand{\grbbns}{GRB170817A}
 \newcommand{\afterglowpy}{{\tt afterglowpy}}
@@
 \newcommand{\beppoSAX}{{\em BeppoSAX}}
+\newcommand{\swift}{{\em Swift}}
+\newcommand{\swiftXRT}{{\em Swift-XRT}}
+\newcommand{\chandra}{{\em Chandra}}
 
@@
 \newcommand{\som}{\ensuremath{s_{\Omega}}}
+\newcommand{\OO}{\ensuremath{\mathcal{O}}}
 
@@
 
+\subsection{Wowee! 170817}
+
+The binary neutron star merger \gwbns{} and its associated electromagnetic counterparts provided a wealth of data to high energy astrophysics (CITE).
+Not least among these was its peculiar non-thermal afterglow, first detected in X-rays 9 days after the merger \citep{Troja:2017aa}.
+This was followed by radio 16 days after the merger and optical 73 days after the merger (CITE Radio \& Optical follow-up).
+Unlike any short gamma-ray burst (GRB) afterglow observed before, \grbbns{} steadily {\em rose} in brightness for ~160 days in all observed bands.
+After peak, the emission quickly decayed at a rate similar to other GRB afterglows.
+
+The absence of early X-ray emission, with early non-detections by \swiftXRT{} and a deep upper limit from \chandra{}, led early analyses to consider the effect if viewing angle on the emission \citep{Troja:2017aa} (CITE MORE).
+Given the gravitational wave signal of a binary neutron star merger is observable almost regardless of of orientation, it is in fact expected that GRB/GW events would be viewed at moderate inclination.
+
+As \grbbns{}'s afterglow continued to rise for weeks after the burst, it became evident the emission could not be explained by a simple uniform ``top hat'' jet viewed off axis.
+More sophisticated models were considered: ``structured jets'' with non-uniform angular distribution of energy and quasi-isotropic ``refreshed shocks'' with significant velocity stratification of the ejecta and modest Lorentz factors.
+The observation of apparent superluminal motion of the radio centroid and the steep turnover of the light curve after 160 days confirmed the relativistic and collimated nature of the outflow, in accordance with the structured jet picture.
+
+\subsection{History of structure and viewing angle}
+
+The first GRB afterglow was discovered by \beppoSAX{} as part of GRB 970228 \citep{Wijers:1997aa}.
+GRB afterglows present as broadband synchrotron emission following the prompt gamma-ray signal and can last for days, weeks, months, and years.
+
+\subsubsection{Standard model}
+
+The GRB afterglow emission arises from the
+
+\subsubsection{Angular Structure}
+\subsubsection{Viewing Angle}
+
+\subsection{Overview of 170817A analysis/models}
+
+\subsection{What we're doing}
+
+In this paper we develop a theoretical model of the electromagnetic afterglow of generic structured jets for arbitrary viewing inclinations.
+The model takes as input the energy and Lorentz factor angular profiles, which may be intrinsic to the jet launching mechanism
+
+The light curves resemble broken power laws.
+We calculate viewing angle dependent closure relations, directly relating the effective temporal evolution of the light curve to the viewing angle and explosion geometry.
+
+\newpage
+
+\newpage
+
+\subsection{Lit Review}
 \begin{itemize}
 \item \citet{Meszaros:1998aa} First discusses effect of angular structure in $E$ and $\Gamma$, predicts rising light curves when seen off axis, calculates closure relations in various cases.
-\item \citet{Dalal:2002aa} Considers emission from boosted lightbulb, refers to $\thobs > \theta_j$ as ``off-axis,'' points out off-axis jet breaks will be delayed and dim, light curves converge at late time.
+\item \citet{Nakamura:1999aa} Far off-axis emission from top-hat jet in stellar wind environment, application to GRB 980425.
 \item \citet{Moderski:2000aa} Relativistic effects (equal arrival time surface, etc) smear jet-break.
+\item \citet{Ioka:2001aa} Viewing angle dependent prompt emission.  GRB prompt peak $L$ - spectral lag relation from viewing angle.  
+\item \citet{Lipunov:2001aa, Zhang:2002aa} universal structured jet, $\theta^{-2}$, may explain jet breaks, etc.
 \item \citet{Rossi:2002aa} Considers jets with $E\propto \theta^{-2}$.
@@
 $t_b \propto \thobs^{8/3}$.
+\item \citet{Dalal:2002aa} Considers emission from boosted lightbulb, refers to $\thobs > \theta_j$ as ``off-axis,'' points out off-axis jet breaks will be delayed and dim, light curves converge at late time.
 \item \citet{Granot:2002ab} Off-axis viewing of top hat jets, computed as boosted light bulb, analytic top-hat, and hydro sim.
 $\thobs < \theta_j$ look like on-axis top-hats, jet breaks increase with $\thobs$, evidence for $\thobs$-dependent slope before jet break in hydro models.
-\item \citet{Lipunov:2001aa, Zhang:2002aa} universal structured jet, $\theta^{-2}$, may explain jet breaks, etc.
+\item \citet{Yamazaki:2002aa, Yamazaki:2003aa} XRF as off-axis prompt GRB using \citet{Ioka:2001aa} model.
 \item \citet{Panaitescu:2003aa} Off-axis viewing of power-law jets $E\propto \theta^{-q}$ with sharp cores.
@@
 Time dependence of polarization signal may distinguish between USJ and Gaussian.
+\item \citet{Yamazaki:2004aa} $E_P$ -- $E_{iso}$ prompt relation from viewing angle.
+\item \citet{Peng:2005aa} Two-component (narrow + wide) jet, afterglows, blurred jet breaks, off-axis as XRF.
 \end{itemize}
@@
 
-We find the light curves of structured jets show two modes of behaviour, depending on whether the observer is \emph{aligned} ($\thobs < \thC$) or \emph{misaligned} ($\thobs > \thC$) TODO: CITE PREVIOUS STRUCTURED JET WORK
+Using the definition of $\thC$ in Equation \eqref{eq:thCdef} we may write the angular energy profile near the jet axis as:
+\begin{equation}
+	E(\theta) = E_0 \left (1 - \frac{\theta^2}{2\thC^2} \right) + \OO(\theta^3) \label{eq:EthetaNear}
+\end{equation}
+
+The light curves of structured jets show two modes of behaviour, depending on whether the observer is \emph{aligned} ($\thobs < \thC$) or \emph{misaligned} ($\thobs > \thC$).
 In the \emph{aligned} case, the light curves follow the standard on-axis top hat behaviour modified slightly for non-zero viewing angle.

### 2019-07-08 code/paperPlots.py

@@ -1214,6 +1214,47 @@ def calcSlopePost(jetModel, Y, regime):
     return alpha
 
 
+def calcThetaEff(jetModel, Y):
+
+    thEff = 0.0
+    thV = jetModel[0]
+    thC = jetModel[2]
+    b = jetModel[4]
+
+    if jetModel == 0:
+        thEff = 0.5*thV
+    elif jetModel == 4:
+        thEff = thV / np.sqrt(1.83+2.10*np.power(b, -1.25)
+                              + (0.486-0.862*np.power(b, -1.15)) * thV/thC)
+    return thEff
+
+
+def calcGEff(jetModel, Y):
+
+    thV = jetModel[0]
+    thC = jetModel[2]
+    b = jetModel[4]
+
+    dlfdth = 0.0
+    thEff = calcThetaEff(jetModel, Y)
+
+    if jetModel == 0:
+        dlfdth = -thEff / (thC*thC)
+    elif jetModel == 4:
+        dlfdth = -thEff / (thC*thC + thEff*thEff/b)
+
+    return -(thEff-thV) * dlfdth
+
+
+def calcSlopeStructEff(jetModel, Y, regime):
+
+    geff = calcGEff(jetModel, Y)
+
+    al = calcSlopeStruct(jetModel, Y, regime, g=geff, som=1.0)
+
+    return al
+
+
 def makeAnalyticTestPlots():
 
     regimes = ['D', 'E', 'F', 'G', 'H']

### 2019-07-08 code/plotModelThV.py

@@ -1,6 +1,7 @@
 import numpy as np
 import grbpy as grb
 import matplotlib.pyplot as plt
+# import paperPlots as pp
 
 
 def plotPanel(fig, gs0, t, nu, thV, Y, Z, modelLegend=False):

### 2019-07-09 structuredJets.tex
Intro additions

@@
 
-\subsection{Wowee! 170817}
+The binary neutron star merger event \gwbns{} provided, quite literally, a new view on gamma-ray burst (GRB) afterglows (CITE LIGO, Discovery papers).
+Unlike typical short GRB afterglows, which begin bright and decay from detection with a ~week timescale, \gwbns{}'s non-thermal afterglow was undetectable for nine days whereupon it began steadily increasing in brightness in all bands for ~160 days \citep{Troja:2017aa, Troja:2018aa, van-Eerten:2018aa} (CITE OTHERS).
+Very long baseline (VLBI) radio imagery over this period identified a radio core with an apparent superluminal motion, indicating the emitting surface was moving at relativistically at an oblique angle towards the Earth (CITE Mooley, Ghirlanda).
+The emission peaked at 160 days and proceeded to sharply decay at a rate commensurate with other short GRB afterglows (CITE YITL, peak-decay papers).
+
+The lack of early emission, slow rising light curve, apparent motion of the radio centroid, and sharp decline post-peak are all consistent with emission from a \emph{structured jet}, a collimated blast wave with a non-trivial angular distribution of energy, viewed a moderate angle away from the jet axis (CITE YITL, Mooley, Ghirlanda, Lamb, Hotokezaka, ...).
+The combined effects of a moderate viewing angle and angular structure in the jet produce a light curve significantly different from the standard on-axis uniform ``top-hat'' jet used extensively in GRB afterglow analysis.
+Since the gravitational wave signal of a binary neutron star merger is nearly isotropic, it is expected the majority of future GW-GRBs will also be viewed at significant inclination and may have similarly peculiar light curves as \gwbns{}.
+
+A solid theoretical understanding of structured jet afterglows, including viewing angle effects, will be required to make the most use of future GW-GRB observations, the \gwbns{} dataset, and re-analysis of archival short GRBs.
+To this end, we have calculated the explicit viewing angle and structure-dependent closure relations governing the afterglows of structured jets.
+We have also developed the computational tool \afterglowpy{}: a public, open source \python{} package for on-the-fly computation of structured jet afterglows with arbitrary viewing angle.
+
+Jet structure and viewing angle have a long history as potential explanations for temporal behaviors and breaks in GRB afterglows.
+\citet{Meszaros:1998aa} first considered anisotropic models and noted they may present as ``orphan afterglows'' without a prompt GRB signal if viewed sufficiently off-axis.
+Detailed theoretical calculations of structured jet afterglow light curves concluded several facts: on-axis structured light curves resemble those from top hat jets, off-axis structured light curves show a temporal break at an observer time $t_b$ that scales with the viewing angle $\thobs$ as $t_b\propto \thobs^{8/3}$, and the pre-break slope can depend on the viewing angle and particular structure model \citep{Rossi:2002aa, Dalal:2002aa, Granot:2002aa, Panaitescu:2003aa, Kumar:2003aa, Granot:2003aa, Salmonson:2003aa, Rossi:2004aa}.
+The ``Universal Structured Jet'' was a structured jet with isotropic-equivalent energy $E \propto \theta^{-2}$ proposed to explain the diversity of jet-break times as a viewing angle effect  \citep{Lipunov:2001aa, Zhang:2002aa}, although this was ultimately unsuccessful \citep{Nakar:2004aa}.
+
+The temporal break in the structured jet afterglow light curve can be more significant than in top hat models, and has been invoked to explain some observed jet breaks which do not easily fit the standard closure relations \citep{Panaitescu:2005aa, Panaitescu:2005ab}, although other dynamical and spectral processes can have similar effects (CITE Piro2005, COrsi\&Piro2006).
+GRB prompt emission viewed significantly off-axis was (is?) the proposed origin for X-ray flashes \citep{Ioka:2001aa, Yamazaki:2002aa, Yamazaki:2003aa, Peng:2005aa}.
+More recently, small non-zero viewing angles have been measured in a subset of the \swiftXRT{} afterglow sample \citep{Ryan:2015aa}.
+
+In this paper, we calculate.
+In Section \ref{sec:motivation} we review the general properties of structured jets and their necessity to GRB afterglows.
+In Section \ref{sec:numerical} we develop our theoretical framework and describe its numerical implementation in \afterglowpy{}.
+Section \ref{sec:structuredJets} characterizes the general behavior of structured jet afterglow light curves, provides the closure relations with explicit viewing angle dependence, and relates structured jets to standard energy injection models.
+Section \ref{sec:gw170817} demonstrates an application to \gwbns{}.
+Section \ref{sec:discussion} gives further discussion and Section \ref{sec:summary} gives the summary.
+Detailed derivation of the closure relations is provided in Appendices \ref{app:derive1} and \ref{app:derive2}.
+
+\newpage
+
+\subsection{Old Draft}
 
@@
 More sophisticated models were considered: ``structured jets'' with non-uniform angular distribution of energy and quasi-isotropic ``refreshed shocks'' with significant velocity stratification of the ejecta and modest Lorentz factors.
-The observation of apparent superluminal motion of the radio centroid and the steep turnover of the light curve after 160 days confirmed the relativistic and collimated nature of the outflow, in accordance with the structured jet picture.
-
-\subsection{History of structure and viewing angle}
+The observation of apparent superluminal motion of the radio centroid and the steep turnover of the light curve after 160 days confirmed the relativistic and collimated nature of the outflow, in accordance with the structured jet picture (CITE Mooley, Ghirlanda, YITL, other steepening paper).
+
+It is expected, of course, that
+
+Structured jets, blast waves with a non-uniform angular distribution of energy, have been invoked to explain several temporal features in GRB afterglow light curves.
+
+\subsubsection{History of structure and viewing angle}
 
@@
 
-\subsubsection{Standard model}
-
-The GRB afterglow emission arises from the
-
-\subsubsection{Angular Structure}
-\subsubsection{Viewing Angle}
-
-\subsection{Overview of 170817A analysis/models}
-
-\subsection{What we're doing}
+\subsubsection{What we're doing}
 
@@
 We calculate viewing angle dependent closure relations, directly relating the effective temporal evolution of the light curve to the viewing angle and explosion geometry.
-
-\newpage
 
@@
 
+\subsection{Old Old Draft}
+
 The electromagnetic afterglow of \gwbns{} gave, quite literally, a new view on gamma-ray burst (GRB) afterglows.
@@
 
-The transition between pre-jet break and post-jet break begins at $\tbm$ and completes at $\tbp$, given in the single shell approximation (see Appendix \ref{sec:derive1}) by:
+The transition between pre-jet break and post-jet break begins at $\tbm$ and completes at $\tbp$, given in the single shell approximation (see Appendix \ref{app:derive1}) by:
 \begin{align}
@@
 Table \ref{tab:slopes} gives the temporal power law slope of the light curve in this phase.
-These slopes are derived in Appendix \ref{sec:derive1}.
+These slopes are derived in Appendix \ref{app:derive1}.
 
@@
 
-The temporal and spectral slopes for various regimes are given in Table \ref{tab:slopes}.  The derivation of the closure relations, $\tW$, and $\tb$ are given in Appendix \ref{sec:derive1}.
+The temporal and spectral slopes for various regimes are given in Table \ref{tab:slopes}.  The derivation of the closure relations, $\tW$, and $\tb$ are given in Appendix \ref{app:derive1}.
 
@@
 As in Figure \ref{fig:slopesG} the width of the $G$ and $H$ regimes reflects varying the value of $p$ between two and three.
-For a derivation see Appendix \ref{sec:derive3}.
+For a derivation see Appendix \ref{app:derive3}.
 
@@
 
-\section{Application: \gwbns{}}
+\section{Application: \gwbns{}}\label{sec:gw170817}
 
@@
 
-\section{Discussion}
+\section{Discussion}\label{sec:discussion}
 
@@
 
-\section{Summary}
+\section{Summary}\label{sec:summary}
 
@@
 \appendix
-\section{Derivation of the Off-Axis Jet equations}\label{sec:derive1}
+\section{Derivation of the Off-Axis Jet equations}\label{app:derive1}
 
@@
 
-\section{Derivation of the Structured Jet equations}\label{sec:derive2}
+\section{Derivation of the Structured Jet equations}\label{app:derive2}
 

### 2019-07-24 structuredJets.tex
Implemented comments, finished Sec 3.1.

@@
 \newcommand{\epsB}{\ensuremath{\varepsilon_{\mathrm{B}}}}
+\newcommand{\xiN}{\ensuremath{\xi_N}}
 \newcommand{\sigT}{\ensuremath{\sigma_{\mathrm{T}}}}
@@
 
-\title{GRB Afterglows In The Multi-Messenger Era  OR  Electromagnetic Afterglows Of Structured Jets  OR  Structured Jets At All Angles}
+\title{GRB Afterglows In The Multi-Messenger Era  \hspace{10in} OR\hspace{10in}   Electromagnetic Afterglows Of Structured Jets \hspace{10in}  OR\hspace{10in}  Structured Jets At All Angles\hspace{10in}  OR \hspace{10in}The Electromagnetic Afterglows of Structured Jets: Numerical Models and Closure Relations}
+
 \correspondingauthor{Geoffrey Ryan}
@@
 
+% Add sentence explaining "jet structure" ==> "angular jet structure", we calculate closure relations and explicitly relate them to energy injection/refreshed shock/velocity stratification models.
+
 \end{abstract}
@@
 A solid theoretical understanding of structured jet afterglows, including viewing angle effects, will be required to make the most use of future GW-GRB observations, the \gwbns{} dataset, and re-analysis of archival short GRBs.
+% Mention standard tools, explain closure relations
 To this end, we have calculated the explicit viewing angle and structure-dependent closure relations governing the afterglows of structured jets.
 We have also developed the computational tool \afterglowpy{}: a public, open source \python{} package for on-the-fly computation of structured jet afterglows with arbitrary viewing angle.
+
+% We generalize closure relations... mention energy injection
 
@@
 
-In this paper, we calculate.
+In this paper, we provide...
 In Section \ref{sec:motivation} we review the general properties of structured jets and their necessity to GRB afterglows.
@@
 Detailed derivation of the closure relations is provided in Appendices \ref{app:derive1} and \ref{app:derive2}.
+
+% Explicitly say we were the first to find x-ray, predict steep post-break slope.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%
+%
+%  WHY STRUCTURED JETS
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Motivation: Why Structured Jets?}\label{sec:motivation}
 
-The \emph{structured jet} is a GRB emission model where the isotropic-equivalent energy of a blast wave is a function of the angle from the jet axis: $\Eiso = E(\theta)$.
-The specific structure of a jet is determined by the intrinsic structure of the jet launching mechanism as well as the sculpting that occurs as the jet burrows out of the encasing ejecta debris (as in a binary neutron star merger) or stellar envelope (as in a collapsar).
+The \emph{structured jet} is a GRB jet model where the isotropic-equivalent energy of the blast wave is a function of the angle from the jet axis: $\Eiso = E(\theta)$.
+The particular angular structure of a jet is first imposed by the jet launching mechanism and then modified by the sculpting that occurs as the jet burrows out of the surrounding ejecta debris (as in a binary neutron star merger) or stellar envelope (as in a collapsar).
+In the case of neutron star mergers, it is not a given that there is sufficient ejecta in the polar regions to significantly alter the intrinsic jet structure.
 
@@
 \end{align}
-
-%
-% Update jet Structure models paper.
-%
 
@@
 The blue line is the B1 numerical simulation of \cite{Aloy:2005aa}, orange the HE16N numerical simulation of \cite{Mizuta:2009aa}, green an analytic ``boosted fireball'' model with $\gamma_{\rm{B}}=10$ and $\eta_0=3$ from \cite{Duffell:2013aa}, red the numerical simulation from \cite{Lazzati:2017aa} (L17), and purple the numerical simulation from \cite{Margutti:2018aa} (M18).
-The thick solid grey line is a Gaussian profile (Equation \eqref{eq:gauss}) with $E_0 = 3\times 10^{52}$ erg, $\thC = 6^\circ$, and $\thW=12^\circ$ and the thick dashed grey line is a smoothed power law profile (Equation \eqref{eq:pl}) with $E_0 = 10^{52}$ erg, $\thC = 2^\circ$, $\thW=20^\circ$, and $b=4.5$.
+The thick solid grey line is a Gaussian profile (Equation \eqref{eq:gauss}) with $E_0 = 3\times 10^{52}$ erg, $\thC = 6^\circ$, and $\thW=12^\circ$ and the thick dashed grey line is a power law profile (Equation \eqref{eq:pl}) with $E_0 = 10^{52}$ erg, $\thC = 2^\circ$, $\thW=20^\circ$, and $b=4.5$.
 The Gaussian and power law profiles can emulate the basic properties of the energy profiles found in the literature.
@@
 
+% Add description of each paper, explaining method of collimation/structure generation.
+
+% Gaussian is  b--> infty
+
 Figure \ref{fig:jetStruct} shows an example of each model together with jet energy profiles drawn from the literature, mostly the result of numerical relativistic hydrodynamic simulations.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%
+%
+%  METHODS
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Methods And The \afterglowpy{} Package}\label{sec:numerical}
@@
 To compute the light curves of structured jet afterglows we constructed numerical and analytic models utilizing the single shell approximation of \cite{van-Eerten:2010aa, van-Eerten:2018ab}.
+Iterations of this model have been applied in the \gwbns{} x-ray discovery paper \citep{Troja:2017aa}, follow-up studies of \gwbns{} \citep{Troja:2018aa, Piro:2019aa, van-Eerten:2018aa}, and in examinations of archival kilonova candidates \citep{Troja:2018ab, Troja:2019aa}.
 This approach integrates over the massive ejecta, contact discontinuity, and forward shock complex, treating it as a single fluid element with uniform radial structure.
-We utilize a trans-relativistic equation of state which smoothly interpolates between the ultra-relativistic and non-relativistic limits and include an approximate prescription for jet spreading.
+We utilize a trans-relativistic equation of state which smoothly interpolates between the ultra-relativistic and non-relativistic limits \citep{van-Eerten:2013ab, Nava:2013aa} and include an approximate prescription for jet spreading.
 This approach, with a simplified equation of state and jet spreading model, has been used successfully to model the synthetic light curves of top hat jets from multidimensional numerical relativistic hydrodynamics simulations \citep{van-Eerten:2010aa}.
@@
 The observer is located in a direction $\hat{\bf n}$ which makes an angle $\thobs$ with the $z$-axis, $\hat{\bf n} \cdot \hat{\bf z} = \cos \thobs$, and is oriented along the $x$-axis, $\phobs = 0$.
-A particular point on the blast wave $\hat{\bf r} = (\theta, \phi)$ makes an angle $\psi$ (with cosine $\mu$) with the viewer, $\mu = \cos \psi = \hat{\bf n} \cdot \hat{\bf r}$.
+A particular point on the blast wave $\hat{\bf r} = (\theta, \phi)$ makes an angle $\psi$ (with cosine $\mu$) with the viewer direction, $\mu = \cos \psi = \hat{\bf n} \cdot \hat{\bf r}$.
 
@@
 
-To compute the light curve of a top-hat jet of initial width $\thC$ we first must calculate the time evolution of the blast wave.
+To compute the light curve of a top-hat jet of initial width $\theta_0$ we first must calculate the time evolution of the blast wave.
 In the single-shell approximation we treat the ejecta mass, contact discontinuity, and forward shock as a single unit propagating through a cold ambient medium with constant rest-mass density $\rho_0 = \Mp n_0$.
-We utilize the TM trans-relativistic equation of state to describe the fluid consistently throughout its evolution \citep{Mignone:2005aa}.
-The forward shock is a radius $R$ from the explosion, and the fluid behind the shock has four-velocity $u$ and Lorentz factor $\gamma$.
+We utilize the ``TM'' trans-relativistic equation of state to describe the fluid consistently throughout its evolution \citep{Mignone:2005aa}.
+The forward shock is at radius $R$ from the explosion, and the fluid behind the shock has four-velocity $u$ and Lorentz factor $\gamma$.
 The shock jump conditions can be used to determine the shock speed:
@@
 \end{align}
+% TODO: Update spreading description
 In Equation \eqref{eq:E} the first term is the kinetic energy of the ejected mass $\Mej$, assumed to have already accelerated and adiabatically cooled to its coasting velocity.
@@
 Equation \eqref{eq:fOm} describes the fractional solid angle of the jet in terms of the time dependent opening angle $\theta_j(t)$.
-While the blast wave is relativistic $\theta_j = \thC$ and $f_\Omega$ is constant, but once the jet edge comes in causal contact with the core it begins to spread due to its own internal pressure.
-The jet spreads and $\theta_j$ increases until the blast wave is spherical and $f_\Omega=1$.
-The spreading occurs at sound speed $c_s$ in the fluid rest-frame, causing the opening angle of the jet to increase as \citep{van-Eerten:2010aa, Duffell:2018aa}:
-\begin{equation}
-	\dot{\theta_j} = \frac{c_s}{\gamma R}\ , \qquad \text{if } u < 1/3\thC \text{ and } \theta_j > \pi/2\ . \label{eq:thetadot}
-\end{equation}
-The criterion $u < 1/3\thC$ is satisfied when a sound wave can propagate from $\theta = \thC$ to $\theta=0$ in a blast wave propagating in a uniform ISM (CITE HENDRIK).
-It is similar to the condition given in \cite{Duffell:2018aa}, which found a numerical factor of 2.5 (instead of 3) after calibrating to numerical simulations.
-Our criteria differs from that used in \citet{Troja:2018aa, Piro:2019aa, van-Eerten:2018aa} which used an overly simplistic $u < 1$ criterion to begin jet spreading.
-
-Given an expression for $E$ in terms of $t$, $R$, $u$, and $\theta_j$, Equation \eqref{eq:E} may be differentiated with respect to $t$ and solved for $\dot{u}$.
-A standard adiabatic evolution will maintain $E=$ constant, while in a continuously refreshed shock scenario $E = E_{>u}(u)$ and in standard energy injection models $E \propto t^-q$.
-This defines a three dimensional system of ordinary differential equations (ODEs) in the variables $(R, u, \theta_j)$ which may be solved numerically or, in certain limits, analytically from appropriate initial conditions.
-
+
+Pressure gradients along the blast wave surface can drive lateral spreading of the jet, causing $\theta_j(t)$ (and $f_\Omega$) to increase with time  from its initial value $\theta_j(0) = \theta_0$ (CITE Rhoads?).
+Initially spreading is negligible as each fluid element of the highly relativistic jet is only in causal contact with nearby regions of similar pressure.
+Spreading begins once sound waves have had sufficient time to travel across the surface of the jet and communicate the presence of pressure gradients, launching rarefaction waves which drive the jet to spread at its local sound speed \citep{Rhoads:1999aa, van-Eerten:2012aa, Duffell:2018aa}.
+Spreading continues until the blast wave becomes spherical and $f_\Omega = 1$.
+
+Numerous semi-analytic prescriptions for jet spreading exist in the literature, for example \citet{Rhoads:1999aa} (R99), \citet{Granot:2012aa} (GP12), and \citet{Duffell:2018aa} (DL18).
+To remain consistent with the presence of angular structure in the jet and ensure spreading occurs at sonic speeds in our adopted equation of state it is necessary to construct our own jet spreading prescription.
+
+A wave traveling at the sound speed $c_s$ in the fluid rest frame will maintain a velocity $\beta_{\bot} c$ laterally along the shock front:
+\begin{equation}
+	\beta_\bot = \gamma \sqrt{ (1-\beta \dot{R}/c)c_s^2 - (\dot{R}/c - \beta)^2} \ .
+\end{equation}
+Using the shock-jump conditions and TM equation of state this reduces to:
+\begin{equation}
+	\beta_\bot = \sqrt{\frac{2u^2+3}{4u^2+3}} \frac{\dot{R}}{2\gamma c}\ . \label{eq:spreadVel}
+\end{equation}
+In the ultra-relativistic limit $\beta_\bot = \sqrt{3/8} c_s/(c\gamma) = 1/(\sqrt{8} \gamma)$.
+In this same limit, a signal launched at $t=0$ traveling at $\beta_\bot$ along the shock front will cover an angular distance  $\Delta \theta = 1/(3\sqrt{2}\gamma)$(CITE Hendrik).
+Taking $\thC$, defined by Equation \eqref{eq:thCdef}, as the angular scale for order unity changes in the jet pressure, we can approximate the onset of spreading as when $u = 1/(3\sqrt{2}\thC)$.
+Further taking $\beta_\bot$ as the expansion velocity once spreading begins, we can write an evolution equation for $\theta_j$:
+\begin{equation}
+	\dot{\theta}_j = \begin{cases}
+					0 & \text{if } u > 1/(3\sqrt{2} \thC)\\
+					\beta_\bot c / R &\text{otherwise}
+				\end{cases}\ . \label{eq:thetadot}
+\end{equation}
+The spreading prescription in Equation \eqref{eq:thetadot} is very similar to existing models in the literature.
+Like R99, GP12 ($a=0$ case), and DL18 in the ultra-relativistic limit we have $\dot{\theta}_j \propto 1/(\gamma t)$.
+Like DL18 we freeze spreading completely while $u \thC$ exceeds a threshold value.
+In fact, while $u \gg 1$ our prescription is equivalent to the DL18 model with parameters $P_k = Q_k = 3\sqrt{2}$, a slight modification to their numerically fit values $P_k = 4.0$ and $Q_k = 2.5$.
+Afterglow light curves computed using Equation \eqref{eq:thetadot} were found to agree better with established simulation based models (see Section \ref{subsec:bioxfitcomp}) than those computed with the DL18 parameters.
+This jet spreading prescription differs from that used in \citet{Troja:2018aa, Piro:2019aa, van-Eerten:2018aa} which used a simple $u < 1$ criterion to begin jet spreading and set $\beta_\bot = c_s / (c \gamma)$.
+
+% TODO: clarify role of E, where these formulas come from.
+Given an expression for the total blast wave energy $E$ in terms of $t$, $R$ and $u$, Equations \eqref{eq:Rdot}, \eqref{eq:E}, and \eqref{eq:thetadot} are sufficient to write a system of ordinary differential equations (ODEs) in $R(t)$, $u(t)$, and $\theta_j(t)$.
+A standard adiabatic blast wave maintains constant $E$, while energy injection and refreshed shock models may add dependence on $t$ or $u$.
+The general form of the shock evolution equations are then:
+\begin{align}
+	\dot{R} &= \frac{4 u \gamma}{4 u^2 +3}c  \label{eq:ODE1}\\
+	\dot{\theta}_j &= \frac{1}{2\gamma}\sqrt{\frac{2u^2+3}{4u^2+3}} \frac{\dot{R}}{R}  \label{eq:ODE2} \\
+	\dot{u} &= -\frac{E_{sw}(4u^2+3)\beta^2 (3\dot{R}/R + \cot (\theta_j/2) \dot{\theta}_j) - \partial_t E}{2 E_{sw} u (4u^4 + 8u^2 + 3)\gamma^{-4} + \beta \Mej c^2 - \partial_u E}  \label{eq:ODE3} \\
+	E_{sw} &\equiv \frac{4\pi}{9} \rho_0 c^2 R^3 f_\Omega\ . \nonumber
+\end{align}
+Equations \eqref{eq:ODE1}-\eqref{eq:ODE3} define a three dimensional system of ODEs in the variables $(R, u, \theta_j)$ which may be solved numerically or, in certain limits, analytically from appropriate initial conditions.
 Once the shock evolution ($R(t)$, $u(t)$, $\theta_j(t)$) is known, the flux is given by the integral:
@@
 
-The rest-frame synchrotron emissivity may be calculated to numerous ways with varying degrees of physics and accuracy.
+% TODO: Look at this again, more detail.
+The rest-frame synchrotron emissivity $\epsilon'_{\nu'}$ may be calculated with varying levels of sophistication.
 We use the standard broken power law formalism with characteristic frequencies $\nu_m$ and $\nu_c$, with the cooling frequency $\nu_c$ calculated via the global cooling approximation \citep{Granot:2002aa, van-Eerten:2010aa}.
+The fluid behind the shock has rest-frame number density $n' = 4n_0\gamma$, thermal energy $e'_{th} = (\gamma-1)m_p n' c^2$, and magnetic field strength $B = \sqrt{8\pi e'_{th} \epsB}$, where $\epsB$ is the fraction of thermal energy in the magnetic field.
+We assume a fraction $\xiN$ of the electron population is shock-accelerated electrons with a fraction $\epse$ of the thermal energy and have a Lorentz factor distribution $N(\gamma_e) \propto \gamma_e^{-p}$ with index $p>2$.
+
+Each characteristic frequency $\nu_i$ has a corresponding Lorentz factor $\gamma_i$:
+\begin{equation}
+	\nu_i = \frac{3e B}{4 \pi m_e c}  \gamma_i^2 \ ,
+\end{equation}
+where $e$ is the elementary charge.  These characteristic Lorentz factors are:
+\begin{align}
+	\gamma_m &= \frac{2-p}{1-p} \frac{\epse e'_{th}}{\xiN n' m_e c^2}\ , \\
+	\gamma_c &= \frac{6\pi m_e \gamma c}{\sigma_T B^2 t}\ .
+\end{align}
+The synchrotron spectrum has peak emissivity $\epsilon_P$:
+\begin{equation}
+	\epsilon_P = \frac{p-1}{2}\frac{\sqrt{3} e^3 \xiN n' B}{m_e c^2}\ .
+\end{equation}
+Finally, the rest-frame emissivity $\epsilon'_{\nu'}$ is given as:
+\begin{equation}
+	\epsilon'_{\nu'} = \epsilon_P \times \begin{cases}
+					(\nu' / \nu_m)^{1/3} & \nu' < \nu_m < \nu_c \\
+					(\nu' / \nu_m)^{-(p-1)/2} & \nu_m < \nu' < \nu_c \\
+					(\nu_c / \nu_m)^{-(p-1)/2}(\nu' / \nu_c)^{-p/2} & \nu_m < \nu_c < \nu' \\
+					(\nu' / \nu_c)^{1/3} & \nu' < \nu_c < \nu_m \\
+					(\nu' / \nu_c)^{-1/2} & \nu_c < \nu' < \nu_m \\
+					(\nu_m / \nu_c)^{-1/2}(\nu' / \nu_m)^{-p/2} & \nu_c < \nu_m < \nu'
+				\end{cases} \label{eq:syncSpec}
+\end{equation}
 
@@
 
-\afterglowpy{} uses a standard RK4 algorithm to evolve the $(R(t), u(t), \theta_j(t))$ system of equations on a fixed logarithmically spaced grid of $t$.
+\afterglowpy{} uses the standard fourth order Runge-Kutta algorithm to numerically solve the $(R(t), u(t), \theta_j(t))$ system of ordinary differential equations on a fixed logarithmically spaced grid of $t$ \citep{Press:2007aa}.
 The endpoints of the $t$-grid are chosen to bracket the burster frame times required to calculate the requested $\tobs$.
@@
 The user can set the density of the $t$-grid with the {\tt tRes} parameter: the number of grid points per decade of $t$.
-The default value for {\tt tRes} is 1000, which is sufficiently dense that the shock ODE evolution is not the dominant error source but not so dense as to adversely impact performance.
+The default value for {\tt tRes} is 1000, which is sufficiently dense that the blast wave ODE evolution is not the dominant error source but not so dense as to adversely impact performance.
 
@@
 As the calculation proceeds, the current running sum of the flux is used to set absolute tolerance for the next component.
-This minimizes the computations performed on dim, off-axis sectors of the jet.
+This minimizes the computations performed on dim sectors of the jet far from the line of sight.
 
@@
 \afterglowpy{}, in utilizing the semi-analytic methods of Section \ref{subsec:algo}, trades some amount of physical accuracy for great flexibility.
-We gauge this trade-off by comparing to the \boxfit{} code, a standard tool which calculates high fidelity afterglow light curves based on numerical simulations.
+We gauge this trade-off by comparing to the \boxfit{} code, a standard tool which calculates high fidelity afterglow light curves based on numerical simulations \citep{van-Eerten:2012ab}.
+
 \boxfit{} uses two-dimensional relativistic hydrodynamic simulations to fully capture the non-linear hydrodynamics of a decelerating blast wave and a ray tracing radiative transfer module to compute observed synchrotron light curves.
-
-Comparing to \boxfit{} tests the fidelity of some of the assumptions and approximations of the single shell approach used by \afterglowpy{}.
-The simpler analytic version of the scheme on which \afterglowpy{} is based differed from \boxfit{} by factors from 2 to 8 \citep{van-Eerten:2010aa}.
-We find \afterglowpy{} performs much better, with a relative difference of less than 50\% for the bulk of the evolution.
-The difference is worst, up to a factor of 3 relative to \boxfit{}, at the onset of jet spreading.
+The simulations begin from a top hat jet initial condition with a Blandford-Mckee radial profile \citep{Blandford:1976aa}, are evolved adiabatically with the trans-relativistic TM equation of state, and fully capture the lateral spreading of the jet \citep{van-Eerten:2012ab}.
+Comparison to \boxfit{}, with its much more accurate hydrodynamic evolution, tests the fidelity of the assumptions and approximations of the single shell approach used by \afterglowpy{} and is a very useful calibration point.
 

### 2019-08-05 structuredJets.tex
small updates

@@
 
-\afterglowpy{} uses the standard fourth order Runge-Kutta algorithm to numerically solve the $(R(t), u(t), \theta_j(t))$ system of ordinary differential equations on a fixed logarithmically spaced grid of $t$ \citep{Press:2007aa}.
+\afterglowpy{} uses the standard fourth order Runge-Kutta algorithm to numerically solve the $(R(t), u(t), \theta_j(t))$ system of ordinary differential equations (Equations \eqref{eq:ODE1}-\eqref{eq:ODE3}) on a fixed logarithmically spaced grid of $t$ \citep{Press:2007aa}.
 The endpoints of the $t$-grid are chosen to bracket the burster frame times required to calculate the requested $\tobs$.
@@
 Each evaluation of the integrand requires a binary search to determine the burster time $t$ at which to evaluate $R$, $u$, and $\theta_j$.
-Fluid quantities are then calculated using the shock-jump conditions and the synchrotron emissivity is evaluated using the standard external shock formulae \citep{Granot:2002aa,van-Eerten:2010aa}.
+Fluid quantities are then calculated using the shock-jump conditions and the synchrotron emissivity is evaluated using the standard external shock formulae (Equation \eqref{eq:syncSpec}, see also \citet{Granot:2002aa,van-Eerten:2010aa}).
 
@@
 We find the choice $\mathtt{latRes} = 5$ gives sufficiently quick performance at acceptable errors, typically on the order of $10^{-2}$.
-TODO SHOW CONVERGENCE PLOT
 
@@
 
-Using the definition of $\thC$ in Equation \eqref{eq:thCdef} we may write the angular energy profile near the jet axis as:
-\begin{equation}
-	E(\theta) = E_0 \left (1 - \frac{\theta^2}{2\thC^2} \right) + \OO(\theta^3) \label{eq:EthetaNear}
-\end{equation}
-
-The light curves of structured jets show two modes of behaviour, depending on whether the observer is \emph{aligned} ($\thobs < \thC$) or \emph{misaligned} ($\thobs > \thC$).
+Previous work has demonstrated the light curves of structured jets show two modes of behaviour, depending on whether the observer is \emph{aligned} ($\thobs < \thC$) or \emph{misaligned} ($\thobs > \thC$) \citep{Rossi:2002aa, Granot:2002ab, Panaitescu:2003aa, van-Eerten:2010aa}.
 In the \emph{aligned} case, the light curves follow the standard on-axis top hat behaviour modified slightly for non-zero viewing angle.
 There is little to distinguish between different structure $E(\theta)$, and the light curve is well-approximated by a broken power law with characteristic break times \citep{Granot:2002aa}.
-The \emph{misaligned} light curve also may present as a broken power law, but with closure relations explicitly dependent on viewing angle and jet angular structure.
+The \emph{misaligned} light curve structure is more complicated.
+It also presents as a broken power law, but with closure relations explicitly dependent on viewing angle and jet angular structure.
+
+We can write the received flux as:
+\begin{equation}
+	F_\nu = I_\nu^*\ \Delta \Omega\ , 
+\end{equation}
+where $I_\nu^* = I_\nu(\theta^*)$ is the peak specific intensity, located at $\theta=\theta^*$ and $\phi=0$, and $\Delta \Omega$ is the effective solid angle of the blast wave contributing to the emission.
+
+From the definition of $\thC$ in Equation \eqref{eq:thCdef} we can see $E(\theta) = E_0(1 - \theta^2/(2\thC^2) + \OO(\theta^3))$.
 
@@
 
-\begin{figure}
-	\includegraphics[width=\columnwidth]{figs/lc_on.pdf}
-	\caption{Aligned ($\thobs = \thC/2$) afterglow light curves for top-hat (blue), Gaussian (orange), and power law (green) jets.
+%\begin{figure}
+%	\includegraphics[width=\columnwidth]{figs/lc_on.pdf}
+%	\caption{Aligned ($\thobs = \thC/2$) afterglow light curves for top-hat (blue), Gaussian (orange), and power law (green) jets.
 When viewed on-axis, jets containing angular structure are very difficult to distinguish from top-hats.
@@
 \label{fig:onaxis}}
-\end{figure}
+%\end{figure}
 
@@
 Emission is dominated by material on the edge nearest the observer and the angular size of the visible patch is constant in time.
-This phase ends at $\tW$ when $\gamma^{-1} \sim \thobs-\thW$.
+This phase ends at $\tW$ when $\gamma^{-1}(\thW) \sim \thobs-\thW$.
 If $\thobs < \thW$ this phase is entirely absent.
@@
 
-\begin{deluxetable*}{CCCCCCC}
-	\tablecaption{Structured jet temporal and spectral slopes: $F_\nu \propto \tobs^{-\alpha} \nu^{-\beta}$.
+\begin{deluxetable*}{CCCCCCCC}
+	\tablecaption{Structured jet closure relations: $F_\nu \propto \tobs^{\alpha} \nuobs^{\beta}$.
+The ``far-off-axis'' phase occurs at early times and only if there is no material directly in the observer's line of sight ($\thobs > \thW$).
+The ``generic'' slope applies whenever the jet is relativistic, non-spreading, and the observer is within the beaming cone of some part of the jet ($|\thobs - \theta_*| < \gamma^{-1}(\theta_*)$).
+The $g$ parameter is positive and depends on the viewing angle $\thobs$ and the specific structure profile $E(\theta)$.
 See Equations \eqref{eq:gdef} and \eqref{eq:geff} for the definition and effective values of $g$.
+For a top hat jet $g=0$ and for a Gaussian jet $g \approx \thobs^2/(4\thC^2)$.
+The $\som$ parameter encodes how the effective angular size of the jet is changing with Lorentz factor: $\Delta \Omega \propto \gamma^{-\som}$.
+The ``structured'' phase is seen by misaligned viewers ($\thobs > \thC$), occurs before the jet break, and corresponds to $\som \approx 1$.
+The ``pre-jet break'' phase is seen by aligned viewers ($\thobs < \thC$).
+The ``post-jet break'' slope given here does not include the effects of jet spreading and as such is an over-estimate of the true post-jet break slope.
 \label{tab:slopes}}
-	\tablehead{\colhead{Regime}& \colhead{Label} & \colhead{$\alpha_{\mathrm{off-axis}}$}& \colhead{$\alpha_{\mathrm{struct}}$}& \colhead{$\alpha_{\mathrm{struct,max}}$}& \colhead{$\alpha_{\mathrm{post, analytic}}$} & \colhead{$\beta$}}
+	\tablehead{\colhead{Regime}& \colhead{Label} & \colhead{$\alpha_{\mathrm{far-off-axis}}$} & \colhead{$\alpha_{\mathrm{generic}}$} & \colhead{$\alpha_{\mathrm{struct}}$}& \colhead{$\alpha_{\mathrm{pre}}$}& \colhead{$\alpha_{\mathrm{post, no-spreading}}$} & \colhead{$\beta$}}
 	\startdata
-	\nu<\nu_m<\nu_c     & D & 7 			& \frac{1 + 3g}{8+g} 		& 3		& -1/4		& 1/3 \\
-	\nu_m<\nu<\nu_c     & G & 15/2 - 3p/2 	& \frac{3 - 6p +3g}{8+g} 	& 3		& -3p/4		& (1-p)/2 \\
-	\nu < \nu_c < \nu_m & E & 17/3 		& \frac{-5/3 + 11g/3}{8+g} 	& 11/3	& -7/12		& 1/3 \\
-	\nu_c < \nu < \nu_m & F & 13/2 		& \frac{-5 + 2g}{8+g} 		& 2		& -1			& -1/2 \\
-	\nu_c < \nu_m < \nu & H & 8 - 3p/2 		& \frac{1-6p  +2g}{8+g} 	& 2		& -(3p+1)/4	& -p/2 \\ 
+	& & & & (\som = 1) & (\som=2, g=0) & (\som=0, g=0) & \\[0.3cm]
+	\nu<\nu_m<\nu_c     & D	& 7 		& \dfrac{-2 + 3\som + 3g}{8+g} 		& \dfrac{1 + 3g}{8+g} 	&1/2		& -1/4	& 1/3 \\[0.3cm]
+	\nu < \nu_c < \nu_m & E	& 17/3 	& \dfrac{-14/3 + 3\som + 11g/3}{8+g}  & \dfrac{-5/3 + 11g/3}{8+g} &1/6 	& -7/12	& 1/3 \\[0.3cm]
+	\nu_c < \nu < \nu_m & F	& 13/2 	& \dfrac{-8 + 3\som + 2g}{8+g} 		& \dfrac{-5 + 2g}{8+g} 	& -1/4 	& -1		& -1/2 \\[0.3cm]
+	\nu_m<\nu<\nu_c     & G 	&15/2 - 3p/2 & \dfrac{-6p + 3\som + 3g}{8+g} 	& \dfrac{3 - 6p +3g}{8+g} 	& -3(p-1)/4 & -3p/4	& (1-p)/2 \\[0.3cm]
+	\nu_m, \nu_c < \nu & H 	& 8 - 3p/2 	& \dfrac{-6p - 2 + 3\som + 2g}{8+g} 	& \dfrac{1-6p  +2g}{8+g} 	& -3p/4	& -(3p+1)/4 & -p/2 \\[0.3cm]
 	\enddata
@@
 	\geff &= \frac{\thobs^2}{4\thC^2} && \text{Gaussian}\ , \\
-	\geff &= \frac{b \thobs^2}{4 \thC^2+\thobs^2} && \text{power law}\ . \label{eq:geff}
+	\geff &= \frac{2 b (\thobs-\theff)\theff}{b \thC^2+\theff^2} && \text{power law}\ . \label{eq:geff}
 \end{align}
@@
 
-\begin{figure}
-	\includegraphics[width=\columnwidth]{figs/lc_off1.pdf}
-	\caption{As Figure \ref{fig:onaxis} but $\thobs = 2\thC$.
+%\begin{figure}
+%	\includegraphics[width=\columnwidth]{figs/lc_off1.pdf}
+%	\caption{As Figure \ref{fig:onaxis} but $\thobs = 2\thC$.
 The top-hat jet (with opening angle $\thC$) begins in the off-axis phase.
@@
 \label{fig:offaxis1}}
-\end{figure}
-\begin{figure}
-	\includegraphics[width=\columnwidth]{figs/lc_off2.pdf}
-	\caption{As Figure \ref{fig:onaxis} but $\thobs = 6\thC$.
+%\end{figure}
+%\begin{figure}
+%	\includegraphics[width=\columnwidth]{figs/lc_off2.pdf}
+%	\caption{As Figure \ref{fig:onaxis} but $\thobs = 6\thC$.
 All three models exhibit off-axis, structured, and post-jet break phases of evolution.
@@
 \label{fig:offaxis2}}
-\end{figure}
+%\end{figure}
 

### 2019-08-05 code/boxfitComp.py

@@ -100,9 +100,12 @@ def compareAll():
 
 def makeNiceFigure():
 
-    curves = ['100', '130', '102', '132']
+    curves = []
+    curves += ['100', '130', '102', '132']
+    # curves += ['000', '002', '030', '032']
+    # curves += ['200', '202', '230', '232']
 
-    colors = ['C0', 'C1', 'C2', 'C3', 'C4', 'C5', 'C6']
+    colors = ['C0', 'C1', 'C2', 'C3', 'C4', 'C5', 'C6', 'C7', 'C8', 'C9']
 
     fig = plt.figure(figsize=(8, 6))
     gs = fig.add_gridspec(4, 1, hspace=0)
@@ -125,7 +128,7 @@ def makeNiceFigure():
         t, nu, FnuBF, jT, sT, Y, z = out
         thV = Y[0]
         # thC = Y[2]
-        Fnu = grb.fluxDensity(t, nu, jT, sT, *Y, z=z, spread=5)
+        Fnu = grb.fluxDensity(t, nu, jT, sT, *Y, z=z)
         if code[2] == '0':
             log10nu = 9
         elif code[2] == '0':

### 2019-08-05 code/plotModelThC.py

@@ -1,0 +1,127 @@
+import numpy as np
+import grbpy as grb
+import matplotlib.pyplot as plt
+# import paperPlots as pp
+
+
+def plotPanel(fig, gs0, t, nu, thC, Y, Z, modelLegend=False):
+
+    gs = gs0.subgridspec(3, 1, hspace=0.0)
+    axF = fig.add_subplot(gs[0:-1, 0])
+    axa = fig.add_subplot(gs[-1, 0])
+
+    tfac = 0.3
+
+    tb = t * (1.0 + tfac)
+    ta = t / (1.0 - tfac)
+
+    c = ['C0', 'C2', 'C1', 'C3']
+    ls = ['--', '-', '-.', ':']
+
+    Y[3] *= thC/Y[2]
+    Y[2] = thC
+    thV = Y[0]
+    thW = Y[3]
+
+    FnuTH = grb.fluxDensity(t, nu, -1, 0, *Y, **Z)
+    FnuTHa = grb.fluxDensity(ta, nu, -1, 0, *Y, **Z)
+    FnuTHb = grb.fluxDensity(tb, nu, -1, 0, *Y, **Z)
+
+    FnuG = grb.fluxDensity(t, nu, 0, 0, *Y, **Z)
+    FnuGa = grb.fluxDensity(ta, nu, 0, 0, *Y, **Z)
+    FnuGb = grb.fluxDensity(tb, nu, 0, 0, *Y, **Z)
+
+    Y[4] = 3
+    Y[2] = thC / np.sqrt(3)
+    FnuPL1 = grb.fluxDensity(t, nu, 4, 0, *Y, **Z)
+    FnuPL1a = grb.fluxDensity(ta, nu, 4, 0, *Y, **Z)
+    FnuPL1b = grb.fluxDensity(tb, nu, 4, 0, *Y, **Z)
+
+    Y[4] = 6
+    Y[2] = thC / np.sqrt(6)
+    FnuPL2 = grb.fluxDensity(t, nu, 4, 0, *Y, **Z)
+    FnuPL2a = grb.fluxDensity(ta, nu, 4, 0, *Y, **Z)
+    FnuPL2b = grb.fluxDensity(tb, nu, 4, 0, *Y, **Z)
+
+    alTH = np.log(FnuTHb/FnuTHa) / np.log(tb/ta)
+    alG = np.log(FnuGb/FnuGa) / np.log(tb/ta)
+    alPL1 = np.log(FnuPL1b/FnuPL1a) / np.log(tb/ta)
[…]

### 2019-08-05 code/plotModelThV.py

@@ -4,67 +4,109 @@ import matplotlib.pyplot as plt
 # import paperPlots as pp
 
 
-def plotPanel(fig, gs0, t, nu, thV, Y, Z, modelLegend=False):
+def plotPanel(fig, gs0, t, nu, jetType, Y, Z, thVLegend=False):
 
     gs = gs0.subgridspec(3, 1, hspace=0.0)
     axF = fig.add_subplot(gs[0:-1, 0])
     axa = fig.add_subplot(gs[-1, 0])
+    # axs = fig.add_subplot(gs[-1, 0])
 
     tfac = 0.3
 
     tb = t * (1.0 + tfac)
     ta = t / (1.0 - tfac)
 
-    c = ['C0', 'C2', 'C1', 'C3']
-    ls = ['--', '-', '-.', ':']
+    b = Y[4]
+
+    if jetType == -1:
+        c = 'C0'
+        ls = '--'
+        name = 'top hat'
+    elif jetType == 0:
+        c = 'C2'
+        ls = '-'
+        name = 'Gaussian'
+    elif jetType == 4 and b < 4:
+        c = 'C1'
+        ls = '-.'
+        name = 'power law b={0:d}'.format(int(b))
+    elif jetType == 4 and b >= 4:
+        c = 'C3'
+        ls = ':'
+        name = 'power law b={0:d}'.format(int(b))
+    else:
+        c = 'C4'
+        ls = '-'
+        name = 'unknown'
 
     thC = Y[2]
 
-    Y[0] = thV
+    thVs = np.array([0.0, 0.5*thC, 0.9*thC, 2*thC, 4*thC, 6*thC, 8*thC])
+    alpha = np.linspace(0.2, 1.0, len(thVs))
 
-    FnuTH = grb.fluxDensity(t, nu, -1, 0, *Y, **Z)
-    FnuTHa = grb.fluxDensity(ta, nu, -1, 0, *Y, **Z)
-    FnuTHb = grb.fluxDensity(tb, nu, -1, 0, *Y, **Z)
+    th = np.linspace(0.0, Y[3], 300)
+    # phi = np.zeros(th.shape)
+    # t_th = np.empty(th.shape)
+    nu_th = np.empty(th.shape)
+    nu_th[:] = nu[0]
 
-    FnuG = grb.fluxDensity(t, nu, 0, 0, *Y, **Z)
[…]

### 2019-08-05 code/plotThVModel.py

@@ -1,0 +1,122 @@
+import numpy as np
+import grbpy as grb
+import matplotlib.pyplot as plt
+# import paperPlots as pp
+
+
+def plotPanel(fig, gs0, t, nu, thV, Y, Z, thVLegend=False):
+
+    gs = gs0.subgridspec(3, 1, hspace=0.0)
+    axF = fig.add_subplot(gs[0:-1, 0])
+    axa = fig.add_subplot(gs[-1, 0])
+
+    tfac = 0.3
+
+    tb = t * (1.0 + tfac)
+    ta = t / (1.0 - tfac)
+
+    c = ['C0', 'C2', 'C1', 'C3']
+    ls = ['--', '-', '-.', ':']
+
+    thC = Y[2]
+
+    Y[0] = thV
+
+    FnuTH = grb.fluxDensity(t, nu, -1, 0, *Y, **Z)
+    FnuTHa = grb.fluxDensity(ta, nu, -1, 0, *Y, **Z)
+    FnuTHb = grb.fluxDensity(tb, nu, -1, 0, *Y, **Z)
+
+    FnuG = grb.fluxDensity(t, nu, 0, 0, *Y, **Z)
+    FnuGa = grb.fluxDensity(ta, nu, 0, 0, *Y, **Z)
+    FnuGb = grb.fluxDensity(tb, nu, 0, 0, *Y, **Z)
+
+    Y[4] = 2
+    FnuPL1 = grb.fluxDensity(t, nu, 4, 0, *Y, **Z)
+    FnuPL1a = grb.fluxDensity(ta, nu, 4, 0, *Y, **Z)
+    FnuPL1b = grb.fluxDensity(tb, nu, 4, 0, *Y, **Z)
+
+    Y[4] = 6
+    # Y[2] = np.sqrt(3)*thC
+    FnuPL2 = grb.fluxDensity(t, nu, 4, 0, *Y, **Z)
+    FnuPL2a = grb.fluxDensity(ta, nu, 4, 0, *Y, **Z)
+    FnuPL2b = grb.fluxDensity(tb, nu, 4, 0, *Y, **Z)
+    Y[2] = thC
+
+    alTH = np.log(FnuTHb/FnuTHa) / np.log(tb/ta)
+    alG = np.log(FnuGb/FnuGa) / np.log(tb/ta)
+    alPL1 = np.log(FnuPL1b/FnuPL1a) / np.log(tb/ta)
[…]

### 2019-08-19 structuredJets.tex
Reworked Section 4, cleaned intro finally, other edits

@@
 
-\title{GRB Afterglows In The Multi-Messenger Era  \hspace{10in} OR\hspace{10in}   Electromagnetic Afterglows Of Structured Jets \hspace{10in}  OR\hspace{10in}  Structured Jets At All Angles\hspace{10in}  OR \hspace{10in}The Electromagnetic Afterglows of Structured Jets: Numerical Models and Closure Relations}
+\title{The Electromagnetic Afterglows of Structured Jets: Numerical Models and Closure Relations  \hspace{10in} OR\hspace{10in}   Electromagnetic Afterglows Of Structured Jets \hspace{10in}  OR\hspace{10in}  Structured Jets At All Angles\hspace{10in}  OR \hspace{10in}GRB Afterglows In The Multi-Messenger Era}
 
@@
 As demonstrated by the afterglow of \gwbns{}, this requires an extension of the common GRB afterglow models which typically assume emission from an on-axis top hat jet.
-We present a characterization of the afterglows arising from structured jets, utilizing both trans-relativistic numerical calculations and simple analytic approximations.
+We present a characterization of the afterglows arising from structured jets, jets with a non-trivial angular energy profile, utilizing both trans-relativistic numerical calculations and simple analytic approximations.
+We compute new closure relations for structured jets and compare with the established relations for energy injection and refreshed shock models.
 In many cases the temporal slope before the jet break is found to be a simple function of the ratio between the viewing angle and effective half opening angle of the jet.
@@
 The binary neutron star merger event \gwbns{} provided, quite literally, a new view on gamma-ray burst (GRB) afterglows (CITE LIGO, Discovery papers).
-Unlike typical short GRB afterglows, which begin bright and decay from detection with a ~week timescale, \gwbns{}'s non-thermal afterglow was undetectable for nine days whereupon it began steadily increasing in brightness in all bands for ~160 days \citep{Troja:2017aa, Troja:2018aa, van-Eerten:2018aa} (CITE OTHERS).
+Unlike typical short GRB afterglows, which begin bright and decay from detection with a ~week timescale, \gwbns{}'s non-thermal afterglow was undetectable until the first observation of x-rays nine days after the GRB \citep{Troja:2017aa}.
+At this point it began steadily increasing in brightness in all bands for ~160 days \citep{Troja:2018aa, Troja:2019ab} (CITE OTHERS).
 Very long baseline (VLBI) radio imagery over this period identified a radio core with an apparent superluminal motion, indicating the emitting surface was moving at relativistically at an oblique angle towards the Earth (CITE Mooley, Ghirlanda).
@@
 The combined effects of a moderate viewing angle and angular structure in the jet produce a light curve significantly different from the standard on-axis uniform ``top-hat'' jet used extensively in GRB afterglow analysis.
-Since the gravitational wave signal of a binary neutron star merger is nearly isotropic, it is expected the majority of future GW-GRBs will also be viewed at significant inclination and may have similarly peculiar light curves as \gwbns{}.
+Being sources at cosmological distances, GRBs must typically be observed nearly on-axis or at least within the original opening angle of the jet \citep{Ryan:2015aa}.
+At these small viewing angles lateral structure plays a sub-dominant role and the ubiquitous top hat jet has been a sufficiently spherical cow for the majority of studies.
+Since the gravitational wave signal of a binary neutron star merger is nearly isotropic, it is expected the majority of future GW-GRBs will be viewed at significant inclination and may have similarly peculiar light curves as \gwbns{}.
 
 A solid theoretical understanding of structured jet afterglows, including viewing angle effects, will be required to make the most use of future GW-GRB observations, the \gwbns{} dataset, and re-analysis of archival short GRBs.
-% Mention standard tools, explain closure relations
-To this end, we have calculated the explicit viewing angle and structure-dependent closure relations governing the afterglows of structured jets.
+Standard tools for GRB analysis include closure relations, equations relating the temporal and spectral power law slopes of GRB afterglow light curves, jet breaks, achromatic breaks in the light curve related to the opening angle fo the jet, and full light curve modeling.
+To this end, we have calculated generalized closure relations for GRB afterglows including explicit viewing angle and jet structure dependence, putting these effects into a similar context as standard energy injection models \citep{Zhang:2006aa}.
  We have also developed the computational tool \afterglowpy{}: a public, open source \python{} package for on-the-fly computation of structured jet afterglows with arbitrary viewing angle.
@@
 
-The temporal break in the structured jet afterglow light curve can be more significant than in top hat models, and has been invoked to explain some observed jet breaks which do not easily fit the standard closure relations \citep{Panaitescu:2005aa, Panaitescu:2005ab}, although other dynamical and spectral processes can have similar effects (CITE Piro2005, COrsi\&Piro2006).
+The jet break in the structured jet afterglow light curve can exhibit a larger jump between pre- and post-break slopes than in top hat models, and has been invoked to explain some observed jet breaks which do not easily fit the standard closure relations \citep{Panaitescu:2005aa, Panaitescu:2005ab}, although other dynamical and spectral processes can have similar effects \citep{Piro:2005aa, Corsi:2006aa}.
 GRB prompt emission viewed significantly off-axis was (is?) the proposed origin for X-ray flashes \citep{Ioka:2001aa, Yamazaki:2002aa, Yamazaki:2003aa, Peng:2005aa}.
@@
 
-In this paper, we provide...
+In this paper, we provide a characterization of the afterglows of structured jets, explicit closure relations, and a description of our numerical tool \afterglowpy{}.
 In Section \ref{sec:motivation} we review the general properties of structured jets and their necessity to GRB afterglows.
@@
 
-\newpage
-
-\subsection{Old Draft}
-
-The binary neutron star merger \gwbns{} and its associated electromagnetic counterparts provided a wealth of data to high energy astrophysics (CITE).
+%\newpage
+%
+%\subsection{Old Draft}
+%
+%The binary neutron star merger \gwbns{} and its associated electromagnetic counterparts provided a wealth of data to high energy astrophysics (CITE).
 Not least among these was its peculiar non-thermal afterglow, first detected in X-rays 9 days after the merger \citep{Troja:2017aa}.
@@
 After peak, the emission quickly decayed at a rate similar to other GRB afterglows.
-
-The absence of early X-ray emission, with early non-detections by \swiftXRT{} and a deep upper limit from \chandra{}, led early analyses to consider the effect if viewing angle on the emission \citep{Troja:2017aa} (CITE MORE).
+%
+%The absence of early X-ray emission, with early non-detections by \swiftXRT{} and a deep upper limit from \chandra{}, led early analyses to consider the effect if viewing angle on the emission \citep{Troja:2017aa} (CITE MORE).
 Given the gravitational wave signal of a binary neutron star merger is observable almost regardless of of orientation, it is in fact expected that GRB/GW events would be viewed at moderate inclination.
-
-As \grbbns{}'s afterglow continued to rise for weeks after the burst, it became evident the emission could not be explained by a simple uniform ``top hat'' jet viewed off axis.
+%
+%As \grbbns{}'s afterglow continued to rise for weeks after the burst, it became evident the emission could not be explained by a simple uniform ``top hat'' jet viewed off axis.
 More sophisticated models were considered: ``structured jets'' with non-uniform angular distribution of energy and quasi-isotropic ``refreshed shocks'' with significant velocity stratification of the ejecta and modest Lorentz factors.
 The observation of apparent superluminal motion of the radio centroid and the steep turnover of the light curve after 160 days confirmed the relativistic and collimated nature of the outflow, in accordance with the structured jet picture (CITE Mooley, Ghirlanda, YITL, other steepening paper).
-
-It is expected, of course, that
-
-Structured jets, blast waves with a non-uniform angular distribution of energy, have been invoked to explain several temporal features in GRB afterglow light curves.
-
-\subsubsection{History of structure and viewing angle}
-
-The first GRB afterglow was discovered by \beppoSAX{} as part of GRB 970228 \citep{Wijers:1997aa}.
+%
+%It is expected, of course, that 
+%
+%Structured jets, blast waves with a non-uniform angular distribution of energy, have been invoked to explain several temporal features in GRB afterglow light curves.  
+%
+%\subsubsection{History of structure and viewing angle}
+%
+%The first GRB afterglow was discovered by \beppoSAX{} as part of GRB 970228 \citep{Wijers:1997aa}.
 GRB afterglows present as broadband synchrotron emission following the prompt gamma-ray signal and can last for days, weeks, months, and years.
-
-\subsubsection{What we're doing}
-
-In this paper we develop a theoretical model of the electromagnetic afterglow of generic structured jets for arbitrary viewing inclinations.
+%
+%
+%\subsubsection{What we're doing}
+%
+%In this paper we develop a theoretical model of the electromagnetic afterglow of generic structured jets for arbitrary viewing inclinations.
 The model takes as input the energy and Lorentz factor angular profiles, which may be intrinsic to the jet launching mechanism
-
-The light curves resemble broken power laws.
+%
+%The light curves resemble broken power laws.
 We calculate viewing angle dependent closure relations, directly relating the effective temporal evolution of the light curve to the viewing angle and explosion geometry.
-
-\newpage
-
-\subsection{Lit Review}
-\begin{itemize}
-\item \citet{Meszaros:1998aa} First discusses effect of angular structure in $E$ and $\Gamma$, predicts rising light curves when seen off axis, calculates closure relations in various cases.
-\item \citet{Nakamura:1999aa} Far off-axis emission from top-hat jet in stellar wind environment, application to GRB 980425.
-\item \citet{Moderski:2000aa} Relativistic effects (equal arrival time surface, etc) smear jet-break.
-\item \citet{Ioka:2001aa} Viewing angle dependent prompt emission.  GRB prompt peak $L$ - spectral lag relation from viewing angle.  
-\item \citet{Lipunov:2001aa, Zhang:2002aa} universal structured jet, $\theta^{-2}$, may explain jet breaks, etc.
-\item \citet{Rossi:2002aa} Considers jets with $E\propto \theta^{-2}$.
-Verifies at early times line-of-sight material dominates over core and wings, light curves resemble on-axis top-hats, but jet break is due to observer angle.
-Simple emission model.
-Postulates variety of jet-breaks due to off-axis structured jets, instead of distribution of $\Eiso$, $\thC$.
-$t_b \propto \thobs^{8/3}$.
-\item \citet{Dalal:2002aa} Considers emission from boosted lightbulb, refers to $\thobs > \theta_j$ as ``off-axis,'' points out off-axis jet breaks will be delayed and dim, light curves converge at late time.
-\item \citet{Granot:2002ab} Off-axis viewing of top hat jets, computed as boosted light bulb, analytic top-hat, and hydro sim.
-$\thobs < \theta_j$ look like on-axis top-hats, jet breaks increase with $\thobs$, evidence for $\thobs$-dependent slope before jet break in hydro models.
-\item \citet{Yamazaki:2002aa, Yamazaki:2003aa} XRF as off-axis prompt GRB using \citet{Ioka:2001aa} model.
-\item \citet{Panaitescu:2003aa} Off-axis viewing of power-law jets $E\propto \theta^{-q}$ with sharp cores.
-Analytic blast waves, detailed treatment of relativistic emission and synchrotron spectrum.
-When viewing within the core, no large effect so long as $q \geq 2$.
-Analytic formulae for aligned observers, numerical only for misaligned.
-Core visible at $t_a \sim E_0^{1/3} \thobs^{8/3}$ in ISM.
-Structure may only steepen jet breaks, proposes examining pre- and post- jet break slopes to determine whether structure is evident.
-\item \citet{Kumar:2003aa} Numerical evolution of radially-integrated Gaussian, top-hat, and power-law jets/  ``Therefore, a simple model in which the energy per unit solid angle is taken to be time independent and each element of the jet behaves as if it were part of a spherical flow with the same can serve as a useful approximation for the jet dynamics, as long as the jet is sufficiently relativistic.''
-\item \citet{Granot:2003aa} ``structured jet:'' jet with angular structure.
-Smooth power law in $\Theta = \sqrt{1 + \theta^2/\thC^2}$.
-Analysis of power-law jet light curves from \citet{Kumar:2003aa}.
-Only considers USJ, top-hat, and permutations.
-Find deviations from top-hat appearance small, USJ must have $E\approx \theta^{-2}$, $\Gamma\approx \theta^{0 < 1}$.
-\item \citet{Salmonson:2003aa} Numerical and analytic study of top-hat and structured jets.
-Computes doppler factor and angular size in asymptotic limits (no cooling frequency), finds far-off-axis closure relations.
-Examines `bump' seen when initially strongly beamed emission becomes structured, then proceeds to jet break.
-\item \citet{Nakar:2004aa} Distribution of luminosity and jet-breaks rules out USJ. 
-\item \citet{Rossi:2004aa}.
-Light curves and polarization for top-hat, USJ, and Gaussian jet.
-Gaussian jet shows slowly rising flux at sufficiently large viewing angles.
-Time dependence of polarization signal may distinguish between USJ and Gaussian.
-\item \citet{Yamazaki:2004aa} $E_P$ -- $E_{iso}$ prompt relation from viewing angle.
-\item \citet{Peng:2005aa} Two-component (narrow + wide) jet, afterglows, blurred jet breaks, off-axis as XRF.
-\end{itemize}
-
-\subsection{Old Old Draft}
-
-The electromagnetic afterglow of \gwbns{} gave, quite literally, a new view on gamma-ray burst (GRB) afterglows.
-
-A canonical afterglow was almost immediately ruled out \citep{Troja:2017aa}.
-
-The structure of the blast wave giving rise to gamma-ray burst (GRB) afterglows has been a subject of interest since their discovery by \beppoSAX{} in GRB 970228 \citep{Wijers:1997aa}.
-
-{\color{blue} LUIGI: ?was found since early afterglow observations with BeppoSAX, when the
-presence of a structured outflow has been considered for explaining some of the
-temporal breaks observed in the light curves of a number of GRBs (Panaitescu and
-Kumar 2003, Apj 592: 390, Panaitescu 2005 MNRAS 362, 921). Candidates for
-structured jet exhibit a variation of the decay index at the break smaller that that
-expected for a top-hat spreading jet ($\Delta \alpha \approx 0.8$) and larger than
-that induced by the crossing of the cooling frequency ($\Delta\alpha=0.25$). Energy
-injection by a long lasting central engine can also induce temporal breaks, either
-flattening or steepening. Other effects such as transition to non-relativistic
-expansion, the transition from wind-like to ISM (Piro et al. 2005, Apj 623 314) or the
-emergence of an Inverse compton component (Corsi \& Piro
-2006A\&A...458..741C) can also produce breaks, in these case associated with a
-flattening of the light curve.
-More recenlty Ryan et al (2015) presented evidence of a structured jet in a sample
-based on SWIFT observations. Considering the number of processes that can
-produce breaks mentioned above, no undisputable observational evidence of a
-structured jet became available till the observations of GW170817. Real jets}
-
-Gamma-ray burst (GRB) afterglows, since their discovery by \beppoSAX{} in GRB 970228, have been a potent tool for studying GRBs and their progenitors.
-
-Gamma-ray burst (GRB) afterglows are commonly modeled as top hat blast waves with no internal structure pointed directly at the observer.
+%
+%
+%\subsection{Old Old Draft}
+%
+%The electromagnetic afterglow of \gwbns{} gave, quite literally, a new view on gamma-ray burst (GRB) afterglows.  
+%
+%A canonical afterglow was almost immediately ruled out \citep{Troja:2017aa}.  
+%
+%
+%The structure of the blast wave giving rise to gamma-ray burst (GRB) afterglows has been a subject of interest since their discovery by \beppoSAX{} in GRB 970228 \citep{Wijers:1997aa}.
+%
+%{\color{blue} LUIGI: ?was found since early afterglow observations with BeppoSAX, when the
+%presence of a structured outflow has been considered for explaining some of the
+%temporal breaks observed in the light curves of a number of GRBs (Panaitescu and
+%Kumar 2003, Apj 592: 390, Panaitescu 2005 MNRAS 362, 921). Candidates for
+%structured jet exhibit a variation of the decay index at the break smaller that that
+%expected for a top-hat spreading jet ($\Delta \alpha \approx 0.8$) and larger than
+%that induced by the crossing of the cooling frequency ($\Delta\alpha=0.25$). Energy
+%injection by a long lasting central engine can also induce temporal breaks, either
+%flattening or steepening. Other effects such as transition to non-relativistic
+%expansion, the transition from wind-like to ISM (Piro et al. 2005, Apj 623 314) or the
+%emergence of an Inverse compton component (Corsi \& Piro
+%2006A\&A...458..741C) can also produce breaks, in these case associated with a
+%flattening of the light curve.
+%More recenlty Ryan et al (2015) presented evidence of a structured jet in a sample
+%based on SWIFT observations. Considering the number of processes that can
+%produce breaks mentioned above, no undisputable observational evidence of a
+%structured jet became available till the observations of GW170817. Real jets}
+%
+%
+%Gamma-ray burst (GRB) afterglows, since their discovery by \beppoSAX{} in GRB 970228, have been a potent tool for studying GRBs and their progenitors.
+%
+%
+%
+%Gamma-ray burst (GRB) afterglows are commonly modeled as top hat blast waves with no internal structure pointed directly at the observer.
 This has been largely sufficient given the available data, although some evidence of viewing angle effects has been found \citep{Ryan:2015aa}.
@@
 Real jets (of course) have internal structure, but the top hat assumption has been a sufficiently spherical cow.
-
-\gwbns{} changes the picture: new object with a strange afterglow.
+%
+%\gwbns{} changes the picture: new object with a strange afterglow.
 Steep/late rise, LONG slow rise, turnover at 160d.
 The slow rise is impossible to reproduce with standard afterglow evolution: first observation of a \emph{structured} phase of evolution.
-
-The dominant contribution may be an angular distribution of energy within the blast wave (``structured jet'') combined with off-axis viewing (CITE Rossi04).
+%
+%The dominant contribution may be an angular distribution of energy within the blast wave (``structured jet'') combined with off-axis viewing (CITE Rossi04).
 For \gwbns{} this corresponds to the ``successful jet'' picture.
@@
 Understanding the effects of both structures on afterglows, and their dependence on the parameters of the burst, are vital to understanding GW counterparts.
-
-To this end, we have calculated the power law temporal slope of the structured phase in both angular and radial structure dominated cases, along with the corresponding observed break times.
+%
+%To this end, we have calculated the power law temporal slope of the structured phase in both angular and radial structure dominated cases, along with the corresponding observed break times.
 We have developed a semi-analytic numerical model of structured GRB afterglows for detailed comparison to data, which is now publicly available.
-
-Summary: In section 2 we discuss structured jets, in section 3 refreshed shocks, in section 4 our numerical model, section 5 application to \gwbns{}, and section 6 future applications and discussion.
+%
+%Summary: In section 2 we discuss structured jets, in section 3 refreshed shocks, in section 4 our numerical model, section 5 application to \gwbns{}, and section 6 future applications and discussion.
 
@@
 Figure \ref{fig:jetStruct} shows a collection of jet energy distributions from the literature \citep{Aloy:2005aa, Mizuta:2009aa, Duffell:2013aa, Lazzati:2017aa, Margutti:2018aa}.
-Lacking a well-established physical model of the true $E(\theta)$, in particular its dependence on the parameters of the system, we consider two simple parameterized models: a Gaussian jet and a power law jet with a smooth core.
+The \citet{Aloy:2005aa} model (B01 in the paper) was launched as a top hat jet into an accretion torus featuring a narrow underdense funnel region and produced a final energy profile with a relatively sharp edge, although only material with Lorentz factor greater than 100 was included in the $\Eiso$ calculation.
+The \citet{Margutti:2018aa} model used a powerful engine with Gaussian injection profile into a standard BNS merger cloud, resulting in a blunt jet with less energetic wings.
+The \citet{Mizuta:2009aa} model (their HE16N simulation) is of a collapsar jet, injected with a $5^\circ$ opening angle into a collapsing massive star density profile.
+A large degree of interaction with the stellar envelope produces the energetic power law wings.
+The \citet{Lazzati:2017aa} model is meant to emulate a BNS merger and injects a top hat jet into a spherically symmetric ejecta wind, also resulting in a large amount of interaction and energetic power law wings.
+The \citet{Duffell:2013aa} model is an analytic model of a fireball, spherically symmetric in its rest frame, boosted at a bulk Lorentz factor.
+It also produces a narrow core with power law wings.
+
+We note that although a variety of jet energy profiles are produced by these works, none except perhaps \citet{Aloy:2005aa} would be considered a ``top hat.''  Simulations of jets launched in realistic environments reliably produce non-trivial lateral energy profiles.
+Most GRB jets in nature are likely structured jets.
+Given the variation in light curve properties when structured jets are viewed at non-zero inclinations, understanding them is a chief concern for understanding electromagnetic counterparts of gravitational wave sources.
+
+Lacking a well-established physical model of the true $E(\theta)$, in particular its dependence on the parameters of the progenitor system, much of our further discussion considers two simple parameterized models: a Gaussian jet and a power law jet with a smooth core.
 
@@
 
-Figure \ref{fig:jetStruct} shows an example of each model together with jet energy profiles drawn from the literature, mostly the result of numerical relativistic hydrodynamic simulations.
-The Gaussian profile emulates jets with a flat core and sharp edges, typically the result of powerful successful jets \citep{Aloy:2005aa, Margutti:2018aa}.
-Jets which are subject to stronger interactions with the surrounding medium can develop a profile with energetic wings and a narrow core, emulated by the analytic power law profile \citep{Mizuta:2009aa, Duffell:2013aa, Lazzati:2017aa}.
+Figure \ref{fig:jetStruct} also includes an example of each model together with the jet energy profiles drawn from the literature.
+The power law model emulates those jets subject to a large degree of interaction with energetic wings.
+The Gaussian model emulates jets which experienced less (or more focused) interaction and retain sharper sides.
+As $b$ increases the power law profile gets steeper and the wings become less energetic, until in the limit $b\to \infty$ the Gaussian profile is recovered.
 
@@
 
-The afterglow light curve of a structured jet follows one of two qualitatively different regimes depending on the orientation of the viewer with respect to $\thC$.
-We refer to the regimes as ``aligned'' when $\thobs < \thC$, and ``misaligned'' when $\thobs > \thC$.
+The Lorentz factor profile $\gamma(\theta)$ of a jet may also obtain angular structure through its launching and evolution.
+In this work we focus on the consequences of non-trivial $E(\theta)$, as the bulk of successful observations are expected to occur when the jet is in the deceleration regime and the jet is locked to $\gamma(\theta) \propto E(\theta)^{1/2}$.
+We leave the specific consequences of differing $\gamma(\theta)$ profiles, which may affect emission at early times, to future work.
 
@@
 To compute the light curves of structured jet afterglows we constructed numerical and analytic models utilizing the single shell approximation of \cite{van-Eerten:2010aa, van-Eerten:2018ab}.
-Iterations of this model have been applied in the \gwbns{} x-ray discovery paper \citep{Troja:2017aa}, follow-up studies of \gwbns{} \citep{Troja:2018aa, Piro:2019aa, van-Eerten:2018aa}, and in examinations of archival kilonova candidates \citep{Troja:2018ab, Troja:2019aa}.
+Iterations of this model have been applied in the \gwbns{} x-ray discovery paper \citep{Troja:2017aa}, follow-up studies of \gwbns{} \citep{Troja:2018aa, Piro:2019aa, Troja:2019ab}, and in examinations of archival kilonova candidates \citep{Troja:2018ab, Troja:2019aa}.
 This approach integrates over the massive ejecta, contact discontinuity, and forward shock complex, treating it as a single fluid element with uniform radial structure.
@@
 \end{align}
-% TODO: Update spreading description
+
 In Equation \eqref{eq:E} the first term is the kinetic energy of the ejected mass $\Mej$, assumed to have already accelerated and adiabatically cooled to its coasting velocity.
@@
 Afterglow light curves computed using Equation \eqref{eq:thetadot} were found to agree better with established simulation based models (see Section \ref{subsec:bioxfitcomp}) than those computed with the DL18 parameters.
-This jet spreading prescription differs from that used in \citet{Troja:2018aa, Piro:2019aa, van-Eerten:2018aa} which used a simple $u < 1$ criterion to begin jet spreading and set $\beta_\bot = c_s / (c \gamma)$.
-
-% TODO: clarify role of E, where these formulas come from.
+This jet spreading prescription differs from that used in \citet{Troja:2018aa, Piro:2019aa, Troja:2019ab} which used a simple $u < 1$ criterion to begin jet spreading and set $\beta_\bot = c_s / (c \gamma)$.
+
 Given an expression for the total blast wave energy $E$ in terms of $t$, $R$ and $u$, Equations \eqref{eq:Rdot}, \eqref{eq:E}, and \eqref{eq:thetadot} are sufficient to write a system of ordinary differential equations (ODEs) in $R(t)$, $u(t)$, and $\theta_j(t)$.
@@
 
+Due to relativistic beaming the flux at any given time is dominated by a small patch of blast wave surface.
+The angular coordinates of this patch are $\theta = \theta_*$ and $\phi=0$, it has angular size $\Delta \Omega$, Lorentz factor $\gamma_*$, and emits a specific intensity $I_\nu^*$.
 We can write the received flux as:
 \begin{equation}
-	F_\nu = I_\nu^*\ \Delta \Omega\ , 
-\end{equation}
-where $I_\nu^* = I_\nu(\theta^*)$ is the peak specific intensity, located at $\theta=\theta^*$ and $\phi=0$, and $\Delta \Omega$ is the effective solid angle of the blast wave contributing to the emission.
-
-From the definition of $\thC$ in Equation \eqref{eq:thCdef} we can see $E(\theta) = E_0(1 - \theta^2/(2\thC^2) + \OO(\theta^3))$.
-
-We discuss aligned evolution in detail in Section \ref{subsec:aligned} and misaligned in Section \ref{subsec:misaligned}.
-In both cases the transition between phases of evolution depends on the effective solid angle $\Delta \Omega$ of the patch of blast wave dominating the emission.
-The size of this patch tends to scale with the Lorentz factor $\gamma$ of the dominant region as:
-\begin{equation}
-	\Delta \Omega = \gamma^{-\som} \ .
+	F_\nu = I_\nu^*\ \Delta \Omega\ .
+\end{equation}
+
+The behaviour of $\theta_*$ and $\Delta \Omega$ control the overall light curve evolution.  We encode the dependence of $\Delta \Omega$ on the blast wave Lorentz factor as:
+\begin{equation}
+	\Delta \Omega \propto \gamma_*^{-\som} \ .
 \end{equation}
@@
 
-\subsection{Aligned Evolution: $\thobs \lesssim \thC$} \label{subsec:aligned}
-
-The aligned light curve of a structured jet is essentially identical to that of a standard top-hat viewed within the jet cone.
-(CITE Panaitescu \& Kumar).
-The relativistic afterglow is comprised of three phases, \emph{pre-jet break}, \emph{transition}, and \emph{post-jet break}.
-These are well described in the literature and are briefly reviewed here.
-
-\emph{Pre-jet break} ---  At early times the flux is dominated by the small patch of material whose emission is beamed towards the observer of angular width $\psi = |\theta-\thobs| \sim \gamma^{-1}$.
-This patch is within the $\theta < \thC$ region where $E(\theta) \approx E_0$ and the structure plays a sub-dominant role.
-The angular size of the visible patch grows with $\som = 2$.
-Closure relations and scalings of the standard on-axis top-hat apply.
-(CITE Granot and Sari)
-
-\emph{Transition} ---  When $\gamma^{-1} \sim \thC-\thobs$ the near edge of the jet comes in to view.
-Material outside $\thC$ is less energetic and contributes sub-dominantly to the afterglow emission.
-The effective visible patch grows more slowly, $\som \lesssim 2$, and the decay of the afterglow steepens slightly.
-Closure relations and scalings of the standard on-axis top-hat apply only approximately (CITE vanEerten MacFadyen 2010).
-
-\emph{Post-jet break} ---  When $\gamma^{-1} \sim \thC+\thobs$ the far edge of the jet comes in to view and growth of the visible patch ceases, $\som = 0$.
-If the blast wave remains relativistic and non-spreading, the slope of the light curve is reduced by $-3/4$ relative to the pre-jet break slope.
-However, in many circumstances the jet break begins when the blast wave is only trans-relativistic and spreading may have begun.
-In these cases an analytic treatment of the light curve is slope is more difficult, but numerical simulations and analytic work estimate an additional reduction of "???" over the simple analytic result.
-
-The transition between pre-jet break and post-jet break begins at $\tbm$ and completes at $\tbp$, given in the single shell approximation (see Appendix \ref{app:derive1}) by:
-\begin{align}
-	\tbpm &= \left(\frac{9}{16\pi} \frac{E_0}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thC\pm\thobs}{2}\right)\right)^{8/3} .\label{eq:tbpm}
-\end{align}
-\begin{figure}
-	\includegraphics[width=\columnwidth]{figs/breaks_alignedOA_all.pdf}
-	\caption{Jet break time for on-axis ($\thobs=0$) observers for top-hat (blue circles), Gaussian (orange squares), and power law (green triangles) jets as a function of $\thC$.
-The dashed grey line is the analytic approximation $\tbpm = t_N (2\sin \thC/2)^{8/3}$.
-These particular light curves use $\thW = 5 \thC$, $E_0 = 10^{52}$erg, $n_0=10^{-3}$cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, and $\epsB = 10^{-4}$.
-\label{fig:tbOA}}
-\end{figure}
-
-It is important to note that when $\thobs \neq 0$ the transition period is extended, and the most significant transition in the light curve occurs at $\tbp$, the \emph{jet break}.
-The jet break occurs, in all jets, when the effective angular size of the visible patch of the jet ceases to increase, that is when $\som = 0$.
-
-Figure \ref{fig:tbOA} shows the jet break time for on-axis ($\thobs = 0$) viewers as a function of $\thC$ for top-hat, Gaussian, and power law jets calculated with \afterglowpy{}.
-Break times were extracted by fitting the numerical light curve with a two-component broken power law.
-
-%\begin{figure}
-%	\includegraphics[width=\columnwidth]{figs/lc_on.pdf}
-%	\caption{Aligned ($\thobs = \thC/2$) afterglow light curves for top-hat (blue), Gaussian (orange), and power law (green) jets.
-When viewed on-axis, jets containing angular structure are very difficult to distinguish from top-hats.
-The transition phase marking the onset of the jet break begins at $\tbm\sim3$ days with a shallow break and ends sharply at $\tbp \sim 100$ days.
-These particular light curves use $\thC = 0.1$ rad, $\thW = 0.4$ rad, $E_0 = 10^{52}$erg, $n_0=10^{-2}$cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, $\epsB = 10^{-3}$, and $d_L=40$Mpc.
-\label{fig:onaxis}}
-%\end{figure}
-
-\begin{figure*}
-	\includegraphics[width=\textwidth]{figs/lc_thV_model_multi.pdf}
-	\caption{X-ray afterglow light curves from structured jets at different viewing angles $\thobs$, calculated with \afterglowpy{}.
-Each panel shows the 1 keV flux density $F_\nu$ and the corresponding temporal slope $\alpha = d\log F_\nu / d\log \tobs$.
-Included models are the top-hat jet (dashed blue), Gaussian jet (solid green), $b=2$ power law (dot-dashed orange), and $b=6$ power law at $\thobs=0$ (upper left), $\thobs=2\thC=0.16$ rad (upper right), $\thobs=4\thC=0.32$ rad (lower left), and $\thobs=6\thC=0.48$ rad (lower right).
-These particular light curves all use $\thC = 0.08$ rad, $\thW = 0.24$ rad, $E_0 = 10^{53}$erg, $n_0=1$ cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, $\epsB = 10^{-2}$, $d_L=10^{28}$cm and $z=0.5454$.
-\label{fig:thVmodel}}
-\end{figure*}
-
-Figure \ref{fig:onaxis} shows representative top-hat, Gaussian, and power law jet light curves in the aligned regime.
-The light curves nearly overlap, demonstrating the similar evolution of all structured jet afterglows when viewed within the jet core.
-Although we expect all afterglow blast waves to contain angular structure, the simple top-hat jet model is sufficient for aligned viewing.
-
-The relativistic stages of evolution are followed by a Newtonian phase ($t > 200$ days in Figure \ref{fig:onaxis}) when the decelerating blast wave becomes non-relativistic, spreads sonically, and approaches a Sedov-Taylor solution.
-We do not address the Newtonian phase of evolution in this work.
-
-\subsection{Misaligned Evolution: $\thobs \gtrsim \thC$} \label{subsec:misaligned}
-
-When viewed at angles larger than $\thC$ the gradient $E'(\theta)$ over the visible patch becomes non-negligible.
-To observers this energy gradient presents itself as a slowly rising or decaying afterglow light curve.
-The relativistic afterglow is comprised of two or three phases depending on whether the observer lies within the truncation angle, \emph{far off-axis}, \emph{structured}, and \emph{post-jet break}.
-
-\emph{Far off-axis} --- If the viewer lies outside the truncation angle, $\thobs > \thW$, then at early times the entire blast wave surface is off-axis and all emission is beaming suppressed.
-This greatly reduces the early flux and leads to a dim but steeply rising light curve as the blast wave decelerates.
-Emission is dominated by material on the edge nearest the observer and the angular size of the visible patch is constant in time.
-This phase ends at $\tW$ when $\gamma^{-1}(\thW) \sim \thobs-\thW$.
-If $\thobs < \thW$ this phase is entirely absent.
-Table \ref{tab:slopes} gives the temporal power law slope of the light curve in this phase.
-These slopes are derived in Appendix \ref{app:derive1}.
-
-\emph{Structured} --- The structured phase is the direct result of the energy gradient along the observer's line of site.
-The usual (pre-jet break) decay is compensated for by regions of higher energy continuously coming into view as the jet decelerates.
-These new contributions to the emission slow the decay and can even cause the observed flux to increase with time.
-
- This phase begins at observer time $\tW$, once the blast wave is decelerating and the observer is within the beaming cone of any part of the emitting surface.
-It ends at observer time $\tb$, when the jet core has become fully visible.
-These times are:
-\begin{align}
-	\tW &= \left(\frac{9}{16\pi} \frac{E(\thW)}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thobs-\thW}{2}\right)\right)^{8/3} \ ,\label{eq:tw} \\
-	\tb &= \left(\frac{9}{16\pi} \frac{E_0}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thobs}{2}\right)\right)^{8/3} \ .\label{eq:tb}
-\end{align}
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{figs/jetDecomp.pdf}
-	\caption{A Gaussian structured jet, decomposed into emission from different latitudes $\theta$.
-The off-axis, structured, and post-jet break phases are all clearly visible.
-The structured phase is the result of the brightest point of the blast-wave tracking from the wings $(\theta =\thW$) to the jet core ($\theta=\thC$).
-\label{fig:decomp}}
-\end{figure}
-Figure \ref{fig:decomp} shows the light curve of a Gaussian structured jet along with the emissions from different latitudes.
-The part of the blast wave dominating the emission tracks from the high latitude wings $\theta \approx \thW$ to the core $\theta \approx 0$.
-The angular size of the visible patch grows approximately as $\gamma^{-1.0}$.
-(NEED PLOT?)
-
-During the structured phase, the afterglow has a temporal spectral slope which depends on the parameter $g(\theta^*)$, where $\theta^*$ is the latitude of material dominating the emission:
-\begin{equation}
-	g(\theta^*) \equiv -2 \tan\left(\frac{\thobs - \theta^*}{2}\right)\frac{d \log E}{d \theta}\ . \label{eq:gdef}
-\end{equation}
-
-The temporal and spectral slopes for various regimes are given in Table \ref{tab:slopes}.  The derivation of the closure relations, $\tW$, and $\tb$ are given in Appendix \ref{app:derive1}.
+\subsection{Phases Of Evolution} \label{subsec:phases}
+
+The afterglow of a structured jet evolves through several phases, depending on the observer orientation, jet structure, and Lorentz factor of the blast wave.
+We summarize each phase below in roughly temporal order.
+Table \ref{tab:slopes} gives the \emph{closure relations}, the temporal and spectral power law slopes of the observed flux, for each of the afterglow phases in the synchrotron spectral regimes D-H.
 
@@
 	\nu_m<\nu<\nu_c     & G 	&15/2 - 3p/2 & \dfrac{-6p + 3\som + 3g}{8+g} 	& \dfrac{3 - 6p +3g}{8+g} 	& -3(p-1)/4 & -3p/4	& (1-p)/2 \\[0.3cm]
-	\nu_m, \nu_c < \nu & H 	& 8 - 3p/2 	& \dfrac{-6p - 2 + 3\som + 2g}{8+g} 	& \dfrac{1-6p  +2g}{8+g} 	& -3p/4	& -(3p+1)/4 & -p/2 \\[0.3cm]
+	\nu_m, \nu_c < \nu & H 	& 8 - 3p/2 	& \dfrac{-6p - 2 + 3\som + 2g}{8+g} 	& \dfrac{1-6p  +2g}{8+g} 	& -(3p-2)/4 & -(3p+1)/4 & -p/2 \\[0.3cm]
 	\enddata
 \end{deluxetable*}
+
+\emph{Coasting} --- Before the blast wave begins to decelerate it coasts at constant Lorentz factor. The emissivity is constant, and the total flux increases $F_\nu \propto t^3$.
+
+\emph{Far Off Axis} --- If the viewer lies outside the truncation angle, $\thobs > \thW$, then at early times there is no material in the line of sight, the entire blast wave surface is off-axis, and all emission is beaming suppressed.
+This greatly reduces the early flux and leads to a dim but steeply rising light curve as the blast wave decelerates.
+Emission is dominated by material on the edge nearest the observer, $\theta_* = \thW$, and the angular size of the visible patch is constant in time, $\som = 0$.
+This phase ends at $\tW$ when $\gamma^{-1}(\thW) \sim \thobs-\thW$.
+If $\thobs < \thW$ this phase is entirely absent.
+Table \ref{tab:slopes} gives the temporal power law slope of the light curve in this phase.
+These slopes are derived in Appendix \ref{app:derive1}.
+
+\emph{Pre-jet break} --- The standard on-axis early afterglow phase.
+The flux is dominated by a small patch of relativistic material directly in the line of sight: $\theta_* = \thobs$.
+The material is relativistic, $\gamma_* \gg 1$, and the angular size is controlled by doppler beaming: $\psi \sim \gamma_*^{-1}$ and $\som = 2$.
+The patch is sufficiently small (or sufficiently on-axis) that $E(\theta)$ is near-uniform over the visible patch.
+Closure relations and scalings of the standard on-axis top hat jet apply, e.g.
+\citet{Granot:2002aa}.
+
+\emph{Structured} --- If the viewer lies outside the core of the blast wave, $\thobs > \thC$, non-trivial angular structure can have a significant effect on the light curve.
+Material from the energetic polar regions continuously comes into view, becoming the new dominant source of emission, and moving the centroid with time: $\theta_* \to 0$ as $\tobs$ increases.
+The centroid obeys $\gamma^{-1}(\theta_*) \sim |\thobs-\theta_*|$.
+The angular size of the visible patch in the azimuthal direction is still controlled by beaming, but in the polar direction it is controlled by the steep gradient in $E(\theta)$, resulting in $\som \approx 1$.
+The temporal evolution of the light curve depends on both the specific angular structure $E(\theta)$ and the viewing angle $\thobs$.
+The specific closure relations are given in Table \ref{tab:slopes} and discussed in Section \ref{subsec:structure}.
+
+\emph{Post-jet break} --- The jet break is an achromatic break in the light curve caused when the angular size of the visible patch ceases to change: $\som = 0$.
+At the same time, jet spreading begins in earnest causing the jet to decelerate quicker \citep{Rhoads:1999aa}.
+Both effects cause an achromatic steepening of the light curve.
+Table \ref{tab:slopes} gives an over-estimate of the post-jet break slope, including the $\som=0$ effect but neglecting jet spreading.
+
+There are three possible orderings of these phases, depending on the viewing angle and particular jet structure.
+The ``standard afterglow'' occurs for aligned observers, $\thobs < \thC$, and follows \emph{coast} $\to$ \emph{pre-jet break} $\to$ \emph{post-jet break}.
+Misaligned viewers inside the truncation angle, $\thC < \thobs < \thW$, will see \emph{coast} $\to$ \emph{pre-jet break} $\to$ \emph{structured} $\to$ \emph{post-jet break}.
+Misaligned viewers outside the truncation angle, $\thobs > \thC, \thW$, will see \emph{coast} $\to$ \emph{far off-axis} $\to$ \emph{structured} $\to$ \emph{post-jet break}.
+
+\begin{figure*}
+	\includegraphics[width=\textwidth]{figs/lc_thV_model_multi.pdf}
+	\caption{X-ray afterglow light curves from structured jets at different viewing angles $\thobs$, calculated with \afterglowpy{}.
+Each panel shows the 1 keV flux density $F_\nu$ and the corresponding temporal slope $\alpha = d\log F_\nu / d\log \tobs$.
+Included models are the top-hat jet (dashed blue), Gaussian jet (solid green), $b=2$ power law (dot-dashed orange), and $b=6$ power law at $\thobs=0$ (upper left), $\thobs=2\thC=0.16$ rad (upper right), $\thobs=4\thC=0.32$ rad (lower left), and $\thobs=6\thC=0.48$ rad (lower right).
+These particular light curves all use $\thC = 0.08$ rad, $\thW = 0.24$ rad, $E_0 = 10^{53}$erg, $n_0=1$ cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, $\epsB = 10^{-2}$, $d_L=10^{28}$cm and $z=0.5454$.
+\label{fig:thVmodel}}
+\end{figure*}
+
+Figure \ref{fig:thVmodel} shows afterglow light curves from structured jet models at several viewing angles computed with \afterglowpy{}.
+The upper left panel shows top-hat, Gaussian, $b=2$ power law, and $b=6$ power law jets viewed exactly on-axis at $\thobs=0$.
+Each model shares $\thC=0.08$ rad, $\thW=0.24$rad, $E_0=10^53$ erg, $n_0 = 1$cm$^{-3}$, $p=2.2$, $\epse=10^{-1}$, $\epsB = 10^{-2}$, $d_L=10^{28}$cm and $z=0.5454$.
+All of the models were computed with zero initial mass loading, so they do not show coasting phases.
+They each show identical pre-jet break phases and similar post-jet break phases.
+Each exhibits a slightly different jet break time, between $10^5$s and $10^6$s with these parameters, due to the different structure profiles $E(\theta)$.
+This causes a discrepancy in the overall normalization, jets with more energetic wings but the same core with $\thC$ break later and remain brighter.
+This discrepancy remains at all inclinations.
+
+The upper right panel of Figure \ref{fig:thVmodel} shows the same models viewed at $\thobs=2\thC=0.16$ rad.
+The top-hat jet exhibits an initial far off-axis phase which ends when the near side of the jet comes into view at $t=10^5$s.
+This initiates a prolonged transition period which completes  $\lesssim 10^6$s as the far edge comes into view, leading into a normal post-jet break phase.
+The structured models show similar pre-jet break phases, with slight normalization differences due to differing energies in the line of sight.
+The light curves converge before the jet break at $t \lesssim 10^6$s due to a brief structured phase in the Gaussian and $b=6$ models, which shallows their decay slightly.
+All models show a jet break and transition to similar post-jet break phases after $10^6$s.
+
+The lower left panel of Figure \ref{fig:thVmodel} shows the same models viewed at $\thobs=4\thC=0.32$ rad.
+Since $\thW=0.24$ rad all models show an initial far-off axis phase.
+The structured models transition to a structured phase between $10^4s$ and $10^5$s, much shallower than the standard pre-jet break behaviour.
+The slope is shallowest in the the models with sharpest profiles: the Gaussian and $b=6$ power law.
+All models show a jet break at $t\approx 2\times 10^6$s and similar post-jet-break phases.
+
+The lower right panel of Figure \ref{fig:thVmodel} shows the same models viewed at $\thobs=6\thC=0.64$ rad.
+The far off axis phase lasts longer, and the structured phases have shallower slopes.
+The Gaussian model even shows an increasing light curve.
+Glitches in the $\alpha(\tobs)$ curves are due to the numerical treatment of jet spreading.
+All models show a jet break at $t\approx 6\times 10^6$s and similar post-jet-break phases.
+
+It should be noted that the tight behaviour of the light curves near the jet break is due in part to our standardized definition of $\thC$ in Equation \eqref{eq:thCdef}.
+Alternative definitions, particularly omitting the factor of $b$ in the denominator of the power law profile expression, lead to larger differences in normalization with less shared features between light curves at the same $\thC$.
+
+\subsection{Structured Phase: Closure Relations and Break Times}\label{subsec:structure}
+
+Closure relations for the pre-jet break and post-jet break afterglow phases are well known in the literature (e.g.
+\citet{Granot:2002aa, Rhoads:1999aa}).
+The closure relations for the far off axis phase in some spectral regimes first appeared in \citep{Salmonson:2003aa}.
+Here we provide closure relations for the structured phase, as well as scalings for the jet break time with viewing angle.
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{figs/jetDecomp.pdf}
+	\caption{A Gaussian structured jet, decomposed into emission from different latitudes $\theta$.
+The off-axis, structured, and post-jet break phases are all clearly visible.
+The structured phase is the result of the brightest point of the blast-wave tracking from the wings $(\theta =\thW$) to the jet core ($\theta=\thC$).
+\label{fig:decomp}}
+\end{figure}
+
+Figure \ref{fig:decomp} shows the afterglow light curve of a Gaussian structured jet at viewed at $\thobs = 5 \thC = 0.5$ rad, clearly showing the far off axis, structured, and post jet break phases.
+Also shown is a decomposition of the light curve into the contributions from each annular shell, from $\theta =\thW$ to $\theta = 0$.
+The emission at any given time is dominated by material in a particular annular shell ($\theta = \theta_*$), which tracks towards the jet axis with time.
+Material closer to the pole ($\theta < \theta_*$) has too high a Lorentz factor and is beaming suppressed, while material closer to the line of sight ($\theta > \theta_*$) has already peaked in emission and decreases with the standard pre-jet-break rate.
+The material dominating the emission is that which just entered the beaming cone, with $\gamma_*^{-1} \sim \thobs-\theta_*$.
+
+We can calculate the structured jet closure relations by determining how the time and magnitude of the peak of each annular section depends on the angle $\theta_*$.
+The details are given in Appendices \ref{app:derive1} and \ref{app:derive2}, we give only the results here.
+For brevity we define:
+\begin{equation}
+	\chi_* \equiv 2 \sin\left[\left(\thobs - \theta_*\right)/2\right] \approx \thobs-\theta_* \ . \label{eq:chiDef}
+\end{equation} 
+During the structured phase, the time at which the $\theta_*$ section peaks (dropping all pre-factors that do not depend on $\theta_*$) is:
+\begin{equation}
+	\tobs(\theta_*) \propto E(\theta_*)^{1/3} \chi_*^{8/3}\ . \label{eq:tobsTheta}
+\end{equation}
+While the blast wave is relativistic the rest-frame synchrotron emissivity has a power law dependence on the Lorentz factor and time in the burster frame: $\epsilon'_{\nu'} \propto \gamma_*^{s_\gamma} t^{s_t}$.
+We can then write the total received flux from section $\theta_*$:
+\begin{equation}
+	F_\nu(\theta_*) \propto E(\theta_*)^{1 + s_t/3} \chi_*^{-s_\gamma + 2s_t/3 + \som + \beta} \nuobs^\beta\ .\label{eq:FnuTheta}
+\end{equation}
+Differentiating Equations \eqref{eq:tobsTheta} and \eqref{eq:FnuTheta} with respect to $\theta_*$ we find the slope of the light curve to be:
+\begin{equation}
+	\alpha \equiv \frac{d \log F_\nu}{d \log \tobs} = \frac{3 \beta - 3s_\gamma + 2s_t + 3\som + (3+s_t) g(\theta_*)}{8+g(\theta_*)}\ , \label{eq:structSlope}
+\end{equation}
+where
+\begin{equation}
+	g(\theta_*) \equiv -2\tan\left(\frac{\thobs-\theta_*}{2}\right) \left . \frac{d \log E}{d \theta}\right |_{\theta_*} \ . \label{eq:gdef}
+\end{equation}
+Equation \eqref{eq:structSlope} is the standard pre-jet break afterglow temporal slope, with dependence on $\som$ made explicit and the additional viewing angle dependent $g$ parameter.
+The $g$ parameter is positive and to first order completely accounts for the presence of angular structure, a non-trivial $E(\theta)$, in the blast wave.
+It is zero when the dominant material is in the line of sight ($\theta_* = \thobs$) or the jet is a top hat ($dE/d\theta = 0$).
+
+The $g$ parameter evolves with time as $\theta^*$ sweeps from the jet edge to the core.
+This produces deviations in the light curve from a pure power law.
+However, we find ultimately these deviations are not too large and the average slope is well approximated by $\geff  = g(\theff)$, where $\theff$ is a fiducial angular section which depends on viewing angle and potentially other structure parameters.
+For the Gaussian model $\theff$ is simply half the viewing angle, for the power law model a suitable fitting function was found through comparison to a grid of \afterglowpy{} light curves:
+\begin{align}
+	\theff &= \frac{\thobs}{2}&& \text{Gaussian} \\
+	\theff &= \thobs \big [1.8+2.1b^{-1.25}  && \text{power law} \nonumber  \\
+	 	& \qquad + (0.49-0.86b^{-1.15}) \thobs/\thC \big ] ^{-1/2} &&\label{eq:theff}
+\end{align}
+In the expressions for $\geff$ it is reasonable to assume $2 \tan((\thobs-\theff)/2) \approx \thobs-\theff$ leading to the manageable expressions:
+\begin{align}
+	\geff &= \frac{\thobs^2}{4\thC^2} && \text{Gaussian}\ , \\
+	\geff &= \frac{2 b (\thobs-\theff)\theff}{b \thC^2+\theff^2} && \text{power law}\ . \label{eq:geff}
+\end{align}
+These values may be used in Table \ref{tab:slopes} for an approximate power law model of a structured jet with an appropriate viewing angle dependent temporal evolution.
+These analytic results are in agreement with previous work on structured jets \citep{Rossi:2004aa} and the trans-relativistic numerical model described in Section \ref{sec:numerical}.
+
+In the structured phase, the temporal slope depends directly on the ratio $\thobs/\thC$.
+Therefore any measurement of the effective power law slope of an afterglow light curve in the structured phase can be used to measure this parameter.
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{figs/slopesJet.png}
+	\caption{Temporal slopes for the off-axis structured jet as a function of the structure parameter $g$ for the synchrotron spectral regimes D (blue, narrow), E (orange, narrow),  F (green, narrow), G (red, wide), and H (purple, wide).
+The width of the G and H bands shows the dependency on $p$, the upper curves for $p=2$ and the lower for $p=3$.
+The temporal power law slope of a structured jet afterglow increases with $g$ in all spectral regimes.
+\label{fig:slopesG}}
+\end{figure}
+
+Figure \ref{fig:slopesG} shows the structured phase power law temporal slope as a function of $g$ for spectral regimes $D$--$H$.
+In the $G$ and $H$ regimes the spectral slope is a function of $p$, this dependence carries over into the temporal slope as well.
+The temporal slope is an increasing function of $g$ in all regimes.
+At sufficiently large $g$ all regimes exhibit rising light curves, the specific $g$ at which the light curve begins to rise is regime dependent.
+
+A viewer outside the truncation angle, $\thobs > \thW$, may observe a steeply rising far-off-axis phase.
+This phase transitions to the structured phase once the near edge of the jet enters the beaming cone: $\gamma^{-1}(\thW) \sim \thobs-\thW$.
+This will occur at observer time:
+\begin{equation}
+	\tW = \left(\frac{9}{16\pi} \frac{E(\thW)}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thobs-\thW}{2}\right)\right)^{8/3} \ .\label{eq:tw}
+\end{equation}
+
+The jet break is the time at which the effective angular size of the jet ceases to increase, $\som = 0$.
+For an on-axis observer of a top hat jet, this is when the jet edges come into view.
+More generally, this is the moment when the blast wave has sufficiently decelerated that the viewer is within the beaming cones of its brightest regions.
+For \emph{aligned} viewers, $\thobs < \thC$, the jet break marks the transition from pre- to post-jet break phases.
+For \emph{misaligned} viewers, $\thobs > \thC$, the jet break marks the transition from structured to post-jet break phases.
+
+It is long established that on-axis viewers observe the jet break in their frame at a time $\tb \propto \thC^{8/3}$ (e.g.
+\citet{Rhoads:1999aa}), while significantly off-axis viewers observe the jet break at $\tb \propto \thobs^{8/3}$ \citep{Rossi:2002aa, Panaitescu:2003aa}.
+More generally, for initially top hat jets it has been shown the jet break corresponds to the far jet edge coming into view, that is $\tb \propto (\thC + \thobs)^{8/3}$ \citep{van-Eerten:2010aa}.
+We find this latter result to hold true for structured jets as well.
+As $\thC$ denotes the angular size of the bright jet core, once this time is reached the jet is essentially entirely in view.
+Wings of the jet on the far side from the viewer may still come into view, but remain a subdominant contribution to the bright core within $\thC$.
+
+In our single shell approximation, then, the jet break occurs near:
+\begin{equation}
+	\tb = \left(\frac{9}{16\pi} \frac{E_0}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thobs+\thC}{2}\right)\right)^{8/3} \ .\label{eq:tb}
+\end{equation}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{figs/breaks_alignedOA_all.pdf}
+	\caption{Jet break time for on-axis ($\thobs=0$) observers for top-hat (blue circles), Gaussian (orange squares), and power law (green triangles) jets as a function of $\thC$.
+The dashed grey line is the analytic approximation $\tbpm = t_N (2\sin \thC/2)^{8/3}$.
+These particular light curves use $\thW = 5 \thC$, $E_0 = 10^{52}$erg, $n_0=10^{-3}$cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, and $\epsB = 10^{-4}$.
+\label{fig:tbOA}}
+\end{figure}
+
+Figure \ref{fig:tbOA} shows the observed jet break time $\tb$ for on-axis, $\thobs=0$ viewers, as a function of core half-width $\thC$ for several structure models.
+The expected scaling with $\thC^{8/3}$ is observed, although as seen in Figure \ref{fig:thVmodel} there is some model-dependent offset due to the particular shape of the wings.
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{figs/breaks_general.pdf}
+	\caption{Jet break time for off-axis ($\thobs\neq0$) observers for top-hat (blue circles), Gaussian (orange squares), and power law (green triangles) jets as a function of $\thC$.
+The dashed grey line is the analytic approximation $\tbpm = t_N (2\sin \thobs/2)^{8/3}$.
+These particular light curves use $\thW = 5 \thC$, $E_0 = 10^{52}$erg, $n_0=10^{-3}$cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, and $\epsB = 10^{-4}$.
+\label{fig:tbG}}
+\end{figure}
+
+Figure \ref{fig:tbG} shows the observed jet break time for generic viewers of various structure models.
+At small viewing angles $\tb$ only depends linearly on $\thobs$, but asymptotically approaches $\thobs^{8/3}$ as $\thobs \gg \thC$.
+
+%\subsection{Aligned Evolution: $\thobs \lesssim \thC$} \label{subsec:aligned}
+%
+%The aligned light curve of a structured jet is essentially identical to that of a standard top-hat viewed within the jet cone.
+(CITE Panaitescu \& Kumar).
+The relativistic afterglow is comprised of three phases, \emph{pre-jet break}, \emph{transition}, and \emph{post-jet break}.
+These are well described in the literature and are briefly reviewed here.
+%
+%\emph{Pre-jet break} ---  At early times the flux is dominated by the small patch of material whose emission is beamed towards the observer of angular width $\psi = |\theta-\thobs| \sim \gamma^{-1}$.
+This patch is within the $\theta < \thC$ region where $E(\theta) \approx E_0$ and the structure plays a sub-dominant role.
+The angular size of the visible patch grows with $\som = 2$.
+Closure relations and scalings of the standard on-axis top-hat apply.
+(CITE Granot and Sari)
+%
+%\emph{Transition} ---  When $\gamma^{-1} \sim \thC-\thobs$ the near edge of the jet comes in to view.
+Material outside $\thC$ is less energetic and contributes sub-dominantly to the afterglow emission.
+The effective visible patch grows more slowly, $\som \lesssim 2$, and the decay of the afterglow steepens slightly.
+Closure relations and scalings of the standard on-axis top-hat apply only approximately (CITE vanEerten MacFadyen 2010).
+%
+%\emph{Post-jet break} ---  When $\gamma^{-1} \sim \thC+\thobs$ the far edge of the jet comes in to view and growth of the visible patch ceases, $\som = 0$.
+If the blast wave remains relativistic and non-spreading, the slope of the light curve is reduced by $-3/4$ relative to the pre-jet break slope.
+However, in many circumstances the jet break begins when the blast wave is only trans-relativistic and spreading may have begun.
+In these cases an analytic treatment of the light curve is slope is more difficult, but numerical simulations and analytic work estimate an additional reduction of "???" over the simple analytic result.
+%
+%The transition between pre-jet break and post-jet break begins at $\tbm$ and completes at $\tbp$, given in the single shell approximation (see Appendix \ref{app:derive1}) by:
+%\begin{align}
+%	\tbpm &= \left(\frac{9}{16\pi} \frac{E_0}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thC\pm\thobs}{2}\right)\right)^{8/3} .\label{eq:tbpm}
+%\end{align}
+%
+%It is important to note that when $\thobs \neq 0$ the transition period is extended, and the most significant transition in the light curve occurs at $\tbp$, the \emph{jet break}.
+The jet break occurs, in all jets, when the effective angular size of the visible patch of the jet ceases to increase, that is when $\som = 0$.
+%
+%Figure \ref{fig:tbOA} shows the jet break time for on-axis ($\thobs = 0$) viewers as a function of $\thC$ for top-hat, Gaussian, and power law jets calculated with \afterglowpy{}.
+Break times were extracted by fitting the numerical light curve with a two-component broken power law.
+%
+%%\begin{figure}
+%%	\includegraphics[width=\columnwidth]{figs/lc_on.pdf}
+%%	\caption{Aligned ($\thobs = \thC/2$) afterglow light curves for top-hat (blue), Gaussian (orange), and power law (green) jets.
+When viewed on-axis, jets containing angular structure are very difficult to distinguish from top-hats.
+The transition phase marking the onset of the jet break begins at $\tbm\sim3$ days with a shallow break and ends sharply at $\tbp \sim 100$ days.
+These particular light curves use $\thC = 0.1$ rad, $\thW = 0.4$ rad, $E_0 = 10^{52}$erg, $n_0=10^{-2}$cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, $\epsB = 10^{-3}$, and $d_L=40$Mpc.
+\label{fig:onaxis}}
+%%\end{figure}
+%
+%
+%Figure \ref{fig:onaxis} shows representative top-hat, Gaussian, and power law jet light curves in the aligned regime.
+The light curves nearly overlap, demonstrating the similar evolution of all structured jet afterglows when viewed within the jet core.
+Although we expect all afterglow blast waves to contain angular structure, the simple top-hat jet model is sufficient for aligned viewing.
+%
+%The relativistic stages of evolution are followed by a Newtonian phase ($t > 200$ days in Figure \ref{fig:onaxis}) when the decelerating blast wave becomes non-relativistic, spreads sonically, and approaches a Sedov-Taylor solution.
+We do not address the Newtonian phase of evolution in this work.
+%
+%\subsection{Misaligned Evolution: $\thobs \gtrsim \thC$} \label{subsec:misaligned}
+%
+%When viewed at angles larger than $\thC$ the gradient $E'(\theta)$ over the visible patch becomes non-negligible.
+To observers this energy gradient presents itself as a slowly rising or decaying afterglow light curve.
+The relativistic afterglow is comprised of two or three phases depending on whether the observer lies within the truncation angle, \emph{far off-axis}, \emph{structured}, and \emph{post-jet break}.
+%
+%\emph{Far off-axis} --- If the viewer lies outside the truncation angle, $\thobs > \thW$, then at early times the entire blast wave surface is off-axis and all emission is beaming suppressed.
+This greatly reduces the early flux and leads to a dim but steeply rising light curve as the blast wave decelerates.
+Emission is dominated by material on the edge nearest the observer and the angular size of the visible patch is constant in time.
+This phase ends at $\tW$ when $\gamma^{-1}(\thW) \sim \thobs-\thW$.
+If $\thobs < \thW$ this phase is entirely absent.
+Table \ref{tab:slopes} gives the temporal power law slope of the light curve in this phase.
+These slopes are derived in Appendix \ref{app:derive1}.
+%
+%\emph{Structured} --- The structured phase is the direct result of the energy gradient along the observer's line of site.
+The usual (pre-jet break) decay is compensated for by regions of higher energy continuously coming into view as the jet decelerates.
+These new contributions to the emission slow the decay and can even cause the observed flux to increase with time.
+%
+% This phase begins at observer time $\tW$, once the blast wave is decelerating and the observer is within the beaming cone of any part of the emitting surface.
+It ends at observer time $\tb$, when the jet core has become fully visible.
+These times are:
+%\begin{align}
+%	\tW &= \left(\frac{9}{16\pi} \frac{E(\thW)}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thobs-\thW}{2}\right)\right)^{8/3} \ ,\label{eq:tw} \\
+%	\tb &= \left(\frac{9}{16\pi} \frac{E_0}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thobs}{2}\right)\right)^{8/3} \ .\label{eq:tb}
+%\end{align}
+%
+%Figure \ref{fig:decomp} shows the light curve of a Gaussian structured jet along with the emissions from different latitudes.
+The part of the blast wave dominating the emission tracks from the high latitude wings $\theta \approx \thW$ to the core $\theta \approx 0$.
+The angular size of the visible patch grows approximately as $\gamma^{-1.0}$.
+(NEED PLOT?)
+%
+%During the structured phase, the afterglow has a temporal spectral slope which depends on the parameter $g(\theta^*)$, where $\theta^*$ is the latitude of material dominating the emission:
+%\begin{equation}
+%	g(\theta^*) \equiv -2 \tan\left(\frac{\thobs - \theta^*}{2}\right)\frac{d \log E}{d \theta}\ . \label{eq:gdef}
+%\end{equation}
+%
+%The temporal and spectral slopes for various regimes are given in Table \ref{tab:slopes}.  The derivation of the closure relations, $\tW$, and $\tb$ are given in Appendix \ref{app:derive1}.
 
@@
 
-The $g$ parameter evolves with time as $\theta^*$ sweeps from the jet edge to the core.
+%The $g$ parameter evolves with time as $\theta^*$ sweeps from the jet edge to the core.
 This produces deviations in the light curve from a pure power law.
@@
 For the power law and Gaussian jet models this gives:
-\begin{align}
-	\theff &= \frac{\thobs}{2}&& \text{Gaussian}\ , \\
-	\theff &= \frac{\thobs}{\sqrt{1.8+2.1b^{-1.25} + (0.49-0.86b^{-1.25})\thobs/\thC}}&& \text{power law}\ . \label{eq:theff}
-\end{align}
-\begin{align}
-	\geff &= \frac{\thobs^2}{4\thC^2} && \text{Gaussian}\ , \\
-	\geff &= \frac{2 b (\thobs-\theff)\theff}{b \thC^2+\theff^2} && \text{power law}\ . \label{eq:geff}
-\end{align}
-These values may be used in Table \ref{tab:slopes} for an approximate power law model of a structured jet with an appropriate viewing angle dependent temporal evolution.
+%\begin{align}
+%	\theff &= \frac{\thobs}{2}&& \text{Gaussian}\ , \\
+%	\theff &= \frac{\thobs}{\sqrt{1.8+2.1b^{-1.25} + (0.49-0.86b^{-1.25})\thobs/\thC}}&& \text{power law}\ . \label{eq:theff}
+%\end{align}
+%\begin{align}
+%	\geff &= \frac{\thobs^2}{4\thC^2} && \text{Gaussian}\ , \\
+%	\geff &= \frac{2 b (\thobs-\theff)\theff}{b \thC^2+\theff^2} && \text{power law}\ . \label{eq:geff}
+%\end{align}
+%These values may be used in Table \ref{tab:slopes} for an approximate power law model of a structured jet with an appropriate viewing angle dependent temporal evolution.
 These analytic results are in agreement with previous work on structured jets (CITE ROSSI) and the trans-relativistic numerical model described in Section \ref{sec:numerical}.
-
-In the structured phase, the temporal slope depends directly on the ratio $\thobs/\thC$.
+%
+%In the structured phase, the temporal slope depends directly on the ratio $\thobs/\thC$.
 Therefore any measurement of the effective power law slope of an afterglow light curve in the structured phase can be used to measure this parameter.
-
-\emph{Post-jet break} --- Once the entire jet is visible (ie.
+%
+%\emph{Post-jet break} --- Once the entire jet is visible (ie.
 the observer is within the beaming cone of the entire jet) the visible patch no longer grows and emission is dominated by the decelerating core.
@@
 
-Figures \ref{fig:offaxis1} and \ref{fig:offaxis2} display afterglows from the fiducial models in the misaligned regime at $\thobs = 2\thC$ and $\thobs=6\thC$ respectively.
+%Figures \ref{fig:offaxis1} and \ref{fig:offaxis2} display afterglows from the fiducial models in the misaligned regime at $\thobs = 2\thC$ and $\thobs=6\thC$ respectively.
 At the moderate $2\thC$ viewing angle both structured models exhibit similar decaying light curves with slopes somewhat shallower than the aligned case.
@@
 At late times as more of the jet comes in to view the difference between all three models becomes negligible.
-
-At the larger $6\thC$ viewing angle all three models exhibit off-axis, structured, and post-jet break phases of the afterglow.
+%
+%At the larger $6\thC$ viewing angle all three models exhibit off-axis, structured, and post-jet break phases of the afterglow.
 The different $\tW$ between the Gaussian and power law models is due to the different $E(\thW)$ of the two models.
@@
 %
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{figs/slopesJet.png}
-	\caption{Temporal slopes for the off-axis structured jet as a function of the structure parameter $g$ for the synchrotron spectral regimes D (blue, narrow), E (orange, narrow),  F (green, narrow), G (red, wide), and H (purple, wide).
-The width of the G and H bands shows the dependency on $p$, the upper curves for $p=2$ and the lower for $p=3$.
-The temporal power law slope of a structured jet afterglow increases with $g$ in all spectral regimes.
-\label{fig:slopesG}}
-\end{figure}
-
-Figure \ref{fig:slopesG} shows the structured phase power law temporal slope as a function of $g$ for spectral regimes $D$--$H$.
-In the $G$ and $H$ regimes the spectral slope is a function of $p$, this dependence carries over into the temporal slope as well.
-The temporal slope is an increasing function of $g$ in all regimes.
-At sufficiently large $g$ all regimes exhibit rising light curves, the specific $g$ at which the light curve begins to rise is regime dependent.
 
@@
 In the simplest case the visible part of the blast wave is assumed to be quasi-spherical.
-The velocity distribution of material behind the blast wave is specified by $E_{>}(u)$, the energy of all material in the ejecta with four-velocity greater than $u$.
+The velocity distribution of material behind the blast wave is specified by $E(u)$, the energy of all material in the ejecta with four-velocity greater than $u$.
 This is typically taken to be a power law in $u$ within the finite domain $[\umin, \umax]$:
 \begin{equation}
-	E_>(u) = E_r u^{-k}\ , \label{eq:Eu}
+	E(u) = E_r u^{-k}\ , \label{eq:Eu}
 \end{equation}
@@
 \end{align}
-Equation \eqref{eq:tumin} assumes $E_r \gg \Mej c^2$.
-The temporal and spectral slopes in this mechanism depend on the energy distribution index $k$ and are given in Table \ref{tab:refreshSlopes}.
-Figure \ref{fig:slopesK} shows the temporal slopes in each spectral regime as a function of $k$.
-As in Figure \ref{fig:slopesG} the width of the $G$ and $H$ regimes reflects varying the value of $p$ between two and three.
-For a derivation see Appendix \ref{app:derive3}.
-
-%
-% Comment: Add dashed line at 0 to slopes plot.
-%
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{figs/slopesCocoon.png}
-	\caption{The temporal power law slope of the spherical refreshed-shock afterglow light curve as a function of $k$.
-Otherwise as Figure \ref{fig:slopesG}.
-The temporal power law slope of a structured jet afterglow increases with $k$ in all spectral regimes.
-\label{fig:slopesK}}
-\end{figure}
-
-\begin{deluxetable*}{CCCCCCC}
-	\tablecaption{Refreshed shock temporal and spectral slopes: $F_\nu \propto \tobs^{-\alpha} \nu^{-\beta}$. See Equation \eqref{eq:Eu} for the definition of $k$.  \label{tab:refreshSlopes}}
-	\tablehead{\colhead{Regime}& \colhead{Label} & \colhead{$\alpha_{\mathrm{coast}}$}& \colhead{$\alpha_{\mathrm{refresh}}$}& \colhead{$\alpha_{\mathrm{refresh,max}}$}& \colhead{$\alpha_{\mathrm{post}}$}  & \colhead{$\beta$}}
+Equation \eqref{eq:tumin} assumes $E_r \gg \Mej c^2$.   The temporal and spectral slopes in this mechanism depend on the energy distribution index $k$ and are given in Table \ref{tab:refreshSlopes}.
+
+\begin{deluxetable}{CCCCC}
+	\tablecaption{Refreshed shock temporal and spectral slopes: $F_\nu \propto \tobs^{\alpha} \nu^{\beta}$. See Equation \eqref{eq:Eu} for the definition of $k$.  \label{tab:refreshSlopes}}
+	\tablehead{\colhead{Regime}& \colhead{Label} & \colhead{$\alpha_{\mathrm{coast}}$}& \colhead{$\alpha_{\mathrm{refresh}}$} & \colhead{$\beta$}}
 	\startdata
-	\nu<\nu_m<\nu_c     & D & 3 	& -\frac{4 + 3k}{8+k} 		& -3		& -1/2	& -1/3 \\
-	\nu_m<\nu<\nu_c     & G & 3 	& \frac{-6 + 6p - 3k}{8+k} 	& -3		& 3(p-1)/4	& (p-1)/2 \\
-	\nu < \nu_c < \nu_m & E & 3 	& -\frac{4/3 + 11k/3}{8+k} 	& -11/3	& -1/6	& -1/3 \\
-	\nu_c < \nu < \nu_m & F & 3 	& \frac{2 - 2k}{8+k} 		& -2		& 1/4		& 1/2 \\
-	\nu_c < \nu_m < \nu & H & 3 	& \frac{- 4 +6p - 2k}{8+k}	& -2		& (3p-2)/4	& p/2 \\ 
+	\nu<\nu_m<\nu_c     & D & 3 	& \frac{4 + 3k}{8+k} 		& 1/3 \\
+	\nu < \nu_c < \nu_m & E & 3 	& \frac{4/3 + 11k/3}{8+k} 	& 1/3 \\
+	\nu_c < \nu < \nu_m & F & 3 	& \frac{-2 + 2k}{8+k} 		& -1/2 \\
+	\nu_m<\nu<\nu_c     & G & 3 	& \frac{-6p + 6 + 3k}{8+k} 	& -(p-1)/2 \\
+	\nu_c < \nu_m < \nu & H & 3 	& \frac{-6p + 4 + 2k}{8+k}	& -p/2 \\ 
 	\enddata
-\end{deluxetable*}
+\end{deluxetable}
 
@@
 \begin{align}
-	q &= (8-2g) / (8+g)  \label{eq:struct2ei} \\
-	\som &= 1
+	q &= (8-2g) / (8+g)\ ,  \label{eq:struct2ei} \\
+	\som &= 1\ .
 \end{align}
 
-Generic closure relations leaving the dependence on $\som$ explicit are presented in Table \ref{tab:generalSlopes}.
-
-%
-% Comment: replace s_3 with s_Omega, s_{1,2} with s_gamma, s_t.
-%
-% "It is insightful..."
-%
-
-%
-% Comment: Emphasize this is in "misaligned" case for structured case, but also applies to refreshed shock.  Just use "alpha".
-%
-
-%
-% Comment: THE JET BREAK *IS* WHEN THE VISIBLE PATCH STOPS GROWING
-%
-
-\begin{deluxetable*}{CCCCCC}
-	\tablecaption{Generic closure relations for the afterglow of a relativistic blast wave in a homogeneous medium: $F_\nu \propto \tobs^{\alpha} \nu^{\beta}$.
-See Equations \eqref{eq:gdef} and \eqref{eq:geff} for the definition and effective values of $g$ for misaligned structured jets.
-Jets aligned with the viewer or without angular structure have $g=0$.
-The visible patch of the jet has a solid angle which scales as $\gamma^{-\som}$.
-A uniform relativistic blast wave pre-jet break has $\som=2$, a relativistic blast wave with angular structure pre-jet break has $\som \approx 1$, and a relativistic blast wave post jet-break has $\som = 0$.
-For a refreshed-shock model replace $g$ with $k$, defined in Equation \eqref{eq:Eu}.
-\label{tab:generalSlopes}}
-	\tablehead{\colhead{Regime}& \colhead{Label} & \colhead{$\alpha$} & \colhead{$\beta$}}
-	\startdata
-	\nu<\nu_m<\nu_c     & D & \frac{-2 + 3\som + 3g}{8+g} 		& 1/3 \\
-	\nu_m<\nu<\nu_c     & G & \frac{-6p + 3\som + 3g}{8+g} 	& (1-p)/2 \\
-	\nu < \nu_c < \nu_m & E & \frac{-14/3 + 3\som + 11g/3}{8+g} 	& 1/3 \\
-	\nu_c < \nu < \nu_m & F & \frac{-8 + 3\som + 2g}{8+g} 		& -1/2 \\
-	\nu_c < \nu_m < \nu & H & \frac{-6p - 2 + 3\som + 2g}{8+g} 	& -p/2 
-	\enddata
-\end{deluxetable*}
+%%%%%%%%%%%%%%%%%%%%%%%
+%
+%  GW170817A
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-Figure \ref{fig:170817Alc} shows the observations in radio, optical, and x-ray bands of the \gwbns{} afterglow.
+Figure \ref{fig:cornerGaussian} (inset) shows the observations in radio, optical, and x-ray bands of the \gwbns{} afterglow.
 No afterglow emission was detected until an x-ray detection by the Chandra observatory nine days after the GW trigger \cite{Troja:2017aa}.
 Further radio, optical, and x-ray observations showed a steady rising light curve with constant power law slope until a peak near day 160.
-At this point the light curve turned over and began a steep decay that continues to the present \citep{van-Eerten:2018aa}.
+At this point the light curve turned over and began a steep decay that continues to the present \citep{Troja:2019ab}.
 
@@
 Aligned jets may only have a rising light curve when viewed at frequencies below the peak frequency, that is when $\beta < 0$.
-	\item The rising light curve maintains $\alpha  = 0.90 \pm 0.06$ (CITE YITL).
+	\item The rising light curve maintains $\alpha  = 0.90 \pm 0.06$ \citep{Troja:2019ab}.
 Using the closure relations from Table \ref{tab:slopes} we can identify this as the \emph{structured} phase and determine $\geff = 7.5 \pm 0.4$.
@@
 For a more detailed analysis we performed Bayesian parameter estimation utilizing \afterglowpy{} and the \emcee{} Markov chain Monte Carlo sampler \citep{Foreman-Mackey:2013aa}.
-We used the light curve data reported in \citet{van-Eerten:2018aa} with additional \hubble{} observations reported in \citet{Lamb:2019aa}.
+We used the light curve data reported in \citet{Troja:2019ab} with additional \hubble{} observations reported in \citet{Lamb:2019aa}.
 Reported measurement uncertainties were assumed to be independent and Gaussian, upper limits were treated as observations of zero flux with a 1-sigma Gaussian uncertainty.
@@
 Since the afterglow presumably provides good constraints on $\geff$ (via $\alpha$), improved knowledge of $\thobs$ immediately improves knowledge of $\thC$, $b$, and any other parameters relevant to $E(\theta)$.
-In some cases this may rule out a particular $E(\theta)$ entirely by pushing the relevant parameters to extreme values, for instance it is hard (but not impossible) to reconcile the observations of \gwbns{} with a power law jet with $b=2$.
+In some cases this may rule out a particular $E(\theta)$ entirely by pushing the relevant parameters to extreme values, for instance it is hard (but not impossible) to reconcile the observations of \gwbns{} with a $b=2$ power law.
 
@@
 
-\section{Shock Jump Conditions and Synchrotron Parameters}
-\label{sec:shockJump}
-
-Table \ref{tab:shockSync} lists the necessary quantities for calculating synchrotron emission from a forward shock.
-Asymptotic expressions are given in the ultra-relativistic and non-relativistic limits.
-The synchrotron emissivity in the fluid rest frame is:
-\begin{equation}
-	\varepsilon'_{\nu'} = \varepsilon_P \times \left \{ \begin{matrix}
-											\left(\nu' / \nu_m\right)^{1/3} & \text{if } \nu' < \nu_m < \nu_c \\
-											\left(\nu' / \nu_m\right)^{(1-p)/2} & \text{if } \nu_m < \nu'  < \nu_c \\
-											\left(\nu_c/\nu_m\right)^{(1-p)/2}\left(\nu' / \nu_c\right)^{-p/2} & \text{if }\nu_m < \nu_c < \nu'\\
-											\left(\nu' / \nu_c\right)^{1/3} & \text{if } \nu' < \nu_c < \nu_m \\
-											\left(\nu' / \nu_c\right)^{-1/2} & \text{if } \nu_c <\nu' <  \nu_m \\
-											\left(\nu_m / \nu_c\right)^{-1/2}\left(\nu' / \nu_m\right)^{-p/2} & \text{if } \nu_c < \nu_m < \nu'
-											\end{matrix} \right .
-\end{equation}
-
-\begin{deluxetable}{CC|CCC}
-\tablehead{ & \colhead{Expression} & \colhead{Coefficient} & \colhead{$ u \gg 1$} & \colhead{$ u \ll 1$}}
-\tablecaption{Emission parameters at forward shock. \label{tab:shockSync}}
-\startdata
-n & 4 \gamma n_0 & 4 n_0 & \gamma & 1 \\
-e & (\gamma-1)n \Mp c^2 & 4 \Mp c^2 n_0 &  \gamma^2 & \frac{1}{2} \beta^2 \\
-B & \sqrt{8\pi e \epsB} & 4(2 \pi)^{1/2}(\Mp c^2)^{1/2} n_0^{1/2} \epsB^{1/2} & \gamma & 2^{-1/2} \beta \\ 
-\hline
-\gamma_m &  \frac{\epseb e}{n \Me c^2} & \frac{\Mp}{\Me} \epseb &  \gamma & \frac{1}{2} \beta^2 \\
-\gamma_c & \frac{3 \Me c \gamma}{4 \sigT \epsB e t} & \frac{3}{16} \frac{\Me}{\Mp\sigT c}n_0 ^{-1} \epsB^{-1} & \gamma^{-1} t^{-1} & 2 \beta^{-2} t^{-1} \\
-\varepsilon_P & \frac{\sqrt{3}}{2}\frac{\qe^3}{\Me c^2}(p-1)n B & 8 (6\pi)^{1/2} \frac{\Mp^{1/2} \qe^3}{\Me c} (p-1) n_0^{3/2} \epsB^{1/2} & \gamma^2 & 2^{-1/2} \beta \\ 
-\nu_m & \frac{3}{4\pi}\frac{\qe}{\Me c} \gamma_m^2 B & 6 (2\pi)^{-1/2} \frac{\Mp^{5/2} \qe}{\Me^3} n_0^{1/2} \epseb^2 \epsB^{1/2} & \gamma^3 & 2^{-5/2} \beta^5 \\
-\nu_c & \frac{3}{4\pi}\frac{\qe}{\Me c} \gamma_c^2 B & \frac{27}{128} (2\pi)^{-1/2} \frac{\Me \qe}{\Mp^{3/2}\sigT^2 c^2} n_0^{-3/2}  \epsB^{-3/2} & \gamma^{-1}t^{-2} & 2^{3/2}\beta^{-3}t^{-2} \\
-\hline
-E & \frac{4\pi}{9} \rho_0 c^2 R^3(4u^2+3)\beta^2 & \frac{16\pi}{9}\rho_0 c^2 & R^3 \gamma^2 & \frac{3}{4} R^3 \beta^2 \\
-\beta_s & \frac{4 u \gamma}{4u^2+3} & 1 & 1 & \frac{4}{3}\beta 
-\enddata
-\end{deluxetable}
-
 \bibliography{structuredJets_sources}

### 2019-08-19 code/paperPlots.py

@@ -1148,27 +1148,26 @@ def calcSlopeOffaxis(jetModel, Y, regime):
 
 def calcSlopeStruct(jetModel, Y, regime, g=None, som=None):
 
-    thV = Y[0]
-    thC = Y[2]
-    thW = Y[3]
-    b = Y[4]
     p = Y[9]
 
     beta, al1, D, s1, s2, p = get_powers(regime, p)
     al2 = 3+s2
 
-    f = get_f(jetModel, thC, thW, b)
-
-    thS = min(0.5*thV, 0.5*thW)
-    psiS = thV-thS
-
-    dth = max(0.1*thC, 1.0e-6)
-    fR = f(thS+dth)
-    fL = f(thS-dth)
-
-    dlfdth = math.log(fR/fL) / (2*dth)
-
     if g is None:
+        thV = Y[0]
+        thC = Y[2]
+        thW = Y[3]
+        b = Y[4]
+        f = get_f(jetModel, thC, thW, b)
+
+        thS = min(0.5*thV, 0.5*thW)
+        psiS = thV-thS
+
+        dth = max(0.1*thC, 1.0e-6)
+        fR = f(thS+dth)
+        fL = f(thS-dth)
+
+        dlfdth = math.log(fR/fL) / (2*dth)
         g = -psiS * dlfdth
     if som is None:
         som = 1.0
@@ -1217,9 +1216,9 @@ def calcSlopePost(jetModel, Y, regime):
 def calcThetaEff(jetModel, Y):
 
     thEff = 0.0
-    thV = jetModel[0]
-    thC = jetModel[2]
-    b = jetModel[4]
+    thV = Y[0]
+    thC = Y[2]
+    b = Y[4]
 
     if jetModel == 0:
         thEff = 0.5*thV
@@ -1231,9 +1230,9 @@ def calcThetaEff(jetModel, Y):
 
 def calcGEff(jetModel, Y):
 
-    thV = jetModel[0]
-    thC = jetModel[2]
-    b = jetModel[4]
+    thV = Y[0]
+    thC = Y[2]
+    b = Y[4]
 
     dlfdth = 0.0
     thEff = calcThetaEff(jetModel, Y)
@@ -1243,7 +1242,7 @@ def calcGEff(jetModel, Y):
     elif jetModel == 4:
         dlfdth = -thEff / (thC*thC + thEff*thEff/b)
 
-    return -(thEff-thV) * dlfdth
[…]

### 2019-08-19 code/plotModelThV.py

@@ -130,7 +130,7 @@ def plotPanel(fig, gs0, t, nu, jetType, Y, Z, thVLegend=False):
 thV = 0.0
 E0 = 1.0e53
 thC = 0.08
-thW = 3*thC
+thW = 5*thC
 b = 2
 L0 = 0
 ts = 0

### 2019-09-10 structuredJets.tex
Some additions

@@
 \begin{abstract}
-	Gamma-ray bursts (GRBs) associated with gravitational wave events are, and will likely continue to be, viewed at a larger inclination than their fellow GRBs without gravitational wave detections.
+	Gamma-ray bursts (GRBs) associated with gravitational wave events are, and will likely continue to be, viewed at a larger inclination than GRBs without gravitational wave detections.
 As demonstrated by the afterglow of \gwbns{}, this requires an extension of the common GRB afterglow models which typically assume emission from an on-axis top hat jet.
-We present a characterization of the afterglows arising from structured jets, jets with a non-trivial angular energy profile, utilizing both trans-relativistic numerical calculations and simple analytic approximations.
+We present a characterization of the afterglows arising from structured jets, providing a framework covering both successful and choked jets.
 We compute new closure relations for structured jets and compare with the established relations for energy injection and refreshed shock models.
-In many cases the temporal slope before the jet break is found to be a simple function of the ratio between the viewing angle and effective half opening angle of the jet.
-This provides a useful handle in the analysis of structured GRB afterglow light curves, but does not completely resolve the degeneracy between viewing angle and jet structure model.
-Our models, both numerical and analytic, are publicly available as the open source \python{} package \afterglowpy{}.
-
-% Present new closure relations for structured jets, compare with established relations for choked jet models...
-
-% Add sentence explaining "jet structure" ==> "angular jet structure", we calculate closure relations and explicitly relate them to energy injection/refreshed shock/velocity stratification models.
+The temporal slope before the jet break is found to be a simple function of the ratio between the viewing angle and effective opening angle of the jet.
+A numerical model to calculate synthetic light curves and spectra is publicly available as the open source \python{} package \afterglowpy{}.
 
@@
 
-The binary neutron star merger event \gwbns{} provided, quite literally, a new view on gamma-ray burst (GRB) afterglows (CITE LIGO, Discovery papers).
-Unlike typical short GRB afterglows, which begin bright and decay from detection with a ~week timescale, \gwbns{}'s non-thermal afterglow was undetectable until the first observation of x-rays nine days after the GRB \citep{Troja:2017aa}.
-At this point it began steadily increasing in brightness in all bands for ~160 days \citep{Troja:2018aa, Troja:2019ab} (CITE OTHERS).
-Very long baseline (VLBI) radio imagery over this period identified a radio core with an apparent superluminal motion, indicating the emitting surface was moving at relativistically at an oblique angle towards the Earth (CITE Mooley, Ghirlanda).
-The emission peaked at 160 days and proceeded to sharply decay at a rate commensurate with other short GRB afterglows (CITE YITL, peak-decay papers).
+The binary neutron star merger event \gwbns{}, followed quickly by the short gamma-ray burst \grbbns{}, provided a new view on gamma-ray burst (GRB) afterglows (CITE LIGO, Discovery papers).
+Unlike typical afterglows, which begin bright and decay from detection with a ~week timescale, \grbbns{}'s non-thermal emission was undetectable until the first observation of X-rays nine days after the GRB \citep{Troja:2017aa}.
+At this point the afterglow began steadily increasing in brightness in at all wavelengths for ~160 days \citep{Troja:2018aa, Troja:2019ab} (CITE OTHERS).
+Very long baseline (VLBI) radio imagery over this period identified a radio core with an apparent superluminal motion, indicating the emitting surface was moving at relativistically at an oblique angle towards the Earth (CITE Mooley).
+The emission peaked at 160 days and proceeded to sharply decay at a rate $t^{-2.2}$ commensurate with other short GRB afterglows (CITE YITL, peak-decay papers).
 
@@
 Being sources at cosmological distances, GRBs must typically be observed nearly on-axis or at least within the original opening angle of the jet \citep{Ryan:2015aa}.
-At these small viewing angles lateral structure plays a sub-dominant role and the ubiquitous top hat jet has been a sufficiently spherical cow for the majority of studies.
-Since the gravitational wave signal of a binary neutron star merger is nearly isotropic, it is expected the majority of future GW-GRBs will be viewed at significant inclination and may have similarly peculiar light curves as \gwbns{}.
-
-A solid theoretical understanding of structured jet afterglows, including viewing angle effects, will be required to make the most use of future GW-GRB observations, the \gwbns{} dataset, and re-analysis of archival short GRBs.
-Standard tools for GRB analysis include closure relations, equations relating the temporal and spectral power law slopes of GRB afterglow light curves, jet breaks, achromatic breaks in the light curve related to the opening angle fo the jet, and full light curve modeling.
+At these small viewing angles lateral structure plays a sub-dominant role and the ubiquitous top hat jet has been a sufficient model for most studies.
+Since the gravitational wave signal of a binary neutron star merger is nearly isotropic, it is expected the majority of future GW-GRBs will be viewed at significant inclination and may have similarly peculiar light curves as \grbbns{}.
+
+A solid theoretical understanding of structured jet afterglows, including viewing angle effects, will be required to make the most use of future GW-GRB observations, the \grbbns{} dataset, and re-analysis of archival short GRBs (CITE US).
+Standard tools for GRB analysis include closure relations (CITE), equations relating the temporal and spectral power law slopes of GRB afterglow light curves, jet breaks, achromatic breaks in the light curve related to the opening angle fo the jet, and full light curve modeling.
 To this end, we have calculated generalized closure relations for GRB afterglows including explicit viewing angle and jet structure dependence, putting these effects into a similar context as standard energy injection models \citep{Zhang:2006aa}.
@@
 \citet{Meszaros:1998aa} first considered anisotropic models and noted they may present as ``orphan afterglows'' without a prompt GRB signal if viewed sufficiently off-axis.
-Detailed theoretical calculations of structured jet afterglow light curves concluded several facts: on-axis structured light curves resemble those from top hat jets, off-axis structured light curves show a temporal break at an observer time $t_b$ that scales with the viewing angle $\thobs$ as $t_b\propto \thobs^{8/3}$, and the pre-break slope can depend on the viewing angle and particular structure model \citep{Rossi:2002aa, Dalal:2002aa, Granot:2002aa, Panaitescu:2003aa, Kumar:2003aa, Granot:2003aa, Salmonson:2003aa, Rossi:2004aa}.
+Detailed theoretical calculations of structured jet afterglow light curves concluded several facts: on-axis structured light curves resemble those from top hat jets, off-axis structured light curves show an achromatic break at time $t_b\propto \thobs^{8/3}$ (where $\thobs$ is the viewing angle), and the pre-break slope can depend on the viewing angle and particular structure model \citep{Rossi:2002aa, Dalal:2002aa, Granot:2002aa, Panaitescu:2003aa, Kumar:2003aa, Granot:2003aa, Salmonson:2003aa, Rossi:2004aa}.
 The ``Universal Structured Jet'' was a structured jet with isotropic-equivalent energy $E \propto \theta^{-2}$ proposed to explain the diversity of jet-break times as a viewing angle effect  \citep{Lipunov:2001aa, Zhang:2002aa}, although this was ultimately unsuccessful \citep{Nakar:2004aa}.
@@
 The jet break in the structured jet afterglow light curve can exhibit a larger jump between pre- and post-break slopes than in top hat models, and has been invoked to explain some observed jet breaks which do not easily fit the standard closure relations \citep{Panaitescu:2005aa, Panaitescu:2005ab}, although other dynamical and spectral processes can have similar effects \citep{Piro:2005aa, Corsi:2006aa}.
-GRB prompt emission viewed significantly off-axis was (is?) the proposed origin for X-ray flashes \citep{Ioka:2001aa, Yamazaki:2002aa, Yamazaki:2003aa, Peng:2005aa}.
-More recently, small non-zero viewing angles have been measured in a subset of the \swiftXRT{} afterglow sample \citep{Ryan:2015aa}.
+GRB prompt emission viewed significantly off-axis is one of the possible origins for X-ray flashes \citep{Ioka:2001aa, Yamazaki:2002aa, Yamazaki:2003aa, Peng:2005aa}.
+More recently, small non-zero viewing angles have been measured in a subset of the \swiftXRT{} afterglow sample \citep{Ryan:2015aa} (CITE Bin-Bin and Troja E., et al., 2016, ApJ, 827, 102).
+
+% TODO:  Explain what was missing from past studies (that we now include)
 
@@
 
-% Explicitly say we were the first to find x-ray, predict steep post-break slope.
+% Explicitly say we were the first to find X-ray, predict steep post-break slope.
 
@@
 
-Each fiducial model is parameterized by a normalization $E_0$, a width $\thC$, and a truncation angle $\thW$.
+Each fiducial model is parameterized by a normalization $E_0$, a width $\thC$, and a truncation angle $\thW$ outside of which the energy is initially zero.
 The power law model also retains a power law index $b$.
-Outside $\thW$ the energy is initially zero, this acts as an outer truncation angle for the jet.
 Our power law profile includes a factor of $b^{-1}$ in the base which does not usually appear in the literature \citep{Granot:2003aa, Hotokezaka:2018aa}.
@@
 To compute the light curves of structured jet afterglows we constructed numerical and analytic models utilizing the single shell approximation of \cite{van-Eerten:2010aa, van-Eerten:2018ab}.
-Iterations of this model have been applied in the \gwbns{} x-ray discovery paper \citep{Troja:2017aa}, follow-up studies of \gwbns{} \citep{Troja:2018aa, Piro:2019aa, Troja:2019ab}, and in examinations of archival kilonova candidates \citep{Troja:2018ab, Troja:2019aa}.
+Iterations of this model have been applied in the \gwbns{} X-ray discovery paper \citep{Troja:2017aa}, follow-up studies of \gwbns{} \citep{Troja:2018aa, Piro:2019aa, Troja:2019ab}, and in examinations of archival kilonova candidates \citep{Troja:2018ab, Troja:2019aa}.
 This approach integrates over the massive ejecta, contact discontinuity, and forward shock complex, treating it as a single fluid element with uniform radial structure.
@@
 In fact, while $u \gg 1$ our prescription is equivalent to the DL18 model with parameters $P_k = Q_k = 3\sqrt{2}$, a slight modification to their numerically fit values $P_k = 4.0$ and $Q_k = 2.5$.
-Afterglow light curves computed using Equation \eqref{eq:thetadot} were found to agree better with established simulation based models (see Section \ref{subsec:bioxfitcomp}) than those computed with the DL18 parameters.
+Afterglow light curves computed using Equation \eqref{eq:thetadot} were found to agree better with established simulation based models (see Section \ref{subsec:boxfitcomp}) than those computed with the DL18 parameters.
 This jet spreading prescription differs from that used in \citet{Troja:2018aa, Piro:2019aa, Troja:2019ab} which used a simple $u < 1$ criterion to begin jet spreading and set $\beta_\bot = c_s / (c \gamma)$.
@@
 We have constructed the \afterglowpy{} Python package to implement the numerical computation of light curves according to Section \ref{subsec:algo} and provide it to the community.
-The integration routine itself is written in C, wrapped as an extension for Python, and has been optimized to be used in intensive data analysis routines such as Markov Chain Monte-carlo which can require many thousands or millions of evaluations.
+The integration routine itself is written in C, wrapped as an extension for Python, and has been optimized to be used in intensive data analysis routines such as Markov Chain Monte Carlo which can require many thousands or millions of evaluations.
 
@@
 Bottom Panel: Fractional difference between \afterglowpy{} and \boxfit{} light curves.
-Four representative light curves are shown: radio on-axis ($\thobs=0$, $\nu=10^9$Hz, blue), radio off-axis ($\thobs=0.16$rad, $\nu=10^9$Hz, orange), x-ray on-axis ($\thobs=0$, $\nu=10^{18}$Hz, green), and x-ray off-axis ($\thobs=0.16$rad, $\nu=10^{18}$Hz, red).
+Four representative light curves are shown: radio on-axis ($\thobs=0$, $\nu=10^9$Hz, blue), radio off-axis ($\thobs=0.16$rad, $\nu=10^9$Hz, orange), X-ray on-axis ($\thobs=0$, $\nu=10^{18}$Hz, green), and X-ray off-axis ($\thobs=0.16$rad, $\nu=10^{18}$Hz, red).
 Remaining parameters are shared: $\thC=0.1$rad, $\Eiso=10^{52}$erg, $n_0 = 10^{-3}$cm$^{-3}$, $p=2.2$, $\epse=10^{-1}$, $\epsB=10^{-2}$, $\dL=3.09 \times 10^{26}$cm, $z=0.028$.
 \label{fig:boxfitComp}}
+%TODO: put distance in Mpc
 \end{figure*}
@@
 Figure \ref{fig:boxfitComp} shows a comparison between top-hat light curves calculated with \afterglowpy{} and \boxfit{}.
-Figure \ref{fig:boxfitComp} shows the light curve of a $\thC=0.1$ rad top-hat jet at radio and x-ray frequencies ($10^9$Hz and $10^{18}$Hz, respectively) with aligned ($\thobs = 0$) and misaligned ($\thobs=0.16$rad) viewing angles.
+Figure \ref{fig:boxfitComp} shows the light curve of a $\thC=0.1$ rad top-hat jet at radio and X-ray frequencies ($10^9$ Hz and $10^{18}$ Hz, respectively) with aligned ($\thobs = 0$) and misaligned ($\thobs=0.16$ rad) viewing angles.
 The light curves begin in the ultra relativistic Blandford-Mckee phase and continue to the Newtonian Sedov phase.
@@
 After the jet break the \afterglowpy{} light curves show a marked excess relative to \boxfit{}, the relative error increasing to approximately 1.0 and 2.0 for the aligned and misaligned radio light curves, respectively.
-The x-ray light curves achieve approximately half the error of the radio.
+The X-ray light curves achieve approximately half the error of the radio.
 After a short period the \afterglowpy{} light curves begin to decrease, recovering the \boxfit{} slope, and asymptote to similar light curves in the Newtonian regime with a small constant offset from \boxfit{}.
 
-As expected, \afterglowpy{} models the early and late afterglow well, but struggles in an intermediate phase during jet spreading.
+As expected, \afterglowpy{} models the early and late afterglow well, but is somewhat less accurate in an intermediate phase during jet spreading.
 In particular it appears that \afterglowpy{} begins its spreading late relative to \boxfit{}.
@@
 We summarize each phase below in roughly temporal order.
-Table \ref{tab:slopes} gives the \emph{closure relations}, the temporal and spectral power law slopes of the observed flux, for each of the afterglow phases in the synchrotron spectral regimes D-H.
-
-\begin{deluxetable*}{CCCCCCCC}
+Table \ref{tab:slopes} gives the \emph{closure relations}, the temporal and spectral power law slopes of the observed flux, for each of the afterglow phases in the synchrotron spectral regimes D-H (as defined in \citet{Granot:2002aa}).
+
+\begin{deluxetable*}{CCCCCCCCC}
 	\tablecaption{Structured jet closure relations: $F_\nu \propto \tobs^{\alpha} \nuobs^{\beta}$.
-The ``far-off-axis'' phase occurs at early times and only if there is no material directly in the observer's line of sight ($\thobs > \thW$).
-The ``generic'' slope applies whenever the jet is relativistic, non-spreading, and the observer is within the beaming cone of some part of the jet ($|\thobs - \theta_*| < \gamma^{-1}(\theta_*)$).
+The ``far-off-axis'' phase ($\alpha_{\mathrm{far-off-axis}}$)occurs at early times and only if there is no material directly in the observer's line of sight ($\thobs > \thW$).
+The ``generic'' slope ($\alpha_{\mathrm{generic}}$) applies whenever the jet is relativistic, non-spreading, and the observer is within the beaming cone of some part of the jet ($|\thobs - \theta_*| < \gamma^{-1}(\theta_*)$).
 The $g$ parameter is positive and depends on the viewing angle $\thobs$ and the specific structure profile $E(\theta)$.
@@
 The $\som$ parameter encodes how the effective angular size of the jet is changing with Lorentz factor: $\Delta \Omega \propto \gamma^{-\som}$.
-The ``structured'' phase is seen by misaligned viewers ($\thobs > \thC$), occurs before the jet break, and corresponds to $\som \approx 1$.
-The ``pre-jet break'' phase is seen by aligned viewers ($\thobs < \thC$).
-The ``post-jet break'' slope given here does not include the effects of jet spreading and as such is an over-estimate of the true post-jet break slope.
+The ``structured'' phase ($\alpha_{\mathrm{struct}}$) is seen by misaligned viewers ($\thobs > \thC$), occurs before the jet break, and corresponds to $\som \approx 1$.
+The ``pre-jet break'' phase ($\alpha_{\mathrm{pre}}$)  is seen by aligned viewers ($\thobs < \thC$).
+The first ``post-jet break'' slope ($\alpha_{\mathrm{post, 1}}$) given here does not include the effects of jet spreading and as such is an over-estimate of the true post-jet break slope.
+The second ``post-jet break'' slope ($\alpha_{\mathrm{post, 2}}$) was calculated in \citet{Sari:1999aa}, corresponds to a jet undergoing exponential spreading, and is likely an underestimate of the true post-jet break slope.
 \label{tab:slopes}}
-	\tablehead{\colhead{Regime}& \colhead{Label} & \colhead{$\alpha_{\mathrm{far-off-axis}}$} & \colhead{$\alpha_{\mathrm{generic}}$} & \colhead{$\alpha_{\mathrm{struct}}$}& \colhead{$\alpha_{\mathrm{pre}}$}& \colhead{$\alpha_{\mathrm{post, no-spreading}}$} & \colhead{$\beta$}}
+	\tablehead{\colhead{Regime}& \colhead{Label} & \colhead{$\alpha_{\mathrm{far-off-axis}}$} & \colhead{$\alpha_{\mathrm{generic}}$} & \colhead{$\alpha_{\mathrm{struct}}$}& \colhead{$\alpha_{\mathrm{pre}}$}& \colhead{$\alpha_{\mathrm{post, 1}}$} & \colhead{$\alpha_{\mathrm{post, 2}}$} & \colhead{$\beta$}}
 	\startdata
-	& & & & (\som = 1) & (\som=2, g=0) & (\som=0, g=0) & \\[0.3cm]
-	\nu<\nu_m<\nu_c     & D	& 7 		& \dfrac{-2 + 3\som + 3g}{8+g} 		& \dfrac{1 + 3g}{8+g} 	&1/2		& -1/4	& 1/3 \\[0.3cm]
-	\nu < \nu_c < \nu_m & E	& 17/3 	& \dfrac{-14/3 + 3\som + 11g/3}{8+g}  & \dfrac{-5/3 + 11g/3}{8+g} &1/6 	& -7/12	& 1/3 \\[0.3cm]
-	\nu_c < \nu < \nu_m & F	& 13/2 	& \dfrac{-8 + 3\som + 2g}{8+g} 		& \dfrac{-5 + 2g}{8+g} 	& -1/4 	& -1		& -1/2 \\[0.3cm]
-	\nu_m<\nu<\nu_c     & G 	&15/2 - 3p/2 & \dfrac{-6p + 3\som + 3g}{8+g} 	& \dfrac{3 - 6p +3g}{8+g} 	& -3(p-1)/4 & -3p/4	& (1-p)/2 \\[0.3cm]
-	\nu_m, \nu_c < \nu & H 	& 8 - 3p/2 	& \dfrac{-6p - 2 + 3\som + 2g}{8+g} 	& \dfrac{1-6p  +2g}{8+g} 	& -(3p-2)/4 & -(3p+1)/4 & -p/2 \\[0.3cm]
+	& & & & \som = 1 & \som=2 & \som=0 &\\
+	& & & &  & g=0 & g=0 & \\[0.4cm]
+	\nu<\nu_m<\nu_c     & D	& 7 		& \dfrac{-2 + 3\som + 3g}{8+g} 		& \dfrac{1 + 3g}{8+g} 	&1/2		& -1/4	& -1/3 & 1/3 \\[0.4cm]
+	\nu < \nu_c < \nu_m & E	& 17/3 	& \dfrac{-14/3 + 3\som + 11g/3}{8+g}  & \dfrac{-5/3 + 11g/3}{8+g} &1/6 	& -7/12	& -1    & 1/3 \\[0.4cm]
+	\nu_c < \nu < \nu_m & F	& 13/2 	& \dfrac{-8 + 3\som + 2g}{8+g} 		& \dfrac{-5 + 2g}{8+g} 	& -1/4 	& -1		& -1	  & -1/2 \\[0.4cm]
+	\nu_m<\nu<\nu_c     & G 	&\dfrac{15 - 3p}{2} & \dfrac{-6p + 3\som + 3g}{8+g} 	& \dfrac{3 - 6p +3g}{8+g} 	& -\dfrac{3(p-1)}{4} & -\dfrac{3p}{4}	& -p	  & \dfrac{1-p}{2} \\[0.4cm]
+	\nu_m, \nu_c < \nu & H 	& \dfrac{16 - 3p}{2} 	& \dfrac{-6p - 2 + 3\som + 2g}{8+g} 	& \dfrac{1-6p  +2g}{8+g} 	& -\dfrac{3p-2}{4} & -\dfrac{3p+1}{4} & -p & -\dfrac{p}{2} \\[0.4cm]
 	\enddata
 \end{deluxetable*}
+
+\begin{figure*}
+	\includegraphics[width=\textwidth]{figs/lc_phase_sketch.pdf}
+	\caption{Illustration of possible light curves from a structured jet as a function of viewing angle.
+Remaining parameters are shared: $\thC=0.05$rad, $\thW=0.3$rad, $\Eiso=10^{53}$erg, $n_0 = 10^{-3}$cm$^{-3}$, $p=2.2$, $\epse=10^{-1}$, $\epsB=10^{-3}$, $\dL=10^{28}$cm, $z=0.5454$.
+\label{fig:phaseSketch}}
+\end{figure*}
 
@@
 \citet{Granot:2002aa}.
+%TODO Explain when this is valid.
 
@@
 Table \ref{tab:slopes} gives an over-estimate of the post-jet break slope, including the $\som=0$ effect but neglecting jet spreading.
+
+%TODO add a figure about this.
 
@@
 The upper left panel shows top-hat, Gaussian, $b=2$ power law, and $b=6$ power law jets viewed exactly on-axis at $\thobs=0$.
-Each model shares $\thC=0.08$ rad, $\thW=0.24$rad, $E_0=10^53$ erg, $n_0 = 1$cm$^{-3}$, $p=2.2$, $\epse=10^{-1}$, $\epsB = 10^{-2}$, $d_L=10^{28}$cm and $z=0.5454$.
+Each model shares $\thC=0.08$ rad, $\thW=0.24$rad, $E_0=10^{53}$ erg, $n_0 = 1$cm$^{-3}$, $p=2.2$, $\epse=10^{-1}$, $\epsB = 10^{-2}$, $d_L=10^{28}$cm and $z=0.5454$.
 All of the models were computed with zero initial mass loading, so they do not show coasting phases.
@@
 
-Figure \ref{fig:cornerGaussian} (inset) shows the observations in radio, optical, and x-ray bands of the \gwbns{} afterglow.
-No afterglow emission was detected until an x-ray detection by the Chandra observatory nine days after the GW trigger \cite{Troja:2017aa}.
-Further radio, optical, and x-ray observations showed a steady rising light curve with constant power law slope until a peak near day 160.
+Figure \ref{fig:cornerGaussian} (inset) shows the observations in radio, optical, and X-ray bands of the \gwbns{} afterglow.
+No afterglow emission was detected until an X-ray detection by the Chandra observatory nine days after the GW trigger \cite{Troja:2017aa}.
+Further radio, optical, and X-ray observations showed a steady rising light curve with constant power law slope until a peak near day 160.
 At this point the light curve turned over and began a steep decay that continues to the present \citep{Troja:2019ab}.
@@
 Table \ref{tab:MCMC} additionally gives constraints on the total jet energy \Etot{} and the ratio $\thobs/\thC$.
-The parameters $E_0$, $n_0$, $\epse$, and $\epsB$ are only constrained to within an order of magnitude, due partially to the observed radio, optical, and x-ray data all lying on the same synchrotron power-law segment.
+The parameters $E_0$, $n_0$, $\epse$, and $\epsB$ are only constrained to within an order of magnitude, due partially to the observed radio, optical, and X-ray data all lying on the same synchrotron power-law segment.
 These parameters are shared between jet models, and are broadly consistent between the two fits with the possible exception of $n_0$.

### 2019-09-10 code/paperPlots.py

@@ -6,7 +6,7 @@ import matplotlib.pyplot as plt
 import matplotlib.patches as patches
 import matplotlib.collections as collections
 import h5py as h5
-import grbpy as grb
+import afterglowpy as grb
 
 sec2year = grb.sec2day / 365.25
 year2sec = grb.day2sec * 365.25

### 2019-09-10 code/plotClosure.py

@@ -1,7 +1,7 @@
 import math
 import numpy as np
 import matplotlib.pyplot as plt
-import grbpy as grb
+import afterglowpy as grb
 
 decompPlot = False
 

### 2019-09-10 code/plotClosureThv.py

@@ -1,0 +1,106 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import afterglowpy as grb
+import paperPlots as pp
+
+"""
+def plotOnAxes(ax, jetType, Y, regime, thVs=None, thCs=None, thWs=None,
+               name=None):
+
+    if thVs is None and thCs is None and thWs is None:
+        return
+
+    N = 0
+    if thVs is not None:
+        N = max(N, len(thVs))
+    if thCs is not None:
+        N = max(N, len(thCs))
+    if thWs is not None:
+        N = max(N, len(thWs))
+
+    for i in range(N):
+        if thVs is not None:
+            Y[0] = thVs[i]
+        if thCs is not None:
+            Y[2] = thCs[i]
+"""
+
+thV = 0.0
+E0 = 1.0e53
+thC = 0.05
+thW = 4*thC
+b = 10
+L0 = 0
+ts = 0
+q = 0
+n0 = 1.0e-3
+p = 2.2
+epse = 0.1
+epsB = 0.001
+xiN = 1.0
+dL = 1.0e28
+z = 0.5454
+
+Y = np.array([thV, E0, thC, thW, b, L0, ts, q, n0, p, epse, epsB, xiN, dL])
+Z = {'z': z, 'spread': True}
+
+
+t = np.geomspace(1.0e3, 1.0e8, 100)
+nu = np.empty(t.shape)
+nu[:] = 1.0e14
+
+figG, axG = plt.subplots(1, 1)
+figPL, axPL = plt.subplots(1, 1)
+
+colors = ['C0', 'C1', 'C2', 'C3', 'C4', 'C5']
+thVs = [thC, 2*thC, 4*thC, 6*thC, 8*thC]
+thV = 0.3
+thCs = [thV/8, thV/6, thV/4, thV/2, thV]
+
+# for i, thV in enumerate(thVs):
+for i, thC in enumerate(thCs):
+ 
+    Y[0] = thV
+    Y[2] = thC
+
+    alG = pp.calcSlopeStructEff(0, Y, 'G')
+    alPL = pp.calcSlopeStructEff(4, Y, 'G')
+
+    tb = 0.2 * np.power(9*E0/(16*np.pi*n0*grb.mp*grb.c**5), 1.0/3.0)\
+        * np.power(2*np.sin(0.5*(thC+thV)), 8.0/3.0)
+
[…]

### 2019-09-10 code/plotPhaseSketch.py

@@ -1,0 +1,314 @@
+import math
+import numpy as np
+import afterglowpy as grb
+import matplotlib.pyplot as plt
+import paperPlots as pp
+
+
+thV = 0.0
+E0 = 1.0e53
+thC = 0.05
+thW = 6*thC
+b = 6
+L0 = 0
+ts = 0
+q = 0
+n0 = 1.0e-3
+p = 2.2
+epse = 0.1
+epsB = 0.001
+xiN = 1.0
+dL = 1.0e28
+z = 0.5454
+g0 = 1000
+
+underPanel = False
+addG0 = False
+
+highlightPhases = False
+highlightTransitions = True
+
+phaseLabels = True
+
+Y0 = np.array([thV, E0, thC, thW, b, L0, ts, q, n0, p, epse, epsB, xiN, dL])
+Z = {'z': z, 'spread': False}
+Zg = Z.copy()
+Zg['g0'] = g0
+
+width = 7.5
+height = 3.5
+
+fig = plt.figure(figsize=(width, height))
+gs = fig.add_gridspec(1, 3, wspace=0.0)
+ax1 = fig.add_subplot(gs[0])
+ax2 = fig.add_subplot(gs[1])
+ax3 = fig.add_subplot(gs[2])
+
+axs = [ax1, ax2, ax3]
+
+t = np.geomspace(1.0e3, 3.0e8, 300)
+nu = np.empty(t.shape)
+nu[:] = 2.41798926e17  # 1 keV
+
+jetType = 4
+Y1 = Y0.copy()
+Y2 = Y0.copy()
+Y3 = Y0.copy()
+
+Y1[0] = 0.0
+Y2[0] = thW - 2*thC
+Y3[0] = thW + 2*thC
+
+tmin1 = t.min()
+tmax1 = t.max()
+tmin2 = 1.0e4
+tmax2 = t.max()
+tmin3 = 1.0e4
+tmax3 = t.max()
+
+Fmax = 3e-3
+Fmin = 3e-13
+
+Fnu1 = grb.fluxDensity(t, nu, jetType, 0, *Y1, **Z)
+Fnu2 = grb.fluxDensity(t, nu, jetType, 0, *Y2, **Z)
+Fnu3 = grb.fluxDensity(t, nu, jetType, 0, *Y3, **Z)
+Fnu1g = grb.fluxDensity(t, nu, jetType, 0, *Y1, **Zg)
[…]

### 2019-09-11 structuredJets.tex
Updates.

@@
 \newcommand{\gwbns}{GW170817A}
-\newcommand{\grbbns}{GRB170817A}
+\newcommand{\grbbns}{GRB 170817A}
 \newcommand{\afterglowpy}{{\tt afterglowpy}}
@@
 At this point the afterglow began steadily increasing in brightness in at all wavelengths for ~160 days \citep{Troja:2018aa, Troja:2019ab} (CITE OTHERS).
-Very long baseline (VLBI) radio imagery over this period identified a radio core with an apparent superluminal motion, indicating the emitting surface was moving at relativistically at an oblique angle towards the Earth (CITE Mooley).
-The emission peaked at 160 days and proceeded to sharply decay at a rate $t^{-2.2}$ commensurate with other short GRB afterglows (CITE YITL, peak-decay papers).
+Very long baseline (VLBI) radio imagery over this period identified a radio core with an apparent superluminal motion, indicating the emitting surface was moving at relativistically at an oblique angle towards the Earth \citep{Mooley:2018ab}.
+The emission peaked at 160 days and proceeded to sharply decay at a rate $t^{-2.2}$ commensurate with other GRB afterglows \citep{Alexander:2018aa, Fong:2019aa, Lamb:2019aa, Troja:2019ab}.
 
@@
 
-A solid theoretical understanding of structured jet afterglows, including viewing angle effects, will be required to make the most use of future GW-GRB observations, the \grbbns{} dataset, and re-analysis of archival short GRBs (CITE US).
-Standard tools for GRB analysis include closure relations (CITE), equations relating the temporal and spectral power law slopes of GRB afterglow light curves, jet breaks, achromatic breaks in the light curve related to the opening angle fo the jet, and full light curve modeling.
-To this end, we have calculated generalized closure relations for GRB afterglows including explicit viewing angle and jet structure dependence, putting these effects into a similar context as standard energy injection models \citep{Zhang:2006aa}.
+A solid theoretical understanding of structured jet afterglows, including viewing angle effects, will be required to make the most use of future GW-GRB observations, the \grbbns{} dataset, and re-analysis of archival short GRBs \citep{Troja:2018ab, Troja:2019aa}.
+Standard tools for GRB analysis include closure relations, equations relating the temporal and spectral power law slopes of GRB afterglow light curves (e.g.
+\citet{Granot:2002aa, Racusin:2009aa}), jet breaks, achromatic breaks in the light curve related to the opening angle of the jet, and full light curve modeling.
+To this end, we have calculated generalized closure relations for GRB afterglows including explicit viewing angle and jet structure dependence, putting these effects into a similar framework as standard energy injection models \citep{Zhang:2006aa}.
  We have also developed the computational tool \afterglowpy{}: a public, open source \python{} package for on-the-fly computation of structured jet afterglows with arbitrary viewing angle.
-
-% We generalize closure relations... mention energy injection
 
@@
 The jet break in the structured jet afterglow light curve can exhibit a larger jump between pre- and post-break slopes than in top hat models, and has been invoked to explain some observed jet breaks which do not easily fit the standard closure relations \citep{Panaitescu:2005aa, Panaitescu:2005ab}, although other dynamical and spectral processes can have similar effects \citep{Piro:2005aa, Corsi:2006aa}.
-GRB prompt emission viewed significantly off-axis is one of the possible origins for X-ray flashes \citep{Ioka:2001aa, Yamazaki:2002aa, Yamazaki:2003aa, Peng:2005aa}.
-More recently, small non-zero viewing angles have been measured in a subset of the \swiftXRT{} afterglow sample \citep{Ryan:2015aa} (CITE Bin-Bin and Troja E., et al., 2016, ApJ, 827, 102).
-
-% TODO:  Explain what was missing from past studies (that we now include)
-
-In this paper, we provide a characterization of the afterglows of structured jets, explicit closure relations, and a description of our numerical tool \afterglowpy{}.
-In Section \ref{sec:motivation} we review the general properties of structured jets and their necessity to GRB afterglows.
+GRB prompt emission viewed significantly off-axis is one of the possible origins for X-ray flashes \citep{Ioka:2001aa, Yamazaki:2002aa, Yamazaki:2003aa, Peng:2005aa, DAlessio:2006aa}.
+More recently, small non-zero viewing angles have been measured in a subset of the \swiftXRT{} afterglow sample \citep{Ryan:2015aa, Zhang:2015aa, Troja:2016aa}.
+These studies focused on observers positioned within the core opening angle of the jet or relied on closed numerical codes to calculate light curves for misaligned viewers.
+
+In this paper, we provide a characterization of the afterglows of structured jets at all viewing angles, explicit closure relations, and a description of our  public numerical tool \afterglowpy{}.
+In Section \ref{sec:motivation} we review the general properties of structured jets and their necessity for GRB afterglow modelling.
 In Section \ref{sec:numerical} we develop our theoretical framework and describe its numerical implementation in \afterglowpy{}.
@@
 
-% Add description of each paper, explaining method of collimation/structure generation.
-
-% Gaussian is  b--> infty
-
 Figure \ref{fig:jetStruct} also includes an example of each model together with the jet energy profiles drawn from the literature.
@@
 We utilize the ``TM'' trans-relativistic equation of state to describe the fluid consistently throughout its evolution \citep{Mignone:2005aa}.
-The forward shock is at radius $R$ from the explosion, and the fluid behind the shock has four-velocity $u$ and Lorentz factor $\gamma$.
+The forward shock is at radius $R$ from the explosion, and the fluid behind the shock has dimensionless four-velocity $u$ and Lorentz factor $\gamma$.
 The shock jump conditions can be used to determine the shock speed:
@@
 
-Pressure gradients along the blast wave surface can drive lateral spreading of the jet, causing $\theta_j(t)$ (and $f_\Omega$) to increase with time  from its initial value $\theta_j(0) = \theta_0$ (CITE Rhoads?).
+Pressure gradients along the blast wave surface can drive lateral spreading of the jet, causing $\theta_j(t)$ (and $f_\Omega$) to increase with time  from its initial value $\theta_j(0) = \theta_0$ \citep{Rhoads:1999aa}.
 Initially spreading is negligible as each fluid element of the highly relativistic jet is only in causal contact with nearby regions of similar pressure.
@@
 To remain consistent with the presence of angular structure in the jet and ensure spreading occurs at sonic speeds in our adopted equation of state it is necessary to construct our own jet spreading prescription.
+
+The expression for the jet energy, Equation \eqref{eq:E}, implicitly assumes the ``conical'' spreading model, where at a time $t$ all material $r < R(t)$ and $\theta < \theta_j(t)$ is incorporated in the jet.
+Comparisons to numerical simulation have found this to be more accurate than the ``trumpet'' model which only incorporates material that was within the jet cone at each radius (DL18).
 
@@
 
-\afterglowpy{} uses the standard fourth order Runge-Kutta algorithm to numerically solve the $(R(t), u(t), \theta_j(t))$ system of ordinary differential equations (Equations \eqref{eq:ODE1}-\eqref{eq:ODE3}) on a fixed logarithmically spaced grid of $t$ \citep{Press:2007aa}.
+\afterglowpy{} uses the standard fourth-order Runge-Kutta algorithm to numerically solve the $(R(t), u(t), \theta_j(t))$ system of ordinary differential equations (Equations \eqref{eq:ODE1}-\eqref{eq:ODE3}) on a fixed logarithmically spaced grid of $t$ \citep{Press:2007aa}.
 The endpoints of the $t$-grid are chosen to bracket the burster frame times required to calculate the requested $\tobs$.
@@
 Table \ref{tab:slopes} gives the \emph{closure relations}, the temporal and spectral power law slopes of the observed flux, for each of the afterglow phases in the synchrotron spectral regimes D-H (as defined in \citet{Granot:2002aa}).
+Figure \ref{fig:phaseSketch} sketches the three possible ways these phases may be combined in a full afterglow, depending on the viewing angle.
 
@@
 The ``pre-jet break'' phase ($\alpha_{\mathrm{pre}}$)  is seen by aligned viewers ($\thobs < \thC$).
-The first ``post-jet break'' slope ($\alpha_{\mathrm{post, 1}}$) given here does not include the effects of jet spreading and as such is an over-estimate of the true post-jet break slope.
-The second ``post-jet break'' slope ($\alpha_{\mathrm{post, 2}}$) was calculated in \citet{Sari:1999aa}, corresponds to a jet undergoing exponential spreading, and is likely an underestimate of the true post-jet break slope.
+The first ``post-jet break'' slope ($\alpha_{\mathrm{post, 1}}$) given here does not include the effects of jet spreading and as such is shallower than the true post-jet break slope.
+The second ``post-jet break'' slope ($\alpha_{\mathrm{post, 2}}$) was calculated in \citet{Sari:1999aa}, corresponds to a jet undergoing exponential spreading, and is steeper than the true post-jet break slope.
 \label{tab:slopes}}
@@
 	& & & & \som = 1 & \som=2 & \som=0 &\\
-	& & & &  & g=0 & g=0 & \\[0.4cm]
+	& & & &  & g=0 & g=0 & \\[0cm]
 	\nu<\nu_m<\nu_c     & D	& 7 		& \dfrac{-2 + 3\som + 3g}{8+g} 		& \dfrac{1 + 3g}{8+g} 	&1/2		& -1/4	& -1/3 & 1/3 \\[0.4cm]
@@
 	\includegraphics[width=\textwidth]{figs/lc_phase_sketch.pdf}
-	\caption{Illustration of possible light curves from a structured jet as a function of viewing angle.
-Remaining parameters are shared: $\thC=0.05$rad, $\thW=0.3$rad, $\Eiso=10^{53}$erg, $n_0 = 10^{-3}$cm$^{-3}$, $p=2.2$, $\epse=10^{-1}$, $\epsB=10^{-3}$, $\dL=10^{28}$cm, $z=0.5454$.
+	\caption{Illustration of possible synchrotron light curves from the forward shock of a structured jet.
+The specific order of light curve phases depends on where the viewer sits, $\thobs$, relative to the jet half opening angle $\thC$ and the outer truncation angle $\thW$.
+A \emph{coasting} phase, ending at $\tdec$, is assumed to have already completed.
+Each panel shows a fiducial \afterglowpy{} light curve (solid blue lines), power law segments $t^\alpha$ with slopes from the closure relations in Table \ref{tab:slopes} (black dashed lines), and representative break times between each phase of evolution (grey dashed vertical lines).
+The viewing angle $\thobs = 0$ rad, $0.2$ rad, and $0.4$ rad in the left, center, and right panels respectively.
+Remaining parameters are shared: $\thC=0.05$ rad, $\thW=0.3$ rad, $\Eiso=10^{53}$ erg, $n_0 = 10^{-3}$ cm$^{-3}$, $p=2.2$, $\epse=10^{-1}$, $\epsB=10^{-3}$, $\dL=10^{28}$ cm, $z=0.5454$.
 \label{fig:phaseSketch}}
@@
 \citet{Granot:2002aa}.
-%TODO Explain when this is valid.
+This phase occurs for all aligned observers, $\thobs < \thC$.
+It may also occur at early times for misaligned viewers with material in the line of sight, $\thC < \thobs < \thW$, if the Lorentz factor in the line of sight $\gamma_*$ is sufficiently high.
 
@@
 
-%TODO add a figure about this.
-
-There are three possible orderings of these phases, depending on the viewing angle and particular jet structure.
+Figure \ref{fig:phaseSketch} shows the three possible orderings of these phases, depending on the viewing angle and particular jet structure.
 The ``standard afterglow'' occurs for aligned observers, $\thobs < \thC$, and follows \emph{coast} $\to$ \emph{pre-jet break} $\to$ \emph{post-jet break}.
@@
 %
+
+% TODO: Put in obs frame?
 
@@
 
+\section{Acknowledgements} \label{sec:acknowledgements}
+
+GR acknowledges the support from the University of Maryland through the Joint Space Science Institute Prize Postdoctoral Fellowship.
+LP acknowledges partial support from the agreement ASI-INAF n.2017-14-H.0.
+Analysis was performed on the YORP cluster administered by the Center for Theory and Computation, part of the Department of Astronomy at the University of Maryland.
+GR thanks Cato Sandford for many useful discussions.
+
 \newpage
@@
 \end{equation}
-We denote the angle between the viewer and a particular jet sector as $\psi$ and its cosine and $\mu = \cos \psi$.
+As in Section \ref{sec:numerical} we denote the angle between the viewer and a particular jet sector as $\psi$, its cosine as $\mu = \cos \psi$, and define $\chi = 2 \sin(\psi/2) \approx \psi$.
 Photons emitted at time from a sector of the blast wave at time $t$ will be seen by the observer at $\tobs$:
@@
 \end{equation}
+Equation \eqref{eq:tobs} ignores the effect of cosmological redshift as it does not effect the closure relations.
 
@@
 \end{equation}  
-The blast wave emits from a region of width $\Delta R \propto \delta_s \gamma_s \gamma^{-2} R $ where $\delta_s$ is the Doppler factor associated with the shock Lorentz factor $\gamma_s$.
+The blast wave emits from a region of width $\Delta R \propto \delta_s \gamma_s \gamma^{-2} R $ where $\delta_s$ is the Doppler factor associated with the shock Lorentz factor $\gamma_s$ \citep{van-Eerten:2010aa, van-Eerten:2018ab}.
 At a given observer time, the emission will be dominated by a region of (rest-frame) angular size $\Delta \Omega$.
@@
 The emissivity $\varepsilon'_{\nu'}$ depends on the fluid Lorentz factor, the frequency $\nuobs$, and numerous (constant) microphysical parameters.
-We parameterize the dynamic dependence as $\varepsilon'_{\nu'} \propto \gamma^{s_1} t^{s_2} {\nu'}^\beta = t^{s_2} \gamma^{s_1}\delta^{-\beta} \nuobs^\beta$.
-The values of $s_1$, $s_2$, and $\beta$ in synchrotron regimes are given in Table \ref{tab:specSlopes}.
+We parameterize the dynamic dependence as $\varepsilon'_{\nu'} \propto \gamma^{s_\gamma} t^{s_t} {\nu'}^\beta = t^{s_t} \gamma^{s_\gamma}\delta^{-\beta} \nuobs^\beta$.
+The values of $s_\gamma$, $s_t$, and $\beta$ in synchrotron regimes are given in Table \ref{tab:specSlopes}.
 This leads to a flux of:
 \begin{equation}
-	F_\nu \propto \Delta \Omega\ t^{3+s_2} \gamma^{-1+s_1} \delta_s \delta^{2-\beta} \nuobs^\beta\ . \label{eq:fluxApprox}
+	F_\nu \propto \Delta \Omega\ t^{3+s_t} \gamma^{-1+s_\gamma} \delta_s \delta^{2-\beta} \nuobs^\beta\ . \label{eq:fluxApprox}
 \end{equation}
@@
 \begin{deluxetable}{CCCC}
-	\tablecaption{Dependence of $\varepsilon'_{\nu'} \propto \gamma^{s_1} t^{s_2} \nu'^{\beta}$ in various spectral regimes. \label{tab:specSlopes}}
-	\tablehead{\colhead{Regime}& \colhead{$s_1$} & \colhead{$s_2$} & \colhead{$\beta$}}
+	\tablecaption{Dependence of $\varepsilon'_{\nu'} \propto \gamma^{s_\gamma} t^{s_t} \nu'^{\beta}$ in various spectral regimes. \label{tab:specSlopes}}
+	\tablehead{\colhead{Regime}& \colhead{$s_\gamma$} & \colhead{$s_t$} & \colhead{$\beta$}}
 	\startdata
@@
 \end{deluxetable}
-The Doppler factor depends on the fluid Lorentz factor and whether the material is on-axis.
-The on/off axis boundary occurs at $\gamma^{-1} \approx \sin \psi$ (ie.
-$\beta \approx \mu$).
-One can write:
-\begin{equation}
-	\delta = \left \{ \begin{matrix}
-				\frac{1}{2} \gamma^{-1} \sin^{-2}\psi/2,  & \text{if } \gamma \gg 1 \text{ and } \sin{\psi} \gg \gamma^{-1} \ \ \text{(off-axis)} \\
-				2 \gamma, & \text{if } \gamma \gg 1 \text{ and } \sin{\psi} \ll \gamma^{-1} \ \  \text{(on-axis)} \\
-				1  & \text{if } \beta \ll 1\ \  \text{(non-relativistic)} \\ \end{matrix} \right . \ .
+The Doppler factor depends on the fluid Lorentz factor and whether the material is on-axis. The on/off axis boundary occurs at $\gamma^{-1} \approx \chi$ (ie. $\beta \approx \mu$).  One can write:
+\begin{equation}
+	\delta = \begin{cases}
+				2 \gamma^{-1} \chi^{-2},  & \text{if } \gamma \gg 1 \text{ and } \chi \gg \gamma^{-1} \ \ \text{(off-axis)} \\
+				2 \gamma, & \text{if } \gamma \gg 1 \text{ and } \chi \ll \gamma^{-1} \ \  \text{(on-axis)} \\
+				1  & \text{if } \beta \ll 1\ \  \text{(non-relativistic)}
+		     \end{cases}
 \end{equation}
@@
 	\tobs = \left \{ \begin{matrix}
-				\frac{1}{2} \psi^2 t,  & \text{if }\sin{\psi} \gg \gamma^{-1}\ \ \text{(off-axis)} \\
-				\frac{1}{16} \gamma^{-2} t, & \text{if } \sin{\psi} \ll \gamma^{-1} \ \  \text{(on-axis)} \end{matrix} \right . \ .
+				\frac{1}{2} \chi^2 t,  & \text{if } \chi \gg \gamma^{-1}\ \ \text{(off-axis)} \\
+				\frac{1}{16} \gamma^{-2} t, & \text{if } \chi \ll \gamma^{-1} \ \  \text{(on-axis)} \end{matrix} \right . \ .
 \end{equation}
@@
 	F_\nu \propto \left \{ \begin{matrix}
-				\Delta \Omega t^{3+s_2} \gamma^{-4+s_1+\beta} \psi^{-6+2\beta}\nuobs^\beta,  & \text{(off-axis)} \\
+				\Delta \Omega t^{3+s_2} \gamma^{-4+s_1+\beta} \chi^{-6+2\beta}\nuobs^\beta,  & \text{(off-axis)} \\
 				\Delta \Omega t^{3+s_2} \gamma^{2+s_1-\beta} \nuobs^\beta, & \text{(on-axis)} \end{matrix} \right . \ .
@@
 	F_\nu \propto \left \{ \begin{matrix}
-				t^{3+s_2} \gamma^{-4+s_1+\beta} \psi^{-6+2\beta}\nuobs^\beta,  & \text{(off-axis)} \\
+				t^{3+s_2} \gamma^{-4+s_1+\beta} \chi^{-6+2\beta}\nuobs^\beta,  & \text{(off-axis)} \\
 				t^{3+s_2} \gamma^{s_1-\beta} \nuobs^\beta, &  \text{(on-axis, pre jet break)} \\
@@
 	F_\nu \propto \left \{ \begin{matrix}
-				\tobs^{9+s_2 -3(s_1+\beta)/2} \psi^{-6+2\beta}\nuobs^\beta,  & \text{(off-axis)} \\
+				\tobs^{9+s_2 -3(s_1+\beta)/2} \chi^{-6+2\beta}\nuobs^\beta,  & \text{(off-axis)} \\
 				\tobs^{(3+s_2)/4+3(-s_1+\beta)/8} \nuobs^\beta, &\text{(on-axis, pre jet break)} \\
@@
 
-At each moment during the structure phase the emission is dominated by material that just came on-axis, where $\gamma^{-1} = \sin \psi$.
+At each moment during the structure phase the emission is dominated by material that just came on-axis, where $\gamma^{-1} = \chi = 2\sin (\psi/2) \approx \psi$.
 To find the overall behaviour we first determine $\tobs(\psi)$ and $F_\nu(\psi)$ for material whose emission is peaking (coming on-axis).
-Since the structure phase occurs when motion is still relativistic, we can assume $\gamma \gg 1$ and hence $\sin \psi \ll 1$.
+Since the structure phase occurs when motion is still relativistic, we can assume $\gamma \gg 1$ and hence $\chi, \sin \psi \ll 1$.
 In this approximation:
 \begin{eqnarray}
-	\mu \approx 1 - \frac{1}{2}\sin^2\psi \ , \label{eq:muPsi}\\
-	\delta_s \approx \delta \approx \gamma = \csc \psi\ . \label{eq:deltaPsi}
+	\mu = 1 - \frac{1}{2}\chi^2 \ , \label{eq:muPsi}\\
+	\delta_s \approx \delta \approx \gamma = \chi^{-1} \ . \label{eq:deltaPsi}
 \end{eqnarray}
@@
 \begin{equation}
-	\tobs(\psi) = \frac{9}{16} t \sin^2\psi  \propto E(\theta)^{1/3} \sin^{8/3} \psi\ . \label{eq:tobsPsi}
+	\tobs(\psi) = \frac{9}{16} \chi^2 t \propto E(\theta)^{1/3} \chi^{8/3}\ . \label{eq:tobsPsi}
 \end{equation}
 The peak flux from material at $\psi$ can be determined from Equation \eqref{eq:fluxApprox}.
-Using Equation \eqref{eq:deltaPsi} and taking $\Delta \Omega \propto \gamma^{-s_3}$ gives an observed flux:
-\begin{equation}
-	F_\nu(\psi) \propto t^{3+s_2} \gamma^{2+s_1-s_3-\beta} \nuobs^\beta \propto E(\theta)^{1+s_2/3} (\sin \psi)^{-s_1 + 2 s_2/3 +s_3+\beta} \nuobs^\beta  \ . \label{eq:FnuPsi}
+Using Equation \eqref{eq:deltaPsi} and taking $\Delta \Omega \propto \gamma^{-\som}$ gives an observed flux:
+\begin{equation}
+	F_\nu(\psi) \propto t^{3+s_t} \gamma^{2+s_\gamma-\som-\beta} \nuobs^\beta \propto E(\theta)^{1+s_t/3} \chi^{-s_\gamma + 2 s_t/3 +\som+\beta} \nuobs^\beta  \ . \label{eq:FnuPsi}
 \end{equation}
@@
 	We can obtain the temporal power law slope of the light curve by differentiating both Equations \eqref{eq:tobsPsi} and \eqref{eq:FnuPsi} with respect to $\psi$.
-Noting that $dE/d\psi = -dE/d\theta$ we obtain for the individual derivatives:
+Noting that $dE/d\psi = -dE/d\theta$ and $d\chi/d\psi = \cos (\psi/2)$ we obtain for the individual derivatives:
 \begin{eqnarray}
-	\frac{d \log \tobs}{d \psi} = \frac{8}{3} \cot \psi - \frac{1}{3} \frac{d \log E}{d \theta}\ , \\
-	\frac{d \log F_\nu}{d \psi} = \left(-s_1 + \frac{2}{3} s_2 +s_3+\beta\right)\cot \psi - \left(1+\frac{1}{3}s_2\right) \frac{d \log E}{d \theta}\ .
+	\frac{d \log \tobs}{d \psi} = \frac{4}{3} \cot (\psi/2) - \frac{1}{3} \frac{d \log E}{d \theta}\ , \\
+	\frac{d \log F_\nu}{d \psi} = \left(-s_\gamma + \frac{2}{3} s_t +\som+\beta\right)\frac{1}{2}\cot(\psi/2) - \left(1+\frac{1}{3}s_t\right) \frac{d \log E}{d \theta}\ .
 \end{eqnarray}
@@
 \begin{eqnarray}
-	\frac{d \log F_\nu}{d \log \tobs}(\psi) = \frac{3 \beta - 3s_1 + 2s_2+3s_3 + (3+s_2)g(\psi)}{ 8+g(\psi)} \\
-	g(\psi) \equiv -\tan \psi \frac{d \log E}{d \theta}\ .
+	\frac{d \log F_\nu}{d \log \tobs}(\psi) = \frac{3 \beta - 3s_\gamma + 2s_t+3\som + (3+s_t)g(\psi)}{ 8+g(\psi)}  \label{eq:closure} \\
+	g(\psi) \equiv -2\tan(\psi/2) \frac{d \log E}{d \theta}\ .
 \end{eqnarray}
-The parameter $g$ is directly measurable from the light curve, given the spectral information which fixes $\beta$, $s_1$, and $s_2$.
+The parameter $g$ is directly measurable from the light curve, given the spectral information which fixes $\beta$, $s_\gamma$, and $s_t$.
+
+Equation \eqref{eq:closure} is a generic expression for the temporal slope $\alpha$ for synchrotron emission from and relativistic, non-spreading, decelerating blast wave.
+In particular, if $g = 0$ and $\som = 2$ one recovers the standard pre-jet break slopes \citep{Granot:2002aa}.
+If $g=0$ and $s=0$ one recovers the standard beaming-effect jet break where the post-break slope is reduced by $-3/4$ from the the pre-break slope.
+Misaligned viewing of a structured jet corresponds to $\som = 1$, $g$ free.
 
 The full flux scaling equations also require an updated energy and circumburst density scaling.
-We can obtain the scalings for energy and density from dimensional analysis, following \cite{van-Eerten:2012ac} (specifically, by making use of the fact that the overall flux scalings for the different spectral regimes should obey those presented in table 1 of that paper).
-
-{\color{red}[RED STUFF IS WRONG SOMEHOW]
-  For energy, it follows that (below $\nu_c$)
-\begin{equation}
-	\frac{d \log F}{d \log E} = \frac{d \log F}{d \Psi} \frac{d \Psi}{d \log E} = - \frac{d \log F}{d \Psi} \frac{d \theta}{d \log E} = \left(s_1 - \frac{2}{3} s_2 - s_3 -\beta\right) h(\Psi) + 1 + \frac{1}{3} s_2,
-\end{equation}
-where
-\begin{equation}
-	h(\Psi) \equiv \cot \Psi \frac{d \log E}{d \theta}.
-\end{equation}
-For the density $n_0$ we have (below $\nu_c$)
-\begin{equation}
-	\frac{d \log F}{d \log n_0} = \frac{2+s_3}{8}
-\end{equation}
-}
-Altogether, we obtain
-\begin{eqnarray}
-F_D & \propto & (1+z)^{(38-5g(\Psi)-9s_3)/3(8+g(\Psi))} \epsilon_e^{-2/3} \epsilon_B^{1/3} n_0^{(6+4g+3s_3)/3(8+g(\Psi))} E_0^{(26-3s_3)/3(8+g(\Psi))} t_{obs}^{(-2+3s_3+3g(\Psi))/(8+g(\Psi))} \nu^{1/3} \nonumber \\
-F_E & \propto & (1+z)^{(46-7g(\Psi)-9s_3)/3(8+g(\Psi))} \epsilon_B^{1} n_0^{(14+6g(\Psi)+3s_3)/3(8+g(\Psi))} E_0^{(34-3s_3)/3(8+g(\Psi))} t_{obs}^{(-14+9s_3+11g(\Psi))/3(8+g(\Psi))} \nu^{1/3} \nonumber \\
-F_F & \propto & (1+z)^{(24-3g(\Psi)-6s_3)/2(8+g(\Psi))} \epsilon_B^{-1/4} n_0^{(-8+3g(\Psi)+4s_3)/4(8+g(\Psi))} E_0^{(8-s_3)/(8+g(\Psi))} t_{obs}^{(-8+3s_3+2g(\Psi))/(8+g(\Psi))} \nu^{-1/2} \nonumber \\
-F_G & \propto & (1+z)^{\frac{(-pg(\Psi)-3g(\Psi)+4p-6s_3+24)}{2(8+g(\Psi))}} \epsilon_e^{p-1} \epsilon_B^{(1+p)/4} n_0^{(g(\Psi)p + 5 g(\Psi) + 4s_3 + 8)/4(8+g(\Psi))} E_0^{(8+2p-s_3)/(8+g(\Psi))} t_{obs}^{3(-2p+s_3+g(\Psi))/(8+g(\Psi))} \nu^{(1-p)/2} \nonumber \\
-F_H & \propto & (1+z)^{\frac{(-pg(\Psi)-2g(\Psi)+4p-6s_3+20)}{2(8+g(\Psi))}} \epsilon_e^{p-1} \epsilon_B^{(p-2)/4} n_0^{(g(\Psi)p+2g(\Psi)+4s_3-8)/4(8+g(\Psi))} E_0^{(6+2p-s_3)/(8+g)} t_{obs}^{(-6p-2+3s_3+2g(\Psi))/(8+g(\Psi))} \nu^{-p/2} \nonumber \\
-\nu_m & \propto & (1+z)^{\frac{4-g(\Psi)}{8+g(\Psi)}} \epsilon_e^2 \epsilon_B^{1/2} n_0^{g(\Psi)/(16+2g(\Psi))} E_0^{4/(8+g(\Psi))} t_{obs}^{-12/(8+g(\Psi))} \nonumber \\
-\nu_c & \propto & (1+z)^{\frac{-4+g(\Psi)}{8+g(\Psi)}} \epsilon_B^{-3/2} n_0^{-(3g(\Psi)+16)/2(8+g(\Psi))} E_0^{-4/(8+g(\Psi))} t_{obs}^{-2(2+g(\Psi))/(8+g(\Psi))} \nonumber \\
-F_{peak} & \propto & (1+z)^{\frac{14-2g(\Psi)-3s_3}{8+g(\Psi)}} \epsilon_B^{1/2} n_0^{(4+3g(\Psi)+2s_3)/2(8+g(\Psi))} E_0^{(10-s_3)/(8+g(\Psi))} t_{obs}^{3(-2+s_3+g(\Psi))/(8+g(\Psi))}
-\end{eqnarray}
+We can obtain the scalings for energy and density from dimensional analysis, following \citet{van-Eerten:2012ac} (specifically, by making use of the fact that the overall flux scalings for the different spectral regimes should obey those presented in table 1 of that paper).
+
+Introducing the microphysical parameters $p$, $\epse$, and $\epsB$ as in Section \ref{sec:numerical} we can write scalings for the characteristic spectral quantities in the observers frame, where we only neglect constant factors:
+\begin{align}
+	\nu_m (\psi) &\propto \left(1+z\right)^{-1}\left(\frac{p-2}{p-1}\right)^2 n_0^{1/2} \epse^2 \epsB^{1/2}  \chi^{-4} \label{eq:numPsi} \\
+	\nu_c (\psi)&\propto  \left(1+z\right)^{-1} n_0^{-5/6} \epsB^{-3/2} E(\theta)^{-2/3} \chi^{-4/3} \label{eq:nucPsi} \\
+	F_P(\psi)&\propto \left(1+z\right) \left(p-1\right)  d_L^{-2} n_0^{1/2} \epsB^{1/2} E(\theta)  \chi^{-2+\som} \label{eq:FPPsi}
+\end{align}
+
+Their derivatives with respect to $\psi$ are:
+\begin{align}
+	\frac{d \log \nu_m}{d\psi} &= -2 \cot(\psi/2)\ , \\
+	\frac{d \log \nu_c}{d\psi} &= \frac{2}{3} \cot(\psi/2) - \frac{2}{3} \frac{d \log E}{d \theta}\ , \\
+	\frac{d \log F_P}{d\psi} &= \left(-2 + \som\right)\frac{1}{2} \cot(\psi/2) -  \frac{d \log E}{d \theta}\ .
+\end{align}
+Leading to observed temporal slopes of:
+\begin{align}
+	\frac{d \log \nu_m}{d\log \tobs} &= -\frac{12}{8+g(\psi)}\ , \\
+	\frac{d \log \nu_c}{d\log\tobs} &= 2\frac{2 + g(\psi)}{8+g(\psi)}\ , \\
+	\frac{d \log F_P}{d\log \tobs} &= 3\frac{-2 + \som +  g(\psi)}{8+g(\psi)}\ .
+\end{align}
+
+We can obtain full observer frame flux scaling equations in each of the synchrotron spectral regimes, following \citet{van-Eerten:2012ac}.
+Although the scalings of $p$, $\epse$, $\epsB$, and $d_L$ remain unchanged, $n_0$, $E_0$, and $z$ are significantly altered due to their role in normalizing the observer time $\tobs$.
+In particular, by dimensional analysis $\chi$ must be proportional to a power of $(1+z)^{-1} E_0^{-1/3} n_0^{1/3} \tobs$.
+We can use this to write the characteristic spectral quantities semi-explicitly in terms of the observer time $\tobs$:
+\begin{align}
+	\nu_m & \propto  (1+z)^{(4-g)/(8+g)}  \left(\frac{p-2}{p-1}\right)^2  \epse^2 \epsB^{1/2}E_0^{4/(8+g)} n_0^{g/(16+2g)} \tobs^{-12/(8+g)} \\
+	\nu_c & \propto  (1+z)^{(-4+g)/(8+g)} \epsB^{-3/2}   E_0^{-4/(8+g)} n_0^{-(16+3g)/(16+2g)} \tobs^{2(2+g)/(8+g)} \\
+	F_{\mathrm{Peak}} &\propto  (1+z)^{(14-2g-3\som)/(8+g)}  \epsB^{1/2} E_0^{(10-\som)/(8+g)} n_0^{(4+3g+2\som)/(16+2g)} t_{obs}^{3(-2+\som+g)/(8+g)}
+\end{align}
+Formally the above relations are not explicit, as $g$ depends on $\psi$ which depends on $\tobs$ in a non-trivial way.
+However, as demonstrated in Section \ref{sec:structuredJets} in many cases $g$ can be viewed as effectively constant.
+Using $\geff$ (ie.
+Equation \eqref{eq:geff}, for instance) one can treat the above formulae as explicit in $\tobs$.
+
+One can then arrive at the full flux relations, where we have only dropped constant numerical factors and a rational function of $p$:
+\begin{align}
+F_D & \propto  (1+z)^{(38-5g-9\som)/3(8+g)} \epsilon_e^{-2/3} \epsilon_B^{1/3} n_0^{(6+4g+3\som)/3(8+g)} E_0^{(26-3\som)/3(8+g)} t_{obs}^{(-2+3\som+3g)/(8+g)} \nu^{1/3}  \\
+F_E & \propto  (1+z)^{(46-7g-9\som)/3(8+g)} \epsilon_B^{1} n_0^{(14+6g+3\som)/3(8+g)} E_0^{(34-3\som)/3(8+g)} t_{obs}^{(-14+9\som+11g)/3(8+g)} \nu^{1/3}  \\
+F_F & \propto  (1+z)^{(24-3g-6\som)/2(8+g)} \epsilon_B^{-1/4} n_0^{(-8+3g+4\som)/4(8+g)} E_0^{(8-\som)/(8+g)} t_{obs}^{(-8+3\som+2g)/(8+g)} \nu^{-1/2}  \\
+F_G & \propto  (1+z)^{\frac{(-pg-3g+4p-6\som+24)}{2(8+g)}} \epsilon_e^{p-1} \epsilon_B^{(1+p)/4} n_0^{(gp + 5 g + 4\som + 8)/4(8+g)} E_0^{(8+2p-\som)/(8+g)} t_{obs}^{3(-2p+\som+g)/(8+g)} \nu^{(1-p)/2}  \\
+F_H & \propto  (1+z)^{\frac{(-pg-2g+4p-6\som+20)}{2(8+g)}} \epsilon_e^{p-1} \epsilon_B^{(p-2)/4} n_0^{(gp+2g+4\som-8)/4(8+g)} E_0^{(6+2p-\som)/(8+g)} t_{obs}^{(-6p-2+3\som+2g)/(8+g)} \nu^{-p/2} 
+\end{align}
+Again, although formally $g = g(\psi)$ is time variable, it can often be regarded as constant in a particular phase of the light curve.
+
+%{\color{red}[RED STUFF IS WRONG SOMEHOW]
+%  For energy, it follows that (below $\nu_c$)
+%\begin{equation}
+%	\frac{d \log F}{d \log E} = \frac{d \log F}{d \Psi} \frac{d \Psi}{d \log E} = - \frac{d \log F}{d \Psi} \frac{d \theta}{d \log E} = \left(s_1 - \frac{2}{3} s_2 - s_3 -\beta\right) h(\Psi) + 1 + \frac{1}{3} s_2,
+%\end{equation}
+%where
+%\begin{equation}
+%	h(\Psi) \equiv \cot \Psi \frac{d \log E}{d \theta}.
+%\end{equation}
+%For the density $n_0$ we have (below $\nu_c$)
+%\begin{equation}
+%	\frac{d \log F}{d \log n_0} = \frac{2+s_3}{8}
+%\end{equation}
+%}
+%Altogether, we obtain
+%\begin{eqnarray}
+%F_D & \propto & (1+z)^{(38-5g(\Psi)-9s_3)/3(8+g(\Psi))} \epsilon_e^{-2/3} \epsilon_B^{1/3} n_0^{(6+4g+3s_3)/3(8+g(\Psi))} E_0^{(26-3s_3)/3(8+g(\Psi))} t_{obs}^{(-2+3s_3+3g(\Psi))/(8+g(\Psi))} \nu^{1/3} \nonumber \\
+%F_E & \propto & (1+z)^{(46-7g(\Psi)-9s_3)/3(8+g(\Psi))} \epsilon_B^{1} n_0^{(14+6g(\Psi)+3s_3)/3(8+g(\Psi))} E_0^{(34-3s_3)/3(8+g(\Psi))} t_{obs}^{(-14+9s_3+11g(\Psi))/3(8+g(\Psi))} \nu^{1/3} \nonumber \\
+%F_F & \propto & (1+z)^{(24-3g(\Psi)-6s_3)/2(8+g(\Psi))} \epsilon_B^{-1/4} n_0^{(-8+3g(\Psi)+4s_3)/4(8+g(\Psi))} E_0^{(8-s_3)/(8+g(\Psi))} t_{obs}^{(-8+3s_3+2g(\Psi))/(8+g(\Psi))} \nu^{-1/2} \nonumber \\
+%F_G & \propto & (1+z)^{\frac{(-pg(\Psi)-3g(\Psi)+4p-6s_3+24)}{2(8+g(\Psi))}} \epsilon_e^{p-1} \epsilon_B^{(1+p)/4} n_0^{(g(\Psi)p + 5 g(\Psi) + 4s_3 + 8)/4(8+g(\Psi))} E_0^{(8+2p-s_3)/(8+g(\Psi))} t_{obs}^{3(-2p+s_3+g(\Psi))/(8+g(\Psi))} \nu^{(1-p)/2} \nonumber \\
+%F_H & \propto & (1+z)^{\frac{(-pg(\Psi)-2g(\Psi)+4p-6s_3+20)}{2(8+g(\Psi))}} \epsilon_e^{p-1} \epsilon_B^{(p-2)/4} n_0^{(g(\Psi)p+2g(\Psi)+4s_3-8)/4(8+g(\Psi))} E_0^{(6+2p-s_3)/(8+g)} t_{obs}^{(-6p-2+3s_3+2g(\Psi))/(8+g(\Psi))} \nu^{-p/2} \nonumber \\
+%\nu_m & \propto & (1+z)^{\frac{4-g(\Psi)}{8+g(\Psi)}} \epsilon_e^2 \epsilon_B^{1/2} n_0^{g(\Psi)/(16+2g(\Psi))} E_0^{4/(8+g(\Psi))} t_{obs}^{-12/(8+g(\Psi))} \nonumber \\
+%\nu_c & \propto & (1+z)^{\frac{-4+g(\Psi)}{8+g(\Psi)}} \epsilon_B^{-3/2} n_0^{-(3g(\Psi)+16)/2(8+g(\Psi))} E_0^{-4/(8+g(\Psi))} t_{obs}^{-2(2+g(\Psi))/(8+g(\Psi))} \nonumber \\
+%F_{peak} & \propto & (1+z)^{\frac{14-2g(\Psi)-3s_3}{8+g(\Psi)}} \epsilon_B^{1/2} n_0^{(4+3g(\Psi)+2s_3)/2(8+g(\Psi))} E_0^{(10-s_3)/(8+g(\Psi))} t_{obs}^{3(-2+s_3+g(\Psi))/(8+g(\Psi))}
+%\end{eqnarray}
+%
+%\begin{align}
+%	\nu_m &\propto \left(1+z\right)^{-1}\left(\frac{p-2}{p-1}\right)^2 n_0^{1/2} \epse^2 \epsB^{1/2} \gamma^{4} \\
+%		&\propto \left(1+z\right)^{-1}\left(\frac{p-2}{p-1}\right)^2 n_0^{1/2} \epse^2 \epsB^{1/2}  \chi^{-4} \\
+%	\nu_c &\propto \left(1+z\right)^{-1} n_0^{-3/2} \epsB^{-3/2} t^{-2} \\
+%		&\propto  \left(1+z\right)^{-1} n_0^{-5/6} \epsB^{-3/2} E(\theta)^{-2/3} \chi^{-4/3} \\
+%	F_P &\propto \left(1+z\right) \left(p-1\right)  n_0^{3/2} \epsB^{1/2} t^{3} \gamma^{4-\som} \\
+%		&\propto \left(1+z\right) \left(p-1\right)  n_0^{1/2} \epsB^{1/2} E(\theta)  \chi^{-2+\som} 
+%\end{align}
 

### 2019-09-11 code/plotPhaseSketch.py

@@ -29,6 +29,7 @@ highlightPhases = False
 highlightTransitions = True
 
 phaseLabels = True
+breakLabels = True
 
 Y0 = np.array([thV, E0, thC, thW, b, L0, ts, q, n0, p, epse, epsB, xiN, dL])
 Z = {'z': z, 'spread': False}
@@ -36,7 +37,7 @@ Zg = Z.copy()
 Zg['g0'] = g0
 
 width = 7.5
-height = 3.5
+height = 3
 
 fig = plt.figure(figsize=(width, height))
 gs = fig.add_gridspec(1, 3, wspace=0.0)
@@ -59,7 +60,7 @@ Y1[0] = 0.0
 Y2[0] = thW - 2*thC
 Y3[0] = thW + 2*thC
 
-tmin1 = t.min()
+tmin1 = 3.0e3  # t.min()
 tmax1 = t.max()
 tmin2 = 1.0e4
 tmax2 = t.max()
@@ -103,12 +104,12 @@ t3_STR = np.geomspace(3.0e5, 2.0e7, 100)
 t3_POS = np.geomspace(4.0e7, t.max(), 100)
 
 F1_PRE = Fnu1[np.searchsorted(t, t1_PRE[len(t1_PRE)//2])] * 3
-F1_POS = Fnu1[np.searchsorted(t, t1_POS[len(t1_POS)//2])] * 3
-F1_POS2 = Fnu1[np.searchsorted(t, t1_POS[len(t1_POS)//2])] / 3
+F1_POS = Fnu1[np.searchsorted(t, t1_POS[len(t1_POS)//2])] * 5
+F1_POS2 = Fnu1[np.searchsorted(t, t1_POS[len(t1_POS)//2])] / 4
 
 F2_PRE = Fnu2[np.searchsorted(t, t2_PRE[len(t2_PRE)//2])] * 3
-F2_STR = Fnu2[np.searchsorted(t, t2_STR[len(t2_STR)//2])] * 3
-F2_POS = Fnu2[np.searchsorted(t, t2_POS[len(t2_POS)//2])] * 3
+F2_STR = Fnu2[np.searchsorted(t, t2_STR[len(t2_STR)//2])] * 2
+F2_POS = Fnu2[np.searchsorted(t, t2_POS[len(t2_POS)//2])] * 4
 F2_POS2 = Fnu2[np.searchsorted(t, t2_POS[len(t2_POS)//2])] / 3
 
[…]

### 2019-09-18 structuredJets.tex
Updating plots

@@
 
-\title{The Electromagnetic Afterglows of Structured Jets: Numerical Models and Closure Relations  \hspace{10in} OR\hspace{10in}   Electromagnetic Afterglows Of Structured Jets \hspace{10in}  OR\hspace{10in}  Structured Jets At All Angles\hspace{10in}  OR \hspace{10in}GRB Afterglows In The Multi-Messenger Era}
+\title{Gamma-Ray Burst Afterglows In The Multi-Messenger Era: Numerical Models and Closure Relations}
 
@@
 \author[0000-0001-9068-7157]{Geoffrey Ryan}
+\altaffiliation{JSI Fellow}
 \affil{Joint Space-Science Institute, University of Maryland, College Park, MD 20742, USA}
@@
 \author{Hendrik van Eerten}
+\affil{Department of Physics, University of Bath, Claverton Down, Bath BA2 7AY, United Kingdom}
 \author{Luigi Piro}
+\affil{INAF, Istituto di Astrofisica e Planetologia Spaziali, via Fosso del Cavaliere 100, 00133 Rome, Italy}
 \author{Eleonora Troja}
+\affil{Department of Astronomy, University of Maryland, College Park, MD 20742-4111, USA}
+\affil{Astrophysics Science Division, NASA Goddard Space Flight Center, 8800 Greenbelt Rd, Greenbelt, MD 20771, USA}
 
@@
 
-The binary neutron star merger event \gwbns{}, followed quickly by the short gamma-ray burst \grbbns{}, provided a new view on gamma-ray burst (GRB) afterglows (CITE LIGO, Discovery papers).
+The binary neutron star merger event \gwbns{}, followed quickly by the short gamma-ray burst \grbbns{}, provided a new view on gamma-ray burst (GRB) afterglows \citep{Abbott:2017ab, Abbott:2017ac}.
 Unlike typical afterglows, which begin bright and decay from detection with a ~week timescale, \grbbns{}'s non-thermal emission was undetectable until the first observation of X-rays nine days after the GRB \citep{Troja:2017aa}.
-At this point the afterglow began steadily increasing in brightness in at all wavelengths for ~160 days \citep{Troja:2018aa, Troja:2019ab} (CITE OTHERS).
+At this point the afterglow began steadily increasing in brightness in at all wavelengths for ~160 days \citep{Haggard:2017aa, Hallinan:2017aa, DAvanzo:2018aa,  Lyman:2018aa, Margutti:2018aa, Mooley:2018aa, Troja:2018aa, Troja:2019ab}.
 Very long baseline (VLBI) radio imagery over this period identified a radio core with an apparent superluminal motion, indicating the emitting surface was moving at relativistically at an oblique angle towards the Earth \citep{Mooley:2018ab}.
@@
 
-The lack of early emission, slow rising light curve, apparent motion of the radio centroid, and sharp decline post-peak are all consistent with emission from a \emph{structured jet}, a collimated blast wave with a non-trivial angular distribution of energy, viewed a moderate angle away from the jet axis (CITE YITL, Mooley, Ghirlanda, Lamb, Hotokezaka, ...).
+The lack of early emission, slow rising light curve, apparent motion of the radio centroid, and sharp decline post-peak are all consistent with emission from a \emph{structured jet}, a collimated blast wave with a non-trivial angular distribution of energy, viewed a moderate angle away from the jet axis \citep{Lamb:2017aa, Alexander:2018aa, Hotokezaka:2018aa, Wu:2018aa, Xie:2018aa,  Ghirlanda:2019aa, Fong:2019aa, Lamb:2019aa, Troja:2019aa}.
 The combined effects of a moderate viewing angle and angular structure in the jet produce a light curve significantly different from the standard on-axis uniform ``top-hat'' jet used extensively in GRB afterglow analysis.
@@
 In the ultra-relativistic limit $\beta_\bot = \sqrt{3/8} c_s/(c\gamma) = 1/(\sqrt{8} \gamma)$.
-In this same limit, a signal launched at $t=0$ traveling at $\beta_\bot$ along the shock front will cover an angular distance  $\Delta \theta = 1/(3\sqrt{2}\gamma)$(CITE Hendrik).
+In this same limit, a signal launched at $t=0$ traveling at $\beta_\bot$ along the shock front will cover an angular distance  $\Delta \theta = 1/(3\sqrt{2}\gamma)$ \citep{van-Eerten:2012aa}.
 Taking $\thC$, defined by Equation \eqref{eq:thCdef}, as the angular scale for order unity changes in the jet pressure, we can approximate the onset of spreading as when $u = 1/(3\sqrt{2}\thC)$.
@@
 Afterglow light curves computed using Equation \eqref{eq:thetadot} were found to agree better with established simulation based models (see Section \ref{subsec:boxfitcomp}) than those computed with the DL18 parameters.
-This jet spreading prescription differs from that used in \citet{Troja:2018aa, Piro:2019aa, Troja:2019ab} which used a simple $u < 1$ criterion to begin jet spreading and set $\beta_\bot = c_s / (c \gamma)$.
+This jet spreading prescription differs from that used in \citet{Troja:2018aa, Piro:2019aa, Troja:2019ab} which used a simple $u < 1$ criterion to begin jet spreading and set $\beta_\bot = c_s / (c \gamma)$, following \citet{van-Eerten:2010aa}.
 
@@
 
-\afterglowpy{} is available on PyPI and may be installed with {\tt pip}.  The source code is open and available at \url{https://github.com/geoffryan/afterglowpy}.
+\afterglowpy{} is available on PyPI and may be installed with {\tt pip} as {\tt pip install afterglowpy}.  The source code is open and available at \url{https://github.com/geoffryan/afterglowpy}.
 
@@
 
+% TODO Finish this paragraph
 To fully characterize the light curves of structured jets we use \afterglowpy{} to construct light curves exploring dependence on jet structure model, viewing angle $\thobs$, opening angle $\thC$, and synchrotron regime.
@@
 The ``structured'' phase ($\alpha_{\mathrm{struct}}$) is seen by misaligned viewers ($\thobs > \thC$), occurs before the jet break, and corresponds to $\som \approx 1$.
-The ``pre-jet break'' phase ($\alpha_{\mathrm{pre}}$)  is seen by aligned viewers ($\thobs < \thC$).
+The ``pre-jet break'' phase ($\alpha_{\mathrm{pre}}$) is seen by aligned viewers ($\thobs \lesssim \thC$) and by early misaligned viewers if there is high Lorentz factor material in their line of sight.
 The first ``post-jet break'' slope ($\alpha_{\mathrm{post, 1}}$) given here does not include the effects of jet spreading and as such is shallower than the true post-jet break slope.
@@
 Each panel shows a fiducial \afterglowpy{} light curve (solid blue lines), power law segments $t^\alpha$ with slopes from the closure relations in Table \ref{tab:slopes} (black dashed lines), and representative break times between each phase of evolution (grey dashed vertical lines).
+The two dashed lines in the ``post-jet break'' section bracket the possible light curve behaviour.
 The viewing angle $\thobs = 0$ rad, $0.2$ rad, and $0.4$ rad in the left, center, and right panels respectively.
@@
 The flux is dominated by a small patch of relativistic material directly in the line of sight: $\theta_* = \thobs$.
-The material is relativistic, $\gamma_* \gg 1$, and the angular size is controlled by doppler beaming: $\psi \sim \gamma_*^{-1}$ and $\som = 2$.
+The material is relativistic, $\gamma_* \gg 1$, and the angular size is controlled by doppler beaming: $\Delta \Omega \sim \gamma_*^{-2}$ and $\som = 2$.
 The patch is sufficiently small (or sufficiently on-axis) that $E(\theta)$ is near-uniform over the visible patch.
@@
 \emph{Structured} --- If the viewer lies outside the core of the blast wave, $\thobs > \thC$, non-trivial angular structure can have a significant effect on the light curve.
-Material from the energetic polar regions continuously comes into view, becoming the new dominant source of emission, and moving the centroid with time: $\theta_* \to 0$ as $\tobs$ increases.
+Material from the energetic regions progressively closer to the jet axis continuously comes into view, becoming the new dominant source of emission, and moving the centroid with time: $\theta_* \to 0$ as $\tobs$ increases.
 The centroid obeys $\gamma^{-1}(\theta_*) \sim |\thobs-\theta_*|$.
@@
 Included models are the top-hat jet (dashed blue), Gaussian jet (solid green), $b=2$ power law (dot-dashed orange), and $b=6$ power law at $\thobs=0$ (upper left), $\thobs=2\thC=0.16$ rad (upper right), $\thobs=4\thC=0.32$ rad (lower left), and $\thobs=6\thC=0.48$ rad (lower right).
-These particular light curves all use $\thC = 0.08$ rad, $\thW = 0.24$ rad, $E_0 = 10^{53}$erg, $n_0=1$ cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, $\epsB = 10^{-2}$, $d_L=10^{28}$cm and $z=0.5454$.
+These particular light curves all use $\thC = 0.08$ rad, $\thW = 0.24$ rad, $E_0 = 10^{53}$ erg, $n_0=1$ cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, $\epsB = 10^{-2}$, $d_L=10^{28}$ cm and $z=0.5454$.
 \label{fig:thVmodel}}
@@
 The upper left panel shows top-hat, Gaussian, $b=2$ power law, and $b=6$ power law jets viewed exactly on-axis at $\thobs=0$.
-Each model shares $\thC=0.08$ rad, $\thW=0.24$rad, $E_0=10^{53}$ erg, $n_0 = 1$cm$^{-3}$, $p=2.2$, $\epse=10^{-1}$, $\epsB = 10^{-2}$, $d_L=10^{28}$cm and $z=0.5454$.
+Each model shares $\thC=0.08$ rad, $\thW=0.24$ rad, $E_0=10^{53}$ erg, $n_0 = 1$cm$^{-3}$, $p=2.2$, $\epse=10^{-1}$, $\epsB = 10^{-2}$, $d_L=10^{28}$ cm and $z=0.5454$.
 All of the models were computed with zero initial mass loading, so they do not show coasting phases.
 They each show identical pre-jet break phases and similar post-jet break phases.
-Each exhibits a slightly different jet break time, between $10^5$s and $10^6$s with these parameters, due to the different structure profiles $E(\theta)$.
+Each exhibits a slightly different jet break time, between $10^5$ s and $10^6$ s with these parameters, due to the different structure profiles $E(\theta)$.
 This causes a discrepancy in the overall normalization, jets with more energetic wings but the same core with $\thC$ break later and remain brighter.
@@
 The upper right panel of Figure \ref{fig:thVmodel} shows the same models viewed at $\thobs=2\thC=0.16$ rad.
-The top-hat jet exhibits an initial far off-axis phase which ends when the near side of the jet comes into view at $t=10^5$s.
-This initiates a prolonged transition period which completes  $\lesssim 10^6$s as the far edge comes into view, leading into a normal post-jet break phase.
+The top-hat jet exhibits an initial far off-axis phase which ends when the near side of the jet comes into view at $t=10^5$ s.
+This initiates a prolonged transition period which completes  $\lesssim 10^6$ s as the far edge comes into view, leading into a normal post-jet break phase.
 The structured models show similar pre-jet break phases, with slight normalization differences due to differing energies in the line of sight.
-The light curves converge before the jet break at $t \lesssim 10^6$s due to a brief structured phase in the Gaussian and $b=6$ models, which shallows their decay slightly.
-All models show a jet break and transition to similar post-jet break phases after $10^6$s.
+The light curves converge before the jet break at $t \lesssim 10^6$ s due to a brief structured phase in the Gaussian and $b=6$ models, which shallows their decay slightly.
+All models show a jet break and transition to similar post-jet break phases after $10^6$ s.
 
@@
 Since $\thW=0.24$ rad all models show an initial far-off axis phase.
-The structured models transition to a structured phase between $10^4s$ and $10^5$s, much shallower than the standard pre-jet break behaviour.
+The structured models transition to a structured phase between $10^4$ s and $10^5$ s, much shallower than the standard pre-jet break behaviour.
 The slope is shallowest in the the models with sharpest profiles: the Gaussian and $b=6$ power law.
-All models show a jet break at $t\approx 2\times 10^6$s and similar post-jet-break phases.
+All models show a jet break at $t\approx 2\times 10^6$ s and similar post-jet-break phases.
 
@@
 Glitches in the $\alpha(\tobs)$ curves are due to the numerical treatment of jet spreading.
-All models show a jet break at $t\approx 6\times 10^6$s and similar post-jet-break phases.
-
-It should be noted that the tight behaviour of the light curves near the jet break is due in part to our standardized definition of $\thC$ in Equation \eqref{eq:thCdef}.
-Alternative definitions, particularly omitting the factor of $b$ in the denominator of the power law profile expression, lead to larger differences in normalization with less shared features between light curves at the same $\thC$.
+All models show a jet break at $t\approx 6\times 10^6$ s and similar post-jet-break phases.
+
+It should be noted that the convergence of the light curves near the jet break is due in part to our standardized definition of $\thC$ in Equation \eqref{eq:thCdef}.
+Alternative definitions, particularly omitting the factor of $b$ in the denominator of the power law profile expression, lead to larger differences in normalization with fewer shared features between light curves at the same $\thC$.
 
@@
 \citet{Granot:2002aa, Rhoads:1999aa}).
-The closure relations for the far off axis phase in some spectral regimes first appeared in \citep{Salmonson:2003aa}.
-Here we provide closure relations for the structured phase, as well as scalings for the jet break time with viewing angle.
+The closure relations for the far off axis phase in some spectral regimes first appeared in \citet{Salmonson:2003aa}.
+Here we provide novel closure relations for the structured phase, as well as scalings for the jet break time with viewing angle.
 
@@
 We can calculate the structured jet closure relations by determining how the time and magnitude of the peak of each annular section depends on the angle $\theta_*$.
-The details are given in Appendices \ref{app:derive1} and \ref{app:derive2}, we give only the results here.
+The details are given in Appendices \ref{app:derive1} and \ref{app:derive2}; we give only the results here.
 For brevity we define:
@@
 
+% TODO FIX THE HELL OUT OF THESE FIGURES
+% MAKE MODEL CURVES CONSISTENT WITH MULTI-PANEL
+% DROP OR DEFINE t_N
 \begin{figure}
-	\includegraphics[width=\columnwidth]{figs/breaks_alignedOA_all.pdf}
+	\includegraphics[width=\columnwidth]{figs/jetbreak_OnAxis.pdf}
 	\caption{Jet break time for on-axis ($\thobs=0$) observers for top-hat (blue circles), Gaussian (orange squares), and power law (green triangles) jets as a function of $\thC$.
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{figs/breaks_general.pdf}
+	\includegraphics[width=\columnwidth]{figs/jetbreak_OffAxis.pdf}
 	\caption{Jet break time for off-axis ($\thobs\neq0$) observers for top-hat (blue circles), Gaussian (orange squares), and power law (green triangles) jets as a function of $\thC$.
@@
 
-\subsection{Refreshed Shocks --- Fast Tails and Spherical Cocoons}\label{subsec:refreshedShocks}
-
-An alternative mechanism to produce slow decays or rises in afterglow light curves is the \emph{refreshed shock}, where velocity stratification of the ejecta causes a prolonged period of energy injection in the afterglow.
+\subsection{Refreshed Shocks --- Fast Tails and Quasi-Spherical Cocoons}\label{subsec:refreshedShocks}
+
+An alternative mechanism to produce slow decays or rises in afterglow light curves is the \emph{refreshed shock}, where velocity stratification of the ejecta causes a prolonged period of energy injection in the afterglow \citep{Rees:1998aa, Panaitescu:1998aa, Sari:2000aa}.
 This material may be a tail of fast outflowing ejecta or ejecta material accelerated through interaction with a possibly choked jet (e.g.
-a cocoon).
-(CITE Mooley, Hotokezaka, Nakar\&Piran, etc).
+a cocoon) \citep{Nakar:2011aa, Hotokezaka:2015aa}.
 In either case, slow material initially coasting behind the shock is gradually incorporated into the blast wave as it decelerates, ``refreshing'' the shock.
-This mechanism was first proposed as an energy injection scenario (CITE), and was proposed as the mechanism behind the \gwbns{} afterglow in the choked-jet scenario.
-(CITE Mooley, Hotokezaka, etc).
+This mechanism is a general scenario for energy injection \citep{Zhang:2006aa}, and was proposed as the mechanism behind the \gwbns{} afterglow in the choked-jet scenario (e.g.
+\citep{Mooley:2018aa, Nakar:2018aa}).
 
@@
 	\nu<\nu_m<\nu_c     & D & 3 	& \frac{4 + 3k}{8+k} 		& 1/3 \\
-	\nu < \nu_c < \nu_m & E & 3 	& \frac{4/3 + 11k/3}{8+k} 	& 1/3 \\
-	\nu_c < \nu < \nu_m & F & 3 	& \frac{-2 + 2k}{8+k} 		& -1/2 \\
+	\nu < \nu_c < \nu_m & E & 11/3 	& \frac{4/3 + 11k/3}{8+k} 	& 1/3 \\
+	\nu_c < \nu < \nu_m & F &  2 	& \frac{-2 + 2k}{8+k} 		& -1/2 \\
 	\nu_m<\nu<\nu_c     & G & 3 	& \frac{-6p + 6 + 3k}{8+k} 	& -(p-1)/2 \\
-	\nu_c < \nu_m < \nu & H & 3 	& \frac{-6p + 4 + 2k}{8+k}	& -p/2 \\ 
+	\nu_c < \nu_m < \nu & H & 2 	& \frac{-6p + 4 + 2k}{8+k}	& -p/2 \\ 
 	\enddata
@@
 
-We use the electromagnetic afterglow of \gwbns{} as an example application of both the analytic and numerical structured jet afterglow models.
+We use the electromagnetic afterglow of \gwbns{} as an example application of both the analytic and numerical structured jet afterglow models, using the dataset from \citet{Troja:2019ab}.
+No new observations are presented in this paper.
 
@@
 
+%TODO - Discuss in text
 \begin{figure}
@@
 Many groups have used structured jet models to analyze the afterglow of \gwbns{}, among the most recent with comparable models are \citet{Hotokezaka:2018aa, Ghirlanda:2019aa, Lamb:2019aa, Wu:2018aa}.
-Of these, \citet{Hotokezaka:2018aa, Ghirlanda:2019aa, Lamb:2019aa} use semi-analytic methods similar to the present work to construct afterglow light curves, while \citet{Wu:2018aa} utilizes analytic scaling relations and a template bank constructed from numerical simulations.
+Of these, \citet{Hotokezaka:2018aa, Ghirlanda:2019aa, Lamb:2019aa} use semi-analytic methods similar to the present work to construct afterglow light curves, while \citet{Wu:2018aa} utilizes analytic scaling relations and a template bank constructed from numerical simulations (following the conceptual approach introduced by \citet{van-Eerten:2012ac}).
 Additionally, \citet{Hotokezaka:2018aa, Ghirlanda:2019aa} include constraints from the VLBI measurements of the \gwbns{} radio centroid's apparent superluminal motion.
@@
   \begin{equation}
-	\gamma(t; \theta) \propto \sqrt{\frac{E(\theta)}{n_0}}\ t^{-3/2}\ . \label{eq:lorentzEvolution}
+	\gamma(t; \theta) \propto \sqrt{\frac{E(\theta)}{n_0}}\ t^{-3/2}\ . \label{eq:app:lorentzEvolution}
 \end{equation}
@@
 \begin{equation}
-	\tobs = t - \frac{\mu}{c} R(t,\theta) = (1-\mu)t + \frac{\mu}{16}\frac{t}{ \gamma^2(t,\theta)} \label{eq:tobs}
-\end{equation}
-Equation \eqref{eq:tobs} ignores the effect of cosmological redshift as it does not effect the closure relations.
+	\tobs = t - \frac{\mu}{c} R(t,\theta) = (1-\mu)t + \frac{\mu}{16}\frac{t}{ \gamma^2(t,\theta)} \label{eq:app:tobs}
+\end{equation}
+Equation \eqref{eq:app:tobs} ignores the effect of cosmological redshift as it does not effect the closure relations.
 
@@
 \begin{equation}
-	F_\nu \propto \Delta \Omega\ t^{3+s_t} \gamma^{-1+s_\gamma} \delta_s \delta^{2-\beta} \nuobs^\beta\ . \label{eq:fluxApprox}
-\end{equation}
-
-\begin{deluxetable}{CCCC}
-	\tablecaption{Dependence of $\varepsilon'_{\nu'} \propto \gamma^{s_\gamma} t^{s_t} \nu'^{\beta}$ in various spectral regimes. \label{tab:specSlopes}}
-	\tablehead{\colhead{Regime}& \colhead{$s_\gamma$} & \colhead{$s_t$} & \colhead{$\beta$}}
+	F_\nu \propto \Delta \Omega\ t^{3+s_t} \gamma^{-1+s_\gamma} \delta_s \delta^{2-\beta} \nuobs^\beta\ . \label{eq:app:fluxApprox}
+\end{equation}
+
+\begin{deluxetable}{CCCCC}
+	\tablecaption{Dependence of rest-frame synchrotron emissivity $\epsilon'_{\nu'}$ on Lorentz factor $\gamma$ and burster-frame time $t$: $\varepsilon'_{\nu'} \propto \gamma^{s_\gamma} t^{s_t} \nu'^{\beta}$ in various spectral regimes.
+\label{tab:specSlopes}}
+	\tablehead{\colhead{Regime}& \colhead{Label}& \colhead{$s_\gamma$} & \colhead{$s_t$} & \colhead{$\beta$}}
 	\startdata
-	\nu'<\nu'_m<\nu'_c     & 1 & 0 & 1/3 \\
-	\nu'_m<\nu'<\nu'_c     & (3p+1)/2 & 0 & (1-p)/2 \\
-	\nu'_m<\nu'_c<\nu'     & 3p/2 & -1 & -p/2 \\ 
-	\hline 
-	\nu' < \nu'_c < \nu'_m & 7/3 & 2/3 & 1/3 \\
-	\nu'_c < \nu' < \nu'_m & 3/2 & -1 & -1/2 \\
-	\nu'_c < \nu'_m < \nu' & 3p/2 & -1 & -p/2 \\ 
+	\nu'<\nu'_m<\nu'_c		& D	& 1 & 0 & 1/3 \\
+	\nu' < \nu'_c < \nu'_m 	& E	& 7/3 & 2/3 & 1/3 \\
+	\nu'_c < \nu' < \nu'_m 	& F	& 3/2 & -1 & -1/2 \\
+	\nu'_m<\nu'<\nu'_c     	& G	& (3p+1)/2 & 0 & (1-p)/2 \\
+	\nu'_m, \nu'_c < \nu' 		& H 	& 3p/2 & -1 & -p/2 \\ 
 	\enddata
@@
 Finally, for off-axis emission $t \propto \tobs$ and hence $\gamma \propto \tobs^{-3/2}$.
-For on-axis observers $\tobs \propto \gamma{-2} t \propto t^4$, hence $t\propto \tobs^{1/4}$ and $\gamma \propto \tobs^{-3/8}$.
+For on-axis observers $\tobs \propto \gamma^{-2} t \propto t^4$, hence $t\propto \tobs^{1/4}$ and $\gamma \propto \tobs^{-3/8}$.
 Giving finally:
@@
 
-At each moment during the structure phase the emission is dominated by material that just came on-axis, where $\gamma^{-1} = \chi = 2\sin (\psi/2) \approx \psi$.
+At each moment during the structure phase the emission is dominated by material that just came on-axis, where $\gamma^{-1} = \chi \equiv 2\sin (\psi/2) \approx \psi$.
 To find the overall behaviour we first determine $\tobs(\psi)$ and $F_\nu(\psi)$ for material whose emission is peaking (coming on-axis).
@@
 \begin{eqnarray}
-	\mu = 1 - \frac{1}{2}\chi^2 \ , \label{eq:muPsi}\\
-	\delta_s \approx \delta \approx \gamma = \chi^{-1} \ . \label{eq:deltaPsi}
+	\mu = 1 - \frac{1}{2}\chi^2 \ , \label{eq:app:muPsi}\\
+	\delta_s \approx \delta \approx \gamma = \chi^{-1} \ . \label{eq:app:deltaPsi}
 \end{eqnarray}
@@
 Along this line we have $\psi = \thobs - \theta$, and can use $\psi$ or $\theta$ interchangeably to denote latitude.
-From Equation \eqref{eq:lorentzEvolution} we have $t\propto E(\theta)^{1/3} \gamma^{-2/3}$.
-Using Equation \eqref{eq:tobs} and \eqref{eq:muPsi} we find that material at $\psi$ will come on-axis at observer time:
-\begin{equation}
-	\tobs(\psi) = \frac{9}{16} \chi^2 t \propto E(\theta)^{1/3} \chi^{8/3}\ . \label{eq:tobsPsi}
-\end{equation}
-The peak flux from material at $\psi$ can be determined from Equation \eqref{eq:fluxApprox}.
-Using Equation \eqref{eq:deltaPsi} and taking $\Delta \Omega \propto \gamma^{-\som}$ gives an observed flux:
-\begin{equation}
-	F_\nu(\psi) \propto t^{3+s_t} \gamma^{2+s_\gamma-\som-\beta} \nuobs^\beta \propto E(\theta)^{1+s_t/3} \chi^{-s_\gamma + 2 s_t/3 +\som+\beta} \nuobs^\beta  \ . \label{eq:FnuPsi}
-\end{equation}
-	Equations \eqref{eq:tobsPsi} and \eqref{eq:FnuPsi} describe the evolution of the flux in the structure phase in terms of the parameter $\psi$, which varies from $\mathrm{min} (0, \thobs-\thW)$ to $\thobs$.
-In principle one would like to invert Equation \eqref{eq:tobsPsi} and substitute into Equation \eqref{eq:FnuPsi} to obtain $F_\nu(\tobs)$ itself.
+From Equation \eqref{eq:app:lorentzEvolution} we have $t\propto E(\theta)^{1/3} \gamma^{-2/3}$.
+Using Equation \eqref{eq:app:tobs} and \eqref{eq:app:muPsi} we find that material at $\psi$ will come on-axis at observer time:
+\begin{equation}
+	\tobs(\psi) = \frac{9}{16} \chi^2 t \propto E(\theta)^{1/3} \chi^{8/3}\ . \label{eq:app:tobsPsi}
+\end{equation}
+The peak flux from material at $\psi$ can be determined from Equation \eqref{eq:app:fluxApprox}.
+Using Equation \eqref{eq:app:deltaPsi} and taking $\Delta \Omega \propto \gamma^{-\som}$ gives an observed flux:
+\begin{equation}
+	F_\nu(\psi) \propto t^{3+s_t} \gamma^{2+s_\gamma-\som-\beta} \nuobs^\beta \propto E(\theta)^{1+s_t/3} \chi^{-s_\gamma + 2 s_t/3 +\som+\beta} \nuobs^\beta  \ . \label{eq:app:FnuPsi}
+\end{equation}
+	Equations \eqref{eq:app:tobsPsi} and \eqref{eq:app:FnuPsi} describe the evolution of the flux in the structure phase in terms of the parameter $\psi$, which varies from $\mathrm{min} (0, \thobs-\thW)$ to $\thobs$.
+In principle one would like to invert Equation \eqref{eq:app:tobsPsi} and substitute into Equation \eqref{eq:app:FnuPsi} to obtain $F_\nu(\tobs)$ itself.
 Unfortunately, in general this is impossible to do in closed form because $E(\theta)$ is non-trivial.
 
-	We can obtain the temporal power law slope of the light curve by differentiating both Equations \eqref{eq:tobsPsi} and \eqref{eq:FnuPsi} with respect to $\psi$.
+	We can obtain the temporal power law slope of the light curve by differentiating both Equations \eqref{eq:app:tobsPsi} and \eqref{eq:app:FnuPsi} with respect to $\psi$.
 Noting that $dE/d\psi = -dE/d\theta$ and $d\chi/d\psi = \cos (\psi/2)$ we obtain for the individual derivatives:
@@
 \begin{eqnarray}
-	\frac{d \log F_\nu}{d \log \tobs}(\psi) = \frac{3 \beta - 3s_\gamma + 2s_t+3\som + (3+s_t)g(\psi)}{ 8+g(\psi)}  \label{eq:closure} \\
+	\frac{d \log F_\nu}{d \log \tobs}(\psi) = \frac{3 \beta - 3s_\gamma + 2s_t+3\som + (3+s_t)g(\psi)}{ 8+g(\psi)}  \label{eq:app:closure} \\
 	g(\psi) \equiv -2\tan(\psi/2) \frac{d \log E}{d \theta}\ .
@@
 
-Equation \eqref{eq:closure} is a generic expression for the temporal slope $\alpha$ for synchrotron emission from and relativistic, non-spreading, decelerating blast wave.
+Equation \eqref{eq:app:closure} is a generic expression for the temporal slope $\alpha$ for synchrotron emission from and relativistic, non-spreading, decelerating blast wave.
 In particular, if $g = 0$ and $\som = 2$ one recovers the standard pre-jet break slopes \citep{Granot:2002aa}.
@@
 \begin{align}
-	\nu_m (\psi) &\propto \left(1+z\right)^{-1}\left(\frac{p-2}{p-1}\right)^2 n_0^{1/2} \epse^2 \epsB^{1/2}  \chi^{-4} \label{eq:numPsi} \\
-	\nu_c (\psi)&\propto  \left(1+z\right)^{-1} n_0^{-5/6} \epsB^{-3/2} E(\theta)^{-2/3} \chi^{-4/3} \label{eq:nucPsi} \\
-	F_P(\psi)&\propto \left(1+z\right) \left(p-1\right)  d_L^{-2} n_0^{1/2} \epsB^{1/2} E(\theta)  \chi^{-2+\som} \label{eq:FPPsi}
+	\nu_m (\psi) &\propto \left(1+z\right)^{-1}\left(\frac{p-2}{p-1}\right)^2 n_0^{1/2} \epse^2 \epsB^{1/2}  \chi^{-4} \label{eq:app:numPsi} \\
+	\nu_c (\psi)&\propto  \left(1+z\right)^{-1} n_0^{-5/6} \epsB^{-3/2} E(\theta)^{-2/3} \chi^{-4/3} \label{eq:app:nucPsi} \\
+	F_P(\psi)&\propto \left(1+z\right) \left(p-1\right)  d_L^{-2} n_0^{1/2} \epsB^{1/2} E(\theta)  \chi^{-2+\som} \label{eq:app:FPPsi}
 \end{align}
@@
 \begin{align}
-F_D & \propto  (1+z)^{(38-5g-9\som)/3(8+g)} \epsilon_e^{-2/3} \epsilon_B^{1/3} n_0^{(6+4g+3\som)/3(8+g)} E_0^{(26-3\som)/3(8+g)} t_{obs}^{(-2+3\som+3g)/(8+g)} \nu^{1/3}  \\
-F_E & \propto  (1+z)^{(46-7g-9\som)/3(8+g)} \epsilon_B^{1} n_0^{(14+6g+3\som)/3(8+g)} E_0^{(34-3\som)/3(8+g)} t_{obs}^{(-14+9\som+11g)/3(8+g)} \nu^{1/3}  \\
-F_F & \propto  (1+z)^{(24-3g-6\som)/2(8+g)} \epsilon_B^{-1/4} n_0^{(-8+3g+4\som)/4(8+g)} E_0^{(8-\som)/(8+g)} t_{obs}^{(-8+3\som+2g)/(8+g)} \nu^{-1/2}  \\
-F_G & \propto  (1+z)^{\frac{(-pg-3g+4p-6\som+24)}{2(8+g)}} \epsilon_e^{p-1} \epsilon_B^{(1+p)/4} n_0^{(gp + 5 g + 4\som + 8)/4(8+g)} E_0^{(8+2p-\som)/(8+g)} t_{obs}^{3(-2p+\som+g)/(8+g)} \nu^{(1-p)/2}  \\
-F_H & \propto  (1+z)^{\frac{(-pg-2g+4p-6\som+20)}{2(8+g)}} \epsilon_e^{p-1} \epsilon_B^{(p-2)/4} n_0^{(gp+2g+4\som-8)/4(8+g)} E_0^{(6+2p-\som)/(8+g)} t_{obs}^{(-6p-2+3\som+2g)/(8+g)} \nu^{-p/2} 
+F_D & \propto  (1+z)^{(38-5g-9\som)/(24+3g)} \epsilon_e^{-2/3} \epsilon_B^{1/3} n_0^{(6+4g+3\som)/(24+3g)} E_0^{(26-3\som)/(24+8g)} t_{obs}^{(-2+3\som+3g)/(8+g)} \nu^{1/3}  \\
+F_E & \propto  (1+z)^{(46-7g-9\som)/(24+3g)} \epsilon_B^{1} n_0^{(14+6g+3\som)/(24+3g)} E_0^{(34-3\som)/(24+3g)} t_{obs}^{(-14+9\som+11g)/(24+3g)} \nu^{1/3}  \\
+F_F & \propto  (1+z)^{(24-3g-6\som)/(16+2g)} \epsilon_B^{-1/4} n_0^{(-8+3g+4\som)/(32+4g)} E_0^{(8-\som)/(8+g)} t_{obs}^{(-8+3\som+2g)/(8+g)} \nu^{-1/2}  \\
+F_G & \propto  (1+z)^{(-(p+3)g+4p-6\som+24)/(16+2g)} \epsilon_e^{p-1} \epsilon_B^{(1+p)/4} n_0^{(gp + 5 g + 4\som + 8)/(32+4g)} E_0^{(8+2p-\som)/(8+g)} \nonumber \\
+ 	& \qquad \times \tobs^{3(-2p+\som+g)/(8+g)} \nu^{(1-p)/2}  \\
+F_H & \propto  (1+z)^{(-(p+2)g+4p-6\som+20)/(16+2g)} \epsilon_e^{p-1} \epsilon_B^{(p-2)/4} n_0^{(gp+2g+4\som-8)/(32+4g)} E_0^{(6+2p-\som)/(8+g)} \nonumber \\
+	&\qquad \times \tobs^{(-6p-2+3\som+2g)/(8+g)} \nu^{-p/2} 
 \end{align}

### 2019-09-18 code/analyzeJetBreaks.py

@@ -1,0 +1,172 @@
+import sys
+import math
+import h5py as h5
+import numpy as np
+import matplotlib.pyplot as plt
+import afterglowpy as grb
+
+
+def loadData(filename):
+    filename = sys.argv[1]
+    f = h5.File(filename, "r")
+    Y = f['Y'][...]
+    tj_th = f['tj_tophat'][...]
+    tj_g = f['tj_gaussian'][...]
+    tj_pl2 = f['tj_powerlaw2'][...]
+    tj_pl6 = f['tj_powerlaw6'][...]
+    try:
+        thV = f['thV'][...]
+        thC = f['thC'][...]
+    except KeyError:
+        thV = np.linspace(0.0, 1.0, 11)
+        thC = np.linspace(0.04, 0.4, 11)
+    f.close()
+
+    E0 = Y[1]
+    n0 = Y[8]
+
+    tN = np.power(9*E0/(16*np.pi*grb.mp*n0*grb.c**5), 1.0/3.0)
+
+    return tN, thV, thC, tj_th, tj_g, tj_pl2, tj_pl6
+
+
+if __name__ == "__main__":
+
+    tN, thVs, thCs, tj_th, tj_g, tj_pl2, tj_pl6 = loadData(sys.argv[1])
+
+    tau_g = tj_g / tN
+    tau_pl2 = tj_pl2 / tN
+    tau_pl6 = tj_pl6 / tN
+
+    thCpVs = thCs[:, None] + thVs[None, :]
+    x = np.linspace(thCpVs.min(), thCpVs.max(), 100)
+
+    num = math.pow(0.15, 3.0/8.0)
+
+    chi = np.maximum(1.18*thCs[:, None], 0.53*(thCs[:, None] + thVs[None, :]))
+    color = ['C{0:d}'.format(i) for i in range(10)]
+
+    fig, ax = plt.subplots(3, 2, figsize=(8, 9))
+    ax[0, 0].plot(thCs, thCs, color='grey', ls='--')
+    ax[0, 0].plot(thCs, num*thCs, color='grey', ls=':')
+    ax[1, 0].plot(thVs, thVs, color='grey', ls='--')
+    ax[1, 0].plot(thVs, num*thVs, color='grey', ls=':')
+    for j in range(len(thVs)):
+        ax[0, 0].plot(thCs, chi[:, j], alpha=0.5, color=color[j % 10])
[…]

### 2019-09-18 code/gEffFit.py

@@ -90,6 +90,9 @@ for i in range(Nb):
     ax.plot(thV, gmed, color=cs[i], marker='o')
 ax.set_xscale('log')
 ax.set_yscale('log')
+ax.set_xlabel(r'$\theta_{\mathrm{obs}}$')
+ax.set_ylabel(r'$g$')
+
 
 coeffs = []
 
@@ -122,6 +125,8 @@ for i in range(Nb):
     ax2.plot(thVoC, g2med, color=cs[i], marker='o')
 ax2.set_xscale('log')
 ax2.set_yscale('log')
+ax2.set_xlabel(r'$\theta_{\mathrm{obs}} / \theta_{\mathrm{c}}$')
+ax2.set_ylabel(r'$\theta_{\mathrm{obs}}^2 / \theta_{\mathrm{c}}^2 times 1/g$')
 # ax2.set_ylim(0, 30)
 
 coeffs = np.array(coeffs)
@@ -136,8 +141,9 @@ fig5, ax5 = plt.subplots(coeffs.shape[1], 1, figsize=(6, 6))
 B = np.linspace(b.min()-1, b.max()+1, 100)
 for i in range(coeffs.shape[1]):
     try:
-        res = opt.curve_fit(f_apbxp, b, coeffs[:, i], [0.0, 0.0, 0.0])
+        res = opt.curve_fit(f_apbxp, b, coeffs[:, i], [0.0, 0.0, -1.0])
     except RuntimeError:
+        print("Runtime Error")
         res = (np.zeros(3), )
 
     print(res[0])
@@ -184,5 +190,40 @@ for i in range(Nb):
 ax4.set_xscale('log')
 ax4.set_yscale('log')
 """
+
+fig6, ax6 = plt.subplots(1, 1, figsize=(8, 6))
+
+coeffs2 = []
+
+for l in range(NVC):
+
+    for k in range(NC):
+        good = (athV/athC == thVoC[l]) & (athC == thC[k])
+        if good.any():
+            sortInds = np.argsort(ab[good])
+            ax6.plot(ab[good][sortInds],
+                     ag[good][sortInds] / (0.25*thVoC[l]**2),
+                     marker=ms[k], alpha=0.4, ls='')
+    gmed = np.empty(Nb)
+    for i in range(Nb):
+        good = (athV/athC == thVoC[l]) & (ab == b[i])
+        if good.any():
[…]

### 2019-09-18 code/paperPlots.py

@@ -1077,6 +1077,25 @@ def calcTN0(Y, aE0=1.0, an0=1.0):
     return tN0
 
 
+def calcTC(jetModel, Y, regime):
+
+    thV = Y[0]
+    thC = Y[2]
+    thW = Y[3]
+    b = Y[4]
+    p = Y[9]
+
+    if thC >= thV:
+        return 0.0
+
+    f = get_f(jetModel, thC, thW, b)
+    tN0 = calcTN0(Y)
+
+    tC = np.asscalar(calc_tp(thC, tN0, thV, f, regime, p))
+
+    return tC
+
+
 def calcTW(jetModel, Y, regime):
 
     thV = Y[0]

### 2019-09-18 code/plotClosureThv.py

@@ -28,8 +28,8 @@ def plotOnAxes(ax, jetType, Y, regime, thVs=None, thCs=None, thWs=None,
 thV = 0.0
 E0 = 1.0e53
 thC = 0.05
-thW = 4*thC
-b = 10
+thW = 6*thC
+b = 4
 L0 = 0
 ts = 0
 q = 0
@@ -53,30 +53,33 @@ figG, axG = plt.subplots(1, 1)
 figPL, axPL = plt.subplots(1, 1)
 
 colors = ['C0', 'C1', 'C2', 'C3', 'C4', 'C5']
-thVs = [thC, 2*thC, 4*thC, 6*thC, 8*thC]
+thVs = np.array([thC, 2*thC, 4*thC, 6*thC, 8*thC])
 thV = 0.3
-thCs = [thV/8, thV/6, thV/4, thV/2, thV]
+thCs = np.array([thV/8, thV/6, thV/4, thV/2])
 
 # for i, thV in enumerate(thVs):
 for i, thC in enumerate(thCs):
- 
+
     Y[0] = thV
     Y[2] = thC
+
+    Y[3] = thV-0.05
 
     alG = pp.calcSlopeStructEff(0, Y, 'G')
     alPL = pp.calcSlopeStructEff(4, Y, 'G')
 
     tb = 0.2 * np.power(9*E0/(16*np.pi*n0*grb.mp*grb.c**5), 1.0/3.0)\
         * np.power(2*np.sin(0.5*(thC+thV)), 8.0/3.0)
+    t0 = tb / 5
 
-    ib = np.searchsorted(t, tb)
+    i0 = np.searchsorted(t, t0)
 
     Fnu = grb.fluxDensity(t, nu, 0, 0, *Y)
     # axG.plot(t/tb, Fnu/Fnu[ib], color=colors[i])
     # axG.plot(t/tb, np.power(t/tb, alG),
     #          color=colors[i], ls='--')
     axG.plot(t, Fnu, color=colors[i])
-    axG.plot(t, 1.5*Fnu[ib] * np.power(t/tb, alG),
+    axG.plot(t, Fnu[i0] * np.power(t/t0, alG),
              color=colors[i], ls='--', lw=3.0, alpha=0.5)
 
     Fnu = grb.fluxDensity(t, nu, 4, 0, *Y)
@@ -84,7 +87,7 @@ for i, thC in enumerate(thCs):
     # axPL.plot(t/tb, np.power(t/tb, alPL),
[…]

### 2019-09-18 code/plotJetBreaks.py

@@ -1,0 +1,523 @@
+import sys
+import math
+import numpy as np
+import scipy.optimize as opt
+import h5py as h5
+import matplotlib.pyplot as plt
+import afterglowpy as grb
+import paperPlots as pp
+
+
+def f_pl2(t, t0, F0, b0, b1):
+    F = np.empty(t.shape)
+    A = t <= t0
+    B = ~A
+    F[A] = F0*np.power(t[A]/t0, b0)
+    F[B] = F0*np.power(t[B]/t0, b1)
+    return F
+
+
+def lf_pl2(t, lt0, lF0, b0, b1):
+    t0 = math.pow(10.0, lt0)
+    F0 = math.pow(10.0, lF0)
+    return f_pl2(t, t0, F0, b0, b1)
+
+
+def f_spl2(t, t0, F0, b0, b1, s):
+    F = F0 * np.power(t/t0, b0) * np.power(0.5 * (1 + np.power(t/t0, s)),
+                                           (b1-b0)/s)
+    return F
+
+
+def lf_spl2(t, lt0, lF0, b0, b1, ls):
+    t0 = math.pow(10.0, lt0)
+    F0 = math.pow(10.0, lF0)
+    s = math.pow(10.0, ls)
+
+    return f_spl2(t, t0, F0, b0, b1, s)
+
+
+def chi2(x, t, F, f):
+    y = x.copy()
+    Fm = f(t, *y)
+    dF = (F-Fm)/(0.1*F)
+    return (dF*dF).sum()
+
+
+def betaRegime(regime, Y):
+
+    p = Y[9]
+    if regime == 'D':
+        return 1.0/3.0
+    elif regime == 'E':
+        return 1.0/3.0
+    elif regime == 'F':
+        return -0.5
+    elif regime == 'G':
+        return 0.5*(1.0-p)
+    else:
+        return -0.5*p
+
+
+def findJetBreak(jetType, Y, Z, regime, NU, printMode=None, returnAll=False,
+                 ax=None):
+
+    tN0 = pp.calcTN0(Y)
+    tb = 10*tN0
+
+    thV = Y[0]
+    thC = Y[2]
+    thW = Y[3]
+
+    chip = 2*math.sin(0.5*(thC+thV))
+
+    tj_guess = 0.24 * tN0 * math.pow(chip, 8.0/3.0)
+
+    if jetType == -1:
+        if thV <= thC:
+            ta = 1.0e-3 * tj_guess
+        else:
[…]

### 2019-09-19 structuredJets.tex
Wrote jetbreak section, added plots

@@
 \newcommand{\tW}{\ensuremath{t_{\mathrm{w}}}}
+\newcommand{\tNR}{\ensuremath{t_{\mathrm{NR}}}}
 \newcommand{\tb}{\ensuremath{t_{\mathrm{b}}}}
@@
 \newcommand{\tbpm}{\ensuremath{t_{\mathrm{b\pm}}}}
+\newcommand{\tbin}{\ensuremath{t_{\mathrm{b, in}}}}
+\newcommand{\tbout}{\ensuremath{t_{\mathrm{b, out}}}}
 \newcommand{\tdec}{\ensuremath{t_{\mathrm{dec}}}}
@@
 
-\subsection{Structured Phase: Closure Relations and Break Times}\label{subsec:structure}
+\subsection{Structured Phase: Closure Relations}\label{subsec:structure}
 
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{figs/slopesJet.png}
-	\caption{Temporal slopes for the off-axis structured jet as a function of the structure parameter $g$ for the synchrotron spectral regimes D (blue, narrow), E (orange, narrow),  F (green, narrow), G (red, wide), and H (purple, wide).
-The width of the G and H bands shows the dependency on $p$, the upper curves for $p=2$ and the lower for $p=3$.
+	\includegraphics[width=\columnwidth]{figs/slopesStruct.pdf}
+	\caption{Temporal slopes $\alpha_{\mathrm{struct}}$ (defined as $F_\nu \propto \tobs^{\alpha}$) for the \emph{structured} phase as a function of the structure parameter $g$ for the synchrotron spectral regimes D (blue, narrow), E (orange, narrow),  F (green, narrow), G (red, wide), and H (purple, wide).
+The width of the G and H bands shows the dependency on $p$, the upper limit for $p=2$, the lower for $p=3$, and the thick internal line for $p=2.2$.
 The temporal power law slope of a structured jet afterglow increases with $g$ in all spectral regimes.
@@
 
-A viewer outside the truncation angle, $\thobs > \thW$, may observe a steeply rising far-off-axis phase.
-This phase transitions to the structured phase once the near edge of the jet enters the beaming cone: $\gamma^{-1}(\thW) \sim \thobs-\thW$.
+\subsection{Structured Phase: Break Times}\label{subsec:structureBreak}
+
+The break times, the times when an afterglow light curve transitions from one phase to another, scale with the blast wave parameters in a well-defined way.
+Firstly, a convenient characteristic time scale is the non-relativistic time $\tNR$, the time at which the core of the jet would become non-relativistic in the absence of spreading:
+\begin{align}
+	\tNR &= (1+z) \left( \frac{9}{16\pi} \frac{E_0}{\rho_0 c^5} \right)^{1/3}  \label{eq:tNRdef} \\
+	&= 882 \ (1+z) E_{53}^{1/3}n_0^{-1/3} \mathrm{ days}\ . \nonumber
+\end{align}
+In Equation \eqref{eq:tNRdef} $E_{53} = E_0 / (10^{53}$ erg) and $n_0$ is the circumburst density measured in cm$^{-3}$.
+While the jet is relativistic any time scale will depend on $E_0$ and $n_0$ only through $\tNR$.
+
+For viewers outside the truncation angle, $\thobs > \thW$, the transition from the far-off-axis phase to the structured phase occurs at $\tW$ (see rightmost panel of Figure \ref{fig:phaseSketch}).
+The transition marks when the observers enters the beaming cone of the near edge of the jet: $\gamma^{-1}(\thW) \sim \thobs-\thW$.
 This will occur at observer time:
-\begin{equation}
-	\tW = \left(\frac{9}{16\pi} \frac{E(\thW)}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thobs-\thW}{2}\right)\right)^{8/3} \ .\label{eq:tw}
-\end{equation}
-
-The jet break is the time at which the effective angular size of the jet ceases to increase, $\som = 0$.
-For an on-axis observer of a top hat jet, this is when the jet edges come into view.
+\begin{align}
+	\tW &= \tNR \left(E(\thW) / E_0\right)^{1/3} \left( \thobs-\thW \right)^{8/3}  \label{eq:tw} \\
+	&= 12.1 \ (1+z) E_{53}^{1/3} n_0^{-1/3} \nonumber \\
+	& \qquad \times \left(\frac{E(\thW) }{ E_0}\right)^{1/3} \left( \frac{\thobs-\thW}{0.2\ \mathrm{ rad}} \right)^{8/3}  \mathrm{ days}\ .
+\end{align}
+The factor of $(E(\thW) / E_0)^{1/3}$ in $\tW$ compensates for the lower Lorentz factor (and hence larger beaming cone) in the wings of the jet relative to the core.
+It depends only on geometric parameters (e.g.
+$\thC$, $\thW$, and $b$) and may be much smaller than 1.
+
+The \emph{jet break} $\tb$ is the time at which the effective angular size of the jet ceases to increase: $\som = 0$.
+For an on-axis observer of a top hat jet, in the absence of spreading, this is when the jet edges come into view.
 More generally, this is the moment when the blast wave has sufficiently decelerated that the viewer is within the beaming cones of its brightest regions.
@@
 
-It is long established that on-axis viewers observe the jet break in their frame at a time $\tb \propto \thC^{8/3}$ (e.g.
+To determine the normalization and scaling for the observed jet break time $\tb$ we computed a grid of afterglow light curves for Gaussian, $b=2$ power law, and $b=6$ power law jets, varying $\thC$ and $\thobs$.
+We used 11 values each for $\thC$ between 0.04 rad and 0.40 rad and $\thobs$ between 0 rad and 1.0 rad.
+The truncation angle $\thW$ was set to $10 \thC$, and all other parameters were fixed.
+Each light curve was fit with a smoothly broken power law $F_\nu \propto (\tobs/\tb)^{\alpha_1} [(1+(\tobs/\tb)^s)/2]^{(\alpha_2-\alpha_1)/s}$ in the region surrounding the jet break to identify the precise break time $\tb$.
+
+\begin{figure*}
+	\plottwo{figs/jetbreak_OnAxis.pdf}{figs/jetbreak_OffAxis.pdf}
+	\caption{Jet break time $t_b$ for Gaussian (green solid line), $b=2$ power law (orange dash-dotted line), and $b=6$ power law (red dotted line) jets.
+The left panel shows $t_b$ as a function of $\thC$ for on-axis (\thobs=0) observers.
+The right panel shows $t_b$ as a function of $\thobs$: the lower, middle, and upper curves correspond to $\thC = $ 0.04 rad, 0.184 rad, and 0.328 rad respectively.
+The dashed grey line is the analytic approximation Equation \eqref{eq:tb}.
+Each break time was determined by fitting a smoothly broken power law to an \afterglowpy{} light curve.
+\label{fig:tb}}
+\end{figure*}
+
+Figure \ref{fig:tb} shows the extracted jet break times from \afterglowpy{} light curves for several jet structure models.
+The left panel shows $\tb$ as a function of $\thC$ for on-axis ($\thobs=0$) viewers, while the right panel shows $\tb$ as a function of $\thobs$ for 3 particular values of $\thC$.
+The scale for $\tb$ has been normalized by $\tNR$, isolating the variation due to structure geometry and viewing angle.
+The different structure models show remarkably tight agreement, particularly as $\thobs \to 0$.
+This is primarily due to the shared definition of $\thC$.
+As $\thobs \to 1$ rad the power law jets show a slight increase relative to the Gaussian jet, particularly for the larger $\thC$.
+
+It has been long established that on-axis viewers observe the jet break in their frame at a time $\tb \propto \thC^{8/3}$ (e.g.
 \citet{Rhoads:1999aa}), while significantly off-axis viewers observe the jet break at $\tb \propto \thobs^{8/3}$ \citep{Rossi:2002aa, Panaitescu:2003aa}.
 More generally, for initially top hat jets it has been shown the jet break corresponds to the far jet edge coming into view, that is $\tb \propto (\thC + \thobs)^{8/3}$ \citep{van-Eerten:2010aa}.
-We find this latter result to hold true for structured jets as well.
+We find this latter result to hold approximately true for structured jets as well.
 As $\thC$ denotes the angular size of the bright jet core, once this time is reached the jet is essentially entirely in view.
@@
 
-In our single shell approximation, then, the jet break occurs near:
-\begin{equation}
-	\tb = \left(\frac{9}{16\pi} \frac{E_0}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thobs+\thC}{2}\right)\right)^{8/3} \ .\label{eq:tb}
-\end{equation}
+We find $\tb(\thC, \thobs)$ to show two modes of behaviour, split roughly by the whether the viewer is aligned ($\thobs < \thC$) or misaligned ($\thobs > \thC$).
+Aligned viewing shows $\tb$ to follow $\thC^{8/3}$ quite strongly with very little dependence on $\thobs$.
+Misaligned viewing better tracks with $(\thC + \thobs)^{8/3}$, although there are discrepancies for very large viewing angles.
+
+A good fit for $\tb$ to the full grid of models is obtained by taking the maximum of the aligned $\tbin$ and misaligned $\tbout$ relations:
+\begin{equation}
+	\tb = \max(\tbin,\  \tbout)\ , \label{eq:tb}
+\end{equation}
+where
+\begin{align}
+	\tbin &= 1.55\ \tNR \thC^{8/3} \label{eq:tbin}\\
+		&= 2.95\ E_{53}^{1/3} n_0^{-1/3} \left(\frac{\thC}{0.1\ \mathrm{rad}}\right)^{8/3}\ \mathrm{days}\ , \nonumber \\
+	\tbout &= 0.184\ \tNR (\thC+\thobs)^{8/3} \label{eq:tbout} \\
+		&= 6.54\ E_{53}^{1/3} n_0^{-1/3} \left(\frac{\thC+\thobs}{0.3\ \mathrm{rad}}\right)^{8/3}\ \mathrm{days}\ . \nonumber 			
+\end{align}
+
+Figure \ref{fig:tb} also shows Equation \eqref{eq:tb} compared to the measured jet break times.
+The on-axis relation $\tbin$ fits very well over the span of $\thC$ considered, with a mean fractional error of 0.053.
+Over the full $\thC$ and $\thobs$ domain the mean fractional error is 0.17, with the largest contributions coming from wide jets (e.g.
+the upper curve, $\thC = 0.328$ rad, in Figure \ref{fig:tb}) at viewing angles $\thobs > 0.8$ rad.
 
@@
 % DROP OR DEFINE t_N
-\begin{figure}
-	\includegraphics[width=\columnwidth]{figs/jetbreak_OnAxis.pdf}
-	\caption{Jet break time for on-axis ($\thobs=0$) observers for top-hat (blue circles), Gaussian (orange squares), and power law (green triangles) jets as a function of $\thC$.
-The dashed grey line is the analytic approximation $\tbpm = t_N (2\sin \thC/2)^{8/3}$.
-These particular light curves use $\thW = 5 \thC$, $E_0 = 10^{52}$erg, $n_0=10^{-3}$cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, and $\epsB = 10^{-4}$.
+%\begin{figure}
+%	\includegraphics[width=\columnwidth]{figs/jetbreak_OnAxis.pdf}
+%	\caption{Jet break time for on-axis ($\thobs=0$) observers for Gaussian (green solid line),  $b=2$ power law (orange dash-dotted line), and $b=6$ power law (red dotted line) jets as a function of $\thC$.
+The dashed grey line is the analytic approximation $\tb = 1.55 t_N (\thC/1 rad)^{8/3}$.
 \label{fig:tbOA}}
-\end{figure}
-
-Figure \ref{fig:tbOA} shows the observed jet break time $\tb$ for on-axis, $\thobs=0$ viewers, as a function of core half-width $\thC$ for several structure models.
-The expected scaling with $\thC^{8/3}$ is observed, although as seen in Figure \ref{fig:thVmodel} there is some model-dependent offset due to the particular shape of the wings.
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{figs/jetbreak_OffAxis.pdf}
-	\caption{Jet break time for off-axis ($\thobs\neq0$) observers for top-hat (blue circles), Gaussian (orange squares), and power law (green triangles) jets as a function of $\thC$.
-The dashed grey line is the analytic approximation $\tbpm = t_N (2\sin \thobs/2)^{8/3}$.
-These particular light curves use $\thW = 5 \thC$, $E_0 = 10^{52}$erg, $n_0=10^{-3}$cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, and $\epsB = 10^{-4}$.
-\label{fig:tbG}}
-\end{figure}
-
-Figure \ref{fig:tbG} shows the observed jet break time for generic viewers of various structure models.
-At small viewing angles $\tb$ only depends linearly on $\thobs$, but asymptotically approaches $\thobs^{8/3}$ as $\thobs \gg \thC$.
+%\end{figure}
 

### 2019-09-19 code/analyzeJetBreaks.py

@@ -43,8 +43,70 @@ if __name__ == "__main__":
 
     num = math.pow(0.15, 3.0/8.0)
 
+    chiOnCoeff = 1.18
+    chiOffCoeff = 0.53
+
     chi = np.maximum(1.18*thCs[:, None], 0.53*(thCs[:, None] + thVs[None, :]))
     color = ['C{0:d}'.format(i) for i in range(10)]
+
+    E53 = 1.0e53
+    E50 = 1.0e50
+    n00 = 1.0
+    nm3 = 1.0e-3
+    th0p1 = 0.1
+    th0p2 = 0.2
+    th0p3 = 0.3
+
+    coeff_On_53_00_0p1_s = math.pow(9*E53/(16*math.pi*grb.mp*n00*grb.c**5),
+                                    1.0/3.0) * math.pow(chiOnCoeff * th0p1,
+                                                        8.0/3.0)
+    coeff_On_53_00_0p1_d = coeff_On_53_00_0p1_s * grb.sec2day
+    coeff_Off_53_00_0p1_s = math.pow(9*E53/(16*math.pi*grb.mp*n00*grb.c**5),
+                                     1.0/3.0) * math.pow(chiOffCoeff * th0p1,
+                                                         8.0/3.0)
+    coeff_Off_53_00_0p1_d = coeff_Off_53_00_0p1_s * grb.sec2day
+    coeff_Off_53_00_0p2_s = math.pow(9*E53/(16*math.pi*grb.mp*n00*grb.c**5),
+                                     1.0/3.0) * math.pow(chiOffCoeff * th0p2,
+                                                         8.0/3.0)
+    coeff_Off_53_00_0p2_d = coeff_Off_53_00_0p2_s * grb.sec2day
+    coeff_Off_53_00_0p3_s = math.pow(9*E53/(16*math.pi*grb.mp*n00*grb.c**5),
+                                     1.0/3.0) * math.pow(chiOffCoeff * th0p3,
+                                                         8.0/3.0)
+    coeff_Off_53_00_0p3_d = coeff_Off_53_00_0p3_s * grb.sec2day
+
+    coeff_On_50_m3_0p1_s = math.pow(9*E50/(16*math.pi*grb.mp*nm3*grb.c**5),
+                                    1.0/3.0) * math.pow(chiOnCoeff * th0p1,
[…]

### 2019-09-19 code/plotClosure.py

@@ -557,43 +557,48 @@ def makeNicePlot(t, thV, thC, thW, E0, n0, p, jetType, seg):
 """
 
 
-def plotSlopes(p, s3, name):
+def plotSlopes(p, som, varName, name):
 
-    g = np.linspace(0, 10, 200)
+    g = np.linspace(0, 20, 200)
 
     segs = ['D', 'E', 'F', 'G', 'H']
+    segLabel = [r'D ($\nu < \nu_m < \nu_c$)', r'E ($\nu < \nu_c < \nu_m$)',
+                r'F ($\nu_c < \nu < \nu_m$)', r'G ($\nu_m < \nu < \nu_c$)',
+                r'H ($\nu_m,\nu_c < \nu$)']
 
     fig, ax = plt.subplots(1, 1)
 
     colors = ['tab:blue', 'tab:orange', 'tab:green', 'tab:red', 'tab:purple']
 
     for i, seg in enumerate(segs):
-        s1_p2 = em_slope_g(2.0, seg)
-        s2_p2 = em_slope_t(2.0, seg)
+        sg_p2 = em_slope_g(2.0, seg)
+        st_p2 = em_slope_t(2.0, seg)
         be_p2 = sync_slope(2.0, seg)
 
-        s1 = em_slope_g(p, seg)
-        s2 = em_slope_t(p, seg)
+        sg = em_slope_g(p, seg)
+        st = em_slope_t(p, seg)
         be = sync_slope(p, seg)
 
-        s1_p3 = em_slope_g(3.0, seg)
-        s2_p3 = em_slope_t(3.0, seg)
+        sg_p3 = em_slope_g(3.0, seg)
+        st_p3 = em_slope_t(3.0, seg)
         be_p3 = sync_slope(3.0, seg)
 
-        s = (2*(3+s2)-3*(2+s3+s1-be)+(3+s2)*g) / (8+g)
-        s_p2 = (2*(3+s2_p2)-3*(2+s3+s1_p2-be_p2)+(3+s2_p2)*g) / (8+g)
-        s_p3 = (2*(3+s2_p3)-3*(2+s3+s1_p3-be_p3)+(3+s2_p3)*g) / (8+g)
+        s = (3*be - 3*sg + 2*st + 3*som + (3+st)*g) / (8+g)
+        s_p2 = (3*be_p2 - 3*sg_p2 + 2*st_p2 + 3*som + (3+st_p2)*g) / (8+g)
[…]

### 2019-09-19 code/plotClosureThv.py

@@ -1,34 +1,14 @@
 import numpy as np
+import matplotlib as mpl
 import matplotlib.pyplot as plt
 import afterglowpy as grb
 import paperPlots as pp
 
-"""
-def plotOnAxes(ax, jetType, Y, regime, thVs=None, thCs=None, thWs=None,
-               name=None):
-
-    if thVs is None and thCs is None and thWs is None:
-        return
-
-    N = 0
-    if thVs is not None:
-        N = max(N, len(thVs))
-    if thCs is not None:
-        N = max(N, len(thCs))
-    if thWs is not None:
-        N = max(N, len(thWs))
-
-    for i in range(N):
-        if thVs is not None:
-            Y[0] = thVs[i]
-        if thCs is not None:
-            Y[2] = thCs[i]
-"""
 
 thV = 0.0
 E0 = 1.0e53
 thC = 0.05
-thW = 6*thC
+thW = 5*thC
 b = 4
 L0 = 0
 ts = 0
@@ -44,6 +24,10 @@ z = 0.5454
 Y = np.array([thV, E0, thC, thW, b, L0, ts, q, n0, p, epse, epsB, xiN, dL])
 Z = {'z': z, 'spread': True}
 
+Y2 = Y.copy()
+Y2[4] = 2
+Y6 = Y.copy()
+Y6[4] = 6
 
 t = np.geomspace(1.0e3, 1.0e8, 100)
 nu = np.empty(t.shape)
@@ -52,10 +36,29 @@ nu[:] = 1.0e14
 figG, axG = plt.subplots(1, 1)
 figPL, axPL = plt.subplots(1, 1)
 
+width = 7.5
+height = 3
+
+figM = plt.figure(figsize=(width, height))
+gs = figM.add_gridspec(1, 3, wspace=0.0)
+axMG = figM.add_subplot(gs[0])
+axMPL2 = figM.add_subplot(gs[1])
+axMPL6 = figM.add_subplot(gs[2])
+
 colors = ['C0', 'C1', 'C2', 'C3', 'C4', 'C5']
 thVs = np.array([thC, 2*thC, 4*thC, 6*thC, 8*thC])
 thV = 0.3
 thCs = np.array([thV/8, thV/6, thV/4, thV/2])
+
+solid_line = mpl.lines.Line2D([], [], ls='-', color='grey')
[…]

### 2019-09-19 code/plotJetBreaks.py

@@ -492,12 +492,12 @@ if __name__ == "__main__":
     findJetBreak(-1, Y, Z, regime, NU, printMode='all', ax=ax)
     """
 
-    # thVs = np.linspace(0.0, 1.0, 11)
-    thVs = [0.0]
-    thVs.extend(np.geomspace(1.0e-2, 1.0, 12))
-    thVs = np.array(thVs)
+    thVs = np.linspace(0.0, 1.0, 11)
+    # thVs = [0.0]
+    # thVs.extend(np.geomspace(1.0e-2, 1.0, 12))
+    # thVs = np.array(thVs)
     thCs = np.linspace(0.04, 0.4, 11)
-    thWs = 10*thCs
+    thWs = 5*thCs
     thWs[thWs > 0.5*np.pi] = 0.5*np.pi
 
     """

### 2019-09-19 structuredJets.tex
Added closure plot!

@@
 
-The $g$ parameter evolves with time as $\theta^*$ sweeps from the jet edge to the core.
-This produces deviations in the light curve from a pure power law.
-However, we find ultimately these deviations are not too large and the average slope is well approximated by $\geff  = g(\theff)$, where $\theff$ is a fiducial angular section which depends on viewing angle and potentially other structure parameters.
-For the Gaussian model $\theff$ is simply half the viewing angle, for the power law model a suitable fitting function was found through comparison to a grid of \afterglowpy{} light curves:
-\begin{align}
-	\theff &= \frac{\thobs}{2}&& \text{Gaussian} \\
-	\theff &= \thobs \big [1.8+2.1b^{-1.25}  && \text{power law} \nonumber  \\
-	 	& \qquad + (0.49-0.86b^{-1.15}) \thobs/\thC \big ] ^{-1/2} &&\label{eq:theff}
-\end{align}
-In the expressions for $\geff$ it is reasonable to assume $2 \tan((\thobs-\theff)/2) \approx \thobs-\theff$ leading to the manageable expressions:
-\begin{align}
-	\geff &= \frac{\thobs^2}{4\thC^2} && \text{Gaussian}\ , \\
-	\geff &= \frac{2 b (\thobs-\theff)\theff}{b \thC^2+\theff^2} && \text{power law}\ . \label{eq:geff}
-\end{align}
-These values may be used in Table \ref{tab:slopes} for an approximate power law model of a structured jet with an appropriate viewing angle dependent temporal evolution.
-These analytic results are in agreement with previous work on structured jets \citep{Rossi:2004aa} and the trans-relativistic numerical model described in Section \ref{sec:numerical}.
-
-In the structured phase, the temporal slope depends directly on the ratio $\thobs/\thC$.
-Therefore any measurement of the effective power law slope of an afterglow light curve in the structured phase can be used to measure this parameter.
-
 \begin{figure}
@@
 
-Figure \ref{fig:slopesG} shows the structured phase power law temporal slope as a function of $g$ for spectral regimes $D$--$H$.
-In the $G$ and $H$ regimes the spectral slope is a function of $p$, this dependence carries over into the temporal slope as well.
-The temporal slope is an increasing function of $g$ in all regimes.
+Figure \ref{fig:slopesG} shows the structured phase power law temporal slope $\alpha_{\mathrm{struct}}$ as a function of $g$ for spectral regimes $D$--$H$.
+In the $G$ and $H$ regimes the spectral slope $\beta$ is a function of $p$, this dependence carries over into the temporal slope as well.
+The temporal slope $\alpha_{\mathrm{struct}}$ is an increasing function of $g$ in all regimes.
 At sufficiently large $g$ all regimes exhibit rising light curves, the specific $g$ at which the light curve begins to rise is regime dependent.
+
+The $g$ parameter evolves with time as $\theta^*$ sweeps from the jet edge to the core.
+This produces deviations in the light curve from a pure power law.
+However, we find ultimately these deviations are not too large and the average slope is well approximated by $\geff  = g(\theff)$, where $\theff$ is a fiducial angular section which depends on viewing angle and potentially other structure parameters.
+For the Gaussian model $\theff$ is simply half the viewing angle, for the power law model a suitable fitting function was found through comparison to a grid of \afterglowpy{} light curves:
+\begin{align}
+	\theff &= \frac{\thobs}{2}&& \text{Gaussian} \\
+	\theff &= \thobs \big [1.8+2.1b^{-1.25}  && \text{power law} \nonumber  \\
+	 	& \qquad + (0.49-0.86b^{-1.15}) \thobs/\thC \big ] ^{-1/2} &&\label{eq:theff}
+\end{align}
+In the expressions for $\geff$ it is reasonable to assume $2 \tan((\thobs-\theff)/2) \approx \thobs-\theff$ leading to the manageable expressions:
+\begin{align}
+	\geff &= \frac{\thobs^2}{4\thC^2} && \text{Gaussian}\ , \\
+	\geff &= \frac{2 b (\thobs-\theff)\theff}{b \thC^2+\theff^2} && \text{power law}\ . \label{eq:geff}
+\end{align}
+These values may be used in Table \ref{tab:slopes} for an approximate power law model of a structured jet with an appropriate viewing angle dependent temporal evolution.
+
+\begin{figure*}
+	\includegraphics[width=\textwidth]{figs/lc_closure_multi.pdf}
+	\caption{Optical afterglow light curves in the \emph{structured} phase with corresponding closure relation slopes $\alpha_{\mathrm{struct}}$.
+Each panel shows light curves with $\thobs/\thC$ = 2, 4, 6, and 8 (solid lines in red, green, orange, and blue respectively) calculated with \afterglowpy{} and corresponding power law segments $F_\nu \propto \tobs^{\alpha_{\mathrm{struct}}}$ calculated from the closure relations in Table \ref{tab:slopes} and the $\geff$ values from Equation \eqref{eq:geff}.
+The left panel shows a Gaussian jet, the middle a $b=2$ power law jet, and the right a $b=6$ power law jet.
+The closure relations $\alpha_{\mathrm{struct}}$ capture the approximate power law slope of the numerical light curves, with the agreement improving for larger values of $\thobs/\thC$.
+The light curves use a fixed $\thobs$ = 0.3 rad, $\thW = 0.25$ rad, and vary $\thC$.
+Other parameters are fixed: $E_0 = 10^{53}$ erg, $n_0=10^{-3}$ cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, $\epsB = 10^{-3}$, $d_L=10^{28}$ cm and $z=0.5454$.
+\label{fig:closure}}
+\end{figure*}
+
+Figure \ref{fig:closure} shows \afterglowpy{} light curves for Gaussian, $b=2$ power law, and $b=6$ power law jets at various values of $\thobs / \thC$ and the corresponding $\alpha_{\mathrm{struct}}$ slopes calculated using $\geff$.
+The analytic closure relations capture the light curve behaviour in the structured phase for all 3 models, with somewhat better agreement at larger values of $\thobs/\thC$.
+The Gaussian jet, with its strong energy gradient, is most sensitive to changes in $\thobs/\thC$.
+The $b=6$ power law, with its more energetic wings, displays less sensitivity to changes in $\thobs/\thC$.
+The $b=2$ power law displays almost no variation at all in the temporal decay rate.
+The overall behaviour of the Gaussian and $b=2$ power law jets are in agreement with \citet{Rossi:2004aa} (R04, see for comparison their Figure 12 and 16).
+Their $\thobs/\thC = 4$ Gaussian jet showed a mildly decaying slope instead of the rising light curve seen in Figure \ref{fig:closure}, due to the choice of different values of $p$.
+If $\thobs/\thC=4$, then a Gaussian jet will have also $\geff = 4$ by Equation \eqref{eq:geff}, and Figure \ref{fig:slopesG} shows $\alpha_{\mathrm{struct}}$ will be negative for $p=2.5$ in the G regime as in R04.
+
+In the structured phase, the temporal slope depends directly on $\geff$ in a way independent of the particular jet model.
+If a particular structure is assumed, then $\thobs/\thC$ may easily be inferred from $\geff$, and hence from $\alpha_{\mathrm{struct}}$.
 

### 2019-09-19 code/plotClosure.py

@@ -595,6 +595,9 @@ def plotSlopes(p, som, varName, name):
     ax.set_xlabel(varName)
     ax.set_ylabel(r'$\alpha_{\mathrm{struct}}$')
 
+    ax.set_xticks(np.arange(0, 21), minor=True)
+    ax.set_xticks(np.arange(0, 21, 5), minor=False)
+
     ax.legend()
     print("Saving " + name)
     fig.savefig(name)

### 2019-09-20 structuredJets.tex
BEEETER PLOTS

@@
 Very long baseline (VLBI) radio imagery over this period identified a radio core with an apparent superluminal motion, indicating the emitting surface was moving at relativistically at an oblique angle towards the Earth \citep{Mooley:2018ab}.
-The emission peaked at 160 days and proceeded to sharply decay at a rate $t^{-2.2}$ commensurate with other GRB afterglows \citep{Alexander:2018aa, Fong:2019aa, Lamb:2019aa, Troja:2019ab}.
+The emission peaked at 164 days after the burst and proceeded to sharply decay at a rate $t^{-2.2}$ commensurate with other GRB afterglows \citep{Alexander:2018aa, Fong:2019aa, Lamb:2019aa, Troja:2019ab}.
 
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{figs/jetDecomp.pdf}
+	\includegraphics[width=\columnwidth]{figs/lc_decomp.pdf}
 	\caption{A Gaussian structured jet, decomposed into emission from different latitudes $\theta$.
@@
 
-A good fit for $\tb$ to the full grid of models is obtained by taking the maximum of the aligned $\tbin$ and misaligned $\tbout$ relations:
-\begin{equation}
-	\tb = \max(\tbin,\  \tbout)\ , \label{eq:tb}
-\end{equation}
-where
+We refer to the jet break time in the aligned case as $\tbin$.  It is fit by:
 \begin{align}
 	\tbin &= 1.55\ \tNR \thC^{8/3} \label{eq:tbin}\\
-		&= 2.95\ E_{53}^{1/3} n_0^{-1/3} \left(\frac{\thC}{0.1\ \mathrm{rad}}\right)^{8/3}\ \mathrm{days}\ , \nonumber \\
+		&= 2.95\ E_{53}^{1/3} n_0^{-1/3} \left(\frac{\thC}{0.1\ \mathrm{rad}}\right)^{8/3}\ \mathrm{days}\ . \nonumber 
+\end{align}
+The jet break time in the misaligned case is $\tbout$, and fit by:
+\begin{align}
 	\tbout &= 0.184\ \tNR (\thC+\thobs)^{8/3} \label{eq:tbout} \\
@@
 \end{align}
+
+A good fit for $\tb$ to the full grid of models is obtained piecewise by switching from $\tbin$ to $\tbout$ at the transition point $\thobs = 1.22 \thC$ where $\tbin = \tbout$.  That is:
+\begin{equation}
+	\tb = \begin{cases}
+			\tbin & \thobs < 1.22 \thC \\
+			\tbout & \thobs > 1.22 \thC
+		\end{cases} \ . \label{eq:tb}
+\end{equation}
 
@@
 
-We use the electromagnetic afterglow of \gwbns{} as an example application of both the analytic and numerical structured jet afterglow models, using the dataset from \citet{Troja:2019ab}.
+We use the electromagnetic afterglow of \gwbns{} as an example application of both the analytic and numerical structured jet afterglow models, using the dataset from \citet{Troja:2019ab} with additional \hubble{} observations reported in \citet{Lamb:2019aa}.
 No new observations are presented in this paper.
 
-Figure \ref{fig:cornerGaussian} (inset) shows the observations in radio, optical, and X-ray bands of the \gwbns{} afterglow.
+\begin{figure*}
+	\includegraphics[width=\textwidth]{figs/lc_170817A_Gaussian_map.pdf}
+	\caption{\label{fig:lc170817A}}
+\end{figure*}
+
+Figure \ref{fig:cornerGaussian} shows the observations in radio, optical, and X-ray bands of the \gwbns{} afterglow.
 No afterglow emission was detected until an X-ray detection by the Chandra observatory nine days after the GW trigger \cite{Troja:2017aa}.
-Further radio, optical, and X-ray observations showed a steady rising light curve with constant power law slope until a peak near day 160.
-At this point the light curve turned over and began a steep decay that continues to the present \citep{Troja:2019ab}.
+Further radio, optical, and X-ray observations showed a steady rising light curve with constant power law slope until a peak near day 164 \citep{Haggard:2017aa, Hallinan:2017aa, DAvanzo:2018aa,  Lyman:2018aa, Margutti:2018aa, Mooley:2018aa, Troja:2018aa, Troja:2019ab}.
+At this point the light curve turned over and began a steep decay that continues to the present \citep{Alexander:2018aa, Fong:2019aa, Lamb:2019aa, Troja:2019ab}.
 
@@
 \begin{enumerate}
-	\item The spectral slope $\beta = 0.585$ (CITE, +uncertainties) throughout the entire evolution, identifying the relevant spectral regime as G: $\nu_m < \nuobs < \nu_c$, and $p = 2.17$.
-	\item The initial rising ($\alpha > 0$) light curve with declining spectrum ($\beta < 0$) identify this as a \emph{misaligned} evolution ($\thobs > \thC$).
+	\item The spectral slope $\beta = 0.585 \pm 0.005$ throughout the entire evolution, identifying the relevant spectral regime as G: $\nu_m < \nuobs < \nu_c$, and $p = 2.17 \pm 0.01$ \citep{Troja:2019ab}.
+	\item The initial rising ($\alpha > 0$) light curve with declining spectrum ($\beta < 0$) immediately identify this as a \emph{misaligned} evolution ($\thobs > \thC$).
 Aligned jets may only have a rising light curve when viewed at frequencies below the peak frequency, that is when $\beta < 0$.
 	\item The rising light curve maintains $\alpha  = 0.90 \pm 0.06$ \citep{Troja:2019ab}.
-Using the closure relations from Table \ref{tab:slopes} we can identify this as the \emph{structured} phase and determine $\geff = 7.5 \pm 0.4$.
-If the light curve underwent an \emph{off-axis} phase, it concluded before the afterglow was detected: $\tW < 9$d.
+Using the closure relations from Table \ref{tab:slopes} we can identify this as the \emph{structured} phase and determine $\geff = 8.2 \pm 0.5$.
+If the light curve underwent an \emph{far-off-axis} phase, it concluded before the afterglow was detected: $\tW < 9$d.
 The peak can be identified as the jet-break: $\tb = 164 \pm 12$ d.
-	\item In the context of a Gaussian jet, the measurement of $\geff$ leads immediately to $\thobs / \thC = 5.5 \pm 0.2$.
-	\item Using the Fong 2015 (CITE Fong 2015) fiducial values of $E_0 \sim 2\times 10^{51}$erg and $n_0 \sim 10^{-2}$cm$^{-3}$ we can use the jet break $\tb$ measurement to determine $\thobs \approx 0.5 \pm 0.2$ rad ($29^\circ \pm 12^\circ$), assuming 1 dex uncertainties on $E_0$ and $n_0$.
+	\item In the context of a Gaussian jet, the measurement of $\geff$ leads immediately to $\thobs / \thC = 5.7 \pm 0.2$ using Equation \eqref{eq:geff}.
+A $b=2$ power law jet cannot achieve this $\geff$ for any reasonable value of $\thobs / \thC$.
+A $b=6$ power law jet requires $\thobs/\thC = 14 \pm 1$.
+\end{enumerate}
+To go further we first need to assume a value for $E_0 / n_0$.
+For demonstration we use the \citet{Fong:2015aa} fiducial values of $E_0 \sim 2\times 10^{51}$erg and $n_0 \sim 10^{-2}$cm$^{-3}$, assuming 1 dex uncertainty on both parameters.
+\begin{enumerate}
+	\setcounter{enumi}{4}
+	\item We can use the jet break $\tb$ measurement to determine $\thobs + \thC$ using Equation \eqref{eq:tbout}.
+Using our assumed values for  $E_0$ and $n_0$ leads to $\thobs + \thC \approx 0.92 \pm 0.38$ rad ($53^\circ \pm 22^\circ$).
+This does not depend on the jet model.
+	\item For a Gaussian jet the combined measurements of $\thobs +\thC$ and $\thobs/\thC$ then imply $\thC \approx 0.14 \pm 0.06$ rad ($8.0^\circ  \pm 3.4^\circ$) and $\thobs \approx 0.78 \pm 0.32$ rad ($45^\circ \pm 18^\circ$).
+	\item For a $b=6$ power law jet we get $\thC \approx 0.063 \pm 0.026$ rad ($3.6^\circ  \pm 1.5^\circ$) and $\thobs \approx 0.86 \pm 0.35$ rad ($49^\circ \pm 20^\circ$).
+\end{enumerate}
+
+The relative weak dependence of $\tb$ on $E_0/n_0$ allows one to make estimates of $\thobs$ and $\thC$ even if $E_0$ and $n_0$ are only known to an order of magnitude.
+
+%TODO FINISH THIS PARAGRAPH
+Analysis of the \gwbns{} gravitational wave signal produced estimates of the inclination angle $\iota$ between the binary neutron stars' orbital plane and our line of sight.
+
 This is in agreement with the LIGO measurement $\thobs \approx 28^\circ \pm 15^\circ$ (assuming the SHoES $H_0$).
-	\item The combined measurements of $\thobs$ and $\thobs/\thC$ then imply $\thC \approx 0.09 \pm 0.04$ rad ($5^\circ  \pm 2^\circ$).
-\end{enumerate}
 
@@
 
-\begin{figure*}
-	\includegraphics[width=\textwidth]{figs/cornerGaussian.png}
-	\caption{Views of the posterior parameter distribution for a Gaussian jet fit to the \gwbns{} afterglow.
-The diagonal contains one-dimensional marginalized posteriors for each fit parameter, while the off-diagonal plots contain two-dimensional maps of the posterior marginalized over all but the two corresponding parameters.
-\label{fig:cornerGaussian}}
-\end{figure*}
-
-\begin{figure*}
-	\includegraphics[width=\textwidth]{figs/cornerPowerlaw.png}
-	\caption{Views of the posterior parameter distribution for a power law jet fit to the \gwbns{} afterglow.
-The diagonal contains one-dimensional marginalized posteriors for each fit parameter, while the off-diagonal plots contain two-dimensional maps of the posterior marginalized over all but the two corresponding parameters.
-\label{fig:cornerPowerlaw}}
-\end{figure*}
-
 Figures \ref{fig:cornerGaussian} and \ref{fig:cornerPowerlaw} show the one- and two-dimensional marginalized views of the posterior distribution for the Gaussian.
@@
 
-\newpage
+% \newpage
 
@@
 
+\section{GW170817A - Parameter Estimation Posteriors}\label{sec:corners}
+
+\begin{figure*}
+	\includegraphics[width=\textwidth]{figs/cornerGaussian.pdf}
+	\caption{Views of the posterior parameter distribution for a Gaussian jet fit to the \gwbns{} afterglow.
+The diagonal contains one-dimensional marginalized posteriors for each fit parameter, while the off-diagonal plots contain two-dimensional maps of the posterior marginalized over all but the two corresponding parameters.
+\label{fig:cornerGaussian}}
+\end{figure*}
+
+\begin{figure*}
+	\includegraphics[width=\textwidth]{figs/cornerPowerlaw.pdf}
+	\caption{Views of the posterior parameter distribution for a power law jet fit to the \gwbns{} afterglow.
+The diagonal contains one-dimensional marginalized posteriors for each fit parameter, while the off-diagonal plots contain two-dimensional maps of the posterior marginalized over all but the two corresponding parameters.
+\label{fig:cornerPowerlaw}}
+\end{figure*}
+
 \bibliography{structuredJets_sources}

### 2019-09-20 code/analyzeJetBreaks.py

@@ -169,6 +169,8 @@ if __name__ == "__main__":
            * np.power(thCs, -8.0/3.0)).mean() / 3.0)
 
     tau_theo = np.power(chi, 8.0/3.0)
+    tb_lim_min = 1.0e-4
+    tb_lim_max = 1.0
 
     figOnA, axOnA = plt.subplots(1, 1)
     axOnA.plot(thCs, tau_theo[:, 0],
@@ -191,16 +193,26 @@ if __name__ == "__main__":
     axOnA.set_xlabel(r'$\theta_{\mathrm{c}}$ (rad)')
     axOnA.set_ylabel(r'$t_{\mathrm{b}} / t_{\mathrm{NR}}$')
 
+    axOnA.set_xticks([0.04, 0.1, 0.4])
+    axOnA.set_xticklabels([r'$4\times 10^{-2}$', r'$10^{-1}$',
+                           r'$4\times 10^{-1}$'])
+
+    axOnA.set_ylim(tb_lim_min, tb_lim_max)
+
     figOnA.tight_layout()
     name = "jetbreak_OnAxis.pdf"
     print("Saving " + name)
     figOnA.savefig(name)
 
+    textProps = {'horizontalalignment': 'left',
+                 'verticalalignment': 'bottom',
+                 'fontsize': 8}
+
     figOffA, axOffA = plt.subplots(1, 1)
     for i in range(len(thCs))[::4]:
         thC = thCs[i]
         print("Off-Axis thetaC = {0:.4f}".format(thC))
-        if i == -1:
+        if i == 0:
             labelA = r'Analytic'
             labelG = r'Gaussian Jet'
             labelPL2 = r'Power Law Jet $b=2$'
@@ -221,11 +233,26 @@ if __name__ == "__main__":
         axOffA.plot(thVs, tau_pl6[i, :], ls=':', color='tab:red',
                     label=labelPL6)
 
-        """
-        axOffA.text(0.0, np.power(chi[i, 0], 8.0/3.0),
+        xloc = -0.04
+        yloc = tau_theo[i, 0]
+
+        if i == 0:
+            # xloc = 0.07
+            yloc /= 1.2
+            textProps['horizontalalignment'] = 'left'
+            textProps['verticalalignment'] = 'top'
+        elif i == 4:
+            yloc /= 1.4
+            textProps['horizontalalignment'] = 'left'
+            textProps['verticalalignment'] = 'top'
+        elif i == 8:
[…]

### 2019-09-20 code/paperPlots.py

@@ -11,9 +11,9 @@ import afterglowpy as grb
 sec2year = grb.sec2day / 365.25
 year2sec = grb.day2sec * 365.25
 
-labelsize = 12
-ticksize = 8
-legendsize = 12
+posterLabelsize = 12
+posterTicksize = 8
+posterLegendsize = 12
 
 
 def makeThVPlots():
@@ -117,7 +117,7 @@ def makeThVPlots():
     plt.close(fig)
 
 
-def makeCentralPlots(modelPlots=True):
+def makeCentralPlots(modelPlots=True, poster=True):
 
     thC = 0.1
     thW = 0.4
@@ -141,6 +141,15 @@ def makeCentralPlots(modelPlots=True):
     t = grb.day2sec * tday
     nu = 1.0e14 * np.ones(N)
     Flim = (1.0e-6, 1.0e1)
+
+    if poster:
+        labelsize = posterLabelsize
+        ticksize = posterTicksize
+        legendsize = posterLegendsize
+    else:
+        labelsize = None
+        ticksize = None
+        legendsize = None
 
     if modelPlots:
         thV = 0.5 * thC
@@ -256,7 +265,7 @@ def makeCentralPlots(modelPlots=True):
     save(fig, figname)
     plt.close(fig)
 
-    fig = plt.figure(figsize=(4, 3))
+    fig = plt.figure()
     lbuff = 0.16
     bbuff = 0.16
     rbuff = 0.15
@@ -311,7 +320,7 @@ def makeCentralPlots(modelPlots=True):
     ax.plot(tday, FnuG, color='grey', lw=2)
     ax.set_xscale('log')
     ax.set_yscale('log')
-    ax.set_xlim(1.0e-2, 1.0e3)
+    ax.set_xlim(3.0e-2, 1.0e3)
     ax.set_ylim(1.0e-7, 1.0e-2)
     ax.set_xlabel(r'$t$ (days)', fontsize=labelsize)
     ax.set_ylabel(r'$F_\nu$ (mJy)', fontsize=labelsize)
@@ -1595,10 +1604,10 @@ def save(fig, name):
 if __name__ == "__main__":
 
     # makeThVPlots()
-    # makeCentralPlots(modelPlots=True)
+    makeCentralPlots(modelPlots=False, poster=False)
     # makeConvergencePlots()
     # makeRegimePlots()
     # makeNormalizationPlots('E', 4)
     # makeNumAnaCompPlots('E', 4)
[…]

### 2019-09-20 code/plotStructDecomp.py

@@ -1,6 +1,6 @@
 import numpy as np
 import matplotlib.pyplot as plt
-import grbpy as grb
+import afterglowpy as grb
 
 
 jetType = 0
@@ -40,16 +40,16 @@ for i in range(Nth):
     Y[1] = E
     Y[2] = thin
     Y[3] = thout
-    FnuR[i,:] = grb.fluxDensity(t, nu, -2, 0, *Y)
+    FnuR[i, :] = grb.fluxDensity(t, nu, -2, 0, *Y)
 
-fig, ax =  plt.subplots(1,1)
+fig, ax = plt.subplots(1, 1)
 for i in range(Nth):
     ax.plot(t, FnuR[i])
 ax.plot(t, Fnu, color='k')
 ax.set_xscale('log')
 ax.set_yscale('log')
 ax.set_xlabel(r'$t$ (s)')
-ax.set_ylabel(r'$F_{\nu}$ (erg/cm$^2$s Hz)')
+ax.set_ylabel(r'$F_{\nu}$ (mJy)')
 
 ax.set_ylim(1.0e-12, None)
 

### 2019-09-20 code/quick170817Analysis.py

@@ -1,0 +1,151 @@
+import math
+import numpy as np
+import matplotlib.pyplot as plt
+# import afterglowpy as grb
+
+
+def g2al(g, p):
+    al = (3 - 6*p + 3*g) / (8+g)
+    return al
+
+
+def al2g(al, p):
+    g = (3 - 6*p - 8*al) / (al-3)
+    return g
+
+
+def al2eg(al, p, eal, ep):
+    dgdp = -6/(al-3)
+    dgdal = (21 + 6*p) / ((al-3)*(al-3))
+
+    eg = math.sqrt(dgdp**2 * ep**2 + dgdal**2 * eal**2)
+
+    return eg
+
+
+def th2g_pl(thVoC, b):
+    thEffoC = thVoC / np.sqrt(1.83+2.10*np.power(b, -1.25)
+                              + (0.486-0.862*np.power(b, -1.15)) * thVoC)
+    g = -(thEffoC-thVoC) * thEffoC / (1 + thEffoC*thEffoC/b)
+    return g
+
+
+def tb2thp(tb, Eon):
+    thVpC = 0.3 * np.power(tb/6.54, 0.375) * np.power(Eon, -0.125)
+    return thVpC
+
+
+def tb2ethp(tb, Eon, etb, elEon):
+    thVpC = tb2thp(tb, Eon)
+    dthpdtb = 0.375*thVpC/tb
+    dthpdEon = -0.125*thVpC/Eon
+    dthpdlEon = math.log(10.0) * Eon * dthpdEon
+
+    ethVpC = math.sqrt((dthpdtb*etb)**2 + (dthpdlEon*elEon)**2)
+    return ethVpC
+
+
+def po2C(thVpC, thVoC):
+    thC = thVpC / (1+thVoC)
+    return thC
+
+
+def po2eC(thVpC, thVoC, ethVpC, ethVoC):
+    dCdp = 1.0 / (1+thVoC)
+    dCdo = -thVpC / (1+thVoC)**2
+
+    ethC = np.sqrt((dCdp*ethVpC)**2 + (dCdo*ethVoC)**2)
+
+    return ethC
+
+
+def po2V(thVpC, thVoC):
+    thC = thVpC * thVoC / (1+thVoC)
+    return thC
+
+
+def po2eV(thVpC, thVoC, ethVpC, ethVoC):
[…]

### 2019-09-23 structuredJets.tex
Almost there...

@@
 
-Interpreting the afterglow as arising from a structured jet allows one to quickly draw the following conclusions:
+Interpreting the afterglow as arising from a structured jet allows one to draw the following quick conclusions:
 \begin{enumerate}
@@
 A $b=2$ power law jet cannot achieve this $\geff$ for any reasonable value of $\thobs / \thC$.
-A $b=6$ power law jet requires $\thobs/\thC = 14 \pm 1$.
+A $b=6$ power law jet requires $\thobs/\thC = 14 \pm 1$, while a $b=9$ power law requires $\thobs/\thC = 9.6\pm 0.5$.
 \end{enumerate}
@@
 
-%TODO FINISH THIS PARAGRAPH
-Analysis of the \gwbns{} gravitational wave signal produced estimates of the inclination angle $\iota$ between the binary neutron stars' orbital plane and our line of sight.
-
-This is in agreement with the LIGO measurement $\thobs \approx 28^\circ \pm 15^\circ$ (assuming the SHoES $H_0$).
-
+ Analysis of the \gwbns{} gravitational wave signal produced estimates of the inclination angle $\iota$ between the binary neutron stars' orbital plane and our line of sight, but were dependent on the assumed value of the Hubble constant $H_0$ \citep{Abbott:2017aa}.
+The values obtained were:
+ $\iota = \left({28}^{+27}_{-20}\right)^\circ$ (90\% uncertainties, marginalized over $H_0$), $\iota = \left(26^{+12}_{-15}\right)^\circ$ ($H_0$ from SHoES: \citet{Riess:2016aa}), and $\iota = \left(19^{+12}_{-12}\right)^\circ$ ($H_0$ from \citet{Planck-Collaboration:2016aa}), we have reversed the reported orientation of $\iota$ to ease comparison with $\thobs$.
+
+If the BNS merger produces a jet orthogonal to the orbital plane then $\iota = \thobs$ and we can directly compare the gravitational and electromagnetic estimates.
+With our fiducial values for $E_0$ and $n_0$ the estimated value of $\thobs$ from the afterglow is larger than the gravitational wave $\iota$ measurements, but given the large uncertainties on both values there is no tension in the discrepancy.
+
+There is much more information in the afterglow light curve than just the rising slope and jet break.
 For a more detailed analysis we performed Bayesian parameter estimation utilizing \afterglowpy{} and the \emcee{} Markov chain Monte Carlo sampler \citep{Foreman-Mackey:2013aa}.
@@
 Reported measurement uncertainties were assumed to be independent and Gaussian, upper limits were treated as observations of zero flux with a 1-sigma Gaussian uncertainty.
-
-We fit both the Gaussian and power law structured jet models, fixing $\xi_N = 1$ and $\dL = 1.23 \times 10^{26}$cm.
+We assume $\iota = \thobs$ and use the posterior probability distribution $p_{\mathrm{LIGO}}(\cos \iota)$ reported in \citet{Abbott:2017aa} (assuming Planck $H_0$, their Figure 3) as a prior for $\thobs$ as in \citet{Troja:2018aa}.
+
+We fit both the Gaussian and power law structured jet models, fixing $\xi_N = 1$ and $\dL = 1.23 \times 10^{26}$ cm.
 The fit parameters, their priors, and their marginalized posteriors are given in Table \ref{tab:MCMC}.
 Both models were run with 300 walkers for 64 000 iterations, discarding the first 16 000 iterations as a burn-in.
-The viewing angle prior is the posterior found in analysis of the \gwbns{} gravitational wave signal assuming the value of $H_0$ reported by the \planck{} collaboration \citep{Abbott:2017aa, Planck-Collaboration:2016aa, Troja:2018aa}.
+The $E_0$, $n_0$, $\epse$, and $\epsB$ parameters were given $\log$-uniform priors, while $\thC$, $\thW$, $b$, and $p$ were given uniform priors.
+The specific bounds and priors for each parameter are reported in Table \ref{tab:MCMC}.
 
@@
 	\startdata
-		\thobs	& \text{rad	} & \sin \thobs \times p_\mathrm{LIGO}(\cos \thobs)	& [0, 0.8] 	& 0.48^{+0.08}_{-0.09} & 0.36^{+0.14}_{-0.11} \\
-		\log_{10} E_0	& \text{erg	}	& \text{uniform}	& [45, 57] 			& 52.92^{+0.62}_{-0.49} & 53.01^{+0.99}_{-0.70}\\
-		\thC			& \text{rad	}	& \text{uniform}	& [0.01, $\pi/2$]		& 0.07^{+0.01}_{-0.01} & 0.10^{+0.06}_{-0.03}\\
-		\thW			& \text{rad}	& \text{uniform}	& [0.01, 12$\thC$]	& 0.77^{+0.43}_{-0.38} & 0.18^{+0.07}_{-0.05}\\
-		b			& - 			& \text{uniform}	& [0, 10] 			& - & 7.15^{+2.02}_{-1.12}\\
-		\log_{10}n_0	& \text{cm}^{-3} & \text{uniform}	& [-10, 10] 		& -1.94^{+0.62}_{-0.65} & -2.66^{+1.03}_{-1.11}\\
-		p			& - 			& \text{uniform}	& [2, 5] 			& 2.17^{+0.01}_{-0.01} & 2.17^{+0.01}_{-0.01}\\
-		\log_{10}\epse& - 			& \text{uniform}	& [-5, 0] 			& -1.24^{+0.48}_{-0.69} &-1.30^{+0.66}_{-1.07} \\
-		\log_{10}\epsB	& - 			& \text{uniform}	& [-5, 0] 			& -4.32^{+0.72}_{-0.49} & -3.84^{+1.01}_{-0.80}\\
+		\thobs	& \text{rad	} & \sin \thobs \times p_\mathrm{LIGO}(\cos \thobs)	& [0, 0.8] 	& 0.40^{+0.11}_{-0.11} 	& 0.44^{+0.12}_{-0.12} \\[0.05cm]
+		\log_{10} E_0	& \text{erg	}	& \text{uniform}	& [45, 57] 						& 52.96^{+0.97}_{-0.72} 	& 52.93^{+1.1}_{-0.75}\\[0.05cm]
+		\thC			& \text{rad	}	& \text{uniform}	& [0.01, $\pi/2$]					& 0.066^{+0.018}_{-0.018} & 0.046^{+0.013}_{-0.013}\\[0.05cm]
+		\thW			& \text{rad}	& \text{uniform}	& [0.01, 12$\thC$]				& 0.47^{+0.26}_{-0.19} 	& 0.238^{+0.071}_{-0.69}\\[0.05cm]
+		b			& - 			& \text{uniform}	& [0, 10] 						& - 					& 9.03^{+0.70}_{-1.1}\\[0.05cm]
+		\log_{10}n_0	& \text{cm}^{-3} & \text{uniform}	& [-10, 10] 					& -2.70^{+0.95}_{-1.0} 	& -2.6^{+1.1}_{-1.1}\\[0.05cm]
+		p			& - 			& \text{uniform}	& [2, 5] 						& 2.168^{+0.063}_{-0.0075} & 2.1653^{+0.0085}_{-0.010}\\
+		\log_{10}\epse& - 			& \text{uniform}	& [-5, 0] 						& -1.42^{+0.70}_{-1.1} 	&-1.24^{+0.73}_{-1.2} \\[0.05cm]
+		\log_{10}\epsB	& - 			& \text{uniform}	& [-5, 0] 						& -3.96^{+1.1}_{-0.74} 	& -3.76^{+1.1}_{-0.87}\\[0.05cm]
 		\hline
-		\log_{10}\Etot	& \text{erg}	&	-		&	-			& 50.61^{+0.58}_{-0.44} &50.85^{+0.93}_{-0.63} \\
-		\thobs/\thC	& -			&	-		&	-			& 6.76^{+0.21}_{-0.21} & 3.78^{+0.58}_{-0.84}\\
+		\log_{10}\Etot	& \text{erg}	&	-		&	-						& 50.57^{+0.92}_{-0.66} 	&50.46^{+1.1}_{-0.73} \\[0.05cm]
+		\thobs/\thC	& -			&	-		&	-						& 6.12^{+0.18}_{-0.18} 	& 9.38^{+0.73}_{-0.56}\\[0.05cm]
+		\log_{10} E_0/n_0 &  \text{erg cm}^3	&	- 	&	-						& 55.69^{+1.1}_{-0.85} 	& 55.62^{+1.2}_{-0.83}\\[0.05cm]
 	\enddata
@@
 
-Figures \ref{fig:cornerGaussian} and \ref{fig:cornerPowerlaw} show the one- and two-dimensional marginalized views of the posterior distribution for the Gaussian.
-and power law jet model fits, respectively.
-Table \ref{tab:MCMC} additionally gives constraints on the total jet energy \Etot{} and the ratio $\thobs/\thC$.
+Table \ref{tab:MCMC} gives the posterior median and 68\% quantiles found for each parameter, as well as constraints on the total jet energy \Etot{} and the ratio $\thobs/\thC$.
+Figures \ref{fig:cornerGaussian} and \ref{fig:cornerPowerlaw} show the one- and two-dimensional marginalized views of the posterior distribution for the Gaussian and power law jet model fits, respectively.
 The parameters $E_0$, $n_0$, $\epse$, and $\epsB$ are only constrained to within an order of magnitude, due partially to the observed radio, optical, and X-ray data all lying on the same synchrotron power-law segment.
-These parameters are shared between jet models, and are broadly consistent between the two fits with the possible exception of $n_0$.
+These parameters are shared between jet models, and are consistent between the two fits.
 The electron energy index $p$ is extremely well constrained by both models, of course, due precisely to the large range of data laying on the same synchrotron segment.
-The total jet energy in both models in constrained to be on the order $10^{51}$erg.
+The total jet energy in both models is constrained to be on the order $3 \times 10^{50}$ erg, with uncertainties of an order of magnitude.
 
 Of most interest are the geometric parameters: the viewing angle $\thobs$ and the jet structure parameters $\thC$, $\thW$, and $b$.
-Encouragingly, the fits agree with the back-of-the-envelope reasoning from the analytic closure relations and break time scalings.
-Both models constrain $\thobs$ and $\thC$ reasonably well, but constrain the combination $\thobs/\thC$ far better.
+Both models constrain $\thobs$ and $\thC$ reasonably well, $\thobs = 0.40 \pm 0.11$ rad for the Gaussian jet and $\thobs = 0.44 \pm 0.12$ rad for the power law, but constrain the combination $\thobs/\thC$ far better: $\thobs/\thC  = 6.12 \pm 0.18$ for the Gaussian and $\thobs/\thC  = 9.38^{+0.73}_{-0.56}$ for the power law.
 This is very evident by the corresponding map of the posterior in Figures \ref{fig:cornerGaussian} and \ref{fig:cornerPowerlaw}, which clearly displays a preferred linear relationship between $\thobs$ and $\thC$.
@@
 
+The fits agree with the back-of-the-envelope reasoning from the analytic closure relations and jet break time.
+The closest agreement is in the $\thobs/\thC$ ratio, the Gaussian agrees within the uncertainties and the power law fit agrees well with the $b=9$ estimate.
+The absolute values of $\thobs$ and $\thC$ agree within uncertainties but are systematically higher in the back-of-the-envelope estimates compared to the fit results.
+This can be accounted for by our adopted fiducial value for $E_0/n_0$ which in the estimate was taken to be $10^{53.3}$ erg cm$^3$.
+The MCMC fits, which constrain this value for this particular burst, both find $E_0/n_0 \approx 10^{55.6 \pm 1.0}$ erg cm$^{3}$.
+Adopting this value in the back-of-the-envelope estimates leads to $\thobs = 0.41\pm0.12$ rad, $\thC = 0.07 \pm 0.02$ rad for the Gaussian and $\thobs = 0.43\pm0.12$ rad, $\thC = 0.05 \pm 0.01$ for the power law in excellent agreement with the MCMC fits.
+
+% TODO: RECONSIDER, CLARIFY, OR DROP THIS
 Despite the tight constraints each model gives on $\thobs$, $\thC$, and especially $\thobs/\thC$, the resulting posteriors are incompatible with each other.

### 2019-09-23 code/quick170817Analysis.py

@@ -86,6 +86,10 @@ Eon = 20.0/10.0
 # Eon = 30
 elEon = math.sqrt(2) * 1.0
 
+# GW170817 fits
+Eon = math.pow(10.0, 2.6)
+elEon = 1.0
+
 p = 1-2*be
 ep = 2*ebe
 

### 2019-09-23 structuredJets.tex
updates tb fits

@@
 More generally, for initially top hat jets it has been shown the jet break corresponds to the far jet edge coming into view, that is $\tb \propto (\thC + \thobs)^{8/3}$ \citep{van-Eerten:2010aa}.
-We find this latter result to hold approximately true for structured jets as well.
 As $\thC$ denotes the angular size of the bright jet core, once this time is reached the jet is essentially entirely in view.
-Wings of the jet on the far side from the viewer may still come into view, but remain a subdominant contribution to the bright core within $\thC$.
-
-We find $\tb(\thC, \thobs)$ to show two modes of behaviour, split roughly by the whether the viewer is aligned ($\thobs < \thC$) or misaligned ($\thobs > \thC$).
+Wings of the jet on the far side from the viewer may still enter the beaming cone, but remain a subdominant contribution to the bright core within $\thC$.
+
+For generic structured jets we find $\tb(\thC, \thobs)$ to show two modes of behaviour, split by the whether the viewer is aligned ($\thobs < \thC$) or misaligned ($\thobs > \thC$).
 Aligned viewing shows $\tb$ to follow $\thC^{8/3}$ quite strongly with very little dependence on $\thobs$.
-Misaligned viewing better tracks with $(\thC + \thobs)^{8/3}$, although there are discrepancies for very large viewing angles.
+Misaligned viewing better tracks with a linear combination $(\thobs + c_1 \thC)^{8/3}$.
+To determine the precise normalization we fit each regime with a simple $\chi^2$ minimization.
 
@@
 \begin{align}
-	\tbin &= 1.55\ \tNR \thC^{8/3} \label{eq:tbin}\\
+	\tbin &= 1.56\ \tNR \thC^{8/3} \label{eq:tbin}\\
 		&= 2.95\ E_{53}^{1/3} n_0^{-1/3} \left(\frac{\thC}{0.1\ \mathrm{rad}}\right)^{8/3}\ \mathrm{days}\ . \nonumber 
@@
 \begin{align}
-	\tbout &= 0.184\ \tNR (\thC+\thobs)^{8/3} \label{eq:tbout} \\
-		&= 6.54\ E_{53}^{1/3} n_0^{-1/3} \left(\frac{\thC+\thobs}{0.3\ \mathrm{rad}}\right)^{8/3}\ \mathrm{days}\ . \nonumber 			
-\end{align}
-
-A good fit for $\tb$ to the full grid of models is obtained piecewise by switching from $\tbin$ to $\tbout$ at the transition point $\thobs = 1.22 \thC$ where $\tbin = \tbout$.  That is:
+	\tbout &= 0.180\ \tNR (\thobs+1.24\ \!\thC)^{8/3} \label{eq:tbout} \\
+		&= 24.9\ E_{53}^{1/3} n_0^{-1/3} \left(\frac{\thobs+1.24\ \!\thC}{0.5\ \mathrm{rad}}\right)^{8/3}\ \mathrm{days}\ . \nonumber 			
+\end{align}
+
+A good fit for $\tb$ to the full grid of models is obtained piecewise by switching from $\tbin$ to $\tbout$ at the transition point $\thobs = 1.01 \thC$ where $\tbin = \tbout$.  That is:
 \begin{equation}
 	\tb = \begin{cases}
-			\tbin & \thobs < 1.22 \thC \\
-			\tbout & \thobs > 1.22 \thC
+			\tbin & \thobs < 1.01 \thC \\
+			\tbout & \thobs > 1.01 \thC
 		\end{cases} \ . \label{eq:tb}
@@
 Figure \ref{fig:tb} also shows Equation \eqref{eq:tb} compared to the measured jet break times.
-The on-axis relation $\tbin$ fits very well over the span of $\thC$ considered, with a mean fractional error of 0.053.
-Over the full $\thC$ and $\thobs$ domain the mean fractional error is 0.17, with the largest contributions coming from wide jets (e.g.
-the upper curve, $\thC = 0.328$ rad, in Figure \ref{fig:tb}) at viewing angles $\thobs > 0.8$ rad.
-
-% TODO FIX THE HELL OUT OF THESE FIGURES
-% MAKE MODEL CURVES CONSISTENT WITH MULTI-PANEL
-% DROP OR DEFINE t_N
-%\begin{figure}
-%	\includegraphics[width=\columnwidth]{figs/jetbreak_OnAxis.pdf}
-%	\caption{Jet break time for on-axis ($\thobs=0$) observers for Gaussian (green solid line),  $b=2$ power law (orange dash-dotted line), and $b=6$ power law (red dotted line) jets as a function of $\thC$.
-The dashed grey line is the analytic approximation $\tb = 1.55 t_N (\thC/1 rad)^{8/3}$.
-\label{fig:tbOA}}
-%\end{figure}
-
-%\subsection{Aligned Evolution: $\thobs \lesssim \thC$} \label{subsec:aligned}
-%
-%The aligned light curve of a structured jet is essentially identical to that of a standard top-hat viewed within the jet cone.
-(CITE Panaitescu \& Kumar).
-The relativistic afterglow is comprised of three phases, \emph{pre-jet break}, \emph{transition}, and \emph{post-jet break}.
-These are well described in the literature and are briefly reviewed here.
-%
-%\emph{Pre-jet break} ---  At early times the flux is dominated by the small patch of material whose emission is beamed towards the observer of angular width $\psi = |\theta-\thobs| \sim \gamma^{-1}$.
-This patch is within the $\theta < \thC$ region where $E(\theta) \approx E_0$ and the structure plays a sub-dominant role.
-The angular size of the visible patch grows with $\som = 2$.
-Closure relations and scalings of the standard on-axis top-hat apply.
-(CITE Granot and Sari)
-%
-%\emph{Transition} ---  When $\gamma^{-1} \sim \thC-\thobs$ the near edge of the jet comes in to view.
-Material outside $\thC$ is less energetic and contributes sub-dominantly to the afterglow emission.
-The effective visible patch grows more slowly, $\som \lesssim 2$, and the decay of the afterglow steepens slightly.
-Closure relations and scalings of the standard on-axis top-hat apply only approximately (CITE vanEerten MacFadyen 2010).
-%
-%\emph{Post-jet break} ---  When $\gamma^{-1} \sim \thC+\thobs$ the far edge of the jet comes in to view and growth of the visible patch ceases, $\som = 0$.
-If the blast wave remains relativistic and non-spreading, the slope of the light curve is reduced by $-3/4$ relative to the pre-jet break slope.
-However, in many circumstances the jet break begins when the blast wave is only trans-relativistic and spreading may have begun.
-In these cases an analytic treatment of the light curve is slope is more difficult, but numerical simulations and analytic work estimate an additional reduction of "???" over the simple analytic result.
-%
-%The transition between pre-jet break and post-jet break begins at $\tbm$ and completes at $\tbp$, given in the single shell approximation (see Appendix \ref{app:derive1}) by:
-%\begin{align}
-%	\tbpm &= \left(\frac{9}{16\pi} \frac{E_0}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thC\pm\thobs}{2}\right)\right)^{8/3} .\label{eq:tbpm}
-%\end{align}
-%
-%It is important to note that when $\thobs \neq 0$ the transition period is extended, and the most significant transition in the light curve occurs at $\tbp$, the \emph{jet break}.
-The jet break occurs, in all jets, when the effective angular size of the visible patch of the jet ceases to increase, that is when $\som = 0$.
-%
-%Figure \ref{fig:tbOA} shows the jet break time for on-axis ($\thobs = 0$) viewers as a function of $\thC$ for top-hat, Gaussian, and power law jets calculated with \afterglowpy{}.
-Break times were extracted by fitting the numerical light curve with a two-component broken power law.
-%
-%%\begin{figure}
-%%	\includegraphics[width=\columnwidth]{figs/lc_on.pdf}
-%%	\caption{Aligned ($\thobs = \thC/2$) afterglow light curves for top-hat (blue), Gaussian (orange), and power law (green) jets.
-When viewed on-axis, jets containing angular structure are very difficult to distinguish from top-hats.
-The transition phase marking the onset of the jet break begins at $\tbm\sim3$ days with a shallow break and ends sharply at $\tbp \sim 100$ days.
-These particular light curves use $\thC = 0.1$ rad, $\thW = 0.4$ rad, $E_0 = 10^{52}$erg, $n_0=10^{-2}$cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, $\epsB = 10^{-3}$, and $d_L=40$Mpc.
-\label{fig:onaxis}}
-%%\end{figure}
-%
-%
-%Figure \ref{fig:onaxis} shows representative top-hat, Gaussian, and power law jet light curves in the aligned regime.
-The light curves nearly overlap, demonstrating the similar evolution of all structured jet afterglows when viewed within the jet core.
-Although we expect all afterglow blast waves to contain angular structure, the simple top-hat jet model is sufficient for aligned viewing.
-%
-%The relativistic stages of evolution are followed by a Newtonian phase ($t > 200$ days in Figure \ref{fig:onaxis}) when the decelerating blast wave becomes non-relativistic, spreads sonically, and approaches a Sedov-Taylor solution.
-We do not address the Newtonian phase of evolution in this work.
-%
-%\subsection{Misaligned Evolution: $\thobs \gtrsim \thC$} \label{subsec:misaligned}
-%
-%When viewed at angles larger than $\thC$ the gradient $E'(\theta)$ over the visible patch becomes non-negligible.
-To observers this energy gradient presents itself as a slowly rising or decaying afterglow light curve.
-The relativistic afterglow is comprised of two or three phases depending on whether the observer lies within the truncation angle, \emph{far off-axis}, \emph{structured}, and \emph{post-jet break}.
-%
-%\emph{Far off-axis} --- If the viewer lies outside the truncation angle, $\thobs > \thW$, then at early times the entire blast wave surface is off-axis and all emission is beaming suppressed.
-This greatly reduces the early flux and leads to a dim but steeply rising light curve as the blast wave decelerates.
-Emission is dominated by material on the edge nearest the observer and the angular size of the visible patch is constant in time.
-This phase ends at $\tW$ when $\gamma^{-1}(\thW) \sim \thobs-\thW$.
-If $\thobs < \thW$ this phase is entirely absent.
-Table \ref{tab:slopes} gives the temporal power law slope of the light curve in this phase.
-These slopes are derived in Appendix \ref{app:derive1}.
-%
-%\emph{Structured} --- The structured phase is the direct result of the energy gradient along the observer's line of site.
-The usual (pre-jet break) decay is compensated for by regions of higher energy continuously coming into view as the jet decelerates.
-These new contributions to the emission slow the decay and can even cause the observed flux to increase with time.
-%
-% This phase begins at observer time $\tW$, once the blast wave is decelerating and the observer is within the beaming cone of any part of the emitting surface.
-It ends at observer time $\tb$, when the jet core has become fully visible.
-These times are:
-%\begin{align}
-%	\tW &= \left(\frac{9}{16\pi} \frac{E(\thW)}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thobs-\thW}{2}\right)\right)^{8/3} \ ,\label{eq:tw} \\
-%	\tb &= \left(\frac{9}{16\pi} \frac{E_0}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thobs}{2}\right)\right)^{8/3} \ .\label{eq:tb}
-%\end{align}
-%
-%Figure \ref{fig:decomp} shows the light curve of a Gaussian structured jet along with the emissions from different latitudes.
-The part of the blast wave dominating the emission tracks from the high latitude wings $\theta \approx \thW$ to the core $\theta \approx 0$.
-The angular size of the visible patch grows approximately as $\gamma^{-1.0}$.
-(NEED PLOT?)
-%
-%During the structured phase, the afterglow has a temporal spectral slope which depends on the parameter $g(\theta^*)$, where $\theta^*$ is the latitude of material dominating the emission:
-%\begin{equation}
-%	g(\theta^*) \equiv -2 \tan\left(\frac{\thobs - \theta^*}{2}\right)\frac{d \log E}{d \theta}\ . \label{eq:gdef}
-%\end{equation}
-%
-%The temporal and spectral slopes for various regimes are given in Table \ref{tab:slopes}.  The derivation of the closure relations, $\tW$, and $\tb$ are given in Appendix \ref{app:derive1}.
-
-%\begin{deluxetable*}{CCCCCC}
-%	\tablecaption{Structured jet temporal and spectral slopes: $F_\nu \propto \tobs^{-\alpha} \nu^{-\beta}$.
-See Equations \eqref{eq:gdef} and \eqref{eq:geff} for the definition and effective values of $g$.
-For a refreshed-shock model replace $g$ with $k$, defined in Equation \eqref{eq:Eu}.
-\label{tab:generalSlopes}}
-%	\tablehead{\colhead{Regime}& \colhead{Label} & \colhead{$\alpha_{\mathrm{off-axis}}$}& \colhead{$\alpha_{\mathrm{struct}}$}& \colhead{$\alpha_{\mathrm{struct,max}}$} & \colhead{$\beta$}}
-%	\startdata
-%	\nu<\nu_m<\nu_c     & D & -7 			& -\frac{-2+3s_3 + 3g}{8+g} 		& -3		& -1/3 \\
-%	\nu_m<\nu<\nu_c     & G & -15/2 + 3p/2 	& -\frac{- 6p + 3s_3 + 3g}{8+g} 		& -3		& (p-1)/2 \\
-%	\nu < \nu_c < \nu_m & E & -17/3 		& -\frac{-14/3 + 3s_3 + 11g/3}{8+g} 	& -11/3	& -1/3 \\
-%	\nu_c < \nu < \nu_m & F & -13/2 		& -\frac{-8+3s_3 + 2g}{8+g} 		& -2		& 1/2 \\
-%	\nu_c < \nu_m < \nu & H & -8 + 3p/2 		& -\frac{-6p - 2 + 3s_3 + 2g}{8+g} 	& -2		& p/2 \\ 
-%	\enddata
-%\end{deluxetable*}
-
-%The $g$ parameter evolves with time as $\theta^*$ sweeps from the jet edge to the core.
-This produces deviations in the light curve from a pure power law.
-However, we find ultimately these deviations are not too large and the average slope is well approximated by $\geff  = g(\thobs/2)$.
-For the power law and Gaussian jet models this gives:
-%\begin{align}
-%	\theff &= \frac{\thobs}{2}&& \text{Gaussian}\ , \\
-%	\theff &= \frac{\thobs}{\sqrt{1.8+2.1b^{-1.25} + (0.49-0.86b^{-1.25})\thobs/\thC}}&& \text{power law}\ . \label{eq:theff}
-%\end{align}
-%\begin{align}
-%	\geff &= \frac{\thobs^2}{4\thC^2} && \text{Gaussian}\ , \\
-%	\geff &= \frac{2 b (\thobs-\theff)\theff}{b \thC^2+\theff^2} && \text{power law}\ . \label{eq:geff}
-%\end{align}
-%These values may be used in Table \ref{tab:slopes} for an approximate power law model of a structured jet with an appropriate viewing angle dependent temporal evolution.
-These analytic results are in agreement with previous work on structured jets (CITE ROSSI) and the trans-relativistic numerical model described in Section \ref{sec:numerical}.
-%
-%In the structured phase, the temporal slope depends directly on the ratio $\thobs/\thC$.
-Therefore any measurement of the effective power law slope of an afterglow light curve in the structured phase can be used to measure this parameter.
-%
-%\emph{Post-jet break} --- Once the entire jet is visible (ie.
-the observer is within the beaming cone of the entire jet) the visible patch no longer grows and emission is dominated by the decelerating core.
-This phase follows exactly the post-jet break scalings of the aligned case, except with a much delayed break time $\tb$.
-
-%\begin{figure}
-%	\includegraphics[width=\columnwidth]{figs/lc_off1.pdf}
-%	\caption{As Figure \ref{fig:onaxis} but $\thobs = 2\thC$.
-The top-hat jet (with opening angle $\thC$) begins in the off-axis phase.
-The Gaussian and power law jets begin in the structured phase as $\thobs < \thW$.
-All three models enter similar post-jet break phases.
-\label{fig:offaxis1}}
-%\end{figure}
-%\begin{figure}
-%	\includegraphics[width=\columnwidth]{figs/lc_off2.pdf}
-%	\caption{As Figure \ref{fig:onaxis} but $\thobs = 6\thC$.
-All three models exhibit off-axis, structured, and post-jet break phases of evolution.
-At larger opening angles the difference between structured models is more evident.
-\label{fig:offaxis2}}
-%\end{figure}
-
-%Figures \ref{fig:offaxis1} and \ref{fig:offaxis2} display afterglows from the fiducial models in the misaligned regime at $\thobs = 2\thC$ and $\thobs=6\thC$ respectively.
-At the moderate $2\thC$ viewing angle both structured models exhibit similar decaying light curves with slopes somewhat shallower than the aligned case.
-In this case $\thobs < \thW$ so neither model exhibits an off-axis phase.
-The similar temporal evolution is easy to understand as at this angle both models have $\geff = 1$ and hence approximately equal power law slopes in the structured phase.
-At late times as more of the jet comes in to view the difference between all three models becomes negligible.
-%
-%At the larger $6\thC$ viewing angle all three models exhibit off-axis, structured, and post-jet break phases of the afterglow.
-The different $\tW$ between the Gaussian and power law models is due to the different $E(\thW)$ of the two models.
-In the structured phase the Gaussian shows a rising light curve with slope $~1$ due to the large $\geff = 9$.
-The power law meanwhile has a smaller $\geff$ of $9/5$, giving rise to a very shallow decay.
-As at the other viewing angles, once the entire jet is visible at $\tb$ all models follow similar post-jet break evolutions.
-
-%
-% Comment: Add dashed line at 0 to slopes plot.
-%
+The on-axis relation $\tbin$ fits very well over the span of $\thC$ considered, with a mean fractional error of 5.3\%.
+Over the full $\thC$ and $\thobs$ domain the mean fractional error is 12\%, with the largest contributions coming from large viewing angles $\thobs > 0.8$ rad.
 
@@
 %
-% Comment: define tdec, tmin IN THE TEXT.   Add (brief) discussion of light curve phases.
+%  TODO:  Comment: define tdec, tmin IN THE TEXT.   Add (brief) discussion of light curve phases.
 %
@@
 At this point the light curve turned over and began a steep decay that continues to the present \citep{Alexander:2018aa, Fong:2019aa, Lamb:2019aa, Troja:2019ab}.
+
+% TODO: REDO with new tb fits.
 

### 2019-09-23 code/analyzeJetBreaks.py

@@ -2,6 +2,7 @@ import sys
 import math
 import h5py as h5
 import numpy as np
+import scipy.optimize as opt
 import matplotlib.pyplot as plt
 import afterglowpy as grb
 
@@ -30,6 +31,51 @@ def loadData(filename):
     return tN, thV, thC, tj_th, tj_g, tj_pl2, tj_pl6
 
 
+def f_chi2(c, taus38, thC, thV):
+    chi = c[0]*thC + c[1]*thV
+
+    diff = (taus38-chi)/taus38
+    diff2 = (diff*diff).sum()
+    return diff2
+
+
+def fitOffCoeffs(tauses, thCs, thVs):
+
+    Nt = len(tauses)
+    Nc = len(thCs)
+    Nv = len(thVs)
+
+    atau = np.empty((Nt, Nc*Nv))
+    athC = np.empty((Nt, Nc*Nv))
+    athV = np.empty((Nt, Nc*Nv))
+
+    thCgrid, thVgrid = np.meshgrid(thCs, thVs, indexing='ij')
+
+    for i, taus in enumerate(tauses):
+        atau[i, :] = taus.flatten()
+        athC[i, :] = thCgrid.flatten()
+        athV[i, :] = thVgrid.flatten()
+
+    tau = atau.flatten()
+    thC = athC.flatten()
+    thV = athV.flatten()
+
+    offCoeff = 1.0
+
+    off = thV > offCoeff*thC
+    tau38 = np.power(tau, 3.0/8.0)
+
+    guess = (0.65, 0.5)
+
+    res = opt.minimize(f_chi2, guess, (tau38[off], thC[off], thV[off]),
+                       method='TNC', options={'maxiter': 8000})
+
+    if not res.success:
+        print("Fit failed")
+
+    return res.x
+
+
 if __name__ == "__main__":
 
     tN, thVs, thCs, tj_th, tj_g, tj_pl2, tj_pl6 = loadData(sys.argv[1])
@@ -38,15 +84,43 @@ if __name__ == "__main__":
     tau_pl2 = tj_pl2 / tN
     tau_pl6 = tj_pl6 / tN
 
-    thCpVs = thCs[:, None] + thVs[None, :]
-    x = np.linspace(thCpVs.min(), thCpVs.max(), 100)
-
     num = math.pow(0.15, 3.0/8.0)
 
-    chiOnCoeff = 1.18
-    chiOffCoeff = 0.53
+    cCg, cVg = fitOffCoeffs([tau_g], thCs, thVs)
[…]

### 2019-09-25 structuredJets.tex
Arxiv Version??

@@
 
-%\newpage
-%
-%\subsection{Old Draft}
-%
-%The binary neutron star merger \gwbns{} and its associated electromagnetic counterparts provided a wealth of data to high energy astrophysics (CITE).
-Not least among these was its peculiar non-thermal afterglow, first detected in X-rays 9 days after the merger \citep{Troja:2017aa}.
-This was followed by radio 16 days after the merger and optical 73 days after the merger (CITE Radio \& Optical follow-up).
-Unlike any short gamma-ray burst (GRB) afterglow observed before, \grbbns{} steadily {\em rose} in brightness for ~160 days in all observed bands.
-After peak, the emission quickly decayed at a rate similar to other GRB afterglows.
-%
-%The absence of early X-ray emission, with early non-detections by \swiftXRT{} and a deep upper limit from \chandra{}, led early analyses to consider the effect if viewing angle on the emission \citep{Troja:2017aa} (CITE MORE).
-Given the gravitational wave signal of a binary neutron star merger is observable almost regardless of of orientation, it is in fact expected that GRB/GW events would be viewed at moderate inclination.
-%
-%As \grbbns{}'s afterglow continued to rise for weeks after the burst, it became evident the emission could not be explained by a simple uniform ``top hat'' jet viewed off axis.
-More sophisticated models were considered: ``structured jets'' with non-uniform angular distribution of energy and quasi-isotropic ``refreshed shocks'' with significant velocity stratification of the ejecta and modest Lorentz factors.
-The observation of apparent superluminal motion of the radio centroid and the steep turnover of the light curve after 160 days confirmed the relativistic and collimated nature of the outflow, in accordance with the structured jet picture (CITE Mooley, Ghirlanda, YITL, other steepening paper).
-%
-%It is expected, of course, that 
-%
-%Structured jets, blast waves with a non-uniform angular distribution of energy, have been invoked to explain several temporal features in GRB afterglow light curves.  
-%
-%\subsubsection{History of structure and viewing angle}
-%
-%The first GRB afterglow was discovered by \beppoSAX{} as part of GRB 970228 \citep{Wijers:1997aa}.
-GRB afterglows present as broadband synchrotron emission following the prompt gamma-ray signal and can last for days, weeks, months, and years.
-%
-%
-%\subsubsection{What we're doing}
-%
-%In this paper we develop a theoretical model of the electromagnetic afterglow of generic structured jets for arbitrary viewing inclinations.
-The model takes as input the energy and Lorentz factor angular profiles, which may be intrinsic to the jet launching mechanism
-%
-%The light curves resemble broken power laws.
-We calculate viewing angle dependent closure relations, directly relating the effective temporal evolution of the light curve to the viewing angle and explosion geometry.
-%
-%
-%\subsection{Old Old Draft}
-%
-%The electromagnetic afterglow of \gwbns{} gave, quite literally, a new view on gamma-ray burst (GRB) afterglows.  
-%
-%A canonical afterglow was almost immediately ruled out \citep{Troja:2017aa}.  
-%
-%
-%The structure of the blast wave giving rise to gamma-ray burst (GRB) afterglows has been a subject of interest since their discovery by \beppoSAX{} in GRB 970228 \citep{Wijers:1997aa}.
-%
-%{\color{blue} LUIGI: ?was found since early afterglow observations with BeppoSAX, when the
-%presence of a structured outflow has been considered for explaining some of the
-%temporal breaks observed in the light curves of a number of GRBs (Panaitescu and
-%Kumar 2003, Apj 592: 390, Panaitescu 2005 MNRAS 362, 921). Candidates for
-%structured jet exhibit a variation of the decay index at the break smaller that that
-%expected for a top-hat spreading jet ($\Delta \alpha \approx 0.8$) and larger than
-%that induced by the crossing of the cooling frequency ($\Delta\alpha=0.25$). Energy
-%injection by a long lasting central engine can also induce temporal breaks, either
-%flattening or steepening. Other effects such as transition to non-relativistic
-%expansion, the transition from wind-like to ISM (Piro et al. 2005, Apj 623 314) or the
-%emergence of an Inverse compton component (Corsi \& Piro
-%2006A\&A...458..741C) can also produce breaks, in these case associated with a
-%flattening of the light curve.
-%More recenlty Ryan et al (2015) presented evidence of a structured jet in a sample
-%based on SWIFT observations. Considering the number of processes that can
-%produce breaks mentioned above, no undisputable observational evidence of a
-%structured jet became available till the observations of GW170817. Real jets}
-%
-%
-%Gamma-ray burst (GRB) afterglows, since their discovery by \beppoSAX{} in GRB 970228, have been a potent tool for studying GRBs and their progenitors.
-%
-%
-%
-%Gamma-ray burst (GRB) afterglows are commonly modeled as top hat blast waves with no internal structure pointed directly at the observer.
-This has been largely sufficient given the available data, although some evidence of viewing angle effects has been found \citep{Ryan:2015aa}.
-New observational capabilities have witnessed new phases of afterglow evolution, such as the discovery of plateaus with Swift.
-Real jets (of course) have internal structure, but the top hat assumption has been a sufficiently spherical cow.
-%
-%\gwbns{} changes the picture: new object with a strange afterglow.
-Steep/late rise, LONG slow rise, turnover at 160d.
-The slow rise is impossible to reproduce with standard afterglow evolution: first observation of a \emph{structured} phase of evolution.
-%
-%The dominant contribution may be an angular distribution of energy within the blast wave (``structured jet'') combined with off-axis viewing (CITE Rossi04).
-For \gwbns{} this corresponds to the ``successful jet'' picture.
-Alternately, radial stratification of velocity (``refreshed shock'') can cause a similar phase, most simply with a quasi-spherical (or at least top-hat) angular structure.
-This situation is produced by the ``choked jet''  or ``cocoon'' picture of \gwbns{}.
-Understanding the effects of both structures on afterglows, and their dependence on the parameters of the burst, are vital to understanding GW counterparts.
-%
-%To this end, we have calculated the power law temporal slope of the structured phase in both angular and radial structure dominated cases, along with the corresponding observed break times.
-We have developed a semi-analytic numerical model of structured GRB afterglows for detailed comparison to data, which is now publicly available.
-%
-%Summary: In section 2 we discuss structured jets, in section 3 refreshed shocks, in section 4 our numerical model, section 5 application to \gwbns{}, and section 6 future applications and discussion.
-
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The \emph{structured jet} is a GRB jet model where the isotropic-equivalent energy of the blast wave is a function of the angle from the jet axis: $\Eiso = E(\theta)$.
+The \emph{structured jet} is a GRB jet model where the isotropic-equivalent energy of the blast wave is a function of the angle from the jet axis: $\Eiso = 4\pi dE/d\Omega \equiv E(\theta)$.
 The particular angular structure of a jet is first imposed by the jet launching mechanism and then modified by the sculpting that occurs as the jet burrows out of the surrounding ejecta debris (as in a binary neutron star merger) or stellar envelope (as in a collapsar).
@@
 
-% TODO: Look at this again, more detail.
 The rest-frame synchrotron emissivity $\epsilon'_{\nu'}$ may be calculated with varying levels of sophistication.
@@
 We find the choice $\mathtt{latRes} = 5$ gives sufficiently quick performance at acceptable errors, typically on the order of $10^{-2}$.
+
+\afterglowpy{} is available on PyPI and may be installed with {\tt pip} as {\tt pip install afterglowpy}.  The source code is open and available at \url{https://github.com/geoffryan/afterglowpy}.
 
@@
 Bottom Panel: Fractional difference between \afterglowpy{} and \boxfit{} light curves.
-Four representative light curves are shown: radio on-axis ($\thobs=0$, $\nu=10^9$Hz, blue), radio off-axis ($\thobs=0.16$rad, $\nu=10^9$Hz, orange), X-ray on-axis ($\thobs=0$, $\nu=10^{18}$Hz, green), and X-ray off-axis ($\thobs=0.16$rad, $\nu=10^{18}$Hz, red).
+Four representative light curves are shown: radio aligned ($\thobs=0$, $\nu=10^9$Hz, blue), radio misaligned ($\thobs=0.16$rad, $\nu=10^9$Hz, orange), X-ray aligned ($\thobs=0$, $\nu=10^{18}$Hz, green), and X-ray misaligned ($\thobs=0.16$rad, $\nu=10^{18}$Hz, red).
 Remaining parameters are shared: $\thC=0.1$rad, $\Eiso=10^{52}$erg, $n_0 = 10^{-3}$cm$^{-3}$, $p=2.2$, $\epse=10^{-1}$, $\epsB=10^{-2}$, $\dL=3.09 \times 10^{26}$cm, $z=0.028$.
 \label{fig:boxfitComp}}
-%TODO: put distance in Mpc
 \end{figure*}
@@
 Figure \ref{fig:boxfitComp} shows the light curve of a $\thC=0.1$ rad top-hat jet at radio and X-ray frequencies ($10^9$ Hz and $10^{18}$ Hz, respectively) with aligned ($\thobs = 0$) and misaligned ($\thobs=0.16$ rad) viewing angles.
-The light curves begin in the ultra relativistic Blandford-Mckee phase and continue to the Newtonian Sedov phase.
+The light curves begin in the ultra relativistic Blandford-McKee phase and continue to the Newtonian Sedov phase.
 
@@
 At early times, \boxfit{} lacks the simulation coverage to produce accurate fluxes, leading to a large discrepancy.
-Once proper coverage is attained, \boxfit{} and \afterglowpy{} show less than 50\% relative discrepancy until the jet break passes and jet spreading begins.
-After the jet break the \afterglowpy{} light curves show a marked excess relative to \boxfit{}, the relative error increasing to approximately 1.0 and 2.0 for the aligned and misaligned radio light curves, respectively.
-The X-ray light curves achieve approximately half the error of the radio.
-After a short period the \afterglowpy{} light curves begin to decrease, recovering the \boxfit{} slope, and asymptote to similar light curves in the Newtonian regime with a small constant offset from \boxfit{}.
-
-As expected, \afterglowpy{} models the early and late afterglow well, but is somewhat less accurate in an intermediate phase during jet spreading.
-In particular it appears that \afterglowpy{} begins its spreading late relative to \boxfit{}.
+Once proper coverage is attained \boxfit{} and \afterglowpy{} show less than 50\% relative discrepancy, apart from the on-axis radio light curve which briefly has a 60\% discrepancy at the time of the jet break ($t_b \approx 7 \times 10^5$ s for the aligned light curves, $t_b \approx 3\times 10^6$ s for the misaligned).
+After the jet break the \afterglowpy{} light curves recover the \boxfit{} slope, and asymptote to similar light curves in the Newtonian regime with a small constant offset from \boxfit{}.
+
+As expected, \afterglowpy{} models the early and late afterglow well, but is somewhat less accurate in the intermediate phase during the onset of jet spreading.
 This phase is precisely where the non-linear hydrodynamics of the blast wave are most important, and hardest to model with simple semi-analytic approximations.
@@
 \afterglowpy{} is by no means a replacement for full numerical simulations, but is a useful and flexible tool which captures much of the important physics of GRB afterglows at a very small fraction of the cost of a relativistic numerical hydrodynamic simulation.
-
-\afterglowpy{} is available on PyPI and may be installed with {\tt pip} as {\tt pip install afterglowpy}.  The source code is open and available at \url{https://github.com/geoffryan/afterglowpy}.
 
@@
 
-% TODO Finish this paragraph
+Afterglow light curves, even when viewed off axis, can typically be described as a piecewise set of power law segments $F_\nu \propto \tobs^\alpha \nuobs^\beta$, each denoting particular phases of evolution of the blast wave and its emitting region.
+Particular phases have been identified empirically \citep{Nousek:2006aa} and theoretically \citep{Zhang:2006aa}.
+Within a particular phase, the slopes $\alpha$ and $\beta$ are often related through a \emph{closure relation}: an equality determining $\alpha$ from $\beta$ or vice versa.
+Phases change at \emph{break times} when the temporal slope $\alpha$ (and potentially the spectral slope $\beta$) transition rapidly from the previous phase to the next.
+
 To fully characterize the light curves of structured jets we use \afterglowpy{} to construct light curves exploring dependence on jet structure model, viewing angle $\thobs$, opening angle $\thC$, and synchrotron regime.
+We identify the relevant phases in the afterglow and present new closure relations and jet break time scalings for the \emph{structured} phase of evolution: when the patch of the blast wave dominating the emission is sliding from the line of sight towards the jet core.
 
@@
 	\tablecaption{Structured jet closure relations: $F_\nu \propto \tobs^{\alpha} \nuobs^{\beta}$.
-The ``far-off-axis'' phase ($\alpha_{\mathrm{far-off-axis}}$)occurs at early times and only if there is no material directly in the observer's line of sight ($\thobs > \thW$).
+The ``far-off-axis'' phase ($\alpha_{\mathrm{far-off-axis}}$) occurs at early times and only if there is no relativistic material directly in the observer's line of sight ($\thobs > \thW$).
 The ``generic'' slope ($\alpha_{\mathrm{generic}}$) applies whenever the jet is relativistic, non-spreading, and the observer is within the beaming cone of some part of the jet ($|\thobs - \theta_*| < \gamma^{-1}(\theta_*)$).
@@
 The $\som$ parameter encodes how the effective angular size of the jet is changing with Lorentz factor: $\Delta \Omega \propto \gamma^{-\som}$.
+The ``pre-jet break'' phase ($\alpha_{\mathrm{pre}}$) is seen by aligned viewers ($\thobs \lesssim \thC$) and by early misaligned viewers if there is high Lorentz factor material in their line of sight.
 The ``structured'' phase ($\alpha_{\mathrm{struct}}$) is seen by misaligned viewers ($\thobs > \thC$), occurs before the jet break, and corresponds to $\som \approx 1$.
-The ``pre-jet break'' phase ($\alpha_{\mathrm{pre}}$) is seen by aligned viewers ($\thobs \lesssim \thC$) and by early misaligned viewers if there is high Lorentz factor material in their line of sight.
-The first ``post-jet break'' slope ($\alpha_{\mathrm{post, 1}}$) given here does not include the effects of jet spreading and as such is shallower than the true post-jet break slope.
-The second ``post-jet break'' slope ($\alpha_{\mathrm{post, 2}}$) was calculated in \citet{Sari:1999aa}, corresponds to a jet undergoing exponential spreading, and is steeper than the true post-jet break slope.
-\label{tab:slopes}}
-	\tablehead{\colhead{Regime}& \colhead{Label} & \colhead{$\alpha_{\mathrm{far-off-axis}}$} & \colhead{$\alpha_{\mathrm{generic}}$} & \colhead{$\alpha_{\mathrm{struct}}$}& \colhead{$\alpha_{\mathrm{pre}}$}& \colhead{$\alpha_{\mathrm{post, 1}}$} & \colhead{$\alpha_{\mathrm{post, 2}}$} & \colhead{$\beta$}}
+The ``post-jet break'' slopes ($\alpha_{\mathrm{post, 1}}$ and $\alpha_{\mathrm{post, 2}}$) bracket the possible post-jet break behaviour.
+The first is for a non-spreading jet while the second corresponds to a jet undergoing exponential spreading and was calculated \citet{Sari:1999aa}.\label{tab:slopes}}
+	\tablehead{\colhead{Regime}& \colhead{Label} & \colhead{$\alpha_{\mathrm{far-off-axis}}$} & \colhead{$\alpha_{\mathrm{generic}}$} & \colhead{$\alpha_{\mathrm{pre}}$} & \colhead{$\alpha_{\mathrm{struct}}$}& \colhead{$\alpha_{\mathrm{post, 1}}$} & \colhead{$\alpha_{\mathrm{post, 2}}$} & \colhead{$\beta$}}
 	\startdata
-	& & & & \som = 1 & \som=2 & \som=0 &\\
-	& & & &  & g=0 & g=0 & \\[0cm]
-	\nu<\nu_m<\nu_c     & D	& 7 		& \dfrac{-2 + 3\som + 3g}{8+g} 		& \dfrac{1 + 3g}{8+g} 	&1/2		& -1/4	& -1/3 & 1/3 \\[0.4cm]
-	\nu < \nu_c < \nu_m & E	& 17/3 	& \dfrac{-14/3 + 3\som + 11g/3}{8+g}  & \dfrac{-5/3 + 11g/3}{8+g} &1/6 	& -7/12	& -1    & 1/3 \\[0.4cm]
-	\nu_c < \nu < \nu_m & F	& 13/2 	& \dfrac{-8 + 3\som + 2g}{8+g} 		& \dfrac{-5 + 2g}{8+g} 	& -1/4 	& -1		& -1	  & -1/2 \\[0.4cm]
-	\nu_m<\nu<\nu_c     & G 	&\dfrac{15 - 3p}{2} & \dfrac{-6p + 3\som + 3g}{8+g} 	& \dfrac{3 - 6p +3g}{8+g} 	& -\dfrac{3(p-1)}{4} & -\dfrac{3p}{4}	& -p	  & \dfrac{1-p}{2} \\[0.4cm]
-	\nu_m, \nu_c < \nu & H 	& \dfrac{16 - 3p}{2} 	& \dfrac{-6p - 2 + 3\som + 2g}{8+g} 	& \dfrac{1-6p  +2g}{8+g} 	& -\dfrac{3p-2}{4} & -\dfrac{3p+1}{4} & -p & -\dfrac{p}{2} \\[0.4cm]
+	& & & & \som = 2 & \som=1 & \som=0 &\\
+	& & & &  g = 0 & & g=0 & \\[0cm]
+	\nu<\nu_m<\nu_c     & D	& 7 		& \dfrac{-2 + 3\som + 3g}{8+g} 		&1/2	& \dfrac{1 + 3g}{8+g} 		& -1/4	& -1/3 & 1/3 \\[0.4cm]
+	\nu < \nu_c < \nu_m & E	& 17/3 	& \dfrac{-14/3 + 3\som + 11g/3}{8+g}  &1/6 & \dfrac{-5/3 + 11g/3}{8+g} 	& -7/12	& -1    & 1/3 \\[0.4cm]
+	\nu_c < \nu < \nu_m & F	& 13/2 	& \dfrac{-8 + 3\som + 2g}{8+g} 		& -1/4 & \dfrac{-5 + 2g}{8+g} 		& -1		& -1	  & -1/2 \\[0.4cm]
+	\nu_m<\nu<\nu_c     & G 	&\dfrac{15 - 3p}{2} & \dfrac{-6p + 3\som + 3g}{8+g} & -\dfrac{3(p-1)}{4}	& \dfrac{3 - 6p +3g}{8+g} 	 & -\dfrac{3p}{4}	& -p	  & \dfrac{1-p}{2} \\[0.4cm]
+	\nu_m, \nu_c < \nu & H 	& \dfrac{16 - 3p}{2} 	& \dfrac{-6p - 2 + 3\som + 2g}{8+g} 	& -\dfrac{3p-2}{4} & \dfrac{1-6p  +2g}{8+g} 	& -\dfrac{3p+1}{4} & -p & -\dfrac{p}{2} \\[0.4cm]
 	\enddata
@@
 A \emph{coasting} phase, ending at $\tdec$, is assumed to have already completed.
-Each panel shows a fiducial \afterglowpy{} light curve (solid blue lines), power law segments $t^\alpha$ with slopes from the closure relations in Table \ref{tab:slopes} (black dashed lines), and representative break times between each phase of evolution (grey dashed vertical lines).
+Each panel shows a fiducial light curve (solid blue lines), power law segments $t^\alpha$ with slopes from the closure relations in Table \ref{tab:slopes} (black dashed lines), and representative break times between each phase of evolution (grey dashed vertical lines).
 The two dashed lines in the ``post-jet break'' section bracket the possible light curve behaviour.
@@
 
-\emph{Coasting} --- Before the blast wave begins to decelerate it coasts at constant Lorentz factor. The emissivity is constant, and the total flux increases $F_\nu \propto t^3$.
+\emph{Coasting} --- Before the blast wave begins to decelerate it coasts at constant Lorentz factor.
+The flux depends only on the total volume of the emitting region and the evolution of the cooling frequency $\nu_c$.
 
@@
 a cocoon) \citep{Nakar:2011aa, Hotokezaka:2015aa}.
+Both scenarios are particularly relevant to afterglows arising from binary neutron star mergers.
 In either case, slow material initially coasting behind the shock is gradually incorporated into the blast wave as it decelerates, ``refreshing'' the shock.
-This mechanism is a general scenario for energy injection \citep{Zhang:2006aa}, and was proposed as the mechanism behind the \gwbns{} afterglow in the choked-jet scenario (e.g.
+This mechanism is a general scenario for energy injection \citep{Zhang:2006aa}, and was proposed as the mechanism behind the \gwbns{} afterglow in the choked-jet picture (e.g.
 \citep{Mooley:2018aa, Nakar:2018aa}).
@@
 \begin{equation}
-	E(u) = E_r u^{-k}\ , \label{eq:Eu}
-\end{equation}
-where $u \in (\umin, \umax)$ is the dimensionless four-velocity, $k>0$ is the power law index, and $E_r$ is a normalization factor.  The mass ejected with velocity $\umax$ is $\Mej$.
-
-%
-%  TODO:  Comment: define tdec, tmin IN THE TEXT.   Add (brief) discussion of light curve phases.
-%
-
-% TODO: Put in obs frame?
+	E(u) = E_0 \left(\frac{u}{\umax}\right)^{-k}\ , \label{eq:Eu}
+\end{equation}
+where $u \in (\umin, \umax)$ is the dimensionless four-velocity, $k>0$ is the power law index, and $E_0$ the kinetic energy of the fastest material with $u=\umax$ initially.
+The mass ejected with velocity $\umax$ is $\Mej = E_0 / ((\gmax -1)c^2)$.
 
@@
 The transition between coasting and decelerating occurs in the bursters frame at $\tdec$.
-The shock refreshment ends when the blast wave decelerates past $\umin$, in the observers frame at $\tumin$.
-In the single shell model with trans-relativistic equation of state used here, these times are:
-\begin{align}
-	\tdec &= \left(\frac{9}{4\pi} \frac{\Mej}{n_0 \Mp c^3} \frac{\gmax^2}{\bmax^3(\gmax+1)(4\umax^2+3)} \right)^{1/3}  \ ,\label{eq:tdec} \\
-	\tumin &= \left(\frac{9}{16\pi} \frac{E_r}{n_0 \Mp c^5}\right)^{1/3} \umin^{-8/3} \ .\label{eq:tumin}
-\end{align}
-Equation \eqref{eq:tumin} assumes $E_r \gg \Mej c^2$.   The temporal and spectral slopes in this mechanism depend on the energy distribution index $k$ and are given in Table \ref{tab:refreshSlopes}.
+The shock refreshment ends at $\tumin$ when the blast wave decelerates past $\umin$, when there is no longer any material to refresh it.
+At this point the afterglow transitions to a standard pre-jet break phase.
+In the single shell model with in the limit $\umax \gg 1$, these transition times (in the observer's frame) are:
+\begin{align}
+	\tdec &= \frac{1}{4}(1+z)   \umax^{-8/3}\ \!
+\tNR  \ , \label{eq:tdec} \\ %\left(\frac{9}{4\pi} \frac{\Mej}{n_0 \Mp c^3} \frac{\gmax^2}{\bmax^3(\gmax+1)(4\umax^2+3)} \right)^{1/3}  \ ,\label{eq:tdec} \\
+	\tumin &= \frac{1}{4}(1+z) \frac{2+k}{8+k} \left(\frac{\umax}{\umin}\right)^{(8+k)/3} \umax^{-8/3}\ \! \tNR \ .\label{eq:tumin}
+\end{align}
+ The temporal and spectral slopes for the coasting and refreshing phases are given in Table \ref{tab:refreshSlopes}.
+The refreshing phase slope $\alpha_{\mathrm{refresh}}$ depends on the energy index $k$.
+A quasi-spherical blast wave experiences very little or no jet spreading and should smoothly transition to the Newtonian Sedov phase after $\tumin$ passes and the energy injection ends.
 
@@
 That work specifies the index $s$ of the mass distribution $M_{>u} \propto u^{-s}$, which is related simply to the index $k$ by $k = s-1$.
-Under this mapping the closure relations in Table \ref{tab:slopes} are equivalent to those in \cite{Zhang:2006aa} and the model can be seen as equivalent to an energy injection model with $q = (8-2k) / (8+k)$.
+Under this mapping the closure relations in Table \ref{tab:refreshSlopes} are equivalent to those in \cite{Zhang:2006aa} and the model can be seen as equivalent to an energy injection model with $q = (8-2k) / (8+k)$.
 
@@
 Once this change is accounted for, the $g$ parameter plays the same role as $k$, as can be seen by a simple comparison between $\alpha_{\text{struct}}$ in Table \ref{tab:slopes} and $\alpha_{\text{refresh}}$ in Table \ref{tab:refreshSlopes}.
-That is, a structured jet light curve is equivalent to a standard energy injection model with:
+That is, a structured jet light curve is similar to a standard energy injection model with:
 \begin{align}
@@
 \end{align}
+
+It should be noted that although one can map structured jet light curves onto an energy injection model, there is no energy being added to the blast wave.
+Rather, the ``injection'' of energy is the additional flux from higher energy portions of the jet decelerating to the point the observer is in their beaming cone.
 
@@
 	\includegraphics[width=\textwidth]{figs/lc_170817A_Gaussian_map.pdf}
-	\caption{\label{fig:lc170817A}}
+	\caption{The afterglow light curve of \grbbns{} in radio (3 GHz, green, top), optical (590 nm, blue, middle), and X-ray (5 keV, purple, bottom).
+For illustrative purposes, radio and optical data have been shifted to their fiducial frequencies assuming $F_\nu \propto \nu^{-0.585}$, appropriate for the G synchrotron regime with $p=2.17$.
+Downward pointing triangles are 3-sigma upper limits.
+Solid lines show the best fit (maximum posterior probability) Gaussian jet light curve.
+Some upper limits with low constraining power were not included in the figure.
+The dataset is that of \citet{Troja:2019ab} with additional \hubble{} data points from \citet{Lamb:2019aa}.
+\label{fig:lc170817A}}
 \end{figure*}
@@
 At this point the light curve turned over and began a steep decay that continues to the present \citep{Alexander:2018aa, Fong:2019aa, Lamb:2019aa, Troja:2019ab}.
-
-% TODO: REDO with new tb fits.
 
@@
 	\item We can use the jet break $\tb$ measurement to determine $\thobs + \thC$ using Equation \eqref{eq:tbout}.
-Using our assumed values for  $E_0$ and $n_0$ leads to $\thobs + \thC \approx 0.92 \pm 0.38$ rad ($53^\circ \pm 22^\circ$).
+Using our assumed values for  $E_0$ and $n_0$ leads to $\thobs + 1.24 \thC \approx 0.93 \pm 0.38$ rad ($53^\circ \pm 22^\circ$).
 This does not depend on the jet model.
-	\item For a Gaussian jet the combined measurements of $\thobs +\thC$ and $\thobs/\thC$ then imply $\thC \approx 0.14 \pm 0.06$ rad ($8.0^\circ  \pm 3.4^\circ$) and $\thobs \approx 0.78 \pm 0.32$ rad ($45^\circ \pm 18^\circ$).
-	\item For a $b=6$ power law jet we get $\thC \approx 0.063 \pm 0.026$ rad ($3.6^\circ  \pm 1.5^\circ$) and $\thobs \approx 0.86 \pm 0.35$ rad ($49^\circ \pm 20^\circ$).
+	\item For a Gaussian jet the combined measurements of $\thobs +1.24\thC$ and $\thobs/\thC$ then imply $\thC \approx 0.13 \pm 0.06$ rad ($7.6^\circ  \pm 3.1^\circ$) and $\thobs \approx 0.78 \pm 0.31$ rad ($44^\circ \pm 18^\circ$).
+	\item For a $b=6$ power law jet we get $\thC \approx 0.062 \pm 0.026$ rad ($3.5^\circ  \pm 1.5^\circ$) and $\thobs \approx 0.85 \pm 0.35$ rad ($49^\circ \pm 20^\circ$).
 \end{enumerate}
@@
 This is, of course, due to the very different energy profiles $E(\theta)$ in each model.
-Both models can easily accommodate a rising light curve $F_\nu \sim t^{0.9}$, that is produce an effective structure parameter $\geff = 7.5$, but do so using very different geometries.
+Both models can easily accommodate a rising light curve $F_\nu \sim t^{0.9}$, that is produce an effective structure parameter $\geff = 7.5$, but do so using somewhat different geometries.
 
@@
 
-This degeneracy is a blessing and a curse.
+This degeneracy is both useful and unfortunate.
 The presence of an extended slowly decaying or rising afterglow is a largely model independent prediction of misaligned viewing and the presence of non-trivial jet structure.
@@
 
-%TODO - Discuss in text
 \begin{figure}
-	\includegraphics[width=\columnwidth]{figs/fit_E_theta.pdf}
-	\caption{Inferred $E(\theta)$ for \gwbns{} assuming Gaussian (blue, solid line) or power law (orange, dashed line) structure models.
-Lines show the median posterior value for $E(\theta)$ at each fixed value of $\theta$, shaded regions show the symmetric 68\% confidence interval (16\% and 84\% quantiles) at each $\theta$.
-\label{fig:fit_E_theta.pdf}}
+	\includegraphics[width=\columnwidth]{figs/fit_E_theta_model_0.pdf}
+	\caption{Inferred $E(\theta)$ for \grbbns{} in each quartile of the inferred $\thobs$ distribution, assuming Planck $H_0$ and Gaussian jet structure.
+Shaded bands show the symmetric 95\% confidence interval for $E(\theta)$ for $\thobs$ in the 0\%-25\% quartile (red), 25\%-50\% quartile (green), 50\%-75\% quartile (orange), 75\%-100\% quartile (blue).
+The quartile boundaries are $\theta_{\mathrm{obs}, 0} = 10.9^\circ$, $\theta_{\mathrm{obs}, 25} = 19.9^\circ$, $\theta_{\mathrm{obs}, 50} = 25.0^\circ$, $\theta_{\mathrm{obs}, 75} = 29.7^\circ$, and $\theta_{\mathrm{obs}, 100} = 45.8^\circ$.
+Uncertainty in $E(\theta)$ is directly correlated with uncertainty in $\thobs$: improved knowledge of one improves knowledge of the other.\label{fig:fit_E_theta}}
 \end{figure}
+
+As an example, Figure \ref{fig:fit_E_theta} shows the $95\%$ confidence intervals on $E(\theta)$ for each quartile of the $\thobs$ distribution from the Gaussian jet fit to \grbbns{}.
+The power law jet fit shows similar behaviour.
+Smaller values of $\thobs$ are correlated with more highly collimated profiles and larger energies on the jet axis, while larger values of $\thobs$ require broader profiles and less energy on the jet axis.
+Between the first ($\thobs < 19.9^\circ$) and fourth ($\thobs > 45.8^\circ$) quartiles the upper bound on $E_0$ lowers by more than an order of magnitude, while the bounds on energy at $\theta = 15^\circ$ shift upwards by three orders of magnitude.
+This is a consequence of the tight constraint on $\thobs/\thC$ from $\alpha_{\mathrm{struct}}$ but relatively loose constraints on other parameter combinations.
+At fixed $\thobs/\thC$, smaller inclinations necessarily require smaller jet opening angles and vice versa.
+
+Any attempt to robustly measure $\thobs$ from the afterglow light curve must be sure to allow a large variety of structure profiles $E(\theta)$ to avoid biasing the result.
+Conversely, any attempt to robustly measure the parameters of $E(\theta)$ must consider the full range of $\thobs$.
+On the other hand, any method of breaking the degeneracy and measuring $\thobs$ or $E(\theta)$ independently will also help constrain the other.
 
@@
 Utilizing posteriors from the gravitational wave signal or fitting the VLBI observations of superluminal apparent motion can greatly improve constraints on $\thobs$ \citep{Troja:2018aa, Hotokezaka:2018aa, Ghirlanda:2019aa}.
-Since the afterglow presumably provides good constraints on $\geff$ (via $\alpha$), improved knowledge of $\thobs$ immediately improves knowledge of $\thC$, $b$, and any other parameters relevant to $E(\theta)$.
-In some cases this may rule out a particular $E(\theta)$ entirely by pushing the relevant parameters to extreme values, for instance it is hard (but not impossible) to reconcile the observations of \gwbns{} with a $b=2$ power law.
+Since the afterglow presumably provides good constraints on $\geff$ (via $\alpha$), improved knowledge of $\thobs$ immediately improves knowledge of $\thC$, $b$, and any other parameters relevant to $E(\theta)$ (see for example Table 2 of \citet{Troja:2018aa}).
+In some cases this may rule out a particular $E(\theta)$ entirely by pushing the relevant parameters to extreme values, for instance it is very hard to reconcile the observations of \grbbns{} with a $b=2$ power law jet.
 
@@
 	\includegraphics[width=\columnwidth]{figs/g_plot.pdf}
-	\caption{Structure parameter $g$ as a function of $\thobs/\thC$ for different structured jet models: Gaussian (blue), $b=2$ power law (orange), $b=4$ power law (green), and $b=6$ power law (red).
-The inferred value $g = 8.2\pm0.5$ for \gwbns{} is shown in as the grey band.
+	\caption{Structure parameter $g$ as a function of $\thobs/\thC$ for different structured jet models: Gaussian (green, solid), $b=2$ power law (orange, dash-dotted), $b=6$ power law (red, dotted), and $b=9$ power law (blue, dashed).
+The inferred value $g = 8.2\pm0.5$ for \grbbns{} is shown in as the grey band.
 \label{fig:gPop}}
@@
 
-TODO: INCLUDE BRIEF COMPARISON TO EACH.  NOTE DIFFERENT MODELS PRODUCE SAME LIGHT CURVE, STRONG EFFECT OF VLBI.
+\citet{Hotokezaka:2018aa} finds a very tight constraint for the viewing angle, $\thobs = 0.29 \pm 0.01$ rad and $\thobs = 0.30 \pm 0.01$ rad for their power law and Gaussian models, respectively.
+The large constraining power of the apparent superluminal motion is quite evident.
+They find $\thC \approx 0.05$ rad for the Gaussian jet, which lies along the $\thobs/\thC = 5.7\pm 0.2$ degeneracy from $\alpha_{\mathrm{struct}}$ for the Gaussian jet, in agreement with the closure relations.
+They also find $\thC \approx 0.05$ rad for the power law jet, which is not directly comparable with our constraints due to different formulations of the power law profile.
+They also find $\log_{10} E_0 / n_0 \approx 56$ for both models, in agreement with our constraints.
+\citet{Ghirlanda:2019aa} uses a power law jet structure profile with the same formulation as \citet{Hotokezaka:2018aa} and sees consistent results.
+The inferred parameters have somewhat larger uncertainties as they did not observe apparent superluminal motion and rely on constraints from the size of the radio centroid.
+
+\citet{Lamb:2019aa} fits the \grbbns{} afterglow with both a Gaussian structured jet and a two-component model.
+For the Gaussian they find $\thobs = 0.34 \pm 0.02$ rad and $\thC = 0.06 \pm 0.01$ rad, where we have adjusted their $\thC$ by a factor of $\sqrt{2}$ to keep in line with our definition.
+Their tight bounds on both parameters are due in part to their restricted set of priors, which bound 0.3 rad < $\thobs$ < 0.4 rad.
+Their $\thobs$ and $\thC$ also lie along $\thobs/\thC = 5.7 \pm 0.2$, and within their relatively narrow priors the other inferred parameters are consistent with ours in Table \ref{tab:MCMC} and Figure \ref{fig:cornerGaussian}.
+
+\citet{Wu:2018aa} uses light curves tabulated from numerical simulations initialized with the boosted fireball model \citep{Duffell:2013aa}, parameterized by an initial bulk Lorentz factor $\gamma_B$ and specific internal energy $\eta_0$ instead of an opening angle $\thC$, although roughly $\thC \sim \gamma_B^{-1}$.
+They find $\thobs = 0.47^{+0.17}_{-0.05}$ rad, somewhat larger than other works due primarily to focusing on the afterglow alone and not including GW or VLBI constraints.
+They demonstrate a clear anti-correlation between $\gamma_B$ and $\thobs$ of $\gamma_B \thobs  \sim \thobs/\thC \approx 5$, and other parameters consistent with this and other studies.
+
+It is somewhat remarkable that the disparate structured jet models used by these and other works in the literature to analyze \gwbns{} all manage to recreate the afterglow light curve with similar jet and microphysical parameters.
+It also demonstrates that even with an event as well-observed as \gwbns{} it will be difficult to robustly determine the energy profile of the jet.
 
@@
 Since many of these events may be faint and distant, it will be important to leverage as much information from the afterglow light curve as possible.
-As shown here, and evidenced by the diversity of models that have ``fit'' the \gwbns{} afterglow, there is a large degeneracy between viewing angle and jet structure profile.
+As shown here, and evidenced by the diversity of models that have fit the \gwbns{} afterglow, there is a large degeneracy between viewing angle and jet structure profile.
 To make robust inferences about these events, several flexible jet models must be included in the analysis.
@@
 
-We have constructed flexible models for the electromagnetic afterglows of angularly structured relativistic jets.
+We have constructed flexible models for the electromagnetic afterglows of angularly structured relativistic jets for aligned and misaligned observers.
 Through analytic approximations we can identify the basic phases of the structured afterglow light curve, determining formulae for the characteristic break time scales and closure relations.
-We find the closure relations depend on a single parameter we call $g$ relating to the jet structure and viewing angle.
+We find the closure relations depend on a single parameter we call $g$ related to the jet structure and viewing angle.
 Measurements of $g$ itself are model independent, but relating it back to physical parameters of the jet is not.
@@
 It is fast enough to be incorporated in MCMC parameter estimation routines.
-Fitting the \gwbns{} afterglow with multiple \afterglowpy{} models reveals the degeneracy between jet structure and viewing angle.
+Fitting the \gwbns{} afterglow with multiple \afterglowpy{} models allows jet parameters to be inferred, but the degeneracy between jet structure and viewing angle makes determining a particular jet profile difficult.
+Incorporating data beyond the afterglow light curve, including constraints from gravitational wave observations and detailed electromagnetic followup such as VLBI, will be key to learning as much as we can from future events.
 
@@
 The diagonal contains one-dimensional marginalized posteriors for each fit parameter, while the off-diagonal plots contain two-dimensional maps of the posterior marginalized over all but the two corresponding parameters.
+Dashed lines and labels along the diagonal give the median value and symmetric 68\% uncertainties (the 16\% and 84\% quantiles) for each parameter's marginalized distribution.
+Blue dashed line shows the location of the sample with maximum posterior probability.
 \label{fig:cornerGaussian}}
@@
 	\includegraphics[width=\textwidth]{figs/cornerPowerlaw.pdf}
-	\caption{Views of the posterior parameter distribution for a power law jet fit to the \gwbns{} afterglow.
-The diagonal contains one-dimensional marginalized posteriors for each fit parameter, while the off-diagonal plots contain two-dimensional maps of the posterior marginalized over all but the two corresponding parameters.
-\label{fig:cornerPowerlaw}}
+	\caption{As Figure \ref{fig:cornerGaussian} for the power law jet model. \label{fig:cornerPowerlaw}}
 \end{figure*}

### 2019-09-25 code/gPlot.py

@@ -1,27 +1,43 @@
 import numpy as np
 import matplotlib.pyplot as plt
+import paperPlots as pp
 
 
 def calc_gG(thV, thC):
 
-    return 0.25*thV*thV/(thC*thC)
-
-
-def calc_gPL(thV, thC, b):
-
-    th = 0.2*thV + 2.0*thC/3.0
-
-    g = (thV-th) * b * th / (thC*thC + th*th)
+    athV = np.atleast_1d(thV)
+    g = np.empty(athV.shape)
+    for i in range(len(g)):
+        Y = np.empty(5)
+        Y[0] = athV[i]
+        Y[2] = thC
+        Y[3] = 20*thC
+        g[i] = pp.calcGEff(0, Y)
 
     return g
 
 
-x = np.linspace(0.0, 10.0, 300)
+def calc_gPL(thV, thC, b):
+
+    athV = np.atleast_1d(thV)
+    g = np.empty(athV.shape)
+    for i in range(len(g)):
+        Y = np.empty(5)
+        Y[0] = athV[i]
+        Y[2] = thC
+        Y[3] = 20*thC
+        Y[4] = b
+        g[i] = pp.calcGEff(4, Y)
+
+    return g
+
+
+x = np.linspace(0.0, 15.0, 300)
 
 gG = calc_gG(x, 1.0)
 gPL2 = calc_gPL(x, 1.0, 2)
-gPL4 = calc_gPL(x, 1.0, 4)
 gPL6 = calc_gPL(x, 1.0, 6)
+gPL9 = calc_gPL(x, 1.0, 9)
 
 p = 2.17
 al = 0.9
@@ -39,18 +55,15 @@ dg = np.fabs(dgda) * dal
 print("al = {0:.3f} +/- {1:.3f}".format(al, dal))
 print("g  = {0:.3f} +/- {1:.3f}".format(g, dg))
 
-lw = 3.0
-fontsize = 24
-ticksize = 18
-legendsize = 18
+lw = 1.5
 """
 fig, ax = plt.subplots(1, 1, figsize=(8, 6))
 """
 fig, ax = plt.subplots(1, 1)
-ax.plot(x, gG, lw=lw, label=r'Gaussian')
-ax.plot(x, gPL2, lw=lw, label=r'Power Law $b=2$')
-ax.plot(x, gPL4, lw=lw, label=r'Power Law $b=4$')
[…]

### 2019-09-25 code/plotModelSpread.py

@@ -1,0 +1,538 @@
+import sys
+import numpy as np
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+import afterglowpy as grb
+import h5py as h5
+import corner
+
+
+def E_Gaussian(th, thC, thW, b):
+    E = np.exp(-0.5*th*th/(thC*thC))
+    E[th > thW] = 0.0
+    return E
+
+
+def E_powerlaw1(th, thC, thW, b):
+    TH = np.sqrt(1 + th*th/(thC*thC))
+    E = np.power(TH, -b)
+    E[th > thW] = 0.0
+    return E
+
+
+def E_powerlaw2(th, thC, thW, b):
+    TH = np.sqrt(1 + th*th/(b*thC*thC))
+    E = np.power(TH, -b)
+    E[th > thW] = 0.0
+    return E
+
+
+def weightNull(flatchain):
+
+    return np.ones(flatchain.shape[0])
+
+
+def weightPlanck(flatchain):
+
+    thv = flatchain[:, 0]
+    cthv = np.cos(thv)
+
+    # From Fitting Figure 3 of LIGO Standard Siren Paper
+    cv0 = 0.985
+    sig = 0.070
+
+    x = (cthv-cv0)/sig
+    w = np.exp(-0.5*x*x)
+
+    return w
+
+
+def weightSHoES(flatchain):
+
+    thv = flatchain[:, 0]
+    cthv = np.cos(thv)
+
+    cv0 = 0.909
+    sig = 0.068
+
+    x = (cthv-cv0)/sig
+    w = np.exp(-0.5*x*x)
+
+    return w
+
+
+def weightLIGO(flatchain):
+
+    thv = flatchain[:, 0]
+    cthv = np.cos(thv)
+
+    cv0 = 0.958
+    sig = 0.266
+
+    x = (cthv-cv0)/sig
+    w = np.exp(-0.5*x*x)
+
+    return w
+
+
+def percentile_1d(a, q, w=None):
+
+    if w is None:
+        return np.percentile(a, q)
+
+    return corner.quantile(a, np.array(q)/100.0, w)
+
+
+def percentile_2d(a, q, w=None, axis=None):
+
+    if w is None:
+        return np.percentile(a, q, axis=axis)
+
+    if axis is None:
+        return corner.quantile(a.flat, np.array(q)/100.0, w)
+
+    if axis == 0:
+        ret = np.empty((len(q), a.shape[1]))
[…]

### 2019-09-25 code/quick170817Analysis.py

@@ -31,7 +31,7 @@ def th2g_pl(thVoC, b):
 
 
 def tb2thp(tb, Eon):
-    thVpC = 0.3 * np.power(tb/6.54, 0.375) * np.power(Eon, -0.125)
+    thVpC = 0.5 * np.power(tb/24.9, 0.375) * np.power(Eon, -0.125)
     return thVpC
 
 
@@ -46,13 +46,13 @@ def tb2ethp(tb, Eon, etb, elEon):
 
 
 def po2C(thVpC, thVoC):
-    thC = thVpC / (1+thVoC)
+    thC = thVpC / (1.24+thVoC)
     return thC
 
 
 def po2eC(thVpC, thVoC, ethVpC, ethVoC):
-    dCdp = 1.0 / (1+thVoC)
-    dCdo = -thVpC / (1+thVoC)**2
+    dCdp = 1.0 / (1.24+thVoC)
+    dCdo = -thVpC / (1.24+thVoC)**2
 
     ethC = np.sqrt((dCdp*ethVpC)**2 + (dCdo*ethVoC)**2)
 
@@ -60,13 +60,13 @@ def po2eC(thVpC, thVoC, ethVpC, ethVoC):
 
 
 def po2V(thVpC, thVoC):
-    thC = thVpC * thVoC / (1+thVoC)
-    return thC
+    thV = thVpC * thVoC / (1.24+thVoC)
+    return thV
 
 
 def po2eV(thVpC, thVoC, ethVpC, ethVoC):
-    dVdp = thVoC / (1+thVoC)
-    dVdo = thVpC / (1+thVoC)**2
+    dVdp = thVoC / (1.24+thVoC)
+    dVdo = 1.24*thVpC / (1.24+thVoC)**2
 
     ethV = np.sqrt((dVdp*ethVpC)**2 + (dVdo*ethVoC)**2)
 
@@ -83,12 +83,11 @@ tb = 164
 etb = 12
 
 Eon = 20.0/10.0
-# Eon = 30
 elEon = math.sqrt(2) * 1.0
 
 # GW170817 fits
-Eon = math.pow(10.0, 2.6)
-elEon = 1.0
+# Eon = math.pow(10.0, 2.6)
+# elEon = 1.0
 
 p = 1-2*be
 ep = 2*ebe
@@ -145,11 +144,15 @@ for i, b in enumerate(bs):
     print("thV/thC (PL {0:.1f}) = {1:.3f} +/- {2:.3f}".format(b, thVoC_pl[i],
[…]

### 2019-09-25 structuredJets.tex
Arxiv Version

@@
 Unlike typical afterglows, which begin bright and decay from detection with a ~week timescale, \grbbns{}'s non-thermal emission was undetectable until the first observation of X-rays nine days after the GRB \citep{Troja:2017aa}.
-At this point the afterglow began steadily increasing in brightness in at all wavelengths for ~160 days \citep{Haggard:2017aa, Hallinan:2017aa, DAvanzo:2018aa,  Lyman:2018aa, Margutti:2018aa, Mooley:2018aa, Troja:2018aa, Troja:2019ab}.
+At this point the afterglow began steadily increasing in brightness at all wavelengths for $\sim160$ days \citep{Haggard:2017aa, Hallinan:2017aa, DAvanzo:2018aa,  Lyman:2018aa, Margutti:2018aa, Mooley:2018aa, Troja:2018aa, Troja:2019ab}.
 Very long baseline (VLBI) radio imagery over this period identified a radio core with an apparent superluminal motion, indicating the emitting surface was moving at relativistically at an oblique angle towards the Earth \citep{Mooley:2018ab}.
@@
 In Section \ref{sec:numerical} we develop our theoretical framework and describe its numerical implementation in \afterglowpy{}.
-Section \ref{sec:structuredJets} characterizes the general behavior of structured jet afterglow light curves, provides the closure relations with explicit viewing angle dependence, and relates structured jets to standard energy injection models.
+Section \ref{sec:structuredJets} characterizes the general behavior of structured jet afterglow light curves, provides the closure relations and jet break times with explicit viewing angle dependence, and relates structured jets to standard energy injection models.
 Section \ref{sec:gw170817} demonstrates an application to \gwbns{}.
@@
 Through analytic approximations we can identify the basic phases of the structured afterglow light curve, determining formulae for the characteristic break time scales and closure relations.
-We find the closure relations depend on a single parameter we call $g$ related to the jet structure and viewing angle.
+We find the closure relations depend on a single dimensionless parameter $g$ related to the jet structure and viewing angle.
 Measurements of $g$ itself are model independent, but relating it back to physical parameters of the jet is not.
@@
 \afterglowpy{} computes afterglow light curves on the fly utilizing semi-analytic approximations to the jet evolution and synchrotron emission, taking into account relativistic beaming, the equal time of arrival surface, jet angular structure, trans-relativistic evolution, and jet spreading.
-It is fast enough to be incorporated in MCMC parameter estimation routines.
+It is fast enough to be incorporated in MCMC parameter estimation routines, available via {\tt PyPI} and {\tt pip}, and has source code available at: \url{https://github.com/geoffryan/afterglowpy}.
 Fitting the \gwbns{} afterglow with multiple \afterglowpy{} models allows jet parameters to be inferred, but the degeneracy between jet structure and viewing angle makes determining a particular jet profile difficult.
@@
 
+The marginalized posterior limits on the afterglow parameters presented in Table \ref{tab:MCMC} are a useful summary but do not show how the inferred parameter values correlate with each other.
+Figures \ref{fig:cornerGaussian} and \ref{fig:cornerPowerlaw} show all pairwise correlations between parameters in our fits to \grbbns{} for the Gaussian and power law jet models respectively, as well as the marginalized distributions for each parameter.
+
 \begin{figure*}

### 2020-05-13 refereeResponse.txt
working on ref report

We thank the referee for their thoughtful report and comments. They highlighted several areas where the text was not clear, the revised manuscript is much improved.  Our responses to the referee's comments are below, with the associated changes to the text.

1. My main concern is the Lorentz factor profile which is currently modeled. Right now, it is assumed that the fluid elements at higher latitudes would contribute to the observed emission along the line of sight when their Lorentz factor becomes the same as that along the line of sight. This is not necessarily the case in reality. In my mind, different fluid elements along different polar angles may evolve differently, and the observed emission is roughly from a smaller 1/\gamma half cone near the polar region and a larger 1/\gamma half cone from the wing region. I suppose when such a detailed modeling is included, the lightcurves would be different for different \Gamma(\theta) profiles even if the E(\theta) and \theta_{obs} are the same. The authors should emphasize this issue throughout the paper (including in the abstract and conclusions), especially when closure relations are presented, so that future users can keep this caveat in mind when they apply the relations.

--

The referee is correct: fluid elements at different latitudes evolve differently, and the emitting region is asymmetric due to the differing Lorentz factors (as well as time-of-flights for the emitted photons) along the latitudinal direction.  However, these effects are already accounted for in our numerical model (afterglowpy).  Each annular section of the jet evolves independently, with its own Lorentz factor dependent on its initial energy.  We then integrate over all sections, taking into account doppler factors and time-of-flight, to arrive at a final flux.

We do not assume "fluid elements at higher latitudes would contribute to the observed emission along the line of sight when their Lorentz factor becomes the same as that along the line of sight".  In our numerical model we integrate over the entire jet surface, relativistic doppler factors naturally and appropriately reduce the contribution of sections which are beamed away from the observer.  In our analytic modeling, we assume regions whose beaming cone includes the observer contribute to the flux, but the flux is dominated by the brightest of these regions.  The brightest region will be that with the highest Lorentz factor, which will be located closest to the jet core.  This will be the case so long as E(theta) is a decreasing function of theta.

Once each section of the jet begins decelerating, the initial Lorentz factor profile gamma(theta) becomes less important.  An ultra relativistic, adiabatic, decelerating blast wave obeys E \propto R^3 \gamma^2, hence \gamma \propto E^{1/2} R{-3/2}.  Given an initial profile E(\theta), the profile \gamma(\theta) in the deceleration regime is fixed.  This is true for trans-relativistic blast waves too, although the particular form of the relation \gamma ~ E,R relation will change.  The initial \gamma(\theta) plays an important role in the early evolution of the blast wave and its observed light curve, but is forgotten as more of the jet begins deceleration.

We have added remarks clarifying the role of the Lorentz factor profile and its treatment throughout the text.

-- added "decelerating" to the description of the jets under consideration in the abstract.

-- added Section 2.1: To clarify the role of the Lorentz factor profile, and justify our focus on the energy profile) we expanded the last paragraph of section 2 into a new section 2.1.

-- moved start of Section 3.1 two paragraphs down, appended "Top-Hat Case" to the name

-- added new Section 3.2 detailing how top-hat sections are integrated into a structured jet light curve, emphasizing the non-trivial profile of shock radius and velocity (e.g. Lorentz factor)

-- added two sentences in the "Coasting" paragraph of Section 4.1 noting that we do not model the initial Lorentz factor profile and so may miss some phenomenology in the transition to the later phases of evolution.

-- expanded the explanation of the "structured" phase in Section 4.1 to emphasize the role of the Lorentz factor and the asymmetric shape of the emitting region.

-- Amended the captions of Table 1 and Figure 3 to denote these apply only when the jet is decelerating.

-- Added a sentence to the summary emphasizing the results are only appropriate for decelerating jets.

2. I understand that the authors introduced s_\Omega to partially account for the uncertainty of E(\theta) effect and probably \Gamma(\theta) effect as well. However, I do not understand why the typical value is s_\Omega = 1. I understand that the opening angle scales as 1/\gamma_*. However, the solid angle should carry the dimension of (1/\gamma_*)^2, so that s_\Omega should be approximately 2 to me.

--

s_\Omega is certainly equal to 2 in a standard afterglow when the emitting surface has a (mostly) uniform Lorentz factor.  In the structured phase, we can think of the solid angle as being the product of two parts:  \Delta Phi and \Delta \Theta.  In the azimuthal direction (a line of constant theta), the Lorentz factor is uniform and so \Delta \Phi \propto 1 / \gamma_*  as expected.  In the polar direction (a line of constant phi), however, the situation is not as simple.  We consider a point theta_* on the jet which is the centroid of emission.  If dE/d\theta (or equivalently d\gamma/d\theta) is sufficiently large, then material at theta_* - 1/gamma_* (towards the core) will have substantially larger Lorentz factor and be beamed away from the observer.  Material at \theta_* + 1/gamma_* (away from the core) will have substantially lower Lorentz factor and be subdominant to the emission.  Therefore \Delta \theta can not equal 1/\gamma_*.  In this case it is dE/d\theta which controls the visible solid angle in the polar direction, not \gamma_*.  The solid angle depends on the Lorentz factor like 1/gamma_* and s_\Omega = 1.

In detail s_\Omega will smoothly transition between 2 (in the standard afterglow) 1 (during a structured phase) and 0 (after the jet break).  The detailed evolution depends on the particular energy profile and parameters, but in our explorations (as shown in Figs 3 and 7) s_\Omega = 1 is a good approximation for the bulk behaviour during the structured phase.

Our expanded discussion of the structured phase in Section 4.1 goes into more detail about the shape of the emitting region and why s_\Omega can equal 1.

3. When numerical models reach accuracy better than 10^{-4}, one should avoid introducing physical inaccuracy larger than 10^{-4}. I don't know what is the inaccuracy introduced by the crude treatment of synchrotron radiation, but another source of inaccuracy could originate from the equation of state. According to Eqs.(5) and (6), the adiabatic index \hat\gamma is adopted as 3/4. This is the extreme value for a relativistic fluid. The approximation may not be good for large viewing angles at late times (as is the case for modeling GRB 170817A). If one writes \hat\gamma = (4 \bar\gamma _ 1) / 3 \bar\gamma (\bar\gamma is the average Lorentz factor of shocked protons), one can naturally transit from the relativistic regime (4/3) to the non-relativistic regime (5/3). The formulae also appear more elegant. I suggest the authors adopt such a more precise treatment to match the 10^{-4} numerical accuracy. See e.g.
https://ui.adsabs.harvard.edu/abs/2003ApJ...591.1075K/abstract
https://ui.adsabs.harvard.edu/abs/2011ApJ...733...86U/abstract

--

The referee is mistaken about our equation of state. Equations 5 and 6, as well as all of afterglowpy, are computed using the TM equation of state of Mignone, Plewa, and Bodo 2005 which smoothly interpolates between ultra-relativistic (4/3) and non-relativistic (5/3) adiabatic indices.  This is the same EoS used by the referees ' suggested paper Uhm 2011.

We note for a structured jet the accuracy of our numerical scheme is closer to 10^{-2} than 10^{-4}, as stated at the end of Section 3.3. We do not claim the overall accuracy of the method is at either of these levels, merely the numerical accuracy of the physics we include.  The comparison to BoxFit in section 3.4 is a better (though still not perfect, given BoxFit's similar synchrotron model) measure of our overall accuracy, which is seen to be nearer ~ few * 10^{-1}.

We amended the manuscript to make the choice of equation of state, and its reasons for selection, much more clear.

-- Added several sentences to the second paragraph of section 3.1, providing more explicit details about the equation of state, incorporating the latter reference suggested by the referee, and more references found within.

4. I don't understand why the authors introduce a truncated angle \theta_w for Gaussian jets. It is essentially impossible in reality. Also for GRB 170817A, it seems that the typical viewing angle is greater than \theta_w. If this is the case, one should not expect to have relativistic ejecta along the line of sight in the early phase. This is apparently in contradiction with the prompt emission data, which require a relativistic outflow along the line of sight.

--

The truncation angle \theta_w serves two purposes.  Firstly is to do with numerical efficiency: high latitude wings of the jet have a negligible contribution to the flux (except at very early times) compared to the jet core but require a similar amount of computational time.  Excising these parts of the jet allows for quicker evaluations and the possibility of doing MCMC-type analyses which require many light curves be generated.  Secondly there are simulations, like the Aloy 2005 or Xie/Margutti 2018 works, which do show a very steep energy profile at some large angle. Truncating at theta_w is more extreme than what these simulations show, but is a rough approximation for a tightly collimated jet with structured interior.  Ultimately we find no harm in including theta_w as an optional parameter, any particular application may set it sufficiently high as to be ignorable if it wishes.

We do not yet know the precise origin of the prompt emission in GRB 170817A. It need not have originated from material directly in our line of sight. Both Matsumoto+ 2019 (https://ui.adsabs.harvard.edu/abs/2019MNRAS.483.1247M/abstract) and Ioka+ 2019 (https://ui.adsabs.harvard.edu/abs/2019MNRAS.487.4884I/abstract) consider the prompt emission in a structured jet scenario and find solutions where the prompt emission is emitted several degrees off the line-of-sight from material with a moderate Lorentz factor.  This is analogous to the structured afterglow case where the emission can be dominated by material at intermediate angles between the line of sight and jet axis.

In our fit to the 170817 afterglow we keep theta_w as a free parameter to remain agnostic about its true value.  As seen in Table 3 and Figure 12, the fit really does not constrain theta_w too much. The median value (0.47) is in fact greater than the median viewing angle (0.40), but there are numerous solutions where the hierarchy is reversed. We agree that taking the prompt emission into account would likely require a larger theta_w than the afterglow alone, but this would depend on the details of the prompt emission model and is out of scope for the current work.

This is an important point which was not discussed in the original manuscript, we have added discussion about theta_w and the prompt emission to Section 5.

-- Added a paragraph concerning theta_w and the choice of permissive prior in light of the prompt emission to Section 5.

5. Why didn't the authors consider synchrotron self-absorption? For GRB 170817A, the current modeling is adequate, but maybe in the future one needs to consider \nu_a when modeling off-axis jets.

--

Synchrotron self-absorption is an important process and certainly due a similar analysis in light of off-axis viewing and jet structure.  A proper treatment of self-absorption is complicated, particularly in off-axis viewing when much of the emitting region is at an oblique angle to the observer and near portions of the jet may shadow distant portions.  This adds significant difficulty to both the numeric and analytic understanding of the afterglow in these regimes.

We saw our development of the theory at frequencies above \nu_a to be sufficient for this particular manuscript. Incorporating frequencies below \nu_a will require more care, which we hope to present in future work.

6. The description of the early history of the structured jet model may be revised: Lipunov et al. was talking about "standard energy" and a three-component jet model. Rossi et al. proposed b=2 power law "universal" model. Zhang & Meszaros proposed "quasi-universal" (jet structures can differ somewhat among bursts) models that include both power laws and Gaussian. Nakar et al's test was strictly for the universal b=2 power law structured jet model. The model does not work even without their test: the observed E_iso - \theta_j relation is not a strict E_iso \propto \theta_j^{-2} relation (and the beaming-corrected energy is not strictly constant). In fact, the quasi-universal models, especially the quasi-universal Gaussian jet model works well for long GRBs and probably for short GRBs as well. See early tests of these models for long GRBs:
https://ui.adsabs.harvard.edu/abs/2004ApJ...601L.119Z/abstract
https://ui.adsabs.harvard.edu/abs/2005ApJ...621..875D/abstract
These facts may be clarified in the introduction.

--

We thank the referee for clearing up the history of the subject, and have amended the introduction as necessary.

-- Expanded discussion and added references concerning history of structured jets in paragraphs 5 and 6 of Section 1.

7. Figure 1 presented some structured jet models from numerical simulations. Figure 4 of this paper
https://ui.adsabs.harvard.edu/abs/2019ApJ...877L..40G/abstract
provide more structures. In particular, the shape of E(\theta) depends on the waiting time before the jet is launched. For a delayed launch, one has essentially a two-component jet structure (jet + cocoon). For a prompt launch (negligible delay), the jet penetrates through the ejecta quickly and develop a structured jet outside the ejecta. The jet structure is one-component, similar to the Gaussian profile promoted in this paper. This may be discussed in the paper.

-- Added a sentence to the end of the fourth-to-last paragraph of Section 5 explaining the origin of the constraining power on theta_obs and theta_c.

-- Added a paragraph to section 6.1 discussing the role of gravitational wave data in constraining theta_obs and theta_c.

### 2020-05-13 structuredJets.tex
working on ref report

@@
 We present a characterization of the afterglows arising from structured jets, providing a framework covering both successful and choked jets.
-We compute new closure relations for structured jets and compare with the established relations for energy injection and refreshed shock models.
+We compute new closure relations for {\bf decelerating} structured jets and compare with the established relations for energy injection and refreshed shock models.
 The temporal slope before the jet break is found to be a simple function of the ratio between the viewing angle and effective opening angle of the jet.
@@
 Detailed theoretical calculations of structured jet afterglow light curves concluded several facts: on-axis structured light curves resemble those from top hat jets, off-axis structured light curves show an achromatic break at time $t_b\propto \thobs^{8/3}$ (where $\thobs$ is the viewing angle), and the pre-break slope can depend on the viewing angle and particular structure model \citep{Rossi:2002aa, Dalal:2002aa, Granot:2002aa, Panaitescu:2003aa, Kumar:2003aa, Granot:2003aa, Salmonson:2003aa, Rossi:2004aa}.
-The ``Universal Structured Jet'' was a structured jet with isotropic-equivalent energy $E \propto \theta^{-2}$ proposed to explain the diversity of jet-break times as a viewing angle effect  \citep{Lipunov:2001aa, Zhang:2002aa}, although this was ultimately unsuccessful \citep{Nakar:2004aa}.
+
+{\bf A three component jet model viewed at a range of angles was proposed to unify GRBs to a standard energy \citep{Lipunov:2001aa}.
+The ``Universal Structured Jet'' was a structured jet with isotropic-equivalent energy $E \propto \theta^{-2}$ proposed to give GRBs a standard energy and explain the diversity of jet-break times as a viewing angle effect  \citep{Rossi:2002aa}, although this was ultimately unsuccessful \citep{Nakar:2004aa}.
+Quasi-universal structured jets with both power-law \citep{Zhang:2002aa} and Gaussian \citep{Zhang:2004aa} profiles have also been proposed.
+The Gaussian models are consistent a number of observed correlations in the GRB population and provide a possible origin for X-ray flashes \citep{Dai:2005aa}.}
 
 The jet break in the structured jet afterglow light curve can exhibit a larger jump between pre- and post-break slopes than in top hat models, and has been invoked to explain some observed jet breaks which do not easily fit the standard closure relations \citep{Panaitescu:2005aa, Panaitescu:2005ab}, although other dynamical and spectral processes can have similar effects \citep{Piro:2005aa, Corsi:2006aa}.
-GRB prompt emission viewed significantly off-axis is one of the possible origins for X-ray flashes \citep{Ioka:2001aa, Yamazaki:2002aa, Yamazaki:2003aa, Peng:2005aa, DAlessio:2006aa}.
-More recently, small non-zero viewing angles have been measured in a subset of the \swiftXRT{} afterglow sample \citep{Ryan:2015aa, Zhang:2015aa, Troja:2016aa}.
+{\bf GRB prompt emission viewed significantly off-axis is one of the possible origins for X-ray flashes \citep{Ioka:2001aa, Yamazaki:2002aa, Yamazaki:2003aa, Zhang:2004aa, Dai:2005aa, Peng:2005aa, DAlessio:2006aa}.
+}More recently, small non-zero viewing angles have been measured in a subset of the \swiftXRT{} afterglow sample \citep{Ryan:2015aa, Zhang:2015aa, Troja:2016aa}.
 These studies focused on observers positioned within the core opening angle of the jet or relied on closed numerical codes to calculate light curves for misaligned viewers.
@@
 Detailed derivation of the closure relations is provided in Appendices \ref{app:derive1} and \ref{app:derive2}.
-
-% Explicitly say we were the first to find X-ray, predict steep post-break slope.
 
@@
 
-The Lorentz factor profile $\gamma(\theta)$ of a jet may also obtain angular structure through its launching and evolution.
-In this work we focus on the consequences of non-trivial $E(\theta)$, as the bulk of successful observations are expected to occur when the jet is in the deceleration regime and the jet is locked to $\gamma(\theta) \propto E(\theta)^{1/2}$.
-We leave the specific consequences of differing $\gamma(\theta)$ profiles, which may affect emission at early times, to future work.
+\subsection{The Lorentz Factor Profile $\gamma(\theta)$}
+
+{\bf 
+The Lorentz factor profile $\gamma(\theta)$ of a jet will also obtain angular structure through the jet's launching and evolution.
+Two jets with identical energy profiles $E(\theta)$ may very well acquire different Lorentz factor profiles and display different afterglow light curves.
+However, these differences are restricted to the early phases of the jet's evolution.
+
+As shown in Section \ref{subsec:algo} and Appendix \ref{app:derive1}, once a jet sweeps up enough circumburst material to begin deceleration the Lorentz factor evolves according to $\gamma(t; \theta) \propto \sqrt{E(\theta) / n_0} t^{-3/2}$, where $t$ is time in the burster's frame and $n_0$ is the (uniform) circumburst density.
+While the jet is coasting, before deceleration, two jets may have identical energy profiles but differing Lorentz factor distributions.
+Once deceleration begins the jet forgets its initial Lorentz factor profile $\gamma(\theta)$ and approaches one determined exclusively by $E(\theta)$.
+The bulk of GRB afterglow observations, including those of \grbbns{}, are carried out after deceleration has begun.
+
+ In this work we focus on the consequences of non-trivial energy profiles $E(\theta)$ for jets in the deceleration regime.
+The energy profile is also a useful quantity to focus on as, due to conservation of energy and unlike the Lorentz factor, $E(\theta)$ is constant through the coasting and deceleration phases until the jet begins to spread at late times.
+We leave the specific consequences of generic $\gamma(\theta)$ profiles, which will affect the early time light curve (see \cite{Beniamini:2020ab} for the case of power law profiles), to future work.
+}
 
@@
 
-\subsection{The Single Shell Approximation}\label{subsec:algo}
-
 The observed flux $F_\nu(\tobs, \nuobs)$ at observer time $\tobs$ and frequency $\nuobs$ is calculated via:
@@
 Once jet spreading begins in earnest the errors are larger, and this approach can be best viewed as an interpolation between the correct ultra-relativistic and non-relativistic limits \citep{van-Eerten:2010aa}.
+{\bf 
+\subsection{The Single Shell Approximation -- Top-Hat Case}\label{subsec:algo}
+}
 
@@
 In the single-shell approximation we treat the ejecta mass, contact discontinuity, and forward shock as a single unit propagating through a cold ambient medium with constant rest-mass density $\rho_0 = \Mp n_0$.
-We utilize the ``TM'' trans-relativistic equation of state to describe the fluid consistently throughout its evolution \citep{Mignone:2005aa}.
-The forward shock is at radius $R$ from the explosion, and the fluid behind the shock has dimensionless four-velocity $u$ and Lorentz factor $\gamma$.
+
+{\bf An accurate equation of state is essential in trans-relativistic calculations \citep{Mignone:2007aa}.
+We utilize the ``TM'' trans-relativistic equation of state to describe the fluid consistently throughout its evolution \citep{Mathews:1971aa, Mignone:2005aa}.
+This equation of state smoothly interpolates from a relativistic gas with adiabatic index $\hat \Gamma = 4/3$ at high temperature to a non-relativistic $\hat \Gamma = 5/3$ gas at low temperature, and has been successfully used for many GRB studies \citep[e.g.][]{Uhm:2011aa, van-Eerten:2012aa}.
+} The forward shock is at radius $R$ from the explosion, and the fluid behind the shock has dimensionless four-velocity $u$ and Lorentz factor $\gamma$.
 The shock jump conditions can be used to determine the shock speed:
@@
 	\tobs &= (1+z) \left(t - \mu(\theta, \phi) R(t)/c\right)\ , \label{eq:tobs} \\
-	\nuobs &= (1+z)^{-1} \delta \nu' , \label{eq:nuobs}
+	\nuobs &= (1+z)^{-1} \delta\ \nu' , \label{eq:nuobs}
 \end{align}
@@
 
+\subsection{The Single Shell Approximation -- Structured Case} \label{subsec:algo2}
+
+{\bf
+We model a structured jet as a series of concentric top hat jets, each independently obeying the equations of Section \ref{subsec:algo}.
+In the continuous case, $R(t)$ and $u(t)$ are promoted to functions of $\theta$ as well: $R(t; \theta)$ and $u(t; \theta)$.
+These functions evolve according to their local isotropic-equivalent energy $E(\theta)$.
+At the same lab time $t$ (or equivalently observer time $\tobs$) there will be a gradient of both energy $E$ and four-velocity $u$ over the surface of the jet.
+
+For numerical calculations, we approximate the structured jet with a discrete set of $N_\theta$ top-hat jets.
+The initial widths of each jet are $\theta_{0, i} = i \thW / N_\theta$ for $i = 1, \dots, N_\theta$.
+Each jet is initialized with energy $E_i = E((\theta_{0, i-1} + \theta_{0,i})/2)$ and evolves with independent radius $R_i(t)$, four-velocity $u_i(t)$, and opening angle $\theta_{j, i}(t)$.
+The final flux is found by summing the contributions from each top-hat $i$, integrated as in Equation \eqref{eq:flux2}, from the outer edge of jet $i-1$ to its own edge $\theta_{j, i}$.
+
+\begin{align}
+		&F_\nu(\tobs, \nuobs) = \frac{1+z}{4\pi \dL^2}  \label{eq:flux3} \\
+		&\qquad \times \sum_{i=1}^{N_\theta}  \Bigg [ \int_0^{2\pi} \!\!\!
+\dd \phi   \int_{\theta_{j, i-1}}^{\theta_{j, i}} \!\!\!
+\dd \theta \ \sin \theta\  R_i^2\ \Delta R_i\  \delta_i^2\ \epsilon'_{\nu', i} \Bigg ] \nonumber
+\end{align}
+
+The integrand of Equation \eqref{eq:flux3} is evaluated at a constant observer time $\tobs$ and hence is a function of both $\phi$ and $\theta$.
+Due to jet spreading the integration bounds $\theta_{j, i-1}$ and $\theta_{j, i}$ are also time dependent and hence functions of $\phi$ when evaluated at constant $\tobs$.
+Equation \eqref{eq:flux3} serves as the basis for all structured jet calculations in \afterglowpy{}.
+}
+
 \subsection{\afterglowpy{}} \label{subsec:afterglowpy}
@@
 The numerical accuracy of a top-hat light curve with this integration scheme is typically better than $10^{-4}$.
-The structured jet calculation splits the integration domain into {\tt latRes} disjoint annuli, each evolved as an independent top-hat and their emission summed.
-By default {\tt latRes} is chosen such that there will be 5 zones per $\thC$-sized interval of $\theta$.
+{\bf The structured jet calculation splits the integration domain into $N_\theta$ disjoint annuli, each evolved as an independent top-hat and their emission summed following Equation \eqref{eq:flux3}.
+The resolution $N_\theta$ is controlled by the {\tt latRes} parameter which sets the number of zones per $\thC$-sized interval: $N_\theta = \mathtt{latRes} \times \thW/\thC$.
 The choice of  {\tt latRes} has the largest impact on the code performance and accuracy.
-We find the choice $\mathtt{latRes} = 5$ gives sufficiently quick performance at acceptable errors, typically on the order of $10^{-2}$.
+We find the default choice $\mathtt{latRes} = 5$ gives sufficiently quick performance at acceptable errors, typically on the order of $10^{-2}$.
+}
 
@@
 \begin{equation}
-	F_\nu = I_\nu^*\ \Delta \Omega\ .
+	F_\nu \approx I_\nu^*\ \Delta \Omega\ .
 \end{equation}
@@
 \begin{deluxetable*}{CCCCCCCCC}
-	\tablecaption{Structured jet closure relations: $F_\nu \propto \tobs^{\alpha} \nuobs^{\beta}$.
-The ``far-off-axis'' phase ($\alpha_{\mathrm{far-off-axis}}$) occurs at early times and only if there is no relativistic material directly in the observer's line of sight ($\thobs > \thW$).
-The ``generic'' slope ($\alpha_{\mathrm{generic}}$) applies whenever the jet is relativistic, non-spreading, and the observer is within the beaming cone of some part of the jet ($|\thobs - \theta_*| < \gamma^{-1}(\theta_*)$).
+	\tablecaption{{\bf Closure relations for a structured, decelerating jet: $F_\nu \propto \tobs^{\alpha} \nuobs^{\beta}$.} The \emph{far-off-axis} phase ($\alpha_{\mathrm{far-off-axis}}$) occurs at early times only if there is no relativistic material directly in the observer's line of sight ($\thobs > \thW$).
+The \emph{generic} slope ($\alpha_{\mathrm{generic}}$) applies whenever the jet is relativistic, non-spreading, and the observer is within the beaming cone of some part of the jet ($|\thobs - \theta_*| < \gamma^{-1}(\theta_*)$).
 The $g$ parameter is positive and depends on the viewing angle $\thobs$ and the specific structure profile $E(\theta)$.
@@
 The $\som$ parameter encodes how the effective angular size of the jet is changing with Lorentz factor: $\Delta \Omega \propto \gamma^{-\som}$.
-The ``pre-jet break'' phase ($\alpha_{\mathrm{pre}}$) is seen by aligned viewers ($\thobs \lesssim \thC$) and by early misaligned viewers if there is high Lorentz factor material in their line of sight.
-The ``structured'' phase ($\alpha_{\mathrm{struct}}$) is seen by misaligned viewers ($\thobs > \thC$), occurs before the jet break, and corresponds to $\som \approx 1$.
-The ``post-jet break'' slopes ($\alpha_{\mathrm{post, 1}}$ and $\alpha_{\mathrm{post, 2}}$) bracket the possible post-jet break behaviour.
-The first is for a non-spreading jet while the second corresponds to a jet undergoing exponential spreading and was calculated \citet{Sari:1999aa}.\label{tab:slopes}}
+The \emph{pre-jet break} phase ($\alpha_{\mathrm{pre}}$) is seen by aligned viewers ($\thobs \lesssim \thC$) and by early misaligned viewers if there is high Lorentz factor material in their line of sight.
+The \emph{structured} phase ($\alpha_{\mathrm{struct}}$) is seen by misaligned viewers ($\thobs > \thC$), occurs before the jet break, and corresponds to $\som \approx 1$.
+The \emph{post-jet break} slopes ($\alpha_{\mathrm{post, 1}}$ and $\alpha_{\mathrm{post, 2}}$) bracket the possible post-jet break behaviour.
+The first is for a non-spreading jet while the second corresponds to an exponentially spreading jet and was calculated by \citet{Sari:1999aa}.
+\label{tab:slopes}}
 	\tablehead{\colhead{Regime}& \colhead{Label} & \colhead{$\alpha_{\mathrm{far-off-axis}}$} & \colhead{$\alpha_{\mathrm{generic}}$} & \colhead{$\alpha_{\mathrm{pre}}$} & \colhead{$\alpha_{\mathrm{struct}}$}& \colhead{$\alpha_{\mathrm{post, 1}}$} & \colhead{$\alpha_{\mathrm{post, 2}}$} & \colhead{$\beta$}}
@@
 The specific order of light curve phases depends on where the viewer sits, $\thobs$, relative to the jet half opening angle $\thC$ and the outer truncation angle $\thW$.
-A \emph{coasting} phase, ending at $\tdec$, is assumed to have already completed.
-Each panel shows a fiducial light curve (solid blue lines), power law segments $t^\alpha$ with slopes from the closure relations in Table \ref{tab:slopes} (black dashed lines), and representative break times between each phase of evolution (grey dashed vertical lines).
+{\bf A \emph{coasting} phase, which depends on the initial Lorentz factor profile $\gamma(\theta)$ and ends at $\tdec$, is assumed to have already completed.
+} Each panel shows a fiducial light curve (solid blue lines), power law segments $t^\alpha$ with slopes from the closure relations in Table \ref{tab:slopes} (black dashed lines), and representative break times between each phase of evolution (grey dashed vertical lines).
 The two dashed lines in the ``post-jet break'' section bracket the possible light curve behaviour.
@@
 The flux depends only on the total volume of the emitting region and the evolution of the cooling frequency $\nu_c$.
+{\bf The transition out of the coasting phase to later phases depends on the specific initial Lorentz factor profile $\gamma(\theta)$ of the jet and may show interesting phenomenology \citep{Beniamini:2020ab}.
+We leave these details for future work, and focus now on the decelerating phases where $\gamma(\theta)$ is fully determined by $E(\theta)$.}
 
@@
 \emph{Structured} --- If the viewer lies outside the core of the blast wave, $\thobs > \thC$, non-trivial angular structure can have a significant effect on the light curve.
-Material from the energetic regions progressively closer to the jet axis continuously comes into view, becoming the new dominant source of emission, and moving the centroid with time: $\theta_* \to 0$ as $\tobs$ increases.
-The centroid obeys $\gamma^{-1}(\theta_*) \sim |\thobs-\theta_*|$.
-The angular size of the visible patch in the azimuthal direction is still controlled by beaming, but in the polar direction it is controlled by the steep gradient in $E(\theta)$, resulting in $\som \approx 1$.
-The temporal evolution of the light curve depends on both the specific angular structure $E(\theta)$ and the viewing angle $\thobs$.
+{\bf The centroid of emission is not along the direct line of sight ($\theta_* \neq \thobs$) nor on the jet axis ($\theta_* \neq 0$).}  {\bf Material from the energetic regions progressively closer to the jet axis continuously comes into view, becoming the new dominant source of emission, and moving the centroid with time: $0 < \theta_*(\tobs) < \thobs$  with $\theta_* \to 0$ as $\tobs$ increases.
+The location of the centroid obeys $\gamma^{-1}(\theta_*) \sim |\thobs-\theta_*|$.
+
+The shape of the emitting region $\Delta \Omega$ is complex.
+Material closer to the jet core (at $\theta < \theta_*$) has too high a Lorentz factor and is beamed away form the observer.
+Material closer to the line of sight (at $\theta > \theta_*$) has a lower Lorentz factor than the material at the centroid, the observer is in its beaming cone but the intensity is dimmer than the centroid material.
+This gives the visible patch an asymmetric shape.
+The angular size of the visible patch in the azimuthal direction is still controlled by beaming (is of size $\gamma_*^{-1}$), but in the polar direction it is controlled by the steep gradient in $E(\theta)$ instead, resulting in $\Delta \Omega \propto \gamma_*^{-1}$ and $\som \approx 1$.}  The temporal evolution of the light curve depends on both the specific angular structure $E(\theta)$ and the viewing angle $\thobs$.
 The specific closure relations are given in Table \ref{tab:slopes} and discussed in Section \ref{subsec:structure}.
@@
 
+{\bf Our fit does not penalize solutions with $\thobs > \thW$ and no relativistic material directly in the line of sight.
+At face value, such an orientation seems at odds with observation of the prompt emission in \grbbns{}.
+However, similar to the structured jet afterglow, it is possible the prompt emission originated several degrees off our line of sight, perfectly consistent with $\thobs > \thW$ \citep{Matsumoto:2019aa, Ioka:2019aa}.
+In light of this, we remain agnostic to the prompt emission model and give $\thW$ a permissive prior independent of $\thobs$.
+}
+
 We fit both the Gaussian and power law structured jet models, fixing $\xi_N = 1$ and $\dL = 1.23 \times 10^{26}$ cm.
-The fit parameters, their priors, and their marginalized posteriors are given in Table \ref{tab:MCMC}.
 Both models were run with 300 walkers for 64 000 iterations, discarding the first 16 000 iterations as a burn-in.
 The $E_0$, $n_0$, $\epse$, and $\epsB$ parameters were given $\log$-uniform priors, while $\thC$, $\thW$, $b$, and $p$ were given uniform priors.
-The specific bounds and priors for each parameter are reported in Table \ref{tab:MCMC}.
+The fit parameters, their specific priors and bounds, and their marginalized posteriors are shown in Table \ref{tab:MCMC}.
 
@@
 The looser constraint on $\thobs/\thC$ in the power law jet comes from the additional freedom of the $b$ parameter, which has an effect on $\geff$ in that model (see Equation \eqref{eq:geff}).
-The truncation angle $\thW$ is essentially unconstrained in the Gaussian fit as a far off-axis phase was not observed.
+{\bf Much of the constraining power on $\thobs$ is actually due to the prior from the gravitational wave data.
+This, plus the tight afterglow constraint on $ \thobs/\thC$, leads to the constraint on $\thC$.
+} The truncation angle $\thW$ is essentially unconstrained in the Gaussian fit as a far off-axis phase was not observed.
 In the power law fit, however, $\thW$ is constrained to be quite narrow so as to avoid the early bright wings.
@@
 
-% TODO: RECONSIDER, CLARIFY, OR DROP THIS
 Despite the tight constraints each model gives on $\thobs$, $\thC$, and especially $\thobs/\thC$, the resulting posteriors are incompatible with each other.
@@
 
+{\bf For example, our constraints on $\thobs$ and $\thC$ in the fit to the \grbbns{} afterglow are aided immensely by the included gravitational wave constraints on $\thobs$ \citep{Abbott:2017aa}.
+The afterglow data primarily constrains only the ratio $\thobs/\thC$, leaving $\thobs$ and $\thC$ themselves uncertain and dependent on other parameters like the energy $E_0$ and density $n_0$.
+The gravitational wave posterior provides an independent measure of $\thobs$.
+This leads directly to a constraint on $\thC$ given the tight measure of $\thobs/\thC$ from the afterglow data.
+}
+
 \begin{figure}
@@
 We have constructed flexible models for the electromagnetic afterglows of angularly structured relativistic jets for aligned and misaligned observers.
-Through analytic approximations we can identify the basic phases of the structured afterglow light curve, determining formulae for the characteristic break time scales and closure relations.
+{\bf These models are appropriate for jets which have begun decelerating, at which point Lorentz factor profile and evolution is determined entirely by the angular energy profile of the jet.}  Through analytic approximations we can identify the basic phases of the structured afterglow light curve, determining formulae for the characteristic break time scales and closure relations.
 We find the closure relations depend on a single dimensionless parameter $g$ related to the jet structure and viewing angle.

### 2020-05-13 code/structComp.py

@@ -304,6 +304,22 @@ def aloy2005(theta):
     return g, E
 
 
+def geng2019(theta):
+
+    # data is E_iso
+
+    filenameE = "StructureData/Geng_Etheta_dt0p1.csv"
+    thEp, Ep = np.loadtxt(filenameE, unpack=True, delimiter=',')
+    
+    thEp *= np.pi/180.0
+
+    g = np.zeros(theta.shape)
+    E = np.interp(theta, thEp, Ep, right=0.0)
+
+    return g, E
+
+
+
 if __name__ == "__main__":
 
     print("begin")
@@ -329,6 +345,7 @@ if __name__ == "__main__":
     gM09, EM09 = mizuta2009(theta)
     gL17, EL17 = lazzati2017(theta)
     gA05, EA05 = aloy2005(theta)
+    gG19, EG19 = geng2019(theta)
 
     print("Plotting")
     fig, ax = plt.subplots(2, 1, figsize=(8, 8))
@@ -552,11 +569,13 @@ if __name__ == "__main__":
     #           color=clr[4], ls=ls[0])
     # axEc.plot(theta*deg, EM07p2, label="Morsony 2007 powg2",
     #           color=clr[4], ls=ls[1])
+    axEc.plot(theta*deg, EG19*plNorm/(2*EG19[0]), label="Geng 2019",
+              color=clr[7], ls=ls[0])
 
     axEc.legend(loc='upper right', fontsize=8)
 
     axEc.set_xlabel(r'$\theta$ (degrees)')
-    axEc.set_ylabel(r'$E_{{\rm{iso}}}$ (arbitrary units)')
+    axEc.set_ylabel(r'$E_{{\rm{iso}}}(\theta)$ (arbitrary units)')
     axEc.set_yscale('log')
     axEc.set_ylim(1.0e-3, 1.0e1)
     axEc.set_xlim(0.0, 30.0)

### 2020-05-13 tex2apj.py

@@ -1,6 +1,7 @@
 import errno
 import os
 import sys
+import subprocess
 
 
 def apjify(inName, outDir):
@@ -12,7 +13,7 @@ def apjify(inName, outDir):
     inDir, name = os.path.split(inName)
 
     if inDir == '':
-        inDir = os.getcwd()
+        inDir = '.'
 
     if os.path.exists(outDir):
         if not os.path.isdir(outDir):
@@ -26,37 +27,103 @@ def apjify(inName, outDir):
             .format(outDir, inName)
         raise RuntimeError(msg)
 
-    outName = os.path.join(outDir, name)
-
     with open(inName, 'r') as f:
-        inTxt = f.readlines()
+        inTxt = f.read()
     f.close()
 
+    filelist = getFigFilenames(inTxt)
+    trans = makeTranslator(filelist)
+
+    process(inTxt, trans, inDir, outDir, name)
+
+
+def process(inTxt, trans, inDir, outDir, texName):
+
+    outName = os.path.join(outDir, texName)
+
+    # Make text with replaced figure names
+    outTxt = inTxt
+    for name in trans:
+        outTxt = outTxt.replace(name, trans[name])
+
+    # Write the new file
     with open(outName, 'w') as f:
-        parseTex(inTxt, f, inDir, outDir)
+        f.write(outTxt)
     f.close()
 
+    # Copy the figure files
+    for name in trans:
+        figpath = os.path.join(inDir, name)
+        newfigpath = os.path.join(outDir, trans[name])
+        print("Copy {0:s} to {1:s}".format(figpath, newfigpath))
+        subprocess.run(["cp", figpath, newfigpath])
 
-def parseTex(src, f, inDir, outDir):
+
+def getFigFilenames(src):
 
     inFig = False
-    inSubFig = False
-    fignum = 0
-    subfignum = 0
 
-    beginFig = '\\begin{figure'
-    endFig = '\\end{figure'
+    beginFig = r'\begin{figure'
+    endFig = r'\end{figure'
+    figDir = 'figs/'
 
-    for line in src:
+    filelist = []
+    filenames = []
 
-        # Deal with comments
+    for i, line in enumerate(src.split('\n')):
+
+        # Trim comments
         lineout = line.split('%')[0]
         if lineout == '':
             continue
-        if lineout[-1] != '\n':
-            lineout += '\n'
 
-        f.write(lineout)
+        # Look for figure filenames
+        if inFig:
+            if endFig in lineout:
+                filelist.append(filenames)
+                inFig = False
[…]

### 2020-05-13 refereeResponse.txt
Finished referee response?

@@
 
+-- Added M0.1 model from Geng+ to Figure 1, amended the caption, and added a description to the second paragraph of Section 2.
+
+8. The most complete "closure relations" for GRB afterglow models was presented in a review article
+https://ui.adsabs.harvard.edu/abs/2013NewAR..57..141G/abstract.
+This may be referenced when closure relations are discussed.
+
+-- Added a reference and sentence description of the paper to the first paragraph of Section 4.
+
+Other updates to the text:
+
 -- Added a sentence to the end of the fourth-to-last paragraph of Section 5 explaining the origin of the constraining power on theta_obs and theta_c.
@@
 -- Added a paragraph to section 6.1 discussing the role of gravitational wave data in constraining theta_obs and theta_c.
+
+-- Added a couple sentences to the 6th paragraph of Section 6.1 referencing using Luminosity functions and rates to constrain jet structure, citing recent Beniamini+ works
+
+-- Added Mooley 2018c to references for 170817 post-jet break slope in Section 1 and 5
+
+-- Added paragraph discussing Hajela+ 2019 analysis to Section 6.2.

### 2020-05-13 structuredJets.tex
Finished referee response?

@@
 Very long baseline (VLBI) radio imagery over this period identified a radio core with an apparent superluminal motion, indicating the emitting surface was moving at relativistically at an oblique angle towards the Earth \citep{Mooley:2018ab}.
-The emission peaked at 164 days after the burst and proceeded to sharply decay at a rate $t^{-2.2}$ commensurate with other GRB afterglows \citep{Alexander:2018aa, Fong:2019aa, Lamb:2019aa, Troja:2019ab}.
-
-The lack of early emission, slow rising light curve, apparent motion of the radio centroid, and sharp decline post-peak are all consistent with emission from a \emph{structured jet}, a collimated blast wave with a non-trivial angular distribution of energy, viewed a moderate angle away from the jet axis \citep{Lamb:2017aa, Alexander:2018aa, Hotokezaka:2018aa, Wu:2018aa, Xie:2018aa,  Ghirlanda:2019aa, Fong:2019aa, Lamb:2019aa, Troja:2019aa}.
+The emission peaked at 164 days after the burst and proceeded to sharply decay at a rate $t^{-2.2}$ commensurate with other GRB afterglows \citep{Alexander:2018aa, Fong:2019aa, Lamb:2019aa, Mooley:2018ac, Troja:2019ab}.
+
+The lack of early emission, slow rising light curve, apparent motion of the radio centroid, and sharp decline post-peak are all consistent with emission from a \emph{structured jet}, a collimated blast wave with a non-trivial angular distribution of energy, viewed a moderate angle away from the jet axis \citep{Lamb:2017aa, Alexander:2018aa, Hotokezaka:2018aa, Wu:2018aa, Xie:2018aa,  Ghirlanda:2019aa, Fong:2019aa, Lamb:2019aa, Troja:2019aa, Hajela:2019aa}.
 The combined effects of a moderate viewing angle and angular structure in the jet produce a light curve significantly different from the standard on-axis uniform ``top-hat'' jet used extensively in GRB afterglow analysis.
@@
 Numerical simulations have revealed a variety of jet angular energy distributions, often containing an energetic core with power law tails.
-Figure \ref{fig:jetStruct} shows a collection of jet energy distributions from the literature \citep{Aloy:2005aa, Mizuta:2009aa, Duffell:2013aa, Lazzati:2017aa, Margutti:2018aa}.
+Figure \ref{fig:jetStruct} shows a collection of jet energy distributions from the literature \citep{Aloy:2005aa, Mizuta:2009aa, Duffell:2013aa, Lazzati:2017aa, Margutti:2018aa, Geng:2019aa}.
 The \citet{Aloy:2005aa} model (B01 in the paper) was launched as a top hat jet into an accretion torus featuring a narrow underdense funnel region and produced a final energy profile with a relatively sharp edge, although only material with Lorentz factor greater than 100 was included in the $\Eiso$ calculation.
@@
 The \citet{Lazzati:2017aa} model is meant to emulate a BNS merger and injects a top hat jet into a spherically symmetric ejecta wind, also resulting in a large amount of interaction and energetic power law wings.
-The \citet{Duffell:2013aa} model is an analytic model of a fireball, spherically symmetric in its rest frame, boosted at a bulk Lorentz factor.
+{\bf The \citet{Geng:2019aa} model launches a relativistic magnetized jet into a fiducial BNS merger ejecta cloud with varying delay times.
+In this model the jet was launched 0.1 s after the ejecta, resulting in limited interaction before the jet broke out of the expanding cloud.
+} The \citet{Duffell:2013aa} model is an analytic model of a fireball, spherically symmetric in its rest frame, boosted at a bulk Lorentz factor.
 It also produces a narrow core with power law wings.
@@
 The thick grey lines show fiducial profiles with simple analytic expressions (Equations \eqref{eq:gauss} and \eqref{eq:pl}) while the thin colored lines show results from numerical simulations and analytic models chosen from the literature.
-The blue line is the B1 numerical simulation of \cite{Aloy:2005aa}, orange the HE16N numerical simulation of \cite{Mizuta:2009aa}, green an analytic ``boosted fireball'' model with $\gamma_{\rm{B}}=10$ and $\eta_0=3$ from \cite{Duffell:2013aa}, red the numerical simulation from \cite{Lazzati:2017aa} (L17), and purple the numerical simulation from \cite{Margutti:2018aa} (M18).
-The thick solid grey line is a Gaussian profile (Equation \eqref{eq:gauss}) with $E_0 = 3\times 10^{52}$ erg, $\thC = 6^\circ$, and $\thW=12^\circ$ and the thick dashed grey line is a power law profile (Equation \eqref{eq:pl}) with $E_0 = 10^{52}$ erg, $\thC = 2^\circ$, $\thW=20^\circ$, and $b=4.5$.
+The blue line is the B1 numerical simulation of \cite{Aloy:2005aa}, orange the HE16N numerical simulation of \cite{Mizuta:2009aa}, green an analytic ``boosted fireball'' model with $\gamma_{\rm{B}}=10$ and $\eta_0=3$ from \cite{Duffell:2013aa}, red the numerical simulation from \cite{Lazzati:2017aa} (L17), purple the numerical simulation from \cite{Margutti:2018aa} (M18), and brown the M0.1 numerical simulation of \cite{Geng:2019aa}.
+The thick solid grey line is a Gaussian profile (Equation \eqref{eq:gauss}) with $E_0 = 3$, $\thC = 6^\circ$, and $\thW=12^\circ$ and the thick dashed grey line is a power law profile (Equation \eqref{eq:pl}) with $E_0 = 1$, $\thC = 2^\circ$, $\thW=20^\circ$, and $b=4.5$.
 The Gaussian and power law profiles can emulate the basic properties of the energy profiles found in the literature.
@@
 Afterglow light curves, even when viewed off axis, can typically be described as a piecewise set of power law segments $F_\nu \propto \tobs^\alpha \nuobs^\beta$, each denoting particular phases of evolution of the blast wave and its emitting region.
-Particular phases have been identified empirically \citep{Nousek:2006aa} and theoretically \citep{Zhang:2006aa}.
+Particular phases have been identified empirically \citep{Nousek:2006aa} and theoretically \citep[e.g.][]{Zhang:2006aa}.
 Within a particular phase, the slopes $\alpha$ and $\beta$ are often related through a \emph{closure relation}: an equality determining $\alpha$ from $\beta$ or vice versa.
 Phases change at \emph{break times} when the temporal slope $\alpha$ (and potentially the spectral slope $\beta$) transition rapidly from the previous phase to the next.
+{\bf A review and comprehensive collection of known GRB afterglow phases and closure relations is given in \citet{Gao:2013aa}.}
 
@@
 Further radio, optical, and X-ray observations showed a steady rising light curve with constant power law slope until a peak near day 164 \citep{Haggard:2017aa, Hallinan:2017aa, DAvanzo:2018aa,  Lyman:2018aa, Margutti:2018aa, Mooley:2018aa, Troja:2018aa, Troja:2019ab}.
-At this point the light curve turned over and began a steep decay that continues to the present \citep{Alexander:2018aa, Fong:2019aa, Lamb:2019aa, Troja:2019ab}.
+At this point the light curve turned over and began a steep decay that continues to the present \citep{Alexander:2018aa, Fong:2019aa, Lamb:2019aa, Mooley:2018ac, Troja:2019ab}.
 
@@
  In the future, it may be possible to attack the question of determining $E(\theta)$ at the population level.
+{\bf For instance, since GRB jets have isotropically distributed orientations, the jet structure profile will imprint itself on the GRB luminosity function.
+If the observational biases and selection effects are understood, one can use the observed luminosity function or event rate to constrain structure models \citep{Beniamini:2019aa, Beniamini:2019ab}.
+}
+
+One possible new approach is to make direct use of the structured phase closure relations.
 Figure \ref{fig:gPop} shows the structure parameter $g$ as a function of $\thobs/\thC$ for several jet models, as well as the inferred value from \gwbns{}.
@@
 
-Many groups have used structured jet models to analyze the afterglow of \gwbns{}, among the most recent with comparable models are \citet{Hotokezaka:2018aa, Ghirlanda:2019aa, Lamb:2019aa, Wu:2018aa}.
-Of these, \citet{Hotokezaka:2018aa, Ghirlanda:2019aa, Lamb:2019aa} use semi-analytic methods similar to the present work to construct afterglow light curves, while \citet{Wu:2018aa} utilizes analytic scaling relations and a template bank constructed from numerical simulations (following the conceptual approach introduced by \citet{van-Eerten:2012ac}).
+Many groups have used structured jet models to analyze the afterglow of \gwbns{}, among the most recent with comparable models are \citet{Hotokezaka:2018aa, Ghirlanda:2019aa, Lamb:2019aa, Wu:2018aa, Hajela:2019aa}.
+Of these, \citet{Hotokezaka:2018aa, Ghirlanda:2019aa, Lamb:2019aa} use semi-analytic methods similar to the present work to construct afterglow light curves, while \citet{Wu:2018aa} and \citet{Hajela:2019aa} utilize analytic scaling relations and a template bank constructed from numerical simulations (following the conceptual approach introduced by \citet{van-Eerten:2012ac}).
 Additionally, \citet{Hotokezaka:2018aa, Ghirlanda:2019aa} include constraints from the VLBI measurements of the \gwbns{} radio centroid's apparent superluminal motion.
@@
 They demonstrate a clear anti-correlation between $\gamma_B$ and $\thobs$ of $\gamma_B \thobs  \sim \thobs/\thC \approx 5$, and other parameters consistent with this and other studies.
+
+{\bf \citet{Hajela:2019aa} uses the same model as \citet{Wu:2018aa} with an updated afterglow dataset and a new upper limit on $n_0$ of $9.6\times 10^{-3}$ cm$^{-3}$ computed from a measure of the diffuse X-ray emission in the host galaxy.
+They find $\thobs = 0.53^{+0.07}_{-0.06}$ rad, larger than \citet{Wu:2018aa}, also using only afterglow data.
+Their posterior distributions also display a strong relation $\gamma_B \thobs \approx 5$,  and values of $E_{tot}$ (their $E_0$), $n_0$, $\epse$, and $\epsB$ consistent with other studies.
+}
 
